### 2020-07-12 slides/satcomp20slides.tex
2020 slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass{beamer}

\mode<presentation> {

\usetheme{CambridgeUS}

}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%   TITLE PAGE
%----------------------------------------------------------------------------------------

\title[SAT Competition 2020]{The Results of SAT Competition 2020}

\author[Balyo, Froleyks, Heule, Iser, J\"{a}rvisalo, Suda] {Tom{\'a}{\v s} Balyo, Nils Froleyks, {\bf Marijn Heule},\\
Markus Iser, Matti J\"{a}rvisalo, and Martin Suda}
\institute[] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
SAT 2020 Conference, Alghero, Italy (virtually) \\ % Your institution for the title page
}
\date{July 8, 2020} % Date, can be changed to a custom date

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}{SAT Solver Competitions}

{\bf Goals}
\begin{itemize}
\item identify new challenging benchmarks
\item promote SAT solvers and their development
\item "snapshot" evaluation of current solvers
\end{itemize}

\bigskip

{\bf Long tradition}, starting from 1992
\begin{itemize}
\item 3 competitions in the 90s\hfill (1992,1993, 1996)
\item 13 SAT Competitions \hfill (2002--)
\item 5 SAT Races \hfill (2006, 2008, 2010, 2015, 2019)
\item 1 SAT Challenge \hfill (2012)
\end{itemize}

\end{frame}

\begin{frame}{Key rules}

\begin{itemize}
\item Certified results of unsatisfiability using DRAT proof logging
\medskip
\item Disqualification of buggy solvers
  \begin{itemize}
  \item Producing an incorrect model
  \item Report UNSAT on a known satisfiable instance
  \item Proof checker finds inconsistency (demoted to no-limit)
  \end{itemize}
\medskip
\item Mandatory solver descriptions + open source
\medskip
\item Ranking scheme: PAR-2
\begin{itemize}
\item Favors solvers that are faster (not only count solved instances)
\end{itemize}
\medskip
\item BYOB (Bring Your Own Benchmarks)
\begin{itemize}
\item At most 20 instances per participant are used
\end{itemize} 
\end{itemize}

\end{frame}

\begin{frame}{What is New This Year}

\begin{minipage}{.7\textwidth}
\begin{itemize}
  \item We have two new tracks
  \begin{itemize}
  \item Cloud Track -- evaluate distributed solvers on the Amazon cloud. Solvers are run on 1600 virtual cores for 1000 seconds. 
  Sponsored by Amazon. Participants received AWS credit to develop their solvers.
  \item Planning Track -- dedicated benchmark suite on 200 planning instances. Future competitions will have special benchmark suites for other applications.
  \end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}{.28\textwidth}
\centering
\includegraphics[width=.9\textwidth]{AWSlogo}
\end{minipage}

\medskip

\begin{itemize}
  \item New formally-verified checker
  \begin{itemize}
	\item {\bf cake\_lpr\_array} by Yong Kiam Tan: very easy to install
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Benchmark Instance Selection}

\textbf{GBD Benchmark Database (GBD)}

\begin{itemize}
\item Collaborative Management of Attributes of Benchmark Instances\\[.2em]
\url{https://pypi.org/project/global-benchmark-database-tool}\\[1em]
\item Retrieval of Benchmark Instances by their Attributes\\[.2em]
\url{https://gbd.iti.kit.edu}\\[1em]
\end{itemize}%
%
\parbox{.7\linewidth}{
\begin{thebibliography}{00}%
\tiny
\bibitem{GBD}
M. Iser and C. Sinz, ``A Problem Meta-Data Library for Research in {SAT}'',
Proceedings of Pragmatics of {SAT} 2018, pp. 144--152, 2018
\end{thebibliography}
~\\~\\~\\~\\~\\~\\
}
\hfill
\parbox{.29\linewidth}{
~\\~\\
\includegraphics[width=\linewidth]{gbd_logo.png}
}

\end{frame}

\begin{frame}{Tracks part 1}
\begin{itemize}
\item Main (Sequential) Track (50 solvers)
\begin{itemize}
\item 400 benchmarks, a combination of ``application" and ``crafted"
\item 5,000 sec limit for solving and 40,000 sec for proof checking
\item Solvers run on a single core
\item UNSAT proof logging required
\end{itemize}
\pause
\medskip
\item Parallel Track (14 solvers)
\begin{itemize}
\item The same 400 benchmarks from Main track
\item 5,000 sec limit for solving
\item 1 AWS m4.16xlarge: 64 virtual CPU cores, 256GB RAM
\end{itemize}
\pause
\medskip
\item Cloud Track (6 solvers)
\begin{itemize}
\item The same 400 benchmarks from Main track
\item 1,000 sec limit for solving
\item 100 AWS m4.4xlarge: total of 1600 virtual CPU cores
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Tracks part 2}
\begin{itemize}
\item Incremental Library Track (5 solvers)
\begin{itemize}
\item benchmarks are SAT based applications (bones, essentials, lsp, max, ijtihad, pasar), we used same applications but with different inputs
\item combined rank for each application determines winner
\item 2,000 sec limit for solving
\end{itemize}
\pause
\medskip
\item Planning Track (49 solvers)
\begin{itemize}
\item 200 benchmarks, all coming from planning problems
\item 5,000 sec limit for solving
\end{itemize}
\pause
\medskip
\item No-Limit Track (64 solvers, superset of Main track participants)
\begin{itemize}
\item 300 brand new benchmarks (subset of the Main Track benchmarks)
\item 5,000 sec limit for solving
\item Most of the solvers provided source codes and models, but not all
\item No awards: top solvers were open source and proof producing
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Planning Track -- Results}
The Top 3 solvers of the Planning Track are:
\begin{itemize}
\item[1]<4->{\bf CaDiCaL-alluip-trail} (PAR-2: 3406, 80 solved)\\
{\bf CaDiCaL-alluip} (PAR-2: 3409, 80 solved)\\
by Randy Hickey, Nick Feng, and Fahiem Bacchus
\item[2]<3-> {\bf Cryptominisat-ccnr-lsids} (PAR-2: 3441, 79 solved)\\
{\bf Cryptominisat-ccnr} (PAR-2: 3446, 79 solved)\\
by Mate Soos, Shaowei Cai, Jo Devriendt, Stephan Gocht,\\Arijit Shaw, and  Kuldeep Meel
\item[3]<2-> {\bf Kissat-sc2020-unsat} (PAR-2: 3472, 74 solved)\\
by Armin Biere
\end{itemize}

\bigskip

\only<5->{Unfortunately, no planning specific solvers}

\end{frame}

\begin{frame}{Incremental Library Track}
\begin{itemize}
\item $6$ applications (bones, essentials, lsp, max, ijtihad, pasar)
\item $50$ benchmark instances per application
\item Ranking by PAR-2 ($2000$ seconds timeout)
\item Final Ranking: Number of Won Categories
\end{itemize}~\\

\resizebox{\textwidth}{!}{
\begin{tabular}{l|rr|rr|rr|rr}
 & \multicolumn{2}{c|}{abcdsat-i20} & \multicolumn{2}{c|}{CaDiCaL-sc2020} & \multicolumn{2}{c|}{\bf Cryptominisat5} & \multicolumn{2}{c}{Riss-7.1.2}\\
\hline
bones		& 513 (46)  & 2 & 631 (43)	& 3 & \bf 390 (46) & \bf1 & 903 (40) & 4\\
essentials	& 1333 (35) & 4 & 1210 (37)	& 2 & \bf 1200 (36)& \bf1 & 1241 (36) & 3\\
lsp			& 2495 (21) & 4 & 1959 (26) & 3 & \bf 1789 (29)& \bf1 & 1881 (27) & 2\\
max			&\bf 1987 (27)&\bf1& 2021 (25) & 2 & 2024 (25) & 3 & 2021 (25) & 2\\
ijtihad		& 3238 (10) & 4 &\bf 3002 (13)&\bf1& 3079 (12) & 2 & 3145 (11) & 3\\
pasar		& 471 (45)  & 2 & 506 (45) &   3& 969 (38) & 4 & \bf 386 (46) & \bf1\\
\hline\hline
%$\Sigma$ scores & 10037 (184) & 17 & 9329 (189) & 14 & 9451 (186) & \bf 12 & 9577 (185) & 15\\
final & \multicolumn{2}{c|}{1} & \multicolumn{2}{c|}{1} & \multicolumn{2}{c|}{\bf 3} & \multicolumn{2}{c}{1}\\
\end{tabular}}

\medskip

Winner: {\bf Cryptominisat5}

\end{frame}

\begin{frame}{Parallel Track SAT -- Results}
The Top 3 solvers of the Parallel Track SAT are:
\begin{itemize}
\item[1]<4-> {\bf P-MCOMSPS-STR-32} (PAR-2: 2853, 153 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon
\item[2]<3-> {\bf PaInleSS\_ExMapleLCMDistChronoBT} (PAR-2: 2913, 154 solved)\\
by Rodrigue Konan Tchinda and Cl\'ementin Tayou Djamegni
\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3405, 143 solved)\\
by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
\end{itemize}
\end{frame}

\begin{frame}{Parallel Track SAT -- Plot}

\centering
\includegraphics[width=.8\textwidth]{parallel-SAT}

\end{frame}

\begin{frame}{Parallel Track UNSAT -- Results}
The Top 3 solvers of the Parallel Track UNSAT are:
\begin{itemize}

\item[1]<4-> {\bf Plingeling} (PAR-2: 3630, 137 solved)\\
by Armin Biere
\item[2]<3-> {\bf P-MCOMSPS-STR-32} (PAR-2: 3729, 131 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon

\item[3]<2-> {\bf ManyGlucose-32} (PAR-2 3844, 131 solved)\\
{\bf ManyGlucose-64} (PAR-2: 3974, 129 solved)\\
by Hidetomo Nabeshima and Katsumi Inoue
\end{itemize}
\end{frame}

\begin{frame}{Parallel Track UNSAT -- Plot}

\centering
\includegraphics[width=.8\textwidth]{parallel-UNSAT}

\end{frame}

\begin{frame}{Parallel Track ALL -- Results}
The Top 3 solvers of the Parallel Track ALL are:
\begin{itemize}
\item[1]<4-> {\bf P-MCOMSPS-STR-32} (PAR-2: 3291, 284 solved)\\
{\bf P-MCOMSPS-STR-64} (PAR-2: 3689, 272 solved)\\
by Vincent Vallade, Ludovic Le Frioux, Souheib Baarir,\\Julien Sopena, and Fabrice Kordon
\item[2]<3-> {\bf Plingeling} (PAR-2: 3718, 270 solved)\\
by Armin Biere
\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3797, 270 solved)\\
by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
\end{itemize}
\end{frame}

\begin{frame}{Parallel Track ALL -- Plot}

\centering
\includegraphics[width=.8\textwidth]{parallel-ALL}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Cloud Track -- Results}

The Top 3 solvers of the Cloud Track are:
\begin{itemize}

\item[1]<4-> {\bf mallob-mono} (PAR-2: 2429, 306 solved)\\
by Dominik Schreiber
\item[2]<3-> {\bf TopoSAT2} (PAR-2: 3024, 283 solved)\\
by Thorsten Ehlers, Mitja Kulczynski, Dirk Nowotka, and Philipp Sieweck
\item[3]<2-> {\bf Slime} (PAR-2 4208, 239 solved)\\
by Oscar Riveros
\end{itemize}

\end{frame}

\begin{frame}{Cloud Track -- Plot}

\centering
\includegraphics[width=.8\textwidth]{cloud-ALL}

\end{frame}

\begin{frame}{Main Track SAT -- Results}
The Top 3 solvers of the Main Track SAT are:
\begin{itemize}
\item[1]<4-> {\bf Relaxed\_LCMDCBDL\_newTech} (PAR-2: 2997, 150 solved)  \\
by Xindi Zhang and Shaowei Cai
\item[2]<3-> {\bf Kissat-sc2020-sat}  (PAR-2: 3128, 146 solved)\\
by Armin Biere
\item[3]<2-> {\bf Cryptominisat-ccnr-lsids} (PAR-2: 3263, 144 solved)\\
{\bf Cryptominisat-ccnr} (PAR-2: 3317, 145 solved)\\
by Mate Soos, Shaowei Cai, Jo Devriendt, Stephan Gocht,\\Arijit Shaw, and  Kuldeep Meel
\end{itemize}
\end{frame}

\begin{frame}{Main Track SAT -- Top 10 Plot}

\centering
\includegraphics[width=.8\textwidth]{main-top10-SAT}

\end{frame}

\begin{frame}{Main Track UNSAT -- Results}
The Top 3 solvers of the Main Track UNSAT are:
\begin{itemize}
\item[1]<4-> 
{\bf Kissat-sc2020-unsat}  (PAR-2: 4315, 124 solved)\\
{\bf Kissat-sc2020-default}  (PAR-2: 4336, 126 solved)\\
{\bf Kissat-sc2020-sat} (PAR-2: 4725, 118 solved)\\
by Armin Biere
\item[2]<3-> {\bf CaDiCaL-trail} (PAR-2: 4842, 117 solved)\\
by Randy Hickey, Nick Feng, and Fahiem Bacchus
\item[3]<2-> {\bf MapleLCMDistChronoBT-f2trc-s} (PAR-2: 4991, 110 solved)  \\
by Stepan Kochemazov
\end{itemize}
\end{frame}

\begin{frame}{Main Track UNSAT -- Top 10 Plot}

\centering
\includegraphics[width=.8\textwidth]{main-top10-UNSAT}

\end{frame}

\begin{frame}{Main Track ALL -- Results}
The Top 3 solvers of the Main Track ALL are:
\begin{itemize}
\item[1]<4-> {\bf Kissat-sc2020-sat} (PAR-2: 3926, 264 solved)\\
{\bf Kissat-sc2020-default}  (PAR-2: 4083, 260 solved)\\
by Armin Biere
\item[2]<3-> {\bf Relaxed\_LCMDCBDL\_newTech} (PAR-2: 4179, 253 solved)  \\
by Xindi Zhang and Shaowei Cai
\item[3]<2-> {\bf Cryptominisat-ccnr-lsids} (PAR-2: 4267, 248 solved)\\
{\bf Cryptominisat-ccnr} (PAR-2: 4278, 250 solved)\\
by Mate Soos, Shaowei Cai, Jo Devriendt, Stephan Gocht,\\Arijit Shaw, and  Kuldeep Meel
\end{itemize}
\end{frame}

\begin{frame}{Main Track ALL-- Top 10 Plot}

\centering
\includegraphics[width=.8\textwidth]{main-top10-ALL}

\end{frame}

\begin{frame}{More information and Acknowledgments}
Additionals Information
\begin{itemize}
	\item The Competition Proceedings (solver and benchmark descriptions)
	 will soon be available at https://satcompetition.github.io/2020/
	\item For the detailed competition results see the SAT Competition website
\end{itemize}
\medskip

Acknowledgments
\begin{itemize}
\item Thanks to all the participants
\item Thanks for all the benchmarks
\item Thanks to Mike Whalen, Jonathan Eidelman,\\and Frankie Botero at AWS
\item Thanks to Aaron Stump and StarExec
\item Thanks to CAS Software Karlsruhe for the medals
\end{itemize}
\begin{itemize}
\item Thank You for Your attention
\end{itemize}
\end{frame}

%----------------------------------------------------------------------------------------

\end{document}

### 2020-07-31 tournament.tex
updated slides

\documentclass[conference]{IEEEtran}

\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}
\usetikzlibrary{arrows,shadows} % for pgf-umlsd
\usepackage[underline=true,rounded corners=false]{pgf-umlsd}

\newcommand{\hy}{\hbox{-}\nobreak\hskip0pt}

\newcommand{\NP}{\text{\normalfont NP}}

\usepackage{hyperref}

\begin{document}

% paper title
\title{Improving Directed Ramsey Numbers using SAT}

\author{\IEEEauthorblockN{David Neiman, Marijn Heule, and John Mackey}
\IEEEauthorblockA{Carnegie Mellon University, Pittsburgh, United States}

}

\newcommand{\mc}{}

\maketitle

\section*{Intro}

%The suite consists of miters: equivalence checking problems of 
%Boolean circuits.

A tournament is an orientation of a complete graph, or equivalently a directed graph $D$ 
with no self-loops such that, for all pairs of distinct vertices $u$ and $v$, exactly one of
the edges $uv$ or $vu$ is in $D$. Intuitively, a tournament of order $n$ represents the
results of a round-robin tournament between $n$ teams, where the existence of edge
$uv$ means team $u$ beat team $v$ in their head-to-head match. The exclusivity of
$uv$ and $vu$ means that if team $u$ beats team $v$, team $v$ doesn't beat team
$u$, and the inclusion of one of those edges reflects the fact that in a round-robin
tournament, each team plays each other team. The non-existence of self-loops translates to the fact that no team plays itself.

A tournament is \textit{transitive} if, for all vertices $a$, $b$, and $c$, the existence of edges $ab$ and $bc$ implies the existence of edge $bc$.
If a tournament is not transitive, then it contains a directed cycle of length 3.

\begin{figure}[ht]
\centering
  \begin{tikzpicture}
    \node[circle, draw] (1) at (0,0) {\!1\!};
    \node[circle, draw] (2) at (2,0) {\!2\!};
    \node[circle, draw] (3) at (3,-1.7) {\!3\!};
    \node[circle, draw] (4) at (2,-3.4) {\!4\!};
    \node[circle, draw] (5) at (0,-3.4) {\!5\!};
    \node[circle, draw] (6) at (-1,-1.7) {\!6\!};

    \draw (1) edge[-latex] (2) (1) edge[-latex]  (3) (1) edge[-latex]  (5) (4) edge[-latex] (1) (6) edge[-latex]  (1);
    \draw (2) edge[-latex] (3) (2) edge[-latex]  (4) (2) edge[-latex]  (6) (5) edge[-latex] (2) (3) edge[-latex]  (4);
    \draw (3) edge[-latex] (5) (6) edge[-latex]  (3) (4) edge[-latex]  (5) (4) edge[-latex] (6) (5) edge[-latex]  (6);

  \end{tikzpicture}
\caption{The unique tournament of order 6 without a transitive sub-tournament of order 4.}
\end{figure}

\section*{Directed Ramsey Numbers}
The directed Ramsey number $R(k)$ is the smallest integer $n$ such that all
tournaments on $n$ vertices contain a transitive tournament of order  $k$.

Directed Ramsey numbers were first introduced by Erd\H{o}s and Moser~\cite{ErdosMoser}. 
In particular, they showed that $k \leq 2 \log_2(R(k)) + 1$ and also noted that $k \geq \log_2(R(k)) + 1$. 
In particular, this means $R(k)$ grows roughly as an exponential of $k$, with multiplier somewhere
between $\sqrt{2}$ and 2. The precise limit of that multiplier is not known, but the literature has the following
results on small directed Ramsey numbers:

\begin{itemize}
\item $R(2) = 2$
\item $R(3) = 4$
\item $R(4) = 8$
\item $R(5) = 14$
\item $R(6) = 28$ (\cite{SanchezFlores55})
\item $32 \leq R(7) \leq 54$ (\cite{SanchezFlores54})
\end{itemize}

The tournaments of order 25, 26, and 27 that do not contain a 
transitive sub-tournament of order 6 are unique. We call them $ST_{25}$,
$ST_{26}$, and $ST_{27}$, respectively. There are five 
tournaments of order 24 without a transitive sub-tournament of order 6.

\section*{SAT Encoding}

Lower bounds of directed Ramsey number $R(k)$ can be improved by 
constructing a complete directed graph without a transitive tournament
of order $k$. The direct encoding into SAT would only use boolean 
variables for each edge with the truth value of a variable denoting 
the direction of the edge. Such an encoding uses many clauses and
the resulting formulas are too large to improve the lower bound of
$R(7)$. We therefore constructed a more compact encoding, which
uses the fact that a transitive tournament lacks a directed cycle of
length 3. For each triple of vertices in the graph, we introduce 
a new variable that is true if and only if the edges between them 
form a directed cycle. We use these auxiliary variables to encode 
the absence of transitive tournaments of order $7$ more 
compactly.

\section*{Benchmarks}

We submitted 16 benchmarks to the 2020 SAT Competition. The first
8 formulas encode whether $ST_{25}$, $ST_{26}$, $ST_{27}$, and the five
tournaments of order 24 without a transitive sub-tournament of order 6
can be extended to a tournament of order 33 without creating a
transitive sub-tournament of order 7. All these instances are satisfiable
and thus establish an improved lower bound $R(7) > 33$. Figure~\ref{fig:lowerbound} shows an example. The second 8
formulas are similar, but encode the existence of a tournament of order 34
without creating a transitive sub-tournament of order 7. It is not known 
whether these instances are satisfiable.

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[fill=black,shape=circle,draw,inner sep=1pt] (char) {\textcolor{white}{#1}};}}

\newcommand{\zero}{0}
\newcommand{\one}{\circled{1}}

\begin{figure*}[ht]
\begin{center}

\begin{tabular}{c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c@{\,}c}
\zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \zero& \zero& \zero& \one& \one\\
\zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \one& \zero& \one& \zero& \zero& \one& \one\\
\zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \zero& \one& \one& \zero\\
\zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \one& \zero& \one& \one& \zero& \zero& \one\\
\zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \zero& \one& \zero& \one\\
\one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \one& \zero\\
\zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \one& \zero& \one& \one& \zero& \zero\\
\one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \zero& \one& \zero& \zero\\
\one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \zero& \zero& \zero& \zero& \one& \one& \one\\
\zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \one& \one& \zero& \one& \one& \one& \one\\
\zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \zero& \zero& \zero& \zero& \zero\\
\one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \zero& \one& \one& \zero\\
\zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \one& \zero& \one& \zero& \one& \zero\\
\zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \one& \one& \one& \one& \zero& \zero& \zero\\
\one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \one& \zero& \one\\
\one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \one& \one& \zero& \one& \zero& \zero\\
\one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \zero& \one& \zero& \zero& \zero& \one& \one\\
\zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \one& \zero& \one& \zero& \one& \one& \zero\\
\zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \one& \one& \zero& \one\\
\one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \zero& \zero& \one\\
\one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \one& \zero& \zero& \one& \zero& \one& \zero& \zero& \one\\
\one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \one& \one& \zero& \zero& \zero& \one\\
\one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \one& \zero& \zero& \zero& \one& \one& \one& \zero\\
\zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \zero& \one\\
\one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \zero& \zero& \zero& \one& \one& \one& \zero\\
\zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \zero& \one& \zero& \zero& \one& \one\\
\one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \zero\\
\zero& \one& \zero& \one& \zero& \zero& \zero& \zero& \one& \zero& \zero& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \zero& \one& \zero& \one& \one& \zero\\
\one& \zero& \one& \zero& \one& \one& \one& \zero& \one& \one& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \zero& \zero& \zero& \zero& \zero& \zero& \one& \one\\
\one& \one& \one& \zero& \one& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \zero& \one& \one& \one& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \zero& \one& \one& \zero& \zero& \zero& \zero\\
\one& \one& \zero& \one& \zero& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \one\\
\zero& \zero& \zero& \one& \one& \zero& \one& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \zero& \one& \zero& \zero& \one& \one& \zero& \zero\\
\zero& \zero& \one& \zero& \zero& \one& \one& \one& \zero& \zero& \one& \one& \one& \one& \zero& \one& \zero& \one& \zero& \zero& \zero& \zero& \one& \zero& \one& \zero& \one& \one& \zero& \one& \zero& \one& \zero\\
\end{tabular}

%\begin{verbatim}
%          0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 0 0 0 1 1 
%          0 0 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 1 0 1 0 0 1 1 
%          0 1 0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 0 1 1 0 
%          0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 1 0 1 1 0 0 1 
%          0 1 0 1 0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 0 1 0 1 
%          1 1 0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 1 0 
%          0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 1 0 1 1 0 0 
%          1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 0 1 0 0 
%          1 0 0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 0 0 0 0 1 1 1 
%          0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 1 1 0 1 1 1 1 
%          0 1 1 0 0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 0 0 0 0 0 
%          1 1 0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 0 1 0 1 1 0 
%          0 0 0 1 1 0 0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 1 1 0 1 1 0 1 0 1 0 1 0 
%          0 1 1 1 0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 0 1 1 1 1 0 0 0 
%          1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 1 1 0 0 0 0 1 1 0 1 
%          1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 1 0 0 1 1 1 0 1 0 0 
%          1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 1 0 1 0 0 0 1 1 
%          0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 1 1 0 1 0 1 1 0 
%          0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 1 1 1 0 1 0 0 0 0 1 1 0 1 
%          1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 0 1 0 1 1 0 0 1 
%          1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 1 1 1 0 0 1 0 1 0 0 1 
%          1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 0 0 0 0 1 1 1 0 0 0 1 
%          1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 1 1 0 0 0 1 1 1 0 
%          0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 0 0 1 0 1 0 1 0 1 
%          1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 0 0 0 0 1 0 1 0 1 0 0 0 1 1 1 0 
%          0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 1 0 1 0 0 1 1 
%          1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 0 1 1 1 0 0 0 
%          0 1 0 1 0 0 0 0 1 0 0 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 0 1 0 1 1 0 
%          1 0 1 0 1 1 1 0 1 1 1 0 1 0 1 0 1 0 1 0 1 0 1 0 1 0 0 0 0 0 0 1 1 
%          1 1 1 0 1 0 0 1 1 0 1 1 0 0 0 1 1 1 0 0 0 1 0 1 0 1 0 1 1 0 0 0 0 
%          1 1 0 1 0 1 0 0 0 0 1 0 1 1 0 0 1 0 0 1 1 1 0 0 0 1 1 0 1 1 0 0 1 
%          0 0 0 1 1 0 1 1 0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 0 1 0 0 1 1 0 0 
%          0 0 1 0 0 1 1 1 0 0 1 1 1 1 0 1 0 1 0 0 0 0 1 0 1 0 1 1 0 1 0 1 0
%\end{verbatim}
\end{center}
\caption{Adjacency matrix of a 33-vertex tournament without a transitive sub-tournament of order 7.}
\label{fig:lowerbound}
\end{figure*}

\bibliographystyle{IEEEtran}

\bibliography{references}

\end{document}

### 2020-07-31 slides/satcomp20slides.tex
cloud scores

@@
 by Rodrigue Konan Tchinda and Cl\'ementin Tayou Djamegni
-\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3405, 143 solved)\\
-by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
+\item[3]<2-> {\bf Plingeling} (PAR-2: 3805, 133 solved)\\
+by Armin Biere
+%\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3405, 143 solved)\\
+%by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
 \end{itemize}
@@
 by Armin Biere
-\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3797, 270 solved)\\
-by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
+\item[3]<2-> {\bf ManyGlucose-32} (PAR-2: 3985, 260 solved)\\
+by Hidetomo Nabeshima and Katsumi Inoue
+%\item[3]<2-> {\bf abcd-para-scavel} (PAR-2: 3797, 270 solved)\\
+%by Zhihui Li, Guanfeng Wu, Yanh Xu, and Qingshan Chen
 \end{itemize}
@@
 
-\item[1]<4-> {\bf mallob-mono} (PAR-2: 2429, 306 solved)\\
+\item[1]<4-> {\bf mallob-mono} (PAR-2: 583, 299 solved)\\
 by Dominik Schreiber
-\item[2]<3-> {\bf TopoSAT2} (PAR-2: 3024, 283 solved)\\
+\item[2]<3-> {\bf TopoSAT2} (PAR-2: 706, 278 solved)\\
 by Thorsten Ehlers, Mitja Kulczynski, Dirk Nowotka, and Philipp Sieweck
-\item[3]<2-> {\bf Slime} (PAR-2 4208, 239 solved)\\
+\item[3]<2-> {\bf Slime} (PAR-2 1057, 214 solved)\\
 by Oscar Riveros

### 2020-09-14 paper/main.tex
update

\documentclass{elsarticle}

\usepackage[utf8x]{inputenc}
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{float,lscape}
\usepackage{listings}
\usepackage{tkz-graph}
\lstset{language=C}
\rowcolors{3}{gray!10}{white}

\title{SAT Competition 2020\tnoteref{title}}
\tnotetext[title]{\url{satcompetition.github.io/2020}}

\author[jku]{Nils Froleyks}
\ead{nils.froleyks@jku.at}
\author[cmu]{Marijn Heule}
\ead{marijn@cmu.edu}
\author[kit]{Markus Iser}
\ead{markus.iser@kit.edu}
\author[hiit]{Matti Järvisalo}
\ead{matti.jarvisalo@helsinki.fi}
\author[ctu]{Martin Suda} 
\ead{martin.suda@cvut.cz}

\address[kit] {
KIT Department of Informatics\\
\url{markus.iser@kit.edu}\\[1em]
}

\newcommand{\todo}[1]{{\color{purple}Todo: #1}}

\begin{document}

\begin{abstract}
We describe the 2020 SAT Competition and provide a detailed analysis of its results.
\end{abstract}

\begin{keyword}
SAT, Competition, Retrospective
\end{keyword}

\maketitle

\section{Introduction}

\todo{Motivational paragraphs for SAT and the Competitions and what made this Competition Special}

\todo{Present some important pointers for SAT and CDCL}

\todo{Present the structure of the paper}

\section{Overview: Descriptions of Tracks, List of Participants}

\subsection{Main Track}

\subsection{Planning Track}

\subsection{Incremental Library Track}

\subsection{Parallel Track}

\subsection{Cloud Track}

\section{Selection of Benchmark Instances}

\subsection{Main Instances}

\subsection{Planning Instances}

\subsection{Incremental Library Applications and Instances}

\section{Competition Results}

\todo{for each track summarize the descriptions of the winning solvers}

\section{Analysis of Results}

\subsection{Essential Improvements in Winning Solvers}

\todo{Common and Specific Winning Strategies}

\subsection{Similarity of Solvers}

\todo{Rank Correlation}

\section{Conclusion}

\bibliographystyle{elsarticle-num}
\bibliography{main}

\end{document}

### 2020-09-28 paper/main.tex
table of teams and solvers in main tracks

@@
 \usepackage{float,lscape}
-\usepackage{listings}
+\usepackage[ruled,linesnumbered,vlined]{algorithm2e}
 \usepackage{tkz-graph}
-\lstset{language=C}
-\rowcolors{3}{gray!10}{white}
+\usepackage{lscape}
 
@@
 \begin{keyword}
-SAT, Competition, Retrospective
+SAT, Competition
 \end{keyword}
@@
 
+%\newcommand{\stack}[2]{\begin{tabular}{@{}c@{}}#1 \\#2\end{tabular}}
+
+% Stack a variable number of arguments:
+\makeatletter
+\newcommand{\stack}[1]{%
+    \begin{tabular}{@{}l@{}}#1\checknextarg}
+\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
+\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
+\makeatother
+
+\begin{table}[h]
+\begin{tabular}{|l|l|l|}
+\hline
+Team & Solver & Configuration / Variant / Hack \\
+\hline
+
+\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} 
+ & \multirow{3}{*}{Kissat-sc2020} & --\\
+ &  & sat\\
+ &  & unsat\\
+\cline{2-3}
+ & Cadical-sc2020 & --\\
+\hline
+
+\multirow{3}{*}{Zhang, Cai}
+ & \multirow{3}{*}{Relaxed\_LCMDCBDL} & --\\
+ &  & noTimeParam\\
+ &  & newTech\\
+\hline
+
+\multirow{2}{*}{\stack{Soos, Cai, }{Devriendt, Shaw}}
+ & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
+ &  & lsids\\
+\hline
+
+\stack{Soos, Selman, }{Kautz}~ & CryptoMiniSat-WalkSAT & -- \\
+\hline
+
+\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
+ & \multirow{3}{*}{Cadical} & trail\\
+ &  & alluip\\
+ &  & alluip-trail\\
+ \cline{2-3}
+ & Maple-LCM-Dist & alluip-trail\\
+\hline
+
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc\\
+ & & f2trc-s\\
+ \cline{2-3}
+ & MapleLCMDistChronoBT-DL & f2trc\\
+\hline
+
+\stack{Kochemazov, }{Zaikin, }{Kondratiev, }{Semenov} ~& MapleLCMDistChronoBT-DL-v3 & --\\
+\hline
+
+\multirow{4}{*}{\stack{Lonlac, }{Nguifo}} & \multirow{4}{*}{Undominated-LC-MapleLCMDistChronoBT-DL} & --\\
+ &  & top16\\
+ &  & top24\\
+ &  & top36\\
+\hline
+
+\multirow{5}{*}{\stack{Tchinda, }{Djamegni}}
+ & \multirow{4}{*}{Painless-ExMapleLCMDistChronoBT} & padc\_dl\\
+ &  & padc\_dl\_ovau\_lin\\
+ &  & padc\_dl\_ovau\_exp\\
+ &  & psids\_dl\\
+ \cline{2-3}
+ & Glucose 3.0 & upGlucose-3.0\_PADC\\
+\hline
+
+Shaw, Meel & DurianSat & --\\
+\hline
+
+\multirow{2}{*}{Chen}
+ & Maple & Mix\\
+ & Maple & Simp\\
+\hline
+
+Riveros & SLIME & --\\
+\hline
+
+\multirow{3}{*}{Li, Wu, Xu, Chen} & MLCMDChronoBT-DL-Scavel & --\\
+ & MapleLCMDistChronoBT-DL-Scavel01 & --\\
+ & MapleLCMDistChronoBT-DL-Scavel02 & --\\
+\hline
+
+\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
+ & MapleCOMSPS\_LRB\_VSIDS\_2 & --\\
+ & MapleCOMSPS\_LRB\_VSIDS\_2 & LRB\_VSIDS\_2\_init\\
+\hline
+
+\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}} & exp-V-LGB-MLD-CBT-DL & --\\
+ & exp-V-L-MLDCBT-DL & --\\
+ & exp-L-MLD-CBT-DL & -- \\
+ & exp-V-MLD-CBT-DL & -- \\
+\hline
+
+\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
+ & \multirow{3}{*}{MapleCM} & +dist \\
+ &  & +dist+sattime2s+- \\
+ &  & +dist+simp2-- \\
+ & MapleCMused & +dist \\
+\hline
+
+Kaiser, Hartung & PauSat & -- \\
+\hline
+
+Osama, Wijs & ParaFROST, ParaFROST-CBT & -- \\
+\hline
+\end{tabular}
+\caption{Teams, Solvers and Hacks participating in the Main Tracks}
+\end{table}
+
 \subsection{Planning Track}
@@
 
-\section{Selection of Benchmark Instances}
+\section{Selection and Maintenance of Benchmark Instances}
 
-\subsection{Main Instances}
+GBD Tools is a new tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
+Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}
+
+For selection of benchmarks in this competition, we used a database which contains information about instance author, family and result for a collection of instances used in all SAT competitive events dating back to 2006.\footnote{\url{https://gbd.iti.kit.edu/getdatabase/meta.db}}
+Like this it was possible to query for instances with desired properties, which gives the instance selection process a new quality. 
+Using GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
+
+\subsection{Selection of Instances}
+
+The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition.
+At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.
+
+In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families.
+By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.
+
+In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
+Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
+If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
+Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
+
+\begin{algorithm}[t]
+\DontPrintSemicolon
+
+\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
+\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
+\KwResult{$S$ : Set of Selected Instances}
+\SetKwFunction{rand}{$\mathsf{random.choice}$}
+\BlankLine
+$S \leftarrow \emptyset$\;
+
+\For {$a \in A$} {
+	$I_a^+ \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$, $k=7$}\;	
+	$I_a^- \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$, $k=7$}\;	
+	\If {$|I_a^+|+|I_a^-| < 14$}{
+		$l \leftarrow 14 - (|I_a^+|+|I_a^-|)$\;
+		$I_a^? \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$, $k=l$}\;
+	}
+	$S \leftarrow S \cup I_a^+ \cup I_a^- \cup I_a^?$\;	
+}
+\Return $S$\;
+
+\caption{Benchmark Instance Selection}
+\label{algo:select}
+\end{algorithm}
+
+To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
+We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
+Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
 

### 2020-09-29 paper/main.tex
more tables

@@
 
-\subsection{Main Track}
+\subsection{Main Tracks}
+
+This year in the Main Track, we had a Planning Sub-Track. 
+The general idea is, that next to a balanced selection of benchmark instances in main track, to each year also offer one domain-specific sub-track.
 
@@
 \hline
-Team & Solver & Configuration / Variant / Hack \\
+Team & Solver & Variant \\
 \hline
@@
 
-\multirow{2}{*}{\stack{Soos, Cai, }{Devriendt, Shaw}}
+\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
  & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
@@
 
-\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}} & exp-V-LGB-MLD-CBT-DL & --\\
- & exp-V-L-MLDCBT-DL & --\\
- & exp-L-MLD-CBT-DL & -- \\
- & exp-V-MLD-CBT-DL & -- \\
+\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
+ & \multirow{4}{*}{MapleLCMDistChronoBT-DL-v2.2} & exp-V-LGB-MLD-CBT-DL \\
+ &  & exp-V-L-MLDCBT-DL \\
+ &  & exp-L-MLD-CBT-DL \\
+ &  & exp-V-MLD-CBT-DL \\
 \hline
@@
 \multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
- & \multirow{3}{*}{MapleCM} & +dist \\
- &  & +dist+sattime2s+- \\
- &  & +dist+simp2-- \\
- & MapleCMused & +dist \\
+ & \multirow{4}{*}{MapleCM} & \texttt{+}dist \\
+ &  & \texttt{+}dist\texttt{+}sattime2s\texttt{+}\texttt{-} \\
+ &  & \texttt{+}dist\texttt{+}simp2\texttt{-}\texttt{-} \\
+ &  & used\texttt{+}dist \\
 \hline
@@
 \end{tabular}
-\caption{Teams, Solvers and Hacks participating in the Main Tracks}
+\caption{Teams and Solvers participating in the Main Tracks (Variant refers to a named configuration or a name of a hack)}
 \end{table}
-
-\subsection{Planning Track}
 
@@
 
+\begin{table}[h]
+\begin{tabular}{|l|l|}
+\hline
+Chen & abcdsat-i20 \\
+\hline
+\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 \\
+\hline
+\stack{Soos, Cai, }{Devriendt, Gocht, }{Shaw, Meel}~ & Cryptominisat-5 \\
+\hline
+Manthey & Riss-7.1.2\\
+\hline
+\end{tabular}
+\caption{}
+\end{table}
+
 \subsection{Parallel Track}
 
+\begin{table}[h]
+\begin{tabular}{|l|l|}
+\hline
+\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
+ & P-MCOMSPS-STR-32\\
+ & P-MCOMSPS-STR-64\\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
+ & Plingeling\\
+ & Treengeling\\
+\hline
+\multirow{2}{*}{Nabeshima, Inoue}
+ & ManyGlucose-32\\
+ & ManyGlucose-64\\
+\hline
+\multirow{2}{*}{Tchinda, Djamegni}
+ & painlessmaplevone\\
+ & painlessmaplevtwo\\
+\hline
+Li, Wu, Xu, Chen & syrupscavel\\
+\hline
+Chen & abcdsatptwenty\\
+\hline
+\end{tabular}
+\caption{}
+\end{table}
+
 \subsection{Cloud Track}
+
+\begin{table}[h]
+\begin{tabular}{|l|l|}
+\hline
+Schreiber & mallob-mono\\
+\hline
+\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2\\
+\hline
+Riveros & Slime\\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba\\
+& Paracooba-March\\
+\hline
+Hartung & CTSat\\
+\hline
+\end{tabular}
+\end{table}
 

### 2020-11-17 paper/main.tex
prepared paragraphs for descriptions of winning solvers

--- 2020-09-28 paper/main.tex
@@
 \usepackage{graphicx}
-\usepackage{color}
+\usepackage[table]{xcolor}
 \usepackage{tabularx}
-\usepackage{multirow}
+\usepackage{multirow,makecell}
 \usepackage{float,lscape}
@@
 \begin{tabular}{@{}l@{}}#1\checknextarg}
-\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
-\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{ \end{tabular}}}
+\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
+\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
 \makeatother
 
-\begin{table}[h]
-\begin{tabular}{|l|l|l|}
+\definecolor{gold}{HTML}{FFF3D6}
+\definecolor{silver}{HTML}{F3F5F7}
+\definecolor{cupper}{HTML}{EAD9D7}
+\fboxsep0pt
+\newcommand{\firsto}{\colorbox{gold}{$m^1$}}
+\newcommand{\firsts}{\colorbox{gold}{$s^1$}}
+\newcommand{\firstu}{\colorbox{gold}{$u^1$}}
+\newcommand{\firstp}{\colorbox{gold}{$p^1$}}
+\newcommand{\secondo}{\colorbox{silver}{$m^2$}}
+\newcommand{\seconds}{\colorbox{silver}{$s^2$}}
+\newcommand{\secondu}{\colorbox{silver}{$u^2$}}
+\newcommand{\secondp}{\colorbox{silver}{$p^2$}}
+\newcommand{\thirdo}{\colorbox{cupper}{$m^3$}}
+\newcommand{\thirds}{\colorbox{cupper}{$s^3$}}
+\newcommand{\thirdu}{\colorbox{cupper}{$u^3$}}
+\newcommand{\thirdp}{\colorbox{cupper}{$p^3$}}
+
+\begin{table}[h!]
+\smaller
+\arrayrulecolor{gray}
+\centering
+\begin{tabular}{|l|l|l|l|}
 \hline
-Team & Solver & Configuration / Variant / Hack \\
+\bf Team & \bf Solver & \bf Variant & \bf Award \\
 \hline
 
-\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} 
- & \multirow{3}{*}{Kissat-sc2020} & --\\
- &  & sat\\
- &  & unsat\\
-\cline{2-3}
- & Cadical-sc2020 & --\\
+\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat-sc2020} &  -- & \firsto\firstu\\
+ &  &  sat & \firsto\firstu\seconds\\
+ &  &  unsat & \firstu\thirdp\\
+\cline{2-4}
+ &  Cadical-sc2020 &  -- & \\
 \hline
@@
 \multirow{3}{*}{Zhang, Cai}
- & \multirow{3}{*}{Relaxed\_LCMDCBDL} & --\\
- &  & noTimeParam\\
- &  & newTech\\
+    & \multirow{3}{*}{MapleLCMDistCBT-DL} & Relaxed & \\
+ &  & Rel. noTimeParam & \\
+ &  & Rel. newTech & \secondo\firsts\\
 \hline
 
-\multirow{2}{*}{\stack{Soos, Cai, }{Devriendt, Shaw}}
- & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
- &  & lsids\\
+\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
+ &  \multirow{2}{*}{CryptoMiniSat-CCAnr} &  -- & \thirdo\thirds\secondp\\
+ &  &  lsids & \thirdo\thirds\secondp\\
 \hline
 
-\stack{Soos, Selman, }{Kautz}~ & CryptoMiniSat-WalkSAT & -- \\
+\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & CryptoMiniSat-WalkSAT & -- & \\
 \hline
@@
 \multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
- & \multirow{3}{*}{Cadical} & trail\\
- &  & alluip\\
- &  & alluip-trail\\
- \cline{2-3}
- & Maple-LCM-Dist & alluip-trail\\
+ &  &  trail & \secondu\\
+ &  &  alluip & \firstp\\
+ & \multirow{-3}{*}{Cadical} &  alluip-trail & \firstp\\
+ \cline{2-4}
+ & MapleLCMDist & alluip-trail & \\
 \hline
 
-\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc\\
- & & f2trc-s\\
- \cline{2-3}
- & MapleLCMDistChronoBT-DL & f2trc\\
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc & \\
+ & & f2trc-s & \thirdu\\
+ \cline{2-4}
+ & MapleLCMDistCBT-DL & f2trc & \\
 \hline
 
-\stack{Kochemazov, }{Zaikin, }{Kondratiev, }{Semenov} ~& MapleLCMDistChronoBT-DL-v3 & --\\
+\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& MapleLCMDistCBT-DL-v3 & -- & \\
 \hline
 
-\multirow{4}{*}{\stack{Lonlac, }{Nguifo}} & \multirow{4}{*}{Undominated-LC-MapleLCMDistChronoBT-DL} & --\\
- &  & top16\\
- &  & top24\\
- &  & top36\\
+\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
+ & \multirow{4}{*}{MapleLCMDistCBT-DL-v3} & Undominated & \\
+ &  & Undom. Top16 & \\
+ &  & Undom. Top24 & \\
+ &  & Undom. Top36 & \\
 \hline
 
-\multirow{5}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{Painless-ExMapleLCMDistChronoBT} & padc\_dl\\
- &  & padc\_dl\_ovau\_lin\\
- &  & padc\_dl\_ovau\_exp\\
- &  & psids\_dl\\
- \cline{2-3}
- & Glucose 3.0 & upGlucose-3.0\_PADC\\
+\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
+ & \multirow{4}{*}{ExMapleLCMDistChronoBT} & padc\_dl & \\
+ &  & padc\_dl\_ovau\_lin & \\
+ &  & padc\_dl\_ovau\_exp & \\
+ &  & psids\_dl & \\
+% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
 \hline
 
-Shaw, Meel & DurianSat & --\\
+Shaw, Meel & DurianSat & -- & \\
 \hline
@@
 \multirow{2}{*}{Chen}
- & Maple & Mix\\
- & Maple & Simp\\
+ & \multirow{2}{*}{MapleLCMDistCBT-DL} & Maple\_Mix & \\
+ &  & Maple\_Simp & \\
 \hline
 
-Riveros & SLIME & --\\
+Riveros & SLIME & -- & \\
 \hline
 
-\multirow{3}{*}{Li, Wu, Xu, Chen} & MLCMDChronoBT-DL-Scavel & --\\
- & MapleLCMDistChronoBT-DL-Scavel01 & --\\
- & MapleLCMDistChronoBT-DL-Scavel02 & --\\
+\multirow{3}{*}{Li, Wu, Xu, Chen}
+ & \multirow{3}{*}{MapleLCMDistCBT-DL} & Scavel & \\
+ &  & Scavel01 & \\
+ &  & Scavel02 & \\
 \hline
@@
 \multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
- & MapleCOMSPS\_LRB\_VSIDS\_2 & --\\
- & MapleCOMSPS\_LRB\_VSIDS\_2 & LRB\_VSIDS\_2\_init\\
+ & \multirow{2}{*}{MapleCoMsPS\_LRB\_VSIDS\_2} & -- & \\
+ &  & init & \\
 \hline
 
-\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}} & exp-V-LGB-MLD-CBT-DL & --\\
- & exp-V-L-MLDCBT-DL & --\\
- & exp-L-MLD-CBT-DL & -- \\
- & exp-V-MLD-CBT-DL & -- \\
+\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
+ & \multirow{4}{*}{MapleLCMDistCBT-DL-v2.2} & exp-V-LGB & \\
+ &  & exp-V-L & \\
+ &  & exp-L & \\
+ &  & exp-V & \\
 \hline
@@
 \multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
- & \multirow{3}{*}{MapleCM} & +dist \\
- &  & +dist+sattime2s+- \\
- &  & +dist+simp2-- \\
- & MapleCMused & +dist \\
+ & \multirow{4}{*}{MapleCM} & \texttt{+}dist & \\
+ &  & \texttt{+}dist\texttt{+}sattime2s\texttt{+}\texttt{-} & \\
+ &  & \texttt{+}dist\texttt{+}simp2\texttt{-}\texttt{-} & \\
+ &  & used\texttt{+}dist & \\
 \hline
 
-Kaiser, Hartung & PauSat & -- \\
+Kaiser, Hartung & PauSat & -- & \\
 \hline
 
-Osama, Wijs & ParaFROST, ParaFROST-CBT & -- \\
+\multirow{2}{*}{Osama, Wijs} 
+ & \multirow{2}{*}{ParaFROST} & -- & \\
+ &  & CBT & \\
 \hline
 \end{tabular}
-\caption{Teams, Solvers and Hacks participating in the Main Tracks}
+\caption{Teams and Solvers participating in the Main Tracks (Variant refers to a named configuration or a name of a hack). 
+Note that many teams are only responsible for the variant of a previously existing base solver.
+Awards were given in Main (m), SAT (s), UNSAT (u), and Planning (p) sub-tracks.}
 \end{table}
-
-\subsection{Planning Track}
 
@@
 
+\begin{table}[h]
+\arrayrulecolor{gray}
+\centering
+\begin{tabular}{|l|l|c|}
+\hline
+\bf Team & \bf Solver & \bf Score\\
+\hline
+\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
+\hline
+\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
+\hline
+Chen & abcdsat-i20 & 1 \\
+\hline
+Manthey & Riss-7.1.2 & 1 \\
+\hline
+\end{tabular}
+\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
+\end{table}
+
 \subsection{Parallel Track}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\bf Team & \bf Solver & \bf Awards\\
+\hline
+\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
+ & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
+ & P-MCOMSPS-STR-64 & \firsto \\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
+ & Plingeling & \secondo \thirds \firstu \\
+ & Treengeling & \\
+\hline
+\multirow{2}{*}{Nabeshima, Inoue}
+ & ManyGlucose-32 & \thirdo \thirdu \\
+ & ManyGlucose-64 & \thirdu \\
+\hline
+\multirow{2}{*}{Tchinda, Djamegni}
+ & painlessmaplevone & \seconds \\
+ & painlessmaplevtwo & \seconds \\
+\hline
+Li, Wu, Xu, Chen & syrupscavel & \\
+\hline
+Chen & abcdsatptwenty & \\
+\hline
+\end{tabular}
+\caption{Teams and Solvers participating in the parallel track.}
+\end{table}
 
@@
 
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\bf Team & \bf Solver & \bf Rank\\
+\hline
+Schreiber & mallob-mono & 1\\
+\hline
+\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
+\hline
+Riveros & Slime & 3\\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
+& Paracooba-March & -\\
+\hline
+Hartung & CTSat & -\\
+\hline
+\end{tabular}
+\caption{Teams and Solvers participating in the cloud track.}
+\end{table}
+
 \section{Selection and Maintenance of Benchmark Instances}
 
-GBD Tools is a new tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
+GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
 Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}
@@
 \section{Competition Results}
+\todo{for each track summarize the descriptions of the winning solvers}
 
-\todo{for each track summarize the descriptions of the winning solvers}
+\subsection{Main Track}
+
+\paragraph{Kissat} 
+three configurations submitted, four awards won, cdcl by several mixed strategies
+
+\paragraph{CryptoMiniSat-CCAnr}
+two variants: with and without lsids, with lsids slightly better, three awards won,  combination of cdcl and sls
+
+\paragraph{Cadical Hack}
+three configurations, two awards
+
+\paragraph{MapleLCMDistCBT-DL Relaxed newTech}
+this variant won two awards
+
+\paragraph{MapleLCMDistCBT f2trc-s}
+this variant won onw awards
+
+\subsection{Incremental Library Track}
+\paragraph{Cryptominisat-5}
+
+\subsection{Parallel Track}
+
+\paragraph{P-MCOMSPS-STR} three awards
+
+\paragraph{Plingeling} three awards
+
+\paragraph{ManyGlucose} two awards
+
+\paragraph{Painless Maple} one award
+
+\subsection{Cloud Track}
+
+\paragraph{Mallob Mono}
+
+\paragraph{TopoSAT 2}
+
+\paragraph{Slime}
 

### 2020-11-24 paper/main.tex
abstract and small improvements

@@
 
+% Stack a variable number of arguments:
+\makeatletter
+\newcommand{\stack}[1]{%
+\begin{tabular}{@{}l@{}}#1\checknextarg}
+\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
+\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
+\makeatother
+
 \begin{document}
@@
 \begin{abstract}
-We describe the 2020 SAT Competition and provide a detailed analysis of its results.
+SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
+This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors can compete. 
+Another novelty is the application-specific sub-track of the main track, where solvers compete in solving benchmark instances from one specific domain only, and in this year that was the planning domain.
+We use new tools to select and distribute benchmark instances and their attributes. 
+In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
+It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
 \end{abstract}
@@
 
-\todo{Motivational paragraphs for SAT and the Competitions and what made this Competition Special}
+Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
+Despite its complexity, there is ongoing progress in solving methods and their implementations in SAT solvers. 
+The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
+Today, SAT solvers are used for verification of hard- and software, product configuration, cryptography, planning and scheduling, to name a few. 
+In mathematics, SAT solvers were recently even used to generate a record sized proof (200 TB) for an until then unsolved problem in Ramsey theory.
+
+SAT Competitions are organized regularly since 1992 in order to drive progress and to serve as a public assessment of the state-of-the-art in SAT solving. 
+For each SAT Competition, a set of new benchmark instances is compiled which reflects the various applications of interest to the community.
+
+In this competition, we initiated a new application-specific subtrack. 
+The idea is to provide a large amount of benchmark instances of a specific application, and to evaluate all solvers with respect to these instance in a special track. 
+In this competition, we used 200 instances of the planning domain to run a planning subtrack.
+
+Faster networks, distributed systems, and the increasing number of processors in modern computers show that the trend of increasing parallelism is about to continue.  
+In the new cloud track, for the first time, solver authors could compete in SAT technologies that allow hundreds of SAT solvers to cooperate in solving a SAT instance.
 
@@
 
-\todo{Present the structure of the paper}
+In Section~\ref{sec:tracks}, we start with a detailed description of the competition tracks and their purpose. 
+Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
+In Section~\ref{sec:results}, we present the competition results alongside a survey on the winning strategies of the award winning solvers. 
+A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.
 
-\section{Overview: Descriptions of Tracks, List of Participants}
+\section{Descriptions of Tracks}
+\label{sec:tracks}
 
 \subsection{Main Tracks}
-
-This year in the Main Track, we had a Planning Sub-Track. 
-The general idea is, that next to a balanced selection of benchmark instances in main track, to each year also offer one domain-specific sub-track.
-
-%\newcommand{\stack}[2]{\begin{tabular}{@{}c@{}}#1 \\#2\end{tabular}}
-
-% Stack a variable number of arguments:
-\makeatletter
-\newcommand{\stack}[1]{%
-\begin{tabular}{@{}l@{}}#1\checknextarg}
-\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
-\newcommand{\gobblenextarg}[1]{\\#1\@ifnextchar\bgroup{\gobblenextarg}{\end{tabular}}}
-\makeatother
 
@@
 \hline
-\bf Team & \bf Solver & \bf Variant & \bf Award \\
+\bf Team & \bf Base Solver & \bf Variant & \bf Award \\
 \hline
@@
 
-\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc & \\
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistCBT} & f2trc & \\
  & & f2trc-s & \thirdu\\
@@
 \multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{ExMapleLCMDistChronoBT} & padc\_dl & \\
+ & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
  &  & padc\_dl\_ovau\_lin & \\
@@
 \begin{table}[h]
+\smaller
 \arrayrulecolor{gray}
@@
 \begin{table}[h]
+\smaller
 \centering
@@
 
-\section{Selection and Maintenance of Benchmark Instances}
+\section{Description of Benchmark Instances}
+\label{sec:instances}
 
+For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
 GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
-Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}
+Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
+In GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
 
-For selection of benchmarks in this competition, we used a database which contains information about instance author, family and result for a collection of instances used in all SAT competitive events dating back to 2006.\footnote{\url{https://gbd.iti.kit.edu/getdatabase/meta.db}}
-Like this it was possible to query for instances with desired properties, which gives the instance selection process a new quality. 
-Using GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
+Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.
+Like this it is possible to query for instances with desired properties, e.g., instance author, family and result, which gives the instance selection process a new quality.
 
@@
 \section{Competition Results}
+\label{sec:results}
 \todo{for each track summarize the descriptions of the winning solvers}
@@
 \section{Analysis of Results}
+\label{sec:analysis}
 
@@
 
-\section{Conclusion}
+\section{Conclusion and Prospects}
+\label{sec:conclusion}
 

### 2020-11-24 paper/main.tex
solver description

@@
 
-\paragraph{Kissat} 
-three configurations submitted, four awards won, cdcl by several mixed strategies
+\subsubsection{Kissat}
 
-\paragraph{CryptoMiniSat-CCAnr}
-two variants: with and without lsids, with lsids slightly better, three awards won,  combination of cdcl and sls
+If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
+Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
+Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.
 
-\paragraph{Cadical Hack}
-three configurations, two awards
+Kissat is a reimplementation of Cadical~\cite{} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{}.
 
-\paragraph{MapleLCMDistCBT-DL Relaxed newTech}
-this variant won two awards
+In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{}. 
+For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{}.
 
-\paragraph{MapleLCMDistCBT f2trc-s}
-this variant won onw awards
+Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
+Regarding the duration of alternating restart modes, the Kissat authors considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
+
+Considering target phases~\cite{}, Kissat authors come up with an innovative use-case for autarkies to account for saved phases. 
+Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{}. 
+The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.
+
+\subsubsection{CryptoMiniSat-CCAnr}
+
+This solver won three awards, two third places in the Main Track and its Sat Subtrack, and one second place in the Planning Subtrack. 
+It was submitted in two variants, with and without LSIDS~\cite{}, which is a phase selection heuristic similar to VSIDS and if active it is used only when backtracking is chronological. 
+The version with LSIDS overall performed slightly better.
+
+By tight integration of CCAnr, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies SLS and CDCL in a unique way. 
+As in CaDiCal, they run local search for a short period of time in regular intervals and (just in case SLS finds no solution) change the polarities according to the best assignment found by the SLS solver~\cite{}.
+In addition to this technique known as ``rephasing'' from CaDiCal, they bump VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy.
+
+This version of CryptoMiniSat comes with an highly optimized implementation of Gauss-Jordan Elimination. 
+CryptoMiniSat includes BreakId, a sub-system that calculates symmetry breaking clauses, which it calls on every 5th inprocessing iteration.
+
+CryptoMiniSat changes decay factors of VSIDS and Maple heuristics dynamically after each inprocessing step to avoid sticking to a single best configuration.
+As in CaDiCal (and now Kissat) CryptoMiniSat is switching between Polarity Caching and Stable Phases. \todo{It is not clear if this is also the case when LSIDS is activated.}
+Inprocessing now also include ternary resolution.
+
+\subsubsection{Cadical Hacks: Trail and AllUip}
+
+This modified version of last years CaDiCal was submitted with the two new methods ``trail'' and ``alluip''. 
+It was submitted in three configurations, one with both methods activated and two other with each having only one of them active. 
+These hacks got two awards, second price in the Unsat Sub-Track of the Main Track and first price in the Planning Track.
+
+\todo{describe trail and alluip hacks}
+
+\subsubsection{MapleLCMDistCBT-DL Relaxed newTech}
+
+The variant Relaxed-newTech of the MapleLCMDistCBT-DL solver won two awards, second price in Main Track and first price in its Sat Sub-Track.
+
+\todo{}
+
+\subsubsection{MapleLCMDistCBT f2trc-s}
+
+The variant f2trc-s of the MapleLCMDistCBT solver was ranked third in the Unsat Sub-Track of the Main-Track.
+
+\todo{}
 
 \subsection{Incremental Library Track}
-\paragraph{Cryptominisat-5}
+\subsubsection{Cryptominisat-5}
+\todo{Merge with Main-Track winner description}
 
@@
 
-\paragraph{P-MCOMSPS-STR} three awards
+\subsubsection{P-MCOMSPS-STR} three awards
 
-\paragraph{Plingeling} three awards
+\subsubsection{Plingeling} three awards
 
-\paragraph{ManyGlucose} two awards
+\subsubsection{ManyGlucose} two awards
 
-\paragraph{Painless Maple} one award
+\subsubsection{Painless Maple} one award
 
@@
 
-\paragraph{Mallob Mono}
+\subsubsection{Mallob Mono}
 
-\paragraph{TopoSAT 2}
+\subsubsection{TopoSAT 2}
 
-\paragraph{Slime}
+\subsubsection{Slime}
 

### 2020-11-30 paper/main.tex
references

--- 2020-11-24 paper/main.tex
@@
  &  &  trail & \secondu\\
- &  &  alluip & \firstp\\
- & \multirow{-3}{*}{Cadical} &  alluip-trail & \firstp\\
+ &  &  alluip & \secondu\firstp\\
+ & \multirow{-3}{*}{Cadical} &  alluip-trail & \secondu\firstp\\
  \cline{2-4}
@@
 
-\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistCBT} & f2trc & \\
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistCBT} & f2trc & \thirdu\\
  & & f2trc-s & \thirdu\\
  \cline{2-4}
- & MapleLCMDistCBT-DL & f2trc & \\
+ & MapleLCMDistCBT-DL & f2trc & \thirdu\\
 \hline
@@
 
-\subsection{Main Track}
+\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
 
-\paragraph{Kissat} 
-three configurations submitted, four awards won, cdcl by several mixed strategies
+\subsubsection{Kissat}
 
-\paragraph{CryptoMiniSat-CCAnr}
-two variants: with and without lsids, with lsids slightly better, three awards won,  combination of cdcl and sls
+If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
+Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
+Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.
 
-\paragraph{Cadical Hack}
-three configurations, two awards
+Kissat is a reimplementation of Cadical~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.
 
-\paragraph{MapleLCMDistCBT-DL Relaxed newTech}
-this variant won two awards
+In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
+For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.
 
-\paragraph{MapleLCMDistCBT f2trc-s}
-this variant won onw awards
+Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
+Regarding the duration of alternating restart modes, the Kissat authors considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
 
-\subsection{Incremental Library Track}
-\paragraph{Cryptominisat-5}
+Considering target phases~\cite{Biere:SC2019}, Kissat authors come up with an innovative use-case for autarkies to account for saved phases. 
+Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{Kiesl:2019:Autarkies}. 
+The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.
+
+\subsubsection{CryptoMiniSat-CCAnr and CryptoMiniSat5}
+
+This solver won four awards, two third places in the Main Track and its Sat Subtrack, one second place in the Planning Subtrack, and the first place in the Incremental Library Track.
+
+To the Main track, the solver was submitted in two variants, with and without LSIDS~\cite{Shaw:2020:LSIDS}, which is a phase selection heuristic similar to VSIDS and if active it is used whenever backtracking is chronological~\cite{Nadel:2018:CBT}.
+On top of that, CryptoMiniSat is periodically switching between polarity saving and stable phases~\cite{Biere:SC2019}.
+
+By tight integration of CCAnr~\cite{Cai:2015:CCAnr}, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies SLS and CDCL in a unique way.
+They run local search for a short period of time in regular intervals and (just in case SLS finds no solution) change the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCal~\cite{Biere:SC2019}.
+Moreover, they bump VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.
+
+SLS is tightly integrated and thus is aware of changes occurring during inprocessing. 
+Inprocessing now also include ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
+All modifictions in CrytoMiniSat are fully integrated with resprect to incremental use-cases including the use of assumptions.
+
+CryptoMiniSat periodically changes decay factors of its branching heuristics, thus avoiding usage of a ``single best'' configuration.
+
+This version of CryptoMiniSat comes with an highly optimized implementation of Gauss-Jordan Elimination~\cite{Soos:2020:CNFXOR}. 
+CryptoMiniSat includes BreakId, a sub-system that calculates symmetry breaking clauses, which it calls on every 5th inprocessing iteration~\cite{Devriendt:2016:BreakId}.
+
+\subsubsection{Cadical Hacks: Trail and AllUip}
+
+This modified version of last years CaDiCal was submitted with the two new methods \emph{Trail Saving}~\cite{Hickey:2020:TrailSaving} and \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
+It was submitted in three configurations, one with both methods activated and two other with each having only one of them active. 
+The \emph{Stable AllUIP} variants seemed most successful, in most tracks they were the hightest ranked variants and won the first price in the Planning Sub-Track. 
+However, in the Unsat Sub-Track, the \emph{Trail Saving} variant performed best.
+
+With \emph{Trail Saving}, the solver caches backtracked slices of the assignment trail in order to reuse them when the same decisions are repeated. 
+The authors came up with sophisticated control mechanisms on when and how to reuse the cached trail slices and when to flush that cache.
+
+With \emph{Stable AllUip}, the solver continues resolution beyond the 1st Unit Implication Point (1-UIP) during clause-learning~\cite{Zhang:2001:ClauseLearning} as long that does not increase the LBD value of the learnt clause and then keeps that clause only if it has a smaller size than then 1-UIP clause.
+The authors came up with an additional heuristic to limit the amount of attempted AllUip learning attempts, if the fraction of unsuccessful alluip learning attempts gets to high, which they check and adapt on every restart~\cite{Bacchus:SC2020}.
+
+\subsubsection{Relaxed MapleLCMDistCBT-DL newTech}
+
+The variant \emph{newTech} of the \emph{Relaxed} fork of the MapleLCMDistCBT-DL was especially successful on satisfiable instances. 
+The solver won two awards, second price in Main Track and first price in its Sat Sub-Track.
+
+The \emph{Relaxed} fork of MapleLCMDistCBT-DL already participated in SAT Race 2019~\cite{Xindi:SC2019}.
+They integrated the local search solver CCAnr by extending the current partial assignment of the CDCL solver to a full assignment and for a fixed interval start the local search solver to try to find a nearby solution.
+
+In the new versions of the Relaxed family of Maple solvers~\cite{Xindi:SC2020}, they probabilistically switch between several modes of phase selection, and some of these modes reuse the maximal partially satisfying assignments as determined by the local search solver.
+
+For their successful \emph{newTech} variant~\cite{Xindi:SC2020} of their fork, they count the number of variable-occurrences in unsat clauses for each flip in the local search solver. 
+Then they reuse this information to priorize variables in a modified branching heuristic.
+
+\subsubsection{MapleLCMDistCBT F2TRC}
+
+The MapleLCMDistCBT F2TRC forks were ranked third in the Unsat Sub-Track of the Main-Track.
+
+The F2TRC forks aim at introducing determinism in winning solvers of previous competition, e.g., by replacing time-based intervals for LRB-VSIDS switches by a heuristic based on the conflict-count~\cite{Kochemazov:SC2020}.
+
+Another modification aims at improving three-tier clause management based on the three tiers core, tier2 and local as it was introduced by Chanseok Oh~\cite{Oh:2015:satunsat}.
+In order to limit growth of the core-tier, they introduce a limit on the number of core clauses, and whenever that is reached some of the low-ranked inactive core clauses are moved from core to tier2 and the limit is increased.
+In order to prevent tier2 from starving, they replaced the conflict limit for tier2 reduction by a size limit, then only half of the most recently inactive clauses is moved to local tier~\cite{Kochemazov:SC2020}.
 

### 2020-12-03 paper/main.tex
slight reorganization of paper

@@
 \usepackage{lscape}
+
+\definecolor{gold}{HTML}{FFF3D6}
+\definecolor{silver}{HTML}{F3F5F7}
+\definecolor{cupper}{HTML}{EAD9D7}
+\fboxsep0pt
+\newcommand{\firsto}{\colorbox{gold}{$m^1$}}
+\newcommand{\firsts}{\colorbox{gold}{$s^1$}}
+\newcommand{\firstu}{\colorbox{gold}{$u^1$}}
+\newcommand{\firstp}{\colorbox{gold}{$p^1$}}
+\newcommand{\secondo}{\colorbox{silver}{$m^2$}}
+\newcommand{\seconds}{\colorbox{silver}{$s^2$}}
+\newcommand{\secondu}{\colorbox{silver}{$u^2$}}
+\newcommand{\secondp}{\colorbox{silver}{$p^2$}}
+\newcommand{\thirdo}{\colorbox{cupper}{$m^3$}}
+\newcommand{\thirds}{\colorbox{cupper}{$s^3$}}
+\newcommand{\thirdu}{\colorbox{cupper}{$u^3$}}
+\newcommand{\thirdp}{\colorbox{cupper}{$p^3$}}
 
@@
 
-\definecolor{gold}{HTML}{FFF3D6}
-\definecolor{silver}{HTML}{F3F5F7}
-\definecolor{cupper}{HTML}{EAD9D7}
-\fboxsep0pt
-\newcommand{\firsto}{\colorbox{gold}{$m^1$}}
-\newcommand{\firsts}{\colorbox{gold}{$s^1$}}
-\newcommand{\firstu}{\colorbox{gold}{$u^1$}}
-\newcommand{\firstp}{\colorbox{gold}{$p^1$}}
-\newcommand{\secondo}{\colorbox{silver}{$m^2$}}
-\newcommand{\seconds}{\colorbox{silver}{$s^2$}}
-\newcommand{\secondu}{\colorbox{silver}{$u^2$}}
-\newcommand{\secondp}{\colorbox{silver}{$p^2$}}
-\newcommand{\thirdo}{\colorbox{cupper}{$m^3$}}
-\newcommand{\thirds}{\colorbox{cupper}{$s^3$}}
-\newcommand{\thirdu}{\colorbox{cupper}{$u^3$}}
-\newcommand{\thirdp}{\colorbox{cupper}{$p^3$}}
+\subsection{Incremental Library Track}
 
-\begin{table}[h!]
+\subsection{Parallel Track}
+
+\subsection{Cloud Track}
+
+\section{Description of Benchmark Instances}
+\label{sec:instances}
+
+For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
+GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
+Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
+In GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
+
+Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.
+Like this it is possible to query for instances with desired properties, e.g., instance author, family and result, which gives the instance selection process a new quality.
+
+\subsection{Selection of Instances}
+
+The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition.
+At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.
+
+In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families.
+By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.
+
+In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
+Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
+If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
+Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
+
+\begin{algorithm}[t]
+\DontPrintSemicolon
+
+\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
+\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
+\KwResult{$S$ : Set of Selected Instances}
+\SetKwFunction{rand}{$\mathsf{random.choice}$}
+\BlankLine
+$S \leftarrow \emptyset$\;
+
+\For {$a \in A$} {
+	$I_a^+ \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$, $k=7$}\;	
+	$I_a^- \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$, $k=7$}\;	
+	\If {$|I_a^+|+|I_a^-| < 14$}{
+		$l \leftarrow 14 - (|I_a^+|+|I_a^-|)$\;
+		$I_a^? \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$, $k=l$}\;
+	}
+	$S \leftarrow S \cup I_a^+ \cup I_a^- \cup I_a^?$\;	
+}
+\Return $S$\;
+
+\caption{Benchmark Instance Selection}
+\label{algo:select}
+\end{algorithm}
+
+To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
+We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
+Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
+
+\subsection{Planning Instances}
+Classical planning is the problem of finding a sequence of actions -- a plan --
+that transforms the world from some initial state to a goal state. In 1992 Kautz
+\cite{Kautz1992} proposed to encode planning as satisfiability. In their
+encoding the problem of finding a plan of length $i$ (\textit{i.e.,} the
+\emph{makespan}) is translated into a Boolean formula $F_i$ that is satisfiable
+exactly if a plan of length $i$ \emph{or less} exists. In later encodings
+multiple actions can be executed \emph{in parallel} allowing longer plans to be
+found by solving smaller formulas \cite{Rintanen2006, Rintanen2007, Balyo2013}.
+
+Finding the minimal makespan $i$ for which $F_i$ is satisfiable is important for
+SAT-based planning in general and the generation of this benchmark set in
+particular. The minimal makespan depends on the planning task and the used
+encoding. The hardest formulas that a SAT-based planner has to solve are usually
+the last unsatisfiable $F_i$ before the next higher makespan becomes satisfiable
+\cite{Rintanen2006}. Therefore we preferably pick the last unsatisfiable
+makespan for each planning task to generate unsatisfiable instances. For
+planning tasks where this makespan cannot be determined with available
+computational resources, we use a \emph{sequential} encoding, where the minimal
+makespan equals the length of the shortest valid plan. Together with known
+bounds\footnote{Bounds on plan length are available for some planning tasks from
+  the \emph{optimal track} that have \emph{unit cost} actions.} on the optimal
+plan length we can generate SAT formulas with predetermined satisfiability for
+hard planning problems.
+
+The encodings are generated by the two SAT-based planners \emph{Madagascar}
+\cite{Madagascar14} and \emph{Pasar} \cite{Pasar19}. We use Madagascar both in
+its default configuration to generate a parallel encoding based on
+$\exists$-step plans and to generate the sequential encoding where needed. Pasar
+uses the \emph{grounding routine} deployed by the well known planner \emph{Fast
+  Downward} \cite{FastDownward06} to translate planning tasks into a different
+formalism and then encodes it to SAT using a parallel encoding.
+
+The classical planning benchmarks are selected from the \emph{satisficing} and
+\emph{optimal} tracks of the \emph{International Planning Competitions} 2014
+\footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
+and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.
+
+In addition to the classical planning problems, we also include SAT formulas
+generated by \emph{Tree-REX} \cite{TreeRex19}; a planner for \emph{Hierarchical
+  Task-networks}. In HTN planning the planner is provided with additional domain
+knowledge besides the problem description. The HTN benchmarks are provided by
+the author of \emph{Tree-REX}.
+
+Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
+by each encoding.
+
+\begin{table}[h]
+  \caption{Number of benchmarks generated by each encoding.}
+  \centering
+  \begin{tabular}{@{}|l@{\hspace{3pt}}|l|r|r|@{}}
+    % &Encoding& SAT & UNSAT\\
+    \hline
+    \multicolumn{2}{|@{}l|}{Encoding} & SAT & UNSAT\\
+    % \midrule
+    \hline
+    \textbf{H}  & Tree-REX & 15 & 11\\
+    \textbf{P}  & PASAR & 14 & 14\\
+    \textbf{ME} & Madagascar $\exists$-step & 5 & 10\\
+    \textbf{MS} & Madagascar sequential & 66 & 65\\
+    % \midrule
+    \hline
+    && 100 & 100\\
+    % \bottomrule
+    \hline
+  \end{tabular}
+  \label{tab:planningBenchmarkDist}
+\end{table}
+
+The benchmarks of the planning track adhere to the naming convention below.
+For
+% more details and
+a complete list of the encoded planning tasks we refer to the
+generation script {\color{red}BROKEN LINK}.
+
+${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
+  \texttt{pathToInstance} \rangle\_\langle \texttt{makespan}
+  \rangle\text{.cnf}}$
+
+\subsection{Incremental Library Applications and Instances}
+
+\todo{}
+
+\section{Competition Results}
+\label{sec:results}
+
+\todo{Winners and Runtime Plots for all the tracks}
+
+\todo{Similarity of Solvers: Rank Correlation}
+
+\section{Analysis of Results}
+\label{sec:analysis}
+
+\todo{for each track summarize the descriptions of the winning solvers}
+
+\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
+
+\begin{table}[ht!]
 \smaller
@@
 
-\subsection{Incremental Library Track}
+\subsubsection{Kissat}
 
-\begin{table}[h]
+If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
+Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
+Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.
+
+Kissat is a reimplementation of Cadical~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.
+
+In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
+For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.
+
+Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
+Regarding the duration of alternating restart modes, the Kissat authors considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
+
+Considering target phases~\cite{Biere:SC2019}, Kissat authors come up with an innovative use-case for autarkies to account for saved phases. 
+Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{Kiesl:2019:Autarkies}. 
+The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.
+
+\begin{table}[ht]
 \smaller
@@
 \end{table}
-
-\subsection{Parallel Track}
-
-\begin{table}[h]
-\smaller
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-\bf Team & \bf Solver & \bf Awards\\
-\hline
-\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
- & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
- & P-MCOMSPS-STR-64 & \firsto \\
-\hline
-\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
- & Plingeling & \secondo \thirds \firstu \\
- & Treengeling & \\
-\hline
-\multirow{2}{*}{Nabeshima, Inoue}
- & ManyGlucose-32 & \thirdo \thirdu \\
- & ManyGlucose-64 & \thirdu \\
-\hline
-\multirow{2}{*}{Tchinda, Djamegni}
- & painlessmaplevone & \seconds \\
- & painlessmaplevtwo & \seconds \\
-\hline
-Li, Wu, Xu, Chen & syrupscavel & \\
-\hline
-Chen & abcdsatptwenty & \\
-\hline
-\end{tabular}
-\caption{Teams and Solvers participating in the parallel track.}
-\end{table}
-
-\subsection{Cloud Track}
-
-\begin{table}[h]
-\smaller
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-\bf Team & \bf Solver & \bf Rank\\
-\hline
-Schreiber & mallob-mono & 1\\
-\hline
-\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
-\hline
-Riveros & Slime & 3\\
-\hline
-\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
-& Paracooba-March & -\\
-\hline
-Hartung & CTSat & -\\
-\hline
-\end{tabular}
-\caption{Teams and Solvers participating in the cloud track.}
-\end{table}
-
-\section{Description of Benchmark Instances}
-\label{sec:instances}
-
-For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
-GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
-Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
-In GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
-
-Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.
-Like this it is possible to query for instances with desired properties, e.g., instance author, family and result, which gives the instance selection process a new quality.
-
-\subsection{Selection of Instances}
-
-The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition.
-At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.
-
-In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families.
-By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.
-
-In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
-Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
-If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
-Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
-
-\begin{algorithm}[t]
-\DontPrintSemicolon
-
-\KwData{$I$ : Set of Instances, $A$ : Set of Authors}
-\KwData{Functions $\alpha : I \rightarrow A$ and $\sigma : I \rightarrow \{\mathsf{sat}, \mathsf{unsat}, \mathsf{unknown}\}$}
-\KwResult{$S$ : Set of Selected Instances}
-\SetKwFunction{rand}{$\mathsf{random.choice}$}
-\BlankLine
-$S \leftarrow \emptyset$\;
-
-\For {$a \in A$} {
-	$I_a^+ \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$, $k=7$}\;	
-	$I_a^- \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$, $k=7$}\;	
-	\If {$|I_a^+|+|I_a^-| < 14$}{
-		$l \leftarrow 14 - (|I_a^+|+|I_a^-|)$\;
-		$I_a^? \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$, $k=l$}\;
-	}
-	$S \leftarrow S \cup I_a^+ \cup I_a^- \cup I_a^?$\;	
-}
-\Return $S$\;
-
-\caption{Benchmark Instance Selection}
-\label{algo:select}
-\end{algorithm}
-
-To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
-We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
-Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
-
-\subsection{Planning Instances}
-
-\subsection{Incremental Library Applications and Instances}
-
-\section{Competition Results}
-\label{sec:results}
-\todo{for each track summarize the descriptions of the winning solvers}
-
-\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
-
-\subsubsection{Kissat}
-
-If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
-Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
-Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.
-
-Kissat is a reimplementation of Cadical~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.
-
-In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.
-
-Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
-Regarding the duration of alternating restart modes, the Kissat authors considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
-
-Considering target phases~\cite{Biere:SC2019}, Kissat authors come up with an innovative use-case for autarkies to account for saved phases. 
-Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{Kiesl:2019:Autarkies}. 
-The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.
 
@@
 
+\begin{table}[ht]
+\smaller
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\bf Team & \bf Solver & \bf Awards\\
+\hline
+\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
+ & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
+ & P-MCOMSPS-STR-64 & \firsto \\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
+ & Plingeling & \secondo \thirds \firstu \\
+ & Treengeling & \\
+\hline
+\multirow{2}{*}{Nabeshima, Inoue}
+ & ManyGlucose-32 & \thirdo \thirdu \\
+ & ManyGlucose-64 & \thirdu \\
+\hline
+\multirow{2}{*}{Tchinda, Djamegni}
+ & painlessmaplevone & \seconds \\
+ & painlessmaplevtwo & \seconds \\
+\hline
+Li, Wu, Xu, Chen & syrupscavel & \\
+\hline
+Chen & abcdsatptwenty & \\
+\hline
+\end{tabular}
+\caption{Teams and Solvers participating in the parallel track.}
+\end{table}
+
 \subsubsection{P-MCOMSPS-STR} three awards
@@
 
+\begin{table}[ht]
+\smaller
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\bf Team & \bf Solver & \bf Rank\\
+\hline
+Schreiber & mallob-mono & 1\\
+\hline
+\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
+\hline
+Riveros & Slime & 3\\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
+& Paracooba-March & -\\
+\hline
+Hartung & CTSat & -\\
+\hline
+\end{tabular}
+\caption{Teams and Solvers participating in the cloud track.}
+\end{table}
+
 \subsubsection{Mallob Mono}
@@
 
-\section{Analysis of Results}
-\label{sec:analysis}
-
-\subsection{Essential Improvements in Winning Solvers}
-
-\todo{Common and Specific Winning Strategies}
-
-\subsection{Similarity of Solvers}
-
-\todo{Rank Correlation}
-
 \section{Conclusion and Prospects}
 \label{sec:conclusion}
+
+\todo{Summarize Winning Strategies}
+
+\todo{Ideas for Future Competitions}
 

### 2020-12-10 paper/main.tex
actualy Sect 2 is a more general overview

@@
 
+\address[ctu] {
+Czech Technical University in Prague, Czech Republic\\
+\url{martin.suda@cvut.cz}\\[1em]
+}
+
 \newcommand{\todo}[1]{{\color{purple}Todo: #1}}
@@
 SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
-This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors can compete. 
-Another novelty is the application-specific sub-track of the main track, where solvers compete in solving benchmark instances from one specific domain only, and in this year that was the planning domain.
-We use new tools to select and distribute benchmark instances and their attributes. 
+This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors could compete. 
+Another novelty was the application-specific sub-track of the main track, 
+where solvers competed in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
+We used new tools to select and distribute benchmark instances and their attributes. 
 In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
@@
 
-In Section~\ref{sec:tracks}, we start with a detailed description of the competition tracks and their purpose. 
+In Section~\ref{sec:overview}, we start with an overview of the competition,
+including detailed description of the competition tracks and their purpose,
+the general rules and the used computing environment.
 Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
@@
 
-\section{Descriptions of Tracks}
-\label{sec:tracks}
+\section{Overview of the competition}
+\label{sec:overview}
 
-\subsection{Main Tracks}
+\subsection{Competition tracks}
 
-\subsection{Incremental Library Track}
+\subsubsection{Main Tracks}
 
-\subsection{Parallel Track}
+\subsubsection{Incremental Library Track}
 
-\subsection{Cloud Track}
+\subsubsection{Parallel Track}
+
+\subsubsection{Cloud Track}
+
+\subsection{Rules, ranking, etc.}
+
+\subsection{Computing environments}
 
@@
 
-In Kissat forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-For irredundant clauses forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.
+In Kissat, forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
+For irredundant clauses, forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.
 
@@
 
-To the Main track, the solver was submitted in two variants, with and without LSIDS~\cite{Shaw:2020:LSIDS}, which is a phase selection heuristic similar to VSIDS and if active it is used whenever backtracking is chronological~\cite{Nadel:2018:CBT}.
+To the Main track, the solver was submitted in two variants, with and without LSIDS~\cite{Shaw:2020:LSIDS},
+which is a phase selection heuristic similar to VSIDS and, if active, it is used whenever backtracking is chronological~\cite{Nadel:2018:CBT}.
 On top of that, CryptoMiniSat is periodically switching between polarity saving and stable phases~\cite{Biere:SC2019}.
 
-By tight integration of CCAnr~\cite{Cai:2015:CCAnr}, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies SLS and CDCL in a unique way.
-They run local search for a short period of time in regular intervals and (just in case SLS finds no solution) change the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCal~\cite{Biere:SC2019}.
-Moreover, they bump VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.
+By tight integration of CCAnr~\cite{Cai:2015:CCAnr}, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies, SLS and CDCL, in a unique way.
+The solver runs local search for a short period of time in regular intervals and (just in case SLS finds no solution)
+changes the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCal~\cite{Biere:SC2019}.
+Moreover, it bumps VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.
 
 SLS is tightly integrated and thus is aware of changes occurring during inprocessing. 
-Inprocessing now also include ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
+Inprocessing now also includes ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
 All modifictions in CrytoMiniSat are fully integrated with resprect to incremental use-cases including the use of assumptions.
@@
 
-\subsubsection{P-MCOMSPS-STR} three awards
+\subsubsection{P-MCOMSPS-STR}
+
+P-MCOMSPS-STR is built from the Painless framework~\cite{Frioux:2017:Painless} for solver parallization and uses the MapleCOMSPS solver~\cite{Liang:2017:Maplecomsps} as a building block. 
+The authors submitted a 32 and 64 core version and won 3 awards, first place in the overall ranking, first place in the SAT ranking and second in the UNSAT ranking. 
+The 64 core version performed slightly worse than the 32 core version in the overall ranking, and that gap is bigger for the SAT-only ranking and worst for the UNSAT-only ranking, such that in the separate rankings only the 32 core version is responsible for winning the prices.
+
+The painless framework uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations within the framework boil down to implementing parallelization and clause sharing strategies.
+
+In the submitted version of P-MCOMSPS-STR, diversification is done via diverse fixed configurations of branching strategies (LRB and VSIDS) and sparse random intialization of variable polarities like in~\cite{Balyo:2015:Hordesat}.
+One instance of their ``sequential engines'' performs concurrent clause strengtheing as described in~\cite{Wieringa:2013:CCS} and another single instance is configured to perform Gaussian eliminiation during preprocessing.
+
+For sharing they use an all-to-all strategy with a regular exchange of a fixed size buffer and a dynamic clause lbd limit.
 
@@
 
+\section*{Acknowledgements}
+Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
+the Czech Science Foundataion project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
+
 \bibliographystyle{elsarticle-num}

### 2020-12-10 paper/main.tex
winning strategies, parallel track

@@
 \usepackage{lscape} 
+\usepackage[binary-units=true]{siunitx}
 
@@
 
+TODO: maybe mention \url{https://satcompetition.github.io/2020/}
+
+TODO: Maybe mention proceedings \cite{SC2020}
+
 \section{Overview of the competition}
@@
 
+DRAT checking; cake\_lpr\_array
+
 \subsection{Computing environments}
+
+\label{sec:computing}
+The Main Track with its subtracks was run on the StarExec cluster \cite{starexec},
+whose nodes are equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
+and \SI{128}{\giga\byte} of memory.
+The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
+The solvers were allowed to use up to the full \SI{128}{\giga\byte} of RAM.\footnote{
+Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
+was by mistake advertised on the competition web page prior to solver submission.
+This could result in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
+in the competition.}
+
+TODO: Incremental / Parallel / Cloud ?
 
@@
 
-\todo{for each track summarize the descriptions of the winning solvers}
+In the following we provide a summary of the new strategies implemented in the award winning solvers in this competition.
 
 \subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
+
+In the main track, a total of $18$ teams submitted their solvers to the competition.  
+Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
+$11$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or Cadical~\cite{}.
+
+In the incremental track, four teams submitted their solvers. 
+Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers.
 
@@
 Awards were given in Main (m), SAT (s), UNSAT (u), and Planning (p) sub-tracks.}
+\label{tab:solvers-main}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[ht]
+\smaller
+\arrayrulecolor{gray}
+\centering
+\begin{tabular}{|l|l|c|}
+\hline
+\bf Team & \bf Solver & \bf Score\\
+\hline
+\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
+\hline
+\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
+\hline
+Chen & abcdsat-i20 & 1 \\
+\hline
+Manthey & Riss-7.1.2 & 1 \\
+\hline
+\end{tabular}
+\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
+\label{tab:solvers-incremental}
 \end{table}
@@
 The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.
-
-\begin{table}[ht]
-\smaller
-\arrayrulecolor{gray}
-\centering
-\begin{tabular}{|l|l|c|}
-\hline
-\bf Team & \bf Solver & \bf Score\\
-\hline
-\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
-\hline
-\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
-\hline
-Chen & abcdsat-i20 & 1 \\
-\hline
-Manthey & Riss-7.1.2 & 1 \\
-\hline
-\end{tabular}
-\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
-\end{table}
 
@@
 
-\subsubsection{Plingeling} three awards
+\subsubsection{Plingeling}
 
-\subsubsection{ManyGlucose} two awards
+Plingeling got three awards, first place in the Unsat Category, third place in Sat and second place in the overall evaluation. 
+Plingeling is an extension of the well-known SAT solver Lingeling~\cite{} and did not change since 2016. 
+Via a global master queue, Plingeling shares unit clauses, equivalences and short clauses with clauses with at most 40 literals and glucose LBD level of at most 8 and random seeds, e.g., for diversification via default polarities.~\cite{}
 
-\subsubsection{Painless Maple} one award
+\subsubsection{ManyGlucose}
+
+The authors of ManyGlucose received two awards in this competition. 
+ManyGlucose was submitted in 32-core and 64-core variants~\cite{}.
+The 32-core variant won third prices in the overall evaluation and in the unsat sub-track. 
+ManyGlucose is a fork of GlucoseSyrup~\cite{} and uses strategies similar to those known from ManySAT~\cite{} in order to achive deterministic solver runs.
+
+\subsubsection{Painless Maple}
+
+The authors Painless Maple received one award for second best performance in the Sat sub-track of the parallel track. 
+However, the solver was last in the Unsat sub-track.
+
+The authors implemented a couple of modifications (\todo{name them}) on top of the MapleLCMDistChronoBT~\cite{} solver, which they also submitted in various configurations to the main track. 
+The two submissions in the parallel track use painless as a parallelization framework.
+
+Their sharing strategy includes splitting their workers into two categories, where the solvers in the first category only export clauses and only solvers in the second category import and export clauses.
+
+They submitted two variants with different diversification strategies. 
+In their first variant they use different configurations of configurations of the newly implemented strategies. 
+The second variant uses a more classic diverisification strategy by randomizing polarities and variable scores.
 

### 2020-12-15 paper/img/maple.tex
indicated all maple-forks; prepared icons

\documentclass{article}

\usepackage{tkz-graph}

\begin{document}

\begin{tikzpicture}
\draw[scale=1, domain=0:180, variable=\t, samples=500, fill=red]
plot ({(1 + (cos(6*\t))^2 + (1/5)*(cos(6*\t)*cos(24*\t))^10 + ( (1/4)*(cos(30*\t))^2 + (1/9)*(cos(30*\t))^12) *  (1-(sin(6*\t))^10)) * (sin(2*\t)) * (1-(cos(\t))^4) * (1 - (cos(\t))^10 * (cos(3*\t))^2) + (1/70)*(cos(\t))^9},
{(-21/20)*cos(2*\t)*(1 - (cos(\t))^4 + (1/2)*(cos(\t)*cos(3*\t))^10) * (1 + (cos(6*\t))^2 + (1/5)*(cos(6*\t)*cos(18*\t))^10 + ( (1/4)*(cos(30*\t))^4 + (1/10)*(cos(30*\t))^12 ) * ( 1 - ((cos(\t))^10) * (cos(3*\t))^2 ) * ( 1 - (sin(6*\t))^10 )) });
\end{tikzpicture}

\end{document}

### 2020-12-15 paper/main.tex
indicated all maple-forks; prepared icons

@@
 
-TODO: maybe mention \url{https://satcompetition.github.io/2020/}
+\todo{maybe mention \url{https://satcompetition.github.io/2020/}}
 
-TODO: Maybe mention proceedings \cite{SC2020}
+\todo{Maybe mention proceedings \cite{SC2020}}
 
@@
 
+SAT Competition 2020 consisted of four tracks, 
+the Main track, Incremental Library track, Parallel track,
+and the Cloud Track for massively parallel SAT solvers using up to 1024 cores.
+
 \subsubsection{Main Tracks}
+
+\todo{Did we have a glucose hack track in the end?
+(Mentioned on the web, not in the result slides.)}
 
@@
 
-\subsection{Rules, ranking, etc.}
+\subsection{Mandatory participation requirements}
 
-DRAT checking; cake\_lpr\_array
+\todo{Should we have a discussion (maybe later sections)
+about the future of the portfolio solver rule
+concerning the point raised by Mate Soos (in emails)?}
+
+\subsection{Certificates}
+
+In all tracks it was required to output a model to certify recognising a satisfiable instance.
+On the other hand, certificates for unsatisfiable instances (proofs) were required only 
+in the Main Track (besides the No Limits subtrack).
+
+Proofs of unsatisfiability were to be emitted in the DRAT format~\cite{DRATtrim},
+either in its textual version, which is very similar to the DIMACS input format,
+or on a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
+
+The proofs were validated in a two step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
+was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
+Afterwards, an independent, formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}, 
+was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
+We only considered solved those unsatisfiable formulas that could be validated by {\tt DRAT-trim}.
+There were several cases where {\tt cake\_lpr} ran out of resources before being able to 
+confirm after {\tt DRAT-trim}. However, there was no case where {\tt DRAT-trim} would accept
+a proof and {\tt cake\_lpr} would later disagree with the verdict.
 
@@
 
-TODO: Incremental / Parallel / Cloud ?
+The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
+(4-Core) processors and \SI{24}{\giga\byte} of RAM.
+
+\todo{Parallel / Cloud}
 
@@
 
+\todo{New Codebases}
+
 \todo{Winners and Runtime Plots for all the tracks}
@@
 \multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
+ & \multirow{4}{*}{ExMapleLCMDistCBT} & padc\_dl & \\
  &  & padc\_dl\_ovau\_lin & \\
@@
 
-Shaw, Meel & DurianSat & -- & \\
+Shaw, Meel & MapleLCMDistCBT-DL-v3 & DurianSat & \\
 \hline
@@
 
-Riveros & SLIME & -- & \\
+Riveros & MapleLCMDistCBT & SLIME & \\
 \hline
@@
 
-Kaiser, Hartung & PauSat & -- & \\
+Kaiser, Hartung & MapleLCMDist & PauSat & \\
 \hline
@@
 
-\subsection{Parallel Track}
+\subsection{Parallel SAT Solving: Winners of the Parallel Track}
 
@@
 ManyGlucose was submitted in 32-core and 64-core variants~\cite{}.
-The 32-core variant won third prices in the overall evaluation and in the unsat sub-track. 
+The 32-core variant won two third prices, one in the overall evaluation and one in the unsat sub-track. 
 ManyGlucose is a fork of GlucoseSyrup~\cite{} and uses strategies similar to those known from ManySAT~\cite{} in order to achive deterministic solver runs.
@@
 
-\subsection{Cloud Track}
+\subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}
 
@@
 
+The massively parallel SAT solver Mallob is based on HordeSAT~\cite{}. 
+Mallob is a framework for massivley parallel and distributed \emph{malleable job scheduling}, and thus can perform dynamic load balancing on many jobs of varying priorty.
+However, in the submitted version Mallob Mono, this functionality is disabled, as traditionally in SAT Competition all resources are busy solving one single instance only.
+
+Mallob uses the the 2018 version \emph{bcj} of Lingeling~\cite{} and employs diversification via randomized sparse initialization of branching scores just like it is done in Plingeling~\cite{}. 
+Every 14th process, however, runs the local search solver YalSAT~\cite{}.
+
+Clause exchange is handled considerably different from previous approach. 
+Workers are organized in a binary tree and clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
+Each node performs a three way merge of the local and the two incoming buffers. 
+Only the final aggragate at the root of that binary tree is broadcast to all the solvers.
+
+To limit sharing, there is a global size limit of $5$ for all the shared clauses. 
+The buffer has a limited size as well, but that size depends on the position in the binary tree, with root having the largest buffer and leaves the smallest. 
+Clauses are sorted by there size during aggregation, such that smaller clauses are preferred over longer clauses. 
+Duplicates are filtered out using a bloom filter, which is cleared periodically. 
+There is a special filter for duplicate unit-clause which especially useful during startup.
+
 \subsubsection{TopoSAT 2}
 
+TopoSAT~2 is a massively parallel SAT solver using Glucose~3 with lockfree clause-exchange as in ManySAT~\cite{} on each node, and using MPI to share clauses between nodes.
+
+In Toposat~2, diversification is done via different strategies used for branching, restarting and clause forgetting. 
+Clauses are strengthened before they are exported. 
+Locally, clause import is delayed until the local trail-size is low in a monitored period.
+
 \subsubsection{Slime}
+
+Slime is build on top of MapleLCMDistChronoBT and was first submitted to SAT Race 2019 suggesting the new phase selection heuristic~\cite{}. 
+The 2020 version apparently adds some kind of periodic randomization in geometrically increasing intervals~\cite{}. 
+Even thought the sequential solver was unsuccessful in the Main Track, its MPI-based cloud version, won the third price in this competitions cloud track.
 

### 2020-12-16 paper/main.tex
more on the selected benchmarks

@@
 
+Table~\ref{tab:families} displays the numbers of submitted, interesting and finally selected instances grouped by problem family.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{rrr||l}
+submitted & interesting & selected & family\\
+\hline\hline
+6 & 2 & 2 & 01-integer-programming\\
+187 & 139 & 14 & antibandwidth\\
+40 & 20 & 13 & baseball-lineup\\
+393 & 333 & 14 & bitvector\\
+20 & 15 & 12 & cellular-automata\\
+38 & 18 & 7 & cnf-miter\\
+14 & 14 & 14 & coloring\\
+20 & 20 & 14 & core-based-generator\\
+18 & 13 & 13 & cover\\
+106 & 93 & 34 & cryptography\\
+20 & 19 & 7 & discrete-logarithm\\
+58 & 57 & 7 & edge-matching\\
+8 & 5 & 5 & fermat\\
+40 & 3 & 0 & flood-it-puzzle\\
+20 & 19 & 13 & hgen\\
+56 & 48 & 14 & hypertree-decomposition\\
+20 & 16 & 14 & influence-maximization\\
+20 & 20 & 9 & lam-discrete-geometry\\
+20 & 20 & 8 & polynomial-multiplication\\
+4 & 2 & 2 & schur-coloring\\
+20 & 20 & 12 & station-repacking\\
+23 & 19 & 7 & stedman-triples\\
+5 & 2 & 2 & sum-subset\\
+20 & 20 & 14 & tensors\\
+12 & 7 & 7 & termination\\
+20 & 16 & 14 & timetable\\
+16 & 16 & 14 & tournament\\
+36 & 36 & 14 & vlsat\\
+\hline
+1260 & 1012 & 300 & $\Sigma$
+\end{tabular}
+\caption{Families and amounts of newly submitted instances}
+\label{tab:families}
+\end{table}
+
+\begin{table}[h]
+\centering
+\begin{tabular}{c||ccc|c}
+ & SAT & UNSAT & UNKNOWN & $\Sigma$\\
+\hline\hline
+new instances & 114 & 78 & 108 & 300 \\
+old instances & 21 & 57 & 22 & 100\\
+\hline
+$\Sigma$ & 135 & 135 & 130 & 400
+\end{tabular}
+\caption{Amount of old and new instances by result}
+\label{tab:final}
+\end{table}
+
 \subsection{Planning Instances}
@@
 
-\todo{}
+With the introduction of IPASIR (Re-entrant Incremental Solver API), the incremental library track took place for the first time in SAT~Race~2015~\cite{Balyo:2015:SATRace}, and then again in SAT~Competitions 2016 and 2017.
+In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.
+
+\paragraph{Backbone Detection}
+
+The application $\mathsf{genipabones}$ reads a formula from a given file and transforms it using the dual rail encoding, i.e., it replaces each $x$ by $p_x$ and each $\overline{x}$ by $n_x$ and adds clauses of the form ($\overline{p_x} \vee \overline{n_x}$).
+Incrementally, each variable is then checked if it is a backbone variable or not. 
+For this application, we selected $50$ of the smallest and easiest satisfiable problems of previous SAT competitions.
+
+\paragraph{Essential Variables Calculation}
+
+%Given a satisfiable formula $F$, a variable $x$ is essential for the satisfiability of $F$ if a truth value must be assigned to $x$ in each satisfying partial assignment of F. 
+The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula by testing each variable using the dual-rail encoded formula. 
+For this application, we used the same easy satisfiable problems as in the Backbone Detection application.
+
+\paragraph{Longest Simple Path Computation}
+
+The application $\mathsf{genipalsp}$ finds the longest simple path in a graph. 
+For this application, we selected $50$ instances of the smallest graphs provided by Balyo et al.~\cite{Balyo:2019:LSP}.
+
+\paragraph{MaxSAT}
+
+The application $\mathsf{genipamax}$ is a trivial partial MaxSAT solver based on adding activation literals to soft clauses and 
+subsequent incremental optimization using a cardinality constraint~\cite{Philipp:2015:PBLib} and assumptions. 
+For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.
+
+\paragraph{QBF}
+$\mathsf{Ijtihad}$ is a solver for Quantified Boolean Formulas (QBFs). 
+The solver tackles the a formula iteratively, using counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}.
+For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.
+
+\paragraph{Planning}
+$\mathsf{Pasar}$ is a planer which is based on the principles of counter-example guided abstraction refinement(CEGAR)~\cite{Froleyks:2019:Pasar}. 
+For this application, we selected $50$ sas planning instances.
 
@@
 
-\section{Analysis of Results}
+\section{History of Code and Winning Strategies}
 \label{sec:analysis}
 
-In the following we provide a summary of the new strategies implemented in the award winning solvers in this competition.
+In the following we provide an overview on the participating teams and solvers,  and summarize new strategies which are implemented in the award winning solvers of this competition.
+
+We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
+Our survey of the winning strategies in this competition starts with sequential (including incremental) SAT solving in Section~\ref{sec:part:seq}, then we continue with parallel SAT solving in Section~\ref{sec:part:par} and conclude with solvers in the cloud track in Section~\ref{sec:part:cloud}.
+
+\subsection{On the Shoulders of Giants: The Evolution of SAT Solvers}
+\label{sec:codebases}
+
+With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
+One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{}. 
+The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{}.  
+The authors of Glucose introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{}, which they recently summarized in~\cite{}.
+
+The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{}.
+
+Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh~\cite{}. 
+Maple first emerged as a series of forks submitted to SAT Competition 2016, introducing the two new branching heuristics Learning Rate based Branching (LRB) and Conflict History based Branching (CHB)~\cite{}.
+The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
+The award winning derivatives of MapleCOMSPS in SAT Competition 2017 include a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
+This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}.
+Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
+The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).
+
+CryptoMinisat by Mate Soos emerged as a fork of Minisat with an extension that brings special handling of xor clauses via gaussian elimination, which is especially effective when solving cryptographic instances~\cite{}.
+Today, CryptoMinisat is more of an independent code base than a Minisat fork coming with award winning individual implementations of recent SAT technology (see Section~\ref{}).
+
+The SAT solvers of Armin Biere arguably belong to the best and most well-known independent code-bases. 
+Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
+CaDiCal came up in SAT Competition 2017 and has been award winning since then. 
+The reimplementation of CaDiCal in the new SAT solver Kissat set a new standard in sequential SAT solving in this competition (see Section~\ref{}).
 
 \subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
+\label{sec:part:seq}
 
-In the main track, a total of $18$ teams submitted their solvers to the competition.  
+A total of $18$ teams submitted their solvers to the main track of the competition.  
 Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
-$11$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or Cadical~\cite{}.
+$14$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or Cadical~\cite{}.
 
 In the incremental track, four teams submitted their solvers. 
+All solvers in the incremental library track are created from independent code bases. 
 Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers.
@@
 \subsection{Parallel SAT Solving: Winners of the Parallel Track}
+\label{sec:part:par}
 
@@
 \subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}
+\label{sec:part:cloud}
 

### 2020-12-17 paper/main.tex
Main track

@@
 
-\section{Overview of the competition}
+\section{Overview of the Competition}
 \label{sec:overview}
 
-\subsection{Competition tracks}
+TODO: Fugenelement
 
-SAT Competition 2020 consisted of four tracks, 
+\subsection{Competition Tracks}
+
+SAT Competition 2020 consisted of four tracks:
 the Main track, Incremental Library track, Parallel track,
 and the Cloud Track for massively parallel SAT solvers using up to 1024 cores. 
+Furthermore, the Main track comprised of several sub-tracks.
 
-\subsubsection{Main Tracks}
+\subsubsection{Main Track}
 
-\todo{Did we have a glucose hack track in the end?
-(Mentioned on the web, not in the result slides.)}
+The focus of the traditional Main track is on sequential SAT solvers and their evaluation on structured, non-random benchmarks coming from various application areas.
+To participate in the main track, solvers needed to output certificates both for the satisfiable and the unsatisfiable answer.
+Moreover, the source code of the solver had to be made publicly available.
+
+Solvers not complying with either of the above criteria were only evaluated in a so-called No-Limits sub-track and were not eligible for the Main track awards.
+The No-Limits thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.\ Rules below).
+However, solvers in No-Limits still competed against all other solvers in the Main Track (hence, we consider it a sub-track).
+The No-Limits sub-track was only evaluated with respect to the benchmarks instances which were \emph{newly} submitted to SAT Competition 2020.
+
+Part of the Main track was the Planning sub-track, in which we evaluated the solvers on 200 benchmarks 
+which all came from the same application domain - automated planning. 
+Solver submitted to the Main track automatically participated in the Planning sub-track.
+It is envisioned, that also in the future there will be an application sub-track of the Main track, each time highlighting a different area where the SAT solving technology helps to advance the state of the art.
+
+Finally, the Main Track also had the so-called ``Glucose hack'' sub-track. 
+Since in the past several advances in SAT solving required only a small modification of an established solver
+to achieve a considerable contribution, this sub-track encouraged participation 
+of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
+was set to 1000 non-space character edit distance from the sources of Glucose provided by the organisers. 
+Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
+in the results section.
 
@@
 was by mistake advertised on the competition web page prior to solver submission.
-This could result in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
+This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
 in the competition.}

### 2020-12-17 paper/main.tex
refined ipasir benchmark section; finished sequential codebase overview

--- 2020-12-16 paper/main.tex
@@
 
-With the introduction of IPASIR (Re-entrant Incremental Solver API), the incremental library track took place for the first time in SAT~Race~2015~\cite{Balyo:2015:SATRace}, and then again in SAT~Competitions 2016 and 2017.
+Ihe incremental library track was first introduced in SAT~Race~2015 and then took place again in SAT~Competitions 2016 and 2017. 
+Numerous applications, e.g., SMT solvers or SAT-based planners, use SAT solvers incrementaly, i.e., formulas are repeatedly refined between solve-calls. 
+One important contribution of the founders of this track is the specification of the general incremental interface IPASIR (Re-entrant Incremental Solver API) for SAT applications~\cite{Balyo:2015:SATRace}.
 In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.
 
-\paragraph{Backbone Detection}
+\paragraph{Backbone Variables}
 
-The application $\mathsf{genipabones}$ reads a formula from a given file and transforms it using the dual rail encoding, i.e., it replaces each $x$ by $p_x$ and each $\overline{x}$ by $n_x$ and adds clauses of the form ($\overline{p_x} \vee \overline{n_x}$).
-Incrementally, each variable is then checked if it is a backbone variable or not. 
-For this application, we selected $50$ of the smallest and easiest satisfiable problems of previous SAT competitions.
+The application $\mathsf{genipabones}$ creates the dual rail encoding~\cite{Balyo:2015:SATRace} of a given formula and incrementally checks for each variable if it is a backbone variable or not~\cite{Janota:2015:Backbones}.
+For this application, we selected $50$ of the smallest and easiest satisfiable problems from previous SAT competitions.
 
-\paragraph{Essential Variables Calculation}
+\paragraph{Essential Variables}
 
-%Given a satisfiable formula $F$, a variable $x$ is essential for the satisfiability of $F$ if a truth value must be assigned to $x$ in each satisfying partial assignment of F. 
-The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula by testing each variable using the dual-rail encoded formula. 
-For this application, we used the same easy satisfiable problems as in the Backbone Detection application.
+The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula~\cite{Bryant:1987:Essentials} by incrementally testing each variable using the dual-rail encoded formula.
+For this application, we used the same $50$ easy satisfiable problems as in the backbone variable detection application.
 
-\paragraph{Longest Simple Path Computation}
+\paragraph{Longest Simple Paths}
 
@@
 
-\paragraph{MaxSAT}
+\paragraph{Maximum Satisfiability (MaxSAT)}
 
-The application $\mathsf{genipamax}$ is a trivial partial MaxSAT solver based on adding activation literals to soft clauses and 
-subsequent incremental optimization using a cardinality constraint~\cite{Philipp:2015:PBLib} and assumptions. 
+The application $\mathsf{genipamax}$ solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}.
+The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint.
 For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.
 
-\paragraph{QBF}
-$\mathsf{Ijtihad}$ is a solver for Quantified Boolean Formulas (QBFs). 
-The solver tackles the a formula iteratively, using counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}.
+\paragraph{Quantified Boolean Formulas (QBF)}
+The application $\mathsf{Ijtihad}$ is a QBF solver based on counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}.
 For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.
@@
 \paragraph{Planning}
-$\mathsf{Pasar}$ is a planer which is based on the principles of counter-example guided abstraction refinement(CEGAR)~\cite{Froleyks:2019:Pasar}. 
-For this application, we selected $50$ sas planning instances.
+The application $\mathsf{Pasar}$ is a planner which is based on the principles of counter-example guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}. 
+For this application, we selected $50$ SAS planning instances.
 
@@
 CaDiCal came up in SAT Competition 2017 and has been award winning since then. 
-The reimplementation of CaDiCal in the new SAT solver Kissat set a new standard in sequential SAT solving in this competition (see Section~\ref{}).
+Despite the fact that it seems very hard to lift the state-of-the-art with a completly new codebase, the new SAT solver Kissat by Armin Biere which was submitted for the first time this year set a new standard in sequential SAT solving in this competition (see Section~\ref{}).
+
+ParaFrost by Osama and Wijs is another new codebase introducing several interesting new concepts~\cite{}. 
+Its sequential variant was submitted for the first time in this competition.
 

### 2020-12-17 paper/main.tex
edited some tables

@@
 \subsection{Selection of Instances}
-
-The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition.
-At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.
-
-In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families.
-By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.
-
-In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
-Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
-If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
-Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
 
@@
 
-To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
-We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
-Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
-
-Table~\ref{tab:families} displays the numbers of submitted, interesting and finally selected instances grouped by problem family.
-
-\begin{table}[h]
+\begin{table}[t]
+\small
 \centering
-\begin{tabular}{rrr||l}
-submitted & interesting & selected & family\\
+\begin{tabular}{|l|l||rr|}
+\hline
+Family & Author & Submitted & Selected\\
 \hline\hline
-6 & 2 & 2 & 01-integer-programming\\
-187 & 139 & 14 & antibandwidth\\
-40 & 20 & 13 & baseball-lineup\\
-393 & 333 & 14 & bitvector\\
-20 & 15 & 12 & cellular-automata\\
-38 & 18 & 7 & cnf-miter\\
-14 & 14 & 14 & coloring\\
-20 & 20 & 14 & core-based-generator\\
-18 & 13 & 13 & cover\\
-106 & 93 & 34 & cryptography\\
-20 & 19 & 7 & discrete-logarithm\\
-58 & 57 & 7 & edge-matching\\
-8 & 5 & 5 & fermat\\
-40 & 3 & 0 & flood-it-puzzle\\
-20 & 19 & 13 & hgen\\
-56 & 48 & 14 & hypertree-decomposition\\
-20 & 16 & 14 & influence-maximization\\
-20 & 20 & 9 & lam-discrete-geometry\\
-20 & 20 & 8 & polynomial-multiplication\\
-4 & 2 & 2 & schur-coloring\\
-20 & 20 & 12 & station-repacking\\
-23 & 19 & 7 & stedman-triples\\
-5 & 2 & 2 & sum-subset\\
-20 & 20 & 14 & tensors\\
-12 & 7 & 7 & termination\\
-20 & 16 & 14 & timetable\\
-16 & 16 & 14 & tournament\\
-36 & 36 & 14 & vlsat\\
+0-1 Integer Programming & Riveros & 6 & 2 \\
+Anti-Bandwidth & Biere & 187 & 14 \\
+Baseball Lineup & Hickey & 40 & 13 \\
+Bit-Vector & Preiner & 393 & 14 \\
+Cellular Automata & Chowdhury & 20 & 12 \\
+CNF Miter & Manthey & 38 & 7 \\
+Coloring & Oostema & 14 & 14 \\
+Core-based Generator & Hartung & 20 & 14 \\
+Cover & Gacek & 18 & 13 \\
+Cryptography & Paxian, Shaw, Soos & 106 & 34 \\
+Discrete Logarithm & Jingchao & 20 & 7 \\
+Edge Matching & Holten & 58 & 7 \\
+Fermat & Riveros & 8 & 5 \\
+Flood-It Puzzle & Stiphout & 40 & 0 \\
+HGen & Guanfeng & 20 & 13 \\
+Hypertree Decomposition & Schidler & 56 & 14 \\
+Influence Maximization & Kochemazov & 20 & 14 \\
+Lam Discrete Geometry & Nejati & 20 & 9 \\
+Polynomial Multiplication & Maoluo & 20 & 8 \\
+Schur Coloring & Riveros & 4 & 2 \\
+Station Repacking & Newman & 20 & 12 \\
+Stedman Triples & Johnson & 23 & 7 \\
+Sum Subset & Riveros & 5 & 2 \\
+Tensors & Savicky & 20 & 14 \\
+Termination & Yolcu & 12 & 7 \\
+Timetable & Djamegni & 20 & 14 \\
+Tournament & Heule & 16 & 14 \\
+Vlsat & Bouvier & 36 & 14 \\
 \hline
-1260 & 1012 & 300 & $\Sigma$
+\multicolumn{2}{|r||}{$\Sigma$} & 1260 & 300 \\
+\hline
 \end{tabular}
@@
 
-\begin{table}[h]
+The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition.
+At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.
+
+In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families.
+By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances.
+
+In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
+Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
+If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
+Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
+
+To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
+We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
+Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
+
+Table~\ref{tab:families} displays the numbers of submitted and selected instances grouped by problem family and author.
+
+\begin{table}[t]
 \centering
-\begin{tabular}{c||ccc|c}
+\begin{tabular}{|r|ccc|c|}
+\hline
  & SAT & UNSAT & UNKNOWN & $\Sigma$\\
 \hline\hline
-new instances & 114 & 78 & 108 & 300 \\
-old instances & 21 & 57 & 22 & 100\\
+New Instances & 114 & 78 & 108 & 300 \\
+Old Instances & 21 & 57 & 22 & 100\\
 \hline
-$\Sigma$ & 135 & 135 & 130 & 400
+$\Sigma$ & 135 & 135 & 130 & 400\\
+\hline
 \end{tabular}
@@
 The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
-The award winning derivatives of MapleCOMSPS in SAT Competition 2017 include a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
+The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
 This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}.
@@
 \multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{ExMapleLCMDistCBT} & padc\_dl & \\
+ & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
  &  & padc\_dl\_ovau\_lin & \\

### 2020-12-17 paper/main.tex
CMU

@@
 
+\address[cmu] {
+Computer Science Department, Carnegie Mellon University\\
+{\tt marijn@cmu.edu}\\[1em]
+}
+
 \address[kit] {
 KIT Department of Informatics\\
-\url{markus.iser@kit.edu}\\[1em]
+{\tt markus.iser@kit.edu}\\[1em]
 }
@@
 Czech Technical University in Prague, Czech Republic\\
-\url{martin.suda@cvut.cz}\\[1em]
+{\tt martin.suda@cvut.cz}\\[1em]
 }

### 2020-12-17 paper/main.tex
small things

@@
 Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
-CaDiCal came up in SAT Competition 2017 and has been award winning since then. 
+CaDiCaL came up in SAT Competition 2017 and has been award winning since then. 
 Despite the fact that it seems very hard to lift the state-of-the-art with a completly new codebase, the new SAT solver Kissat by Armin Biere which was submitted for the first time this year set a new standard in sequential SAT solving in this competition (see Section~\ref{}).
@@
 Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
-$14$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or Cadical~\cite{}.
+$14$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or CaDiCaL~\cite{}.
 
@@
 \cline{2-4}
- &  Cadical-sc2020 &  -- & \\
+ &  CaDiCaL-sc2020 &  -- & \\
 \hline
@@
  &  &  alluip & \secondu\firstp\\
- & \multirow{-3}{*}{Cadical} &  alluip-trail & \secondu\firstp\\
+ & \multirow{-3}{*}{CaDiCaL} &  alluip-trail & \secondu\firstp\\
  \cline{2-4}
@@
 \hline
-\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
+\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & CaDiCaL-sc2020 & 1 \\
 \hline
@@
 
-Kissat is a reimplementation of Cadical~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.
+Kissat is a reimplementation of CaDiCaL~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.
 
 In Kissat, forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-For irredundant clauses, forward subsumption is still executed together with variable eliminiation during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurences~\cite{Biere:SC2020}.
+For irredundant clauses, forward subsumption is still executed together with variable elimination during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurrences~\cite{Biere:SC2020}.
 
 Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
-Regarding the duration of alternating restart modes, the Kissat authors considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
+Regarding the duration of alternating restart modes, Kissat's author considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
 
-Considering target phases~\cite{Biere:SC2019}, Kissat authors come up with an innovative use-case for autarkies to account for saved phases. 
+Considering target phases~\cite{Biere:SC2019}, Kissat's author come up with an innovative use-case for autarkies to account for saved phases. 
 Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{Kiesl:2019:Autarkies}. 
@@
 The solver runs local search for a short period of time in regular intervals and (just in case SLS finds no solution)
-changes the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCal~\cite{Biere:SC2019}.
+changes the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
 Moreover, it bumps VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.
@@
 Inprocessing now also includes ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
-All modifictions in CrytoMiniSat are fully integrated with resprect to incremental use-cases including the use of assumptions.
+All modifications in CryptoMiniSat are fully integrated with respect to incremental use-cases including the use of assumptions.
 
@@
 
-\subsubsection{Cadical Hacks: Trail and AllUip}
+\subsubsection{CaDiCaL Hacks: Trail and AllUip}
 
-This modified version of last years CaDiCal was submitted with the two new methods \emph{Trail Saving}~\cite{Hickey:2020:TrailSaving} and \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
+This modified version of last years CaDiCaL was submitted with the two new methods \emph{Trail Saving}~\cite{Hickey:2020:TrailSaving} and \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
 It was submitted in three configurations, one with both methods activated and two other with each having only one of them active. 
-The \emph{Stable AllUIP} variants seemed most successful, in most tracks they were the hightest ranked variants and won the first price in the Planning Sub-Track. 
+The \emph{Stable AllUIP} variants seemed most successful, in most tracks they were the highest ranked variants and won the first price in the Planning Sub-Track. 
 However, in the Unsat Sub-Track, the \emph{Trail Saving} variant performed best.

### 2020-12-17 paper/main.tex

@@
 With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
-One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{}. 
-The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{}.  
-The authors of Glucose introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{}, which they recently summarized in~\cite{}.
+One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{Niklas:2003:Minisat}. 
+The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{Audemard:2018:Glucose}. 
+It introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{Audemard:2009:Glucose}. 
+The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{Manthey:2012:Coprocessor2}.
 
-The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{}.
-
-Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh~\cite{}. 
-Maple first emerged as a series of forks submitted to SAT Competition 2016, introducing the two new branching heuristics Learning Rate based Branching (LRB) and Conflict History based Branching (CHB)~\cite{}.
-The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
+Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
+Maple first emerged as a series of forks submitted to SAT Competition 2016 implementing new innovative branching heuristics on top of available code-bases~\cite{Liang:2016:LRB}. 
+The then award winning variant MapleCOMSPS is an implementation of the new branching heuristics Learning Rate based Branching (LRB) on top of CoMinisatPS~\cite{Liang:2016:MapleCOMSPS}. 
 The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 

### 2020-12-17 paper/main.tex

@@
 
+\subsection{Observations}
+
 \section{History of Code and Winning Strategies}
@@
 
-\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat-sc2020} &  -- & \firsto\firstu\\
+\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat} &  -- & \firsto\firstu\\
  &  &  sat & \firsto\firstu\seconds\\
@@
 \cline{2-4}
- &  CaDiCaL-sc2020 &  -- & \\
+ &  Cadical & SC2020 & \\
 \hline

### 2020-12-17 paper/main.tex
requirements

@@
 
-TODO: Fugenelement
+In this section, we describe the individual 2020 SAT Competition tracks,
+explain the requirements for participation % input/output and proof formats,
+and the ranking criteria, as well as
+the computing infrastructure used for executing the competition.
 
@@
 Solvers not complying with either of the above criteria were only evaluated in a so-called No-Limits sub-track and were not eligible for the Main track awards.
-The No-Limits thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.\ Rules below).
+The No-Limits thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
 However, solvers in No-Limits still competed against all other solvers in the Main Track (hence, we consider it a sub-track).
@@
 Part of the Main track was the Planning sub-track, in which we evaluated the solvers on 200 benchmarks 
-which all came from the same application domain - automated planning. 
+which all came from the same application domain -- automated planning. 
 Solver submitted to the Main track automatically participated in the Planning sub-track.
@@
 
+\todo{MS; look at what Marcus already wrote}
+
 \subsubsection{Parallel Track}
+
+\todo{MH?}
 
@@
 
-\subsection{Mandatory participation requirements}
+\todo{MH?}
 
-\todo{Should we have a discussion (maybe later sections)
+\subsection{Mandatory Participation Requirements}
+\label{sec:rules}
+
+The following requirements were imposed for 
+the participation in the competition.
+
+\paragraph{Source Code}
+The source code of submitted SAT solvers had to be made available 
+(licensed for research purposes) except for the solvers participating only in the No-Limits sub-track.
+
+\paragraph{Description}
+A short system description was required for each solver submission,
+including a list of all the solver's authors and explaining any non-standard algorithmic
+techniques and data structures, as well as references to the relevant literature.
+These system descriptions have been collected and published in the competition
+proceedings \cite{SC2020}.
+
+\paragraph{Benchmarks}
+To participate in the Main track, each team had to submit 20 new benchmark instances.
+This rule guaranteed that the competition could be run on instances mostly unseen to the solver
+developers prior to the competition. Moreover, by making these benchmarks publicly available
+after the competition, the SAT community benefits by having an ever growing repository 
+of diverse problems to target with the next developments.
+
+The exact details of this rule are further explained in Section~\ref{sec:byob}.
+Also the descriptions of the benchmarks have been published \cite{SC2020}.
+
+\paragraph{Input and Output Format}
+
+The benchmark instances were presented to the solvers in the de facto standard
+DIMACS input format for propositional formulas in conjunctive normal form.
+A simple extension of this format was to be adhered to when printing 
+the satisfying assignment 
+(see, e.g., \cite{DBLP:journals/jsat/HeuleJS19}, Section 2.4).
+
+Proofs of unsatisfiability were to be emitted in the DRAT format~\cite{DRATtrim},
+either in its textual version, which is also very similar to the DIMACS input format,
+or on a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
+%
+Details on certification are further discussed below in Section~\ref{sec:certif}.
+
+\paragraph{Number of submissions}
+
+Each participant was restricted to be an author of at most four different sequential solvers,
+two different parallel solvers, and one ``Glucose hack'' sub-track solver.
+Two solvers were considered different as soon as their sources differed
+or the compilation options were different, or different command line options were used
+(with the exception of an option enabling or disabling the proof output).
+
+\paragraph{Portfolio Solvers}
+
+Apart from the No-limits sub-track, participants were not allowed to submit a portfolio of solvers,
+i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{
+In other words, a submission of a combination of solvers was only possible if all the authors of all the parts
+were explicitly listed. This means that all the authors had to be notified if such participation
+was planned and had to consider it carefully, also taking into account the limited number of submissions per author
+as specified by the previous rule.}
+
+This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
+Moreover, while acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
+is interesting, it is not the focus of the SAT competition.
+
+\todo{Should we have a discussion (maybe in later sections)
 about the future of the portfolio solver rule
@@
 
+\paragraph{Organizers}
+The organizers of the competition were not allowed to participate.
+
+\subsection{Solver Ranking and Disqualification}
+
+Solvers were ranked using a PAR-2 score based on a \num{5000}-second timeout.
+A PAR-2 system assigns as many points as the number of seconds it took the solver
+to solve a particular instance and twice the time limit, i.e.~\num{10000} points,
+if the instance was not solved. This means that lowers scores are better.
+We generally report the average score of each solver
+across a benchmark set.
+
+A SAT solver was disqualified if it produced a wrong answer. 
+Specifically, if a solver reported ``unsatisfiable'' on an instance that 
+was proven to be satisfiable by some other solver, or reported ``satisfiable'' 
+but provided a wrong certificate. Solvers disqualified from the competition were
+not eligible to win any award.
+
 \subsection{Certificates}
+
+\label{sec:certif}
 
@@
 On the other hand, certificates for unsatisfiable instances (proofs) were required only 
-in the Main Track (besides the No Limits subtrack).
-
-Proofs of unsatisfiability were to be emitted in the DRAT format~\cite{DRATtrim},
-either in its textual version, which is very similar to the DIMACS input format,
-or on a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
+in the Main track (besides the No Limits sub-track).
 
@@
 was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
-We only considered solved those unsatisfiable formulas that could be validated by {\tt DRAT-trim}.
+In the Main track, we only considered solved those unsatisfiable formulas that 
+could be validated by {\tt DRAT-trim}.
 There were several cases where {\tt cake\_lpr} ran out of resources before being able to 
@@
 \label{sec:computing}
-The Main Track with its subtracks was run on the StarExec cluster \cite{starexec},
+The Main Track with its sub-tracks was run on the StarExec cluster \cite{starexec},
 whose nodes are equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
@@
 The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
+(In the Main track, validation then continued for up to \SI{45000}{\second}.)
 The solvers were allowed to use up to the full \SI{128}{\giga\byte} of RAM.\footnote{
@@
 For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
-GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
+GBD Tools is a tool-chain for maintenance and distribution of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
 Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
@@
 \subsection{Selection of Instances}
+\label{sec:byob}
 

### 2020-12-17 paper/main.tex
some incremental track talk

@@
 
-\todo{MS; look at what Marcus already wrote}
+In the Incremental Library track we mimic scenarios
+where a SAT solver is used as a backend solver in a more complex tool
+(typically solving a harder problem than SAT) and is called multiple times before 
+the enclosing tool reaches its final state. Incrementality means that
+the individual calls to the SAT solver are not independent, but may share 
+a common subset of the input clauses or differ in the presence of additional 
+unit clause assumptions \cite{TODO}.
+
+Instead of using or extending the DIMACS input format, we realize the Incremental track
+by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
+for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
+enclosing tool on its own benchmark and communicate with the competing SAT solver 
+through this interface API. Not only does the SAT solver in this track
+need to solve a sequence of related problems fast, but its answers to the early questions
+may in general influence which questions will follow next.
 
@@
 
-Ihe incremental library track was first introduced in SAT~Race~2015 and then took place again in SAT~Competitions 2016 and 2017. 
-Numerous applications, e.g., SMT solvers or SAT-based planners, use SAT solvers incrementaly, i.e., formulas are repeatedly refined between solve-calls. 
-One important contribution of the founders of this track is the specification of the general incremental interface IPASIR (Re-entrant Incremental Solver API) for SAT applications~\cite{Balyo:2015:SATRace}.
-In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.
+The incremental library track was first introduced in SAT~Race~2015 and 
+then took place again in SAT~Competitions 2016 and 2017. 
+Numerous applications, e.g., SMT solvers or SAT-based planners,
+use SAT solvers incrementally, i.e., formulas are repeatedly refined between the solver calls.
+In SAT~Competitions 2020, we selected a total \num{300} benchmark instances for the Incremental track
+from the six applications described below.
 

### 2020-12-18 paper/main.tex
small refinements in section 3

@@
 a common subset of the input clauses or differ in the presence of additional 
-unit clause assumptions \cite{TODO}.
+unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.
 
@@
 
-For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
+For selection of benchmark instances in this competition, we used GBD Tools.%
+\footnote{\url{https://pypi.org/project/gbd-tools/}} 
+Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
+The association of instance-id and instance attributes is maintained in publicly available databases.%
+\footnote{\url{https://gbd.iti.kit.edu}}
+
 GBD Tools is a tool-chain for maintenance and distribution of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
-Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
-In GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
-
-Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.
-Like this it is possible to query for instances with desired properties, e.g., instance author, family and result, which gives the instance selection process a new quality.
+Its databases provide information about all instances used in SAT competitive events dating back to 2006. 
+In GBD Server, each instance also has an URL, such that instances can be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
 
@@
 
-The ``Bring Your Own Benchmarks'' (BYOB) rule (applied as of SAT Competition 2017~\cite{SC2017}) requires solver authors to submit $20$ new benchmark instances in order to participate in the competition.
-At least $10$ of these instances are required to be ``interesting'', whereby interesting is defined as Minisat~\cite{Niklas:2003:Minisat} needs at least one minute to solve it and the authors own solver does not run into a timeout for the instance.
+The ``Bring Your Own Benchmarks'' (BYOB) rule is established since SAT Competition 2017~\cite{SC2017}. 
+By this rule solver authors are required to submit $20$ new benchmark instances in order to participate in the competition.
+At least $10$ of these instances are required to be ``interesting'', meaning that Minisat must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.
 
-In total, $28$ authors followed our calls for participation and benchmark instances, thus contributing to a set of $1260$ previously unseen benchmark instances with a variety of $27$ different instance families.
+As can be seen in Table~\ref{tab:families}, a total of $28$ authors followed our calls for participation and benchmark instances, thus contributing a set of $1260$ previously unseen benchmark instances in a large variety of different instance families.
+
 By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
-
-In order to compile a balanced set of $300$ benchmark instances, we used the procedure which is depicted in Algorithm~\ref{algo:select} to select a maximium of $14$ submissions per author. 
+In order to compile a balanced set of $300$ benchmark instances, we considered a maximium of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
 Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 

### 2020-12-18 paper/main.tex
comment

@@
 \newcommand{\todo}[1]{{\color{purple}Todo: #1}}
+\newcommand{\solver}[1]{\texttt{#1}}
 
@@
 may in general influence which questions will follow next.
+% E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!
 
@@
 then took place again in SAT~Competitions 2016 and 2017. 
-Numerous applications, e.g., SMT solvers or SAT-based planners,
-use SAT solvers incrementally, i.e., formulas are repeatedly refined between the solver calls.
-In SAT~Competitions 2020, we selected a total \num{300} benchmark instances for the Incremental track
-from the six applications described below.
+Benchmarks for the incremental track are divided into two parts: 
+Applications which implement and use an incremental SAT solver in their backend and benchmark instances which serve as input to these applications. 
+For evaluating the incremental library track of this competition, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning.
+For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.
 
@@
 
-The application $\mathsf{genipabones}$ creates the dual rail encoding~\cite{Balyo:2015:SATRace} of a given formula and incrementally checks for each variable if it is a backbone variable or not~\cite{Janota:2015:Backbones}.
-For this application, we selected $50$ of the smallest and easiest satisfiable problems from previous SAT competitions.
+The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding of the given instance~\cite{Balyo:2015:SATRace}.
+Backbone variables have the same value in all models of a formula~\cite{Janota:2015:Backbones}. 
+We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.
 
@@
 
-The application $\mathsf{genipaessentials}$ incrementally finds all the variables essential for the satisfiability of a given formula~\cite{Bryant:1987:Essentials} by incrementally testing each variable using the dual-rail encoded formula.
-For this application, we used the same $50$ easy satisfiable problems as in the backbone variable detection application.
+The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
+Essential variables have to be assigned in all partial models of a formula~\cite{Bryant:1987:Essentials}. 
+We used the same $50$ easy satisfiable instances as in backbone detection to evaluate solver performance with this application.
 
-\paragraph{Longest Simple Paths}
+\paragraph{Longest Simple Paths (LSP)}
 
-The application $\mathsf{genipalsp}$ finds the longest simple path in a graph. 
-For this application, we selected $50$ instances of the smallest graphs provided by Balyo et al.~\cite{Balyo:2019:LSP}.
+The application \textsf{genipalsp} determines longest simple paths in a graph~\cite{Balyo:2019:LSP}. 
+We selected $50$ easy LSP instances for our evaluation.\footnote{\url{http://algo2.iti.kit.edu/kalp/}}
 
@@
 
-The application $\mathsf{genipamax}$ solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}.
+The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
 The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
-For this application, we selected $50$ instances from MaxSAT Evaluation 2019\footnote{\url{https://maxsat-evaluations.github.io/2019/}}.
+For this application, we selected $50$ instances from \texttt{MaxSAT Evaluation 2019}.\footnote{\url{https://maxsat-evaluations.github.io/2019/}}
 
 \paragraph{Quantified Boolean Formulas (QBF)}
-The application $\mathsf{Ijtihad}$ is a QBF solver based on counterexample-guided expansion~\cite{Bloem:2018:QBFSAT}.
-For this application, we selected $50$ instances from QBF Evaluation 2019\footnote{\url{http://www.qbflib.org/qbfeval19.php}}.
+\textsf{Ijtihad} is a QBF solver which uses counter\-example-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
+Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}
 
-\paragraph{Planning}
-The application $\mathsf{Pasar}$ is a planner which is based on the principles of counter-example guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}. 
-For this application, we selected $50$ SAS planning instances.
+\paragraph{Planning (SAS+)}
+We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar} -- a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
 
@@
 
+\paragraph{Marginal Contributions to VBS} Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth''~\cite{} or ``timetable''~\cite{}.
+
 \section{History of Code and Winning Strategies}
@@
 
-\subsection{On the Shoulders of Giants: The Evolution of SAT Solvers}
+\subsection{On the Shoulders of Giants: Popular Code-Bases}
 \label{sec:codebases}
 
-With a few exceptions, progress in SAT solvers emerged as extensions or forks from existing code bases. 
-One well-known tree of development is rooted in the Codebase of the Minisat solver by Niklas Éen and Niklas Sörenson~\cite{Niklas:2003:Minisat}. 
-The most well-known fork of Minisat is the Glucose solver by Gilles Audemard and Laurent Simon~\cite{Audemard:2018:Glucose}. 
-It introduced numerous implementations of successful new methods, e.g., Literal Block Distance (LBD)~\cite{Audemard:2009:Glucose}. 
-The SAT solver RISS by Norbert Manthey is a successful and award winning fork of Glucose (version 2.2) in combination with the state-of-the-art preprocessor Coprocessor~\cite{Manthey:2012:Coprocessor2}.
+Progress in SAT solvers is usually recorded based on successful evaluations of  modifications of existing code-bases. 
+One well-known tree of development is rooted in the code-base of \solver{Minisat} by Eén and Sörenson~\cite{Niklas:2003:Minisat}. 
+A well-known fork of \solver{Minisat} is \solver{Glucose} by Audemard and Simon~\cite{Audemard:2018:Glucose}, among others introducing Literal Block Distance (LBD) for weighing clauses in forgetting heuristics~\cite{Audemard:2009:Glucose}.
+The SAT solver \solver{RISS} by Manthey is a successful and award winning fork of \solver{Glucose} in combination with the state-of-the-art preprocessor \solver{Coprocessor}~\cite{Manthey:2012:Coprocessor2}.
 
-Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
-Maple first emerged as a series of forks submitted to SAT Competition 2016 implementing new innovative branching heuristics on top of available code-bases~\cite{Liang:2016:LRB}. 
-The then award winning variant MapleCOMSPS is an implementation of the new branching heuristics Learning Rate based Branching (LRB) on top of CoMinisatPS~\cite{Liang:2016:MapleCOMSPS}. 
-The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
-This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}.
-Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
-The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).
+Another more recent string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
+The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heurstics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
+The then award winning variant \solver{MapleCOMSPS} is an implementation of a hybrid branching heuristic of classic Variable-State Independend Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
 
-CryptoMinisat by Mate Soos emerged as a fork of Minisat with an extension that brings special handling of xor clauses via gaussian elimination, which is especially effective when solving cryptographic instances~\cite{}.
-Today, CryptoMinisat is more of an independent code base than a Minisat fork coming with award winning individual implementations of recent SAT technology (see Section~\ref{}).
+In SAT Competition 2017, Luo et al.
+integrated learnt clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
+Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
+They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} to SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
 
-The SAT solvers of Armin Biere arguably belong to the best and most well-known independent code-bases. 
-Lingeling has been around for years now and still we had competitive submissions of its parallel versions Plingeling in this competition. 
-CaDiCaL came up in SAT Competition 2017 and has been award winning since then. 
-Despite the fact that it seems very hard to lift the state-of-the-art with a completly new codebase, the new SAT solver Kissat by Armin Biere which was submitted for the first time this year set a new standard in sequential SAT solving in this competition (see Section~\ref{}).
+Kochemazov et al.
+improved three-tier clause-management by persting additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
+As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning \solver{Maple} solver.
 
-ParaFrost by Osama and Wijs is another new codebase introducing several interesting new concepts~\cite{}. 
-Its sequential variant was submitted for the first time in this competition.
+Starting as a \solver{Minisat}-fork and the integration of special xor treatment~\cite{Soos:2009:Crypto}, \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver.
+One highlight of \solver{CryptoMinisat} is its advanced data-logging capabilities for statistical analysis of SAT solver behavior~\cite{Soos:2019:ChrystalBall}. 
+In its new version~5, \solver{CryptoMinisat} has once again been award winning in SAT Competition~2020 (see Section~\ref{sec:cryptominisat}).
+
+Many independent and award-winning code-bases can be found among the state-of-the-art SAT solvers written by Biere. 
+The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
+As of SAT Competition~2017, \solver{CaDiCaL} by Biere is another independent award winning and structured implementation of the state-of-the-art in SAT solving. 
+Its improved reimplementation \solver{Kissat} won in several of this competitions sequential tracks by a large margin~\cite{Biere:SC2020}.
+
+The sequential variant to the new code-base \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
 
@@
 \subsubsection{CryptoMiniSat-CCAnr and CryptoMiniSat5}
+\label{sec:cryptominisat}
 

### 2020-12-26 paper/main.tex
observations

--- 2020-12-18 paper/main.tex
@@
 \subsection{Observations}
+
+\paragraph{Marginal Contributions to VBS} Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth''~\cite{} or ``timetable''~\cite{}.
 

### 2020-12-26 paper/main.tex

--- 2020-12-18 paper/main.tex
@@
 \fboxsep0pt
-\newcommand{\firsto}{\colorbox{gold}{$m^1$}}
-\newcommand{\firsts}{\colorbox{gold}{$s^1$}}
-\newcommand{\firstu}{\colorbox{gold}{$u^1$}}
-\newcommand{\firstp}{\colorbox{gold}{$p^1$}}
-\newcommand{\secondo}{\colorbox{silver}{$m^2$}}
-\newcommand{\seconds}{\colorbox{silver}{$s^2$}}
-\newcommand{\secondu}{\colorbox{silver}{$u^2$}}
-\newcommand{\secondp}{\colorbox{silver}{$p^2$}}
-\newcommand{\thirdo}{\colorbox{cupper}{$m^3$}}
-\newcommand{\thirds}{\colorbox{cupper}{$s^3$}}
-\newcommand{\thirdu}{\colorbox{cupper}{$u^3$}}
-\newcommand{\thirdp}{\colorbox{cupper}{$p^3$}}
+\newcommand{\firsto}{\colorbox{gold}{\texttt{M1}}}
+\newcommand{\firsts}{\colorbox{gold}{\texttt{s1}}}
+\newcommand{\firstu}{\colorbox{gold}{\texttt{u1}}}
+\newcommand{\firstp}{\colorbox{gold}{\texttt{P1}}}
+\newcommand{\secondo}{\colorbox{silver}{\texttt{M2}}}
+\newcommand{\seconds}{\colorbox{silver}{\texttt{s2}}}
+\newcommand{\secondu}{\colorbox{silver}{\texttt{u2}}}
+\newcommand{\secondp}{\colorbox{silver}{\texttt{P2}}}
+\newcommand{\thirdo}{\colorbox{cupper}{\texttt{M3}}}
+\newcommand{\thirds}{\colorbox{cupper}{\texttt{s3}}}
+\newcommand{\thirdu}{\colorbox{cupper}{\texttt{u3}}}
+\newcommand{\thirdp}{\colorbox{cupper}{\texttt{P3}}}
 
@@
 
-\subsection{On the Shoulders of Giants: Popular Code-Bases}
+\subsection{Code-Bases of SAT Solvers: ``On the Shoulders of Giants''}
 \label{sec:codebases}
@@
 
-The sequential variant to the new code-base \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
+The sequential variant of the \emph{new code-base} \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
 
@@
 
+\renewcommand{\solver}[1]{\underline{\texttt{#1}}}
+\newcommand{\solbert}[1]{\texttt{#1}}
+
 \begin{table}[ht!]
@@
 \hline
-\bf Team & \bf Base Solver & \bf Variant & \bf Award \\
+\bf Team & \bf Base Solver & \bf Variant / Name & \bf Award \\
 \hline
 
-\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat} &  -- & \firsto\firstu\\
- &  &  sat & \firsto\firstu\seconds\\
- &  &  unsat & \firstu\thirdp\\
-\cline{2-4}
- &  Cadical & SC2020 & \\
+\multirow{3}{*}{Biere} & \multirow{3}{*}{\solver{Kissat}} &  -- & \firsto, \firstu\\
+ &  &  \solbert{sat} & \firsto, \firstu, \seconds\\
+ &  &  \solbert{unsat} & \firstu, \thirdp\\
+\hline
+ Biere, Fleury &  \solbert{Cadical} & \solver{SC2020} & \\
 \hline
@@
 \multirow{3}{*}{Zhang, Cai}
-    & \multirow{3}{*}{MapleLCMDistCBT-DL} & Relaxed & \\
- &  & Rel. noTimeParam & \\
- &  & Rel. newTech & \secondo\firsts\\
+    & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
+ &  & \solbert{Rel. noTimeParam} & \\
+ &  & \solbert{Rel. newTech} & \secondo, \firsts\\
 \hline
@@
 \multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
- &  \multirow{2}{*}{CryptoMiniSat-CCAnr} &  -- & \thirdo\thirds\secondp\\
- &  &  lsids & \thirdo\thirds\secondp\\
+ &  \multirow{2}{*}{\solbert{CryptoMiniSat-CCAnr}} &  -- & \thirdo, \thirds, \secondp\\
+ &  &  \solbert{lsids} & \thirdo, \thirds, \secondp\\
 \hline
 
-\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & CryptoMiniSat-WalkSAT & -- & \\
+\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solbert{CryptoMiniSat-WalkSAT} & -- & \\
 \hline
@@
 \multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
- &  &  trail & \secondu\\
- &  &  alluip & \secondu\firstp\\
- & \multirow{-3}{*}{CaDiCaL} &  alluip-trail & \secondu\firstp\\
+ &  &  \solbert{trail} & \secondu\\
+ &  &  \solbert{alluip} & \secondu, \firstp\\
+ & \multirow{-3}{*}{\solbert{CaDiCaL}} &  \solver{alluip-trail} & \secondu, \firstp\\
  \cline{2-4}
- & MapleLCMDist & alluip-trail & \\
+ & \solbert{MapleLCMDist} & \solver{alluip-trail} & \\
 \hline
 
-\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistCBT} & f2trc & \thirdu\\
- & & f2trc-s & \thirdu\\
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solbert{MapleLCMDistCBT}} & \solver{f2trc} & \thirdu\\
+ & & \solbert{f2trc-s} & \thirdu\\
  \cline{2-4}
- & MapleLCMDistCBT-DL & f2trc & \thirdu\\
+ & \solbert{MapleLCMDistCBT-DL} & \solver{f2trc} & \thirdu\\
 \hline
 
-\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& MapleLCMDistCBT-DL-v3 & -- & \\
+\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solver{MapleLCMDistCBT-DL-v3} & -- & \\
 \hline
@@
 \multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
- & \multirow{4}{*}{MapleLCMDistCBT-DL-v3} & Undominated & \\
- &  & Undom. Top16 & \\
- &  & Undom. Top24 & \\
- &  & Undom. Top36 & \\
+ & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v3}} & \solver{Undominated} & \\
+ &  & \solbert{Undom. Top16} & \\
+ &  & \solbert{Undom. Top24} & \\
+ &  & \solbert{Undom. Top36} & \\
 \hline
@@
 \multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
- &  & padc\_dl\_ovau\_lin & \\
- &  & padc\_dl\_ovau\_exp & \\
- &  & psids\_dl & \\
+ & \multirow{4}{*}{\solver{Ex}\solbert{MapleLCMDistCBT}} & \solbert{padc\_dl} & \\
+ &  & \solbert{padc\_dl\_ovau\_lin} & \\
+ &  & \solbert{padc\_dl\_ovau\_exp} & \\
+ &  & \solbert{psids\_dl} & \\
 % \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
@@
 
-Shaw, Meel & MapleLCMDistCBT-DL-v3 & DurianSat & \\
+Shaw, Meel & \solbert{MapleLCMDistCBT-DL-v3} & \solver{DurianSat} & \\
 \hline
@@
 \multirow{2}{*}{Chen}
- & \multirow{2}{*}{MapleLCMDistCBT-DL} & Maple\_Mix & \\
- &  & Maple\_Simp & \\
+ & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Maple\_Mix} & \\
+ &  & \solver{Maple\_Simp} & \\
 \hline
 
-Riveros & MapleLCMDistCBT & SLIME & \\
+Riveros & \solbert{MapleLCMDistCBT} & \solver{SLIME} & \\
 \hline
@@
 \multirow{3}{*}{Li, Wu, Xu, Chen}
- & \multirow{3}{*}{MapleLCMDistCBT-DL} & Scavel & \\
- &  & Scavel01 & \\
- &  & Scavel02 & \\
+ & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Scavel} & \\
+ &  & \solbert{Scavel01} & \\
+ &  & \solbert{Scavel02} & \\
 \hline
@@
 \multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
- & \multirow{2}{*}{MapleCoMsPS\_LRB\_VSIDS\_2} & -- & \\
- &  & init & \\
+ & \multirow{2}{*}{\solver{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & \\
+ &  & \solbert{init} & \\
 \hline
@@
 \multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
- & \multirow{4}{*}{MapleLCMDistCBT-DL-v2.2} & exp-V-LGB & \\
- &  & exp-V-L & \\
- &  & exp-L & \\
- &  & exp-V & \\
+ & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v2.2}} & \solver{exp}\solbert{-V-LGB} & \\
+ &  & \solbert{exp-V-L} & \\
+ &  & \solbert{exp-L} & \\
+ &  & \solbert{exp-V} & \\
 \hline
@@
 \multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
- & \multirow{4}{*}{MapleCM} & \texttt{+}dist & \\
- &  & \texttt{+}dist\texttt{+}sattime2s\texttt{+}\texttt{-} & \\
- &  & \texttt{+}dist\texttt{+}simp2\texttt{-}\texttt{-} & \\
- &  & used\texttt{+}dist & \\
+ & \multirow{4}{*}{\solver{MapleCM}} & \solver{+dist} & \\
+ &  & \solbert{+dist+sattime2s+-} & \\
+ &  & \solbert{+dist+simp2--} & \\
+ &  & \solbert{used+dist} & \\
 \hline
 
-Kaiser, Hartung & MapleLCMDist & PauSat & \\
+Kaiser, Hartung & \solbert{MapleLCMDist} & \solver{PauSat} & \\
 \hline
@@
 \multirow{2}{*}{Osama, Wijs} 
- & \multirow{2}{*}{ParaFROST} & -- & \\
- &  & CBT & \\
+ & \multirow{2}{*}{\solver{ParaFROST}} & -- & \\
+ &  & \solbert{CBT} & \\
 \hline
 \end{tabular}
-\caption{Teams and Solvers participating in the Main Tracks (Variant refers to a named configuration or a name of a hack). 
-Note that many teams are only responsible for the variant of a previously existing base solver.
-Awards were given in Main (m), SAT (s), UNSAT (u), and Planning (p) sub-tracks.}
+\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: In favour of highlighting the relevant branch in the Maple tree of solvers, we identify configuration names of solvers, as well as variants of other base solvers in Column~3 ``Variant / Name''.
+To avoid confusion, we \solver{underlined} the names of the submitted solvers.}
 \label{tab:solvers-main}
 \end{table}
+
+\renewcommand{\solver}[1]{\texttt{#1}} % sorry ;)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-12-27 paper/main.tex
refined incremental and kissat

@@
 
-\section{History of Code and Winning Strategies}
+\section{Code-Bases and Winning Strategies}
 \label{sec:analysis}
@@
 
-\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
+\subsection{Sequential SAT Solving}
 \label{sec:part:seq}
 
-A total of $18$ teams submitted their solvers to the main track of the competition.  
+Sequential SAT solvers have been evaluated in the Main tracks as well as in the Incremental track of SAT Competition~2020. 
+A total of $18$ teams submitted correct solvers to the Main track of the competition. 
 Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
-$14$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or CaDiCaL~\cite{}.
-
-In the incremental track, four teams submitted their solvers. 
-All solvers in the incremental library track are created from independent code bases. 
-Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers.
+The recent genealogy of all submissions, is highlighted by \emph{base solver} and \emph{variant} columns. 
+Underlined text is used to point out the important parts of the respective submissions name.
 
@@
  \cline{2-4}
- & \solbert{MapleLCMDist} & \solver{alluip-trail} & \\
+ & \solbert{MapleLCMDist} & \solbert{alluip-trail} & \\
 \hline
@@
  \cline{2-4}
- & \solbert{MapleLCMDistCBT-DL} & \solver{f2trc} & \thirdu\\
+ & \solbert{MapleLCMDistCBT-DL} & \solbert{f2trc} & \thirdu\\
 \hline
@@
 \end{tabular}
-\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: In favour of highlighting the relevant branch in the Maple tree of solvers, we identify configuration names of solvers, as well as variants of other base solvers in Column~3 ``Variant / Name''.
-To avoid confusion, we \solver{underlined} the names of the submitted solvers.}
+\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks.
+We partially \solver{underlined} submission names.
+Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$.
+}
 \label{tab:solvers-main}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Four submissions made it to participate in the Incremental Library track, some of which, e.g, \solver{CryptoMinisat-5}, have also been evaluated and awarded in the Main sequential track. 
+Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
+Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers. 
+In this table, \emph{Score} denotes the number of application categories in which the solvers won based on their PAR-2 score.
+
 \begin{table}[ht]
@@
 \hline
-\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & CaDiCaL-sc2020 & 1 \\
+\stack{Biere, Fleury}~ & CaDiCaL-sc2020 & 1 \\
 \hline
@@
 \end{tabular}
-\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
+\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
 \label{tab:solvers-incremental}
@@
 
-If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
-Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
-Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.
+Three major configurations of \solver{Kissat} were evaluated in this competition. 
+That includes one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively. 
+\solver{Kissat} won \emph{four awards}, by achieving first place in the Main track, first place in the Unsat track, second place in the Sat track and third place in the Planning track.
 
-Kissat is a reimplementation of CaDiCaL~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.
+\solver{Kissat} is a reimplementation of \solver{CaDiCaL} in C,
+but comes with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
+Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.
 
-In Kissat, forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-For irredundant clauses, forward subsumption is still executed together with variable elimination during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurrences~\cite{Biere:SC2020}.
+\solver{Kissat} uses a new unit (``ticks'') to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses, after conflict-rate has been obeserved to be too unstable for the use-case~\cite{Biere:SC2020}.
 
-Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
-Regarding the duration of alternating restart modes, Kissat's author considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.
-
-Considering target phases~\cite{Biere:SC2019}, Kissat's author come up with an innovative use-case for autarkies to account for saved phases. 
-Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{Kiesl:2019:Autarkies}. 
-The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.
+\solver{Kissat} also exploits an innovative use-case for autarkies to account for saved phases. 
+In order to keep valuable information of saved phases, before each rephasing step, \solver{Kissat} computes the largest autarky for the assignment implied by the current saved phases~\cite{Kiesl:2019:Autarkies}.
+As such an autarky might contain satisfying assignments which imply disconnected components, those variables are subject to subsequent variable elimination.
 

### 2020-12-27 paper/main.tex
cryptominisat

@@
 
-This solver won four awards, two third places in the Main Track and its Sat Subtrack, one second place in the Planning Subtrack, and the first place in the Incremental Library Track.
+\solver{CryptoMinisat} won \emph{four awards}, two third places in the Main and Sat tracks, one second place in the Planning track, and first place in the Incremental Library track. 
+Two submitted variants \solver{default} and \solver{LSIDS} scored mostly adjacent ranks in the evaluation of tracks. 
+The \solver{LSIDS} variant of \solver{CryptoMinisat} comes with a new hybrid phase selection approach~\cite{Shaw:2020:LSIDS,Soos:SC2020}.
 
-To the Main track, the solver was submitted in two variants, with and without LSIDS~\cite{Shaw:2020:LSIDS},
-which is a phase selection heuristic similar to VSIDS and, if active, it is used whenever backtracking is chronological~\cite{Nadel:2018:CBT}.
-On top of that, CryptoMiniSat is periodically switching between polarity saving and stable phases~\cite{Biere:SC2019}.
+\solver{CryptoMinisat} comes with an independent implementation of the recent hybrid branching heuristic which alternates between classic phase saving and target phase selection~\cite{Biere:SC2019}.
 
-By tight integration of CCAnr~\cite{Cai:2015:CCAnr}, a stochastic local search (SLS) solver, into CryptoMinisat, CryptoMiniSat-CCAnr combines the two SAT solving strategies, SLS and CDCL, in a unique way.
-The solver runs local search for a short period of time in regular intervals and (just in case SLS finds no solution)
-changes the polarities according to the best assignment found by the SLS solver, which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
-Moreover, it bumps VSIDS scores of the first 100 variables contained in the clauses which the SLS solver considers most hard to satisfy~\cite{Soos:SC2020}.
+\solver{CryptoMiniSat-CCAnr} integrates stochastic local search (SLS) in a unique way~\cite{Cai:2015:CCAnr}. 
+\solver{CryptoMiniSat-CCAnr} regularly schedules short periods of local search and imports the best assignment found by the SLS solver for phase selection -- a procedure which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
+In addition, \solver{CryptoMiniSat-CCAnr} bumps the VSIDS scores of the first 100 variables in those clauses which the SLS solver weighs most hard to satisfy~\cite{Soos:SC2020}.
 
-SLS is tightly integrated and thus is aware of changes occurring during inprocessing. 
-Inprocessing now also includes ternary resolution and vivification is used a lot more~\cite{ChuMinLi:2020:Vivification}. 
-All modifications in CryptoMiniSat are fully integrated with respect to incremental use-cases including the use of assumptions.
-
-CryptoMiniSat periodically changes decay factors of its branching heuristics, thus avoiding usage of a ``single best'' configuration.
-
-This version of CryptoMiniSat comes with an highly optimized implementation of Gauss-Jordan Elimination~\cite{Soos:2020:CNFXOR}. 
-CryptoMiniSat includes BreakId, a sub-system that calculates symmetry breaking clauses, which it calls on every 5th inprocessing iteration~\cite{Devriendt:2016:BreakId}.
+Inprocessing has been extended to include ternary resolution and more vivification~\cite{ChuMinLi:2020:Vivification}. 
+All the new features are fully supported in \emph{incremental} mode. 
+\solver{CryptoMinisat} alternates decay factors of its branching heuristics, thus avoiding the restriction to a ``single best'' configuration~\cite{Soos:SC2020}. 
+The submitted version of \solver{CryptoMinisat} entails a new optimized implementation of Gauss-Jordan Elimination~\cite{Soos:2020:CNFXOR}. 
+\solver{CryptoMinisat} periodically executes the \solver{BreakId} algorithm to  calculate symmetry breaking clauses~\cite{Devriendt:2016:BreakId}.
 

### 2020-12-27 paper/main.tex
planning and similarity

@@
 
-\todo{Similarity of Solvers: Rank Correlation}
+\subsection{Planning Sub-Track}
+% - 86 out of 100 biggest (number of clauses) are planning
+% - 109 / 200 in the planning track are not solved by any solver
+    % - 186 / 600 in total
+% - all 200 above 90\% binary clauses and half have above 99%
+The instances of the planning sub-track are big compared to the rest of the
+main track. Using the number of clauses as a metric; out of the $100$ biggest
+instances
+% of the main-track
+$86$ belong to the planning track. The large size can mainly be attributed to
+binary clauses. On average, more than $98$\% of the clauses are binary for
+planning instances, where the average for the rest of the instances from the
+main track is below $60$\%.
+
+Despite the large size, only a few instances directly caused memory problems for
+more than just a few solvers. In most cases the \SI{128}{\giga\byte} of RAM
+available were sufficient.
+% The saving grace might have been
+% This can be attributed to
+% the \SI{128}{\giga\byte} of RAM available to each solver.
+However, the three biggest instances from the \emph{childsnack} family of
+planning problems encoded with the \emph{hierarchical} planner \emph{Tree-REX}
+caused over half of the solvers to abort with some error message related to
+memory. Other solvers were still able to solve the same instances within $300$
+seconds.
+
+\subsection{Similarity of Solvers}
+To investigate how similar the solvers of the main track are to each other, we
+define a similarity metric based on the measured runtimes. For that we first
+remove $186$ benchmarks from the collected data that have not been solved by any
+solver. For the rest of the benchmarks we use the PAR-2 score,
+% based on the \num{5000}-second timeout
+i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
+This leaves us with $414$ floats
+$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
+and $B$, normalized to the interval $[0,1]$ is defined
+% as:
+by Equation~\ref{eq-similarity}.
+
+\begin{equation}
+\label{eq-similarity}
+	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{414 \cdot 10000}
+\end{equation}
+We calculated the \emph{similarity} between the $30$ solvers which achieved the
+best PAR-2 score in the main track. The results are displayed in
+Figure~\ref{fig-similarity-main} as a \emph{heat map}. Additionally the result
+of hierarchically clustering the solvers based on their similarity is
+illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
+are joined reflects how similar they are. For example
+enabling the \emph{trail saving} in \emph{CaDiCaL-alluip} has no impact on the
+runtime, resulting in a similarity above \num{0.999}. Thus the two solvers are joined very low in the dendrogram.
+% A similar visualization was used in the SAT Challenge 2012 \todo{cite}. They used
+
+One big cluster we can identify are the \emph{Mapel} decedents in the lower left
+corner, all of which are modifications of the winners of the SAT Competition
+2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
+  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
+has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
+family at the top right. With the exception of \emph{mergesat} and maybe
+\emph{DurianSat} we observe a high similarity within the cluster.
+
+The three \emph{Relaxed} solvers by \emph{Zhang} and \emph{Cai} are using the
+same code base as a lot of the solvers in the Maple-Cluster but their overall
+performance is better and closer to the CMS-Cluster.
+
+The CMS versions differ in their implementation of stochastic local search (SLS)
+but overall have a similar performance.
+
+The last big cluster in the center of the heat map is comprised of the solvers
+originally written by Biere. The three configurations of \emph{Kissat} form a
+subcluster, even though the configurations are fairly distinct from each other.
+% , specialized for satisfiable and unsatisfiable instances.
+% One targets satisfiable instances, while the other is focused on unsatisfiable
+% instances and a third alternating between them.
+
+The other subcluster consists of
+modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
+CaDiCaL-2020 has a worse overall performance than
+% has an overall worse per
+% is lacking behind
+the other solvers in this cluster.
+
+\begin{figure}[tp]
+    \centering
+    \includegraphics[width=\linewidth]{similarity/cross.pdf}
+    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
+      % Similarity is defined as
+      % one minus the average taxicab distance normalized to the interval [0,1].
+      % Spearman's rank correlation coefficient.
+      Darker regions mean that the solvers are more similar.
+      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
+    }
+    \label{fig-similarity-main}
+\end{figure}
+
+% To estimate the similarity between the performance of the solvers of the Main
+% Track we define a similarity metric $s$.
+% identify each solver with a point in the 600-dimensional real vector
+% space. Each component describes the PAR-2 runtime on one instance. We map the
+% taxicab distance to the $[0, 1]$ interval and then to determine how similar two
+% solvers are.
 
@@
 
-\subsubsection{CaDiCaL Hacks: Trail and AllUip}
-
-This modified version of last years CaDiCaL was submitted with the two new methods \emph{Trail Saving}~\cite{Hickey:2020:TrailSaving} and \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
-It was submitted in three configurations, one with both methods activated and two other with each having only one of them active. 
-The \emph{Stable AllUIP} variants seemed most successful, in most tracks they were the highest ranked variants and won the first price in the Planning Sub-Track. 
-However, in the Unsat Sub-Track, the \emph{Trail Saving} variant performed best.
-
-With \emph{Trail Saving}, the solver caches backtracked slices of the assignment trail in order to reuse them when the same decisions are repeated. 
-The authors came up with sophisticated control mechanisms on when and how to reuse the cached trail slices and when to flush that cache.
-
-With \emph{Stable AllUip}, the solver continues resolution beyond the 1st Unit Implication Point (1-UIP) during clause-learning~\cite{Zhang:2001:ClauseLearning} as long that does not increase the LBD value of the learnt clause and then keeps that clause only if it has a smaller size than then 1-UIP clause.
-The authors came up with an additional heuristic to limit the amount of attempted AllUip learning attempts, if the fraction of unsuccessful alluip learning attempts gets to high, which they check and adapt on every restart~\cite{Bacchus:SC2020}.
-
-\subsubsection{Relaxed MapleLCMDistCBT-DL newTech}
-
-The variant \emph{newTech} of the \emph{Relaxed} fork of the MapleLCMDistCBT-DL was especially successful on satisfiable instances. 
-The solver won two awards, second price in Main Track and first price in its Sat Sub-Track.
-
-The \emph{Relaxed} fork of MapleLCMDistCBT-DL already participated in SAT Race 2019~\cite{Xindi:SC2019}.
-They integrated the local search solver CCAnr by extending the current partial assignment of the CDCL solver to a full assignment and for a fixed interval start the local search solver to try to find a nearby solution.
-
-In the new versions of the Relaxed family of Maple solvers~\cite{Xindi:SC2020}, they probabilistically switch between several modes of phase selection, and some of these modes reuse the maximal partially satisfying assignments as determined by the local search solver.
-
-For their successful \emph{newTech} variant~\cite{Xindi:SC2020} of their fork, they count the number of variable-occurrences in unsat clauses for each flip in the local search solver. 
-Then they reuse this information to priorize variables in a modified branching heuristic.
-
-\subsubsection{MapleLCMDistCBT F2TRC}
-
-The MapleLCMDistCBT F2TRC forks were ranked third in the Unsat Sub-Track of the Main-Track.
-
-The F2TRC forks aim at introducing determinism in winning solvers of previous competition, e.g., by replacing time-based intervals for LRB-VSIDS switches by a heuristic based on the conflict-count~\cite{Kochemazov:SC2020}.
-
-Another modification aims at improving three-tier clause management based on the three tiers core, tier2 and local as it was introduced by Chanseok Oh~\cite{Oh:2015:satunsat}.
-In order to limit growth of the core-tier, they introduce a limit on the number of core clauses, and whenever that is reached some of the low-ranked inactive core clauses are moved from core to tier2 and the limit is increased.
-In order to prevent tier2 from starving, they replaced the conflict limit for tier2 reduction by a size limit, then only half of the most recently inactive clauses is moved to local tier~\cite{Kochemazov:SC2020}.
+\subsubsection{Trail Saving and Stable AllUip in CaDiCaL}
+
+Based on \solver{CaDiCaL}, its variants \solver{Trail} and \solver{AllUip} present implementations of a new \emph{Trail Saving} approach~\cite{Hickey:2020:TrailSaving} and improved clause-learing based on the notion of \emph{Stable AllUIP}~\cite{Bacchus:SC2020}.
+Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
+The variants including \emph{Stable AllUIP} were the most successful and won the first price in the Planning Sub-Track.
+
+The \emph{Stable AllUip} variants resolve additional clauses beyond the 1st Unit Implication Point (1-UIP) and keep them if they are of smaller size or LBD than the 1-UIP clause. 
+By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
+The \emph{Trail Saving} variant caches backtracked portions of the trail and uses them to restore decision levels during search if possible~\cite{Hickey:2020:TrailSaving}.
+
+\subsubsection{Relaxed Maple newTech}
+
+The \solver{Relaxed} fork of \solver{MapleLCMDistCBT-DL} was first presented to the community in SAT Race 2019~\cite{Xindi:SC2019}. 
+In SAT Competition~2020, its new variant \solver{newTech} showed a good performance especially on satisfiable instances. 
+The solver won two awards, the second price in the Main track and the first price in the Sat track.
+
+The \solver{Relaxed} fork integrates short runs of the local search solver \solver{CCAnr} through periodic ex- and import of assignments~\cite{Xindi:SC2019}. 
+The submitted versions of \solver{Relaxed Maple} use a probabilistic schedule for switching between $10$ phase selection modes. 
+The award winning variant \solver{newTech} uses occurrence counts of variables in unsatisfied clauses during SLS runs to recalculate variable priorities for their modified branching heuristic~\cite{Xindi:SC2020}.
+
+\subsubsection{Maple F2TRC}
+
+The \solver{F2TRC} fork of \solver{MapleLCMDistCBT} won the third price in the Unsat track. 
+\solver{F2TRC} comes with a deterministic reimplementations of former winning strategies, e.g., by replacing time intervals by conflict intervals~\cite{Kochemazov:SC2020}.
+
+\solver{F2TRC} introduces an improved management of learned clauses in the tree tiers \emph{core}, \emph{tier2} and \emph{local} which are inherited from \solver{CoMinisatPS}~\cite{Oh:2015:satunsat}.
+A dynamic size limit for the \emph{core} tier, triggers the reassignment of inactive clauses from \emph{core} to \emph{tier2}. 
+To conter-act an observered starving of tier2, the conflict-based heuristic that controls demotion of clauses from \emph{tier2} to \emph{local} was replaced by a size based heuristic~\cite{Kochemazov:SC2020}.
 
@@
 
-\begin{table}[ht]
+\begin{table}[b]
 \smaller

### 2020-12-27 paper/main.tex
JKU address
parallel solvers

@@
 
-\subsection{Planning Sub-Track}
-% - 86 out of 100 biggest (number of clauses) are planning
-% - 109 / 200 in the planning track are not solved by any solver
-    % - 186 / 600 in total
-% - all 200 above 90\% binary clauses and half have above 99%
-The instances of the planning sub-track are big compared to the rest of the
-main track. Using the number of clauses as a metric; out of the $100$ biggest
-instances
-% of the main-track
-$86$ belong to the planning track. The large size can mainly be attributed to
-binary clauses. On average, more than $98$\% of the clauses are binary for
-planning instances, where the average for the rest of the instances from the
-main track is below $60$\%.
-
-Despite the large size, only a few instances directly caused memory problems for
-more than just a few solvers. In most cases the \SI{128}{\giga\byte} of RAM
-available were sufficient.
-% The saving grace might have been
-% This can be attributed to
-% the \SI{128}{\giga\byte} of RAM available to each solver.
-However, the three biggest instances from the \emph{childsnack} family of
-planning problems encoded with the \emph{hierarchical} planner \emph{Tree-REX}
-caused over half of the solvers to abort with some error message related to
-memory. Other solvers were still able to solve the same instances within $300$
-seconds.
-
-\subsection{Similarity of Solvers}
-To investigate how similar the solvers of the main track are to each other, we
-define a similarity metric based on the measured runtimes. For that we first
-remove $186$ benchmarks from the collected data that have not been solved by any
-solver. For the rest of the benchmarks we use the PAR-2 score,
-% based on the \num{5000}-second timeout
-i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
-This leaves us with $414$ floats
-$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
-and $B$, normalized to the interval $[0,1]$ is defined
-% as:
-by Equation~\ref{eq-similarity}.
-
-\begin{equation}
-\label{eq-similarity}
-	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{414 \cdot 10000}
-\end{equation}
-We calculated the \emph{similarity} between the $30$ solvers which achieved the
-best PAR-2 score in the main track. The results are displayed in
-Figure~\ref{fig-similarity-main} as a \emph{heat map}. Additionally the result
-of hierarchically clustering the solvers based on their similarity is
-illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
-are joined reflects how similar they are. For example
-enabling the \emph{trail saving} in \emph{CaDiCaL-alluip} has no impact on the
-runtime, resulting in a similarity above \num{0.999}. Thus the two solvers are joined very low in the dendrogram.
-% A similar visualization was used in the SAT Challenge 2012 \todo{cite}. They used
-
-One big cluster we can identify are the \emph{Mapel} decedents in the lower left
-corner, all of which are modifications of the winners of the SAT Competition
-2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
-  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
-has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
-family at the top right. With the exception of \emph{mergesat} and maybe
-\emph{DurianSat} we observe a high similarity within the cluster.
-
-The three \emph{Relaxed} solvers by \emph{Zhang} and \emph{Cai} are using the
-same code base as a lot of the solvers in the Maple-Cluster but their overall
-performance is better and closer to the CMS-Cluster.
-
-The CMS versions differ in their implementation of stochastic local search (SLS)
-but overall have a similar performance.
-
-The last big cluster in the center of the heat map is comprised of the solvers
-originally written by Biere. The three configurations of \emph{Kissat} form a
-subcluster, even though the configurations are fairly distinct from each other.
-% , specialized for satisfiable and unsatisfiable instances.
-% One targets satisfiable instances, while the other is focused on unsatisfiable
-% instances and a third alternating between them.
-
-The other subcluster consists of
-modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
-CaDiCaL-2020 has a worse overall performance than
-% has an overall worse per
-% is lacking behind
-the other solvers in this cluster.
-
-\begin{figure}[tp]
-    \centering
-    \includegraphics[width=\linewidth]{similarity/cross.pdf}
-    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
-      % Similarity is defined as
-      % one minus the average taxicab distance normalized to the interval [0,1].
-      % Spearman's rank correlation coefficient.
-      Darker regions mean that the solvers are more similar.
-      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
-    }
-    \label{fig-similarity-main}
-\end{figure}
-
-% To estimate the similarity between the performance of the solvers of the Main
-% Track we define a similarity metric $s$.
-% identify each solver with a point in the 600-dimensional real vector
-% space. Each component describes the PAR-2 runtime on one instance. We map the
-% taxicab distance to the $[0, 1]$ interval and then to determine how similar two
-% solvers are.
+\todo{Similarity of Solvers: Rank Correlation}
 
@@
 \multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
- & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
- & P-MCOMSPS-STR-64 & \firsto \\
+ & \solver{Painless-MCOMSPS-STR-32} & \firsto \firsts \secondu \\
+ & \solver{Painless-MCOMSPS-STR-64} & \firsto \\
 \hline
 \multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
- & Plingeling & \secondo \thirds \firstu \\
- & Treengeling & \\
+ & \solver{Plingeling} & \secondo \thirds \firstu \\
+ & \solver{Treengeling} & \\
 \hline
 \multirow{2}{*}{Nabeshima, Inoue}
- & ManyGlucose-32 & \thirdo \thirdu \\
- & ManyGlucose-64 & \thirdu \\
+ & \solver{ManyGlucose-32} & \thirdo \thirdu \\
+ & \solver{ManyGlucose-64} & \thirdu \\
 \hline
 \multirow{2}{*}{Tchinda, Djamegni}
- & painlessmaplevone & \seconds \\
- & painlessmaplevtwo & \seconds \\
-\hline
-Li, Wu, Xu, Chen & syrupscavel & \\
-\hline
-Chen & abcdsatptwenty & \\
+ & \solver{painlessmaplevone} & \seconds \\
+ & \solver{painlessmaplevtwo} & \seconds \\
+\hline
+Li, Wu, Xu, Chen & \solver{syrupscavel} & \\
+\hline
+Chen & \solver{abcdsatptwenty} & \\
 \hline
@@
 
-\subsubsection{P-MCOMSPS-STR}
-
-P-MCOMSPS-STR is built from the Painless framework~\cite{Frioux:2017:Painless} for solver parallization and uses the MapleCOMSPS solver~\cite{Liang:2017:Maplecomsps} as a building block. 
-The authors submitted a 32 and 64 core version and won 3 awards, first place in the overall ranking, first place in the SAT ranking and second in the UNSAT ranking. 
-The 64 core version performed slightly worse than the 32 core version in the overall ranking, and that gap is bigger for the SAT-only ranking and worst for the UNSAT-only ranking, such that in the separate rankings only the 32 core version is responsible for winning the prices.
-
-The painless framework uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations within the framework boil down to implementing parallelization and clause sharing strategies.
-
-In the submitted version of P-MCOMSPS-STR, diversification is done via diverse fixed configurations of branching strategies (LRB and VSIDS) and sparse random intialization of variable polarities like in~\cite{Balyo:2015:Hordesat}.
-One instance of their ``sequential engines'' performs concurrent clause strengtheing as described in~\cite{Wieringa:2013:CCS} and another single instance is configured to perform Gaussian eliminiation during preprocessing.
-
-For sharing they use an all-to-all strategy with a regular exchange of a fixed size buffer and a dynamic clause lbd limit.
+\subsubsection{Painless Maple-CoMinisatPS STR}
+
+\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}~\cite{Liang:2017:Maplecomsps}. 
+The authors submitted a \solver{32 core} and a \solver{64 core} variant and were awared three prices: first place in the Main track, first place in the Sat track and second in the Unsat track. 
+The \solver{32 core} variant achieved slightly better scores than the \solver{64 core} variant. 
+The differentiated evaluation of the Sat and Unsat tracks shows the \solver{32 core} variant performed much better, such that the follow-up solvers outperformed the \solver{64 core} variant.
+
+\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies.
+
+\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random intialization of variable polarities~\cite{Balyo:2015:Hordesat}.
+However, a special solver instance performs concurrent clause strengthening~\cite{Wieringa:2013:CCS}. 
+Another special solver instance is configured to perform Gaussian eliminiation during preprocessing. 
+\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit.
 
@@
 
-Plingeling got three awards, first place in the Unsat Category, third place in Sat and second place in the overall evaluation. 
-Plingeling is an extension of the well-known SAT solver Lingeling~\cite{} and did not change since 2016. 
-Via a global master queue, Plingeling shares unit clauses, equivalences and short clauses with clauses with at most 40 literals and glucose LBD level of at most 8 and random seeds, e.g., for diversification via default polarities.~\cite{}
+\solver{Plingeling} got three awards: first place in the Unsat track, second place in the Main track, third place in the Sat track. 
+\solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
+In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
+\solver{Plingeling} uses random seeds for diversification via default polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.
 
@@
 
-The authors of ManyGlucose received two awards in this competition. 
-ManyGlucose was submitted in 32-core and 64-core variants~\cite{}.
-The 32-core variant won two third prices, one in the overall evaluation and one in the unsat sub-track. 
-ManyGlucose is a fork of GlucoseSyrup~\cite{} and uses strategies similar to those known from ManySAT~\cite{} in order to achive deterministic solver runs.
+\solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
+The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
+\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achive deterministic solver behaviour~\cite{GlucoseSyrup}~\cite{ManySat}.
 
@@
 
-The authors Painless Maple received one award for second best performance in the Sat sub-track of the parallel track. 
-However, the solver was last in the Unsat sub-track.
-
-The authors implemented a couple of modifications (\todo{name them}) on top of the MapleLCMDistChronoBT~\cite{} solver, which they also submitted in various configurations to the main track. 
-The two submissions in the parallel track use painless as a parallelization framework.
-
-Their sharing strategy includes splitting their workers into two categories, where the solvers in the first category only export clauses and only solvers in the second category import and export clauses.
-
-They submitted two variants with different diversification strategies. 
-In their first variant they use different configurations of configurations of the newly implemented strategies. 
-The second variant uses a more classic diverisification strategy by randomizing polarities and variable scores.
+\solver{Painless Maple} received the award for second best performance in the Sat track but scored last in the Unsat track. 
+\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT}, which is a modified \solver{MapleLCMDistChronoBT} (see Main track), in the \solver{Painless} parallelization framework.
+
+\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
+\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
+\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics.
 
@@
 
-\begin{table}[ht]
+\begin{table}[t]
 \smaller

### 2020-12-27 paper/main.tex

@@
 \ead{martin.suda@cvut.cz}
+
+\address[jku] {
+Institute for Formal Models and Verification, Johannes Kepler University\\
+{\tt nils.froleyks@jku.at}\\[1em]
+}
 
@@
 that transforms the world from some initial state to a goal state. In 1992 Kautz
+and Selman
 \cite{Kautz1992} proposed to encode planning as satisfiability. In their

### 2020-12-27 paper/main.tex
cloud

@@
 \hline
-Schreiber & mallob-mono & 1\\
-\hline
-\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
-\hline
-Riveros & Slime & 3\\
-\hline
-\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
-& Paracooba-March & -\\
-\hline
-Hartung & CTSat & -\\
+Schreiber & \solver{mallob-mono} & 1\\
+\hline
+\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & \solver{TopoSAT2} & 2\\
+\hline
+Riveros & \solver{Slime} & 3\\
+\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & \solver{Paracooba} & -\\
+& \solver{Paracooba-March} & -\\
+\hline
+Hartung & \solver{CTSat} & -\\
 \hline
@@
 
-The massively parallel SAT solver Mallob is based on HordeSAT~\cite{}. 
-Mallob is a framework for massivley parallel and distributed \emph{malleable job scheduling}, and thus can perform dynamic load balancing on many jobs of varying priorty.
-However, in the submitted version Mallob Mono, this functionality is disabled, as traditionally in SAT Competition all resources are busy solving one single instance only.
-
-Mallob uses the the 2018 version \emph{bcj} of Lingeling~\cite{} and employs diversification via randomized sparse initialization of branching scores just like it is done in Plingeling~\cite{}. 
-Every 14th process, however, runs the local search solver YalSAT~\cite{}.
-
-Clause exchange is handled considerably different from previous approach. 
-Workers are organized in a binary tree and clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
-Each node performs a three way merge of the local and the two incoming buffers. 
-Only the final aggragate at the root of that binary tree is broadcast to all the solvers.
-
-To limit sharing, there is a global size limit of $5$ for all the shared clauses. 
-The buffer has a limited size as well, but that size depends on the position in the binary tree, with root having the largest buffer and leaves the smallest. 
-Clauses are sorted by there size during aggregation, such that smaller clauses are preferred over longer clauses. 
-Duplicates are filtered out using a bloom filter, which is cleared periodically. 
-There is a special filter for duplicate unit-clause which especially useful during startup.
+\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSAT}. 
+\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
+This functionality is disabled in the submitted variant \solver{Mallob Mono}.
+
+\solver{Mallob} mainly uses \solver{Lingeling-bcj} and diversifies via randomized sparse initialization of branching scores. 
+However, as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
+
+\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
+Each node performs a three-way merge of its local export and the two incoming buffers. 
+The aggragate that approaches the root of the binary tree is then broadcast to all solvers~\cite{}.
+
+\solver{Mallob} uses a global clause size limit and a dynamic limit for the sharing buffer, which depends on the position in the binary tree and grows while getting closer to the root. 
+Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
+Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{}.
 
@@
 
-TopoSAT~2 is a massively parallel SAT solver using Glucose~3 with lockfree clause-exchange as in ManySAT~\cite{} on each node, and using MPI to share clauses between nodes.
-
-In Toposat~2, diversification is done via different strategies used for branching, restarting and clause forgetting. 
-Clauses are strengthened before they are exported. 
-Locally, clause import is delayed until the local trail-size is low in a monitored period.
+\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Glucose3,Toposat2}. 
+\solver{TopoSAT~2} uses lockfree clause-exchange for solvers running on the same maching, and MPI to share clauses between machines~\cite{ManySat,Proceedings}.
+
+\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
+\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting.
 
@@
 
-Slime is build on top of MapleLCMDistChronoBT and was first submitted to SAT Race 2019 suggesting the new phase selection heuristic~\cite{}. 
-The 2020 version apparently adds some kind of periodic randomization in geometrically increasing intervals~\cite{}. 
-Even thought the sequential solver was unsuccessful in the Main Track, its MPI-based cloud version, won the third price in this competitions cloud track.
+\solver{Slime} is build from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{SlimeSATRace2019}. 
+The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{}. 
+Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} won the third price in the Cloud track.
 

### 2021-01-03 paper/main.tex
main track plots

@@
 
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
+\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
+\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
+\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
+\end{figure}
+
 \todo{New Codebases}

### 2021-01-03 paper/main.tex
typos

@@
 \usepackage[ruled,linesnumbered,vlined]{algorithm2e}
-\usepackage{tkz-graph}
+
 \usepackage{lscape} 
@@
 Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
-Despite its complexity, there is ongoing progress in solving methods and their implementations in SAT solvers. 
+Despite its complexity, there is an ongoing progress in solving methods and their implementations in SAT solvers. 
 The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
@@
 
-In this competition, we initiated a new application-specific subtrack. 
-The idea is to provide a large amount of benchmark instances of a specific application, and to evaluate all solvers with respect to these instance in a special track. 
-In this competition, we used 200 instances of the planning domain to run a planning subtrack.
+In this competition, we initiated a new application-specific sub-track. 
+The idea is to provide a large amount of benchmark instances of a specific application and to evaluate all solvers with respect to these instance in a special track. 
+In this competition, we used 200 instances of the planning domain to run a planning sub-track.
 
@@
 This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
-Moreover, while acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
+Moreover, while we acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
 is interesting, it is not the focus of the SAT competition.
@@
 (In the Main track, validation then continued for up to \SI{45000}{\second}.)
-The solvers were allowed to use up to the full \SI{128}{\giga\byte} of RAM.\footnote{
+The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
 Unfortunately, the memory limit of \SI{24}{\giga\byte}, that was used in the previous years,
@@
 Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
-If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5-7). 
+If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5--7). 
 Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
@@
 \subsection{Similarity of Solvers}
-To investigate how similar the solvers of the main track are to each other, we
+To investigate how similar the solvers of the Main track are to each other, we
 define a similarity metric based on the measured runtimes. For that we first
@@
 
-In the following we provide an overview on the participating teams and solvers,  and summarize new strategies which are implemented in the award winning solvers of this competition.
+In the following, we provide an overview of the participating teams and solvers, 
+and summarize new strategies which are implemented in the award winning solvers of this competition.
 

### 2021-01-04 paper/main.tex

@@
 \ead{markus.iser@kit.edu}
-\author[hiit]{Matti Järvisalo}
+\author[uh]{Matti J\"arvisalo}
 \ead{matti.jarvisalo@helsinki.fi}
@@
 \address[jku] {
-Institute for Formal Models and Verification, Johannes Kepler University\\
+Institute for Formal Models and Verification, Johannes Kepler University, Austria\\
 {\tt nils.froleyks@jku.at}\\[1em]
@@
 \address[cmu] {
-Computer Science Department, Carnegie Mellon University\\
+Computer Science Department, Carnegie Mellon University, USA\\
 {\tt marijn@cmu.edu}\\[1em]
@@
 \address[kit] {
-KIT Department of Informatics\\
+Department of Informatics, Karlsruhe Institute of Technology, Germany \\
 {\tt markus.iser@kit.edu}\\[1em]
+}
+
+\address[uh] {
+HIIT, Department of Computer Science, University of Helsinki, Finland
+{\tt matti.jarvisalo@helsinki.fi}\\[1em]
 }
@@
 \begin{abstract}
-SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
-This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors could compete. 
-Another novelty was the application-specific sub-track of the main track, 
-where solvers competed in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
-We used new tools to select and distribute benchmark instances and their attributes. 
-In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
-It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
+The SAT Competitions constitute a well-established series of yearly open international competitive algorithm implementation competitions
+focusing on the Boolean satisfiability (or propositional satisfiability, SAT) problem. 
+In this article, we provide
+a detailed account on the 2020 instantiation of the SAT Competition, including the 
+ new competition tracks and benchmark selection procedures, overview of solving strategies implemented in top-performing solvers, 
+and a more detailed analysis of the empirical data obtained from running the competition.
+%SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
+%This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors could compete. 
+%Another novelty was the application-specific sub-track of the main track, 
+%where solvers competed in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
+%We used new tools to select and distribute benchmark instances and their attributes. 
+%In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
+%It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
 \end{abstract}
@@
 \begin{keyword}
-SAT, Competition
+SAT, Boolean satisfiability, SAT Competition, SAT solvers, empirical evaluation,
+benchmarking
 \end{keyword}
@@
 \section{Introduction}
+
+From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
+(or Boolean satisfiability, SAT) has flourished in practice into a success story of modern computer science.
+This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which form today a 
+central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
+With standardized inputformats, readily-available APIs for incrementalapplications,
+and certified proof logging andchecking capabilities, applications of SAT solver technology
+have branched from first breakthrough applications in automated planning, test pattern generation and hardware verification
+to thousands of different application settings.
+
+The success of SAT would not be without the persistent efforts of the SAT community to further develop the performance and robustness
+of SAT solvers. The SAT Competition series, which a history dating back to early 90s, aims to support and provide further incentives 
+for maintaining and furthering this progress. In particular,
+
+WILL CONTINUE FROM HERE -MATTI
+
+===
+
+OLD:
 
@@
 \todo{Maybe mention proceedings \cite{SC2020}}
+
+OLD END ===
 
@@
 By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
-In order to compile a balanced set of $300$ benchmark instances, we considered a maximium of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
+In order to compile a balanced set of $300$ benchmark instances, we considered a maximum of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
 Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
@@
 To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
-We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unkown result. 
+We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unknown result. 
 Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
@@
 originally written by Biere. The three configurations of \emph{Kissat} form a
-subcluster, even though the configurations are fairly distinct from each other.
+sub-cluster, even though the configurations are fairly distinct from each other.
 % , specialized for satisfiable and unsatisfiable instances.
@@
 
-The other subcluster consists of
+The other sub-cluster consists of
 modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
@@
 
-Another more recent string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-managment~\cite{Oh:2015:satunsat}. 
-The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heurstics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
-The then award winning variant \solver{MapleCOMSPS} is an implementation of a hybrid branching heuristic of classic Variable-State Independend Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+Another more recent string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-management~\cite{Oh:2015:satunsat}. 
+The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
+The then award winning variant \solver{MapleCOMSPS} is an implementation of a hybrid branching heuristic of classic Variable-State Independent Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
 
@@
 
-Kochemazov et al.
-improved three-tier clause-management by persting additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
+Kochemazov et al. improved three-tier clause-management by persting \todo{Please check "persting"!}
+additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
 As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning \solver{Maple} solver.
@@
 The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
-As of SAT Competition~2017, \solver{CaDiCaL} by Biere is another independent award winning and structured implementation of the state-of-the-art in SAT solving. 
-Its improved reimplementation \solver{Kissat} won in several of this competitions sequential tracks by a large margin~\cite{Biere:SC2020}.
+As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
+by Biere is another independent award winning and structured implementation of the state-of-the-art in SAT solving. 
+Its improved reimplementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.
 
@@
 Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
-The recent genealogy of all submissions, is highlighted by \emph{base solver} and \emph{variant} columns. 
+The recent genealogy of all submissions is highlighted by \emph{base solver} and \emph{variant} columns. 
 Underlined text is used to point out the important parts of the respective submissions name.
@@
 
-\solver{Kissat} uses a new unit (``ticks'') to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses, after conflict-rate has been obeserved to be too unstable for the use-case~\cite{Biere:SC2020}.
+\solver{Kissat} uses a new unit (``ticks'') to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses, after conflict-rate has been observed to be too unstable for the use-case~\cite{Biere:SC2020}.
 
@@
 
-The \solver{Relaxed} fork integrates short runs of the local search solver \solver{CCAnr} through periodic ex- and import of assignments~\cite{Xindi:SC2019}. 
+The \solver{Relaxed} fork integrates short runs of the local search solver \solver{CCAnr} through periodic export and import of assignments~\cite{Xindi:SC2019}. 
 The submitted versions of \solver{Relaxed Maple} use a probabilistic schedule for switching between $10$ phase selection modes. 
@@
 \solver{F2TRC} introduces an improved management of learned clauses in the tree tiers \emph{core}, \emph{tier2} and \emph{local} which are inherited from \solver{CoMinisatPS}~\cite{Oh:2015:satunsat}.
-A dynamic size limit for the \emph{core} tier, triggers the reassignment of inactive clauses from \emph{core} to \emph{tier2}. 
-To conter-act an observered starving of tier2, the conflict-based heuristic that controls demotion of clauses from \emph{tier2} to \emph{local} was replaced by a size based heuristic~\cite{Kochemazov:SC2020}.
+A dynamic size limit for the \emph{core} tier triggers the reassignment of inactive clauses from \emph{core} to \emph{tier2}. 
+To counter-act an observed starving of tier2, the conflict-based heuristic that controls demotion of clauses from \emph{tier2} to \emph{local} was replaced by a size based heuristic~\cite{Kochemazov:SC2020}.
 
@@
 
-\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}~\cite{Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32 core} and a \solver{64 core} variant and were awared three prices: first place in the Main track, first place in the Sat track and second in the Unsat track. 
+\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
+The authors submitted a \solver{32 core} and a \solver{64 core} variant and were awarded three prices: first place in the Main track, first place in the Sat track and second in the Unsat track. 
 The \solver{32 core} variant achieved slightly better scores than the \solver{64 core} variant. 
@@
 
-\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrenct data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies.
-
-\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random intialization of variable polarities~\cite{Balyo:2015:Hordesat}.
+\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrent data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies.
+
+\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random initialization of variable polarities~\cite{Balyo:2015:Hordesat}.
 However, a special solver instance performs concurrent clause strengthening~\cite{Wieringa:2013:CCS}. 
-Another special solver instance is configured to perform Gaussian eliminiation during preprocessing. 
+Another special solver instance is configured to perform Gaussian elimination during preprocessing. 
 \solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit.
@@
 The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
-\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achive deterministic solver behaviour~\cite{GlucoseSyrup}~\cite{ManySat}.
+\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{GlucoseSyrup}~\cite{ManySat}.
 
@@
 
-\solver{Painless Maple} received the award for second best performance in the Sat track but scored last in the Unsat track. 
+\solver{Painless Maple} received the award for the second best performance in the Sat track but scored last in the Unsat track. 
 \solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT}, which is a modified \solver{MapleLCMDistChronoBT} (see Main track), in the \solver{Painless} parallelization framework.
@@
 Each node performs a three-way merge of its local export and the two incoming buffers. 
-The aggragate that approaches the root of the binary tree is then broadcast to all solvers~\cite{}.
+The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{}.
 
@@
 \solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Glucose3,Toposat2}. 
-\solver{TopoSAT~2} uses lockfree clause-exchange for solvers running on the same maching, and MPI to share clauses between machines~\cite{ManySat,Proceedings}.
+\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and MPI \todo{Please spell out MPI once.}
+to share clauses between machines~\cite{ManySat,Proceedings}.
 
@@
 
-\solver{Slime} is build from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{SlimeSATRace2019}. 
+\solver{Slime} is built from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{SlimeSATRace2019}. 
 The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{}. 
@@
 \section*{Acknowledgements}
+Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.
 Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
-the Czech Science Foundataion project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
+the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
 

### 2021-01-07 paper/main.tex
the remaining tables

@@
 central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
-With standardized inputformats, readily-available APIs for incrementalapplications,
-and certified proof logging andchecking capabilities, applications of SAT solver technology
+With standardized input formats, readily-available APIs for incremental applications,
+and certified proof logging and checking capabilities, applications of SAT solver technology
 have branched from first breakthrough applications in automated planning, test pattern generation and hardware verification
@@
 of SAT solvers. The SAT Competition series, which a history dating back to early 90s, aims to support and provide further incentives 
-for maintaining and furthering this progress. In particular,
-
-WILL CONTINUE FROM HERE -MATTI
+for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
+in the form of SAT Races and SAT Challenge) have a consistent track record of receiving tens of solver submissions yearly, submitted
+by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
+the competition invite through open calls submissions of benchmark instances representing in particular new interesting applications 
+scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
+to construct on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.
+
+This article focuses on the 2020 instantiation of the SAT competitions. 
+To this end, we provide
+a detailed account of SAT Competition 2020 in terms of organizational details, competition tracks,
+participating solvers, benchmarks, and the empirical results from the competition.
+In terms of competition tracks, two new tracks, namely the cloud track and an application-specifc track, where introduced in 2020 
+in addition to the already earlier established main, parallel, and incremental tracks; we
+provide motivation and the new organizational details for both of the tracks.
+In terms of solvers, we provide an overview of solving strategies and other details implemented in top-performing solvers
+from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings.
+ As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
+an overview of the benchmarks contributed to the 2020 competition.
+In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
+on the SAT competition webpages (\url{https://satcompetition.github.io/2020/}). Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.
+
+The rest of this article is organized as follows. TODO -MJ
 
@@
 
-In this competition, we initiated a new application-specific sub-track. 
+In this competition, we initiated a new application-specific track. 
 The idea is to provide a large amount of benchmark instances of a specific application and to evaluate all solvers with respect to these instance in a special track. 
-In this competition, we used 200 instances of the planning domain to run a planning sub-track.
+In this competition, we used 200 instances of the planning domain to run a planning track.
 
@@
 
-SAT Competition 2020 consisted of four tracks:
-the Main track, Incremental Library track, Parallel track,
-and the Cloud Track for massively parallel SAT solvers using up to 1024 cores. 
-Furthermore, the Main track comprised of several sub-tracks.
-
-\subsubsection{Main Track}
+SAT Competition 2020 consisted of seven tracks:
+Main track, No-Limits track, Planning track, ``Glucose hack'' track,
+Incremental Library track, Parallel track,
+and the Cloud Track for massively parallel SAT solvers. % using up to 1024 cores.
+
+\subsubsection{The Main, No-Limits, Planning, and ``Glucose hack'' tracks}
 
@@
 
-Solvers not complying with either of the above criteria were only evaluated in a so-called No-Limits sub-track and were not eligible for the Main track awards.
-The No-Limits thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
-However, solvers in No-Limits still competed against all other solvers in the Main Track (hence, we consider it a sub-track).
-The No-Limits sub-track was only evaluated with respect to the benchmarks instances which were \emph{newly} submitted to SAT Competition 2020.
-
-Part of the Main track was the Planning sub-track, in which we evaluated the solvers on 200 benchmarks 
+Solvers not complying with either of the above criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
+The No-Limits thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) 
+as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
+However, solvers in No-Limits still competed against all other solvers submitted to the Main Track.
+Thus, to deserve a mention, a No-Limits solver would need to beat all the Main Track participants.
+The No-Limits track was only evaluated with respect to the benchmarks instances which were \emph{newly} submitted to SAT Competition 2020.
+
+The same rules for participation as in Main track applied to the Planning track, in which we evaluated the solvers on 200 benchmarks 
 which all came from the same application domain -- automated planning. 
-Solver submitted to the Main track automatically participated in the Planning sub-track.
-It is envisioned, that also in the future there will be an application sub-track of the Main track, each time highlighting a different area where the SAT solving technology helps to advance the state of the art.
+Solver submitted to the Main track automatically participated in the Planning track.
+It is envisioned that also in the future there will be an ``application promotion'' track,
+each time highlighting a different area where the SAT solving technology helps to advance the state of the art.
 
@@
 The source code of submitted SAT solvers had to be made available 
-(licensed for research purposes) except for the solvers participating only in the No-Limits sub-track.
+(licensed for research purposes) except for the solvers participating only in the No-Limits track.
 
@@
 
-Apart from the No-limits sub-track, participants were not allowed to submit a portfolio of solvers,
+Apart from the No-limits track, participants were not allowed to submit a portfolio of solvers,
 i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{
@@
 Solvers were ranked using a PAR-2 score based on a \num{5000}-second timeout.
-A PAR-2 system assigns as many points as the number of seconds it took the solver
+A PAR-2 system assigns as many points as the amount of time (in seconds) it took the solver
 to solve a particular instance and twice the time limit, i.e.~\num{10000} points,
 if the instance was not solved. This means that lowers scores are better.
-We generally report the average score of each solver
-across a benchmark set.
+We generally report the \emph{average score} of each solver across a benchmark set.
 
@@
 On the other hand, certificates for unsatisfiable instances (proofs) were required only 
-in the Main track (besides the No Limits sub-track).
+in the Main track (besides the No Limits track).
 
@@
 \label{sec:computing}
-The Main Track with its sub-tracks was run on the StarExec cluster \cite{starexec},
+The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec},
 whose nodes are equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
@@
 
+\begin{table}
+\caption{Main ALL}
+\label{tab:mainALL}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+1  & 3926.2 & 264 & {\bf Kissat-sc2020-sat} \\
+(1)& 4083.1 & 260 & Kissat-sc2020-default \\
+2  & 4179.3 & 253 & {\bf Relaxed\_LCMDCBDL\_newTech} \\
+3  & 4266.7 & 248 & {\bf cryptominisat-ccnr-lsids} \\
+(3)& 4278.0 & 250 & cryptominisat-ccnr \\
+   & 4428.1 & 250 & cadical-alluip-trail \\
+   & 4429.6 & 250 & cadical-alluip \\
+   & 4436.5 & 245 & Relaxed\_LCMDCBDL \\
+   & 4501.2 & 243 & cryptominisat-walksat \\
+   & 4554.0 & 243 & cadical-trail \\
+   & 4560.0 & 238 & Kissat-sc2020-unsat \\
+   & 4607.6 & 246 & CaDiCaL-sc2020 \\
+   & 5157.7 & 216 & Undominated-LC-MapleLCMDiscChronoBT-DL \\
+   & 5159.6 & 220 & MapleLCMDistChronoBT-DL-f2trc \\
+   & 5177.0 & 214 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\   
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Main SAT}
+\label{tab:mainSAT}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+ 1 & 2997.4 & 150 & {\bf Relaxed\_LCMDCBDL\_newTech} \\
+ 2 & 3127.6 & 146 & {\bf Kissat-sc2020-sat} \\
+ 3 & 3263.0 & 144 & {\bf cryptominisat-ccnr-lsids} \\
+(3)& 3317.4 & 145 & cryptominisat-ccnr \\
+   & 3355.5 & 143 & Relaxed\_LCMDCBDL \\
+   & 3524.7 & 140 & cryptominisat-ccnr-nolimits \\
+   & 3622.4 & 138 & cryptominisat-ccnr-lsids-nolimits \\
+   & 3703.7 & 140 & cryptominisat-walksat-nolimits \\
+   & 3721.2 & 139 & cryptominisat-walksat \\
+   & 3830.5 & 134 & Kissat-sc2020-default \\
+   & 3908.5 & 135 & cadical-alluip-trail \\
+   & 3909.6 & 135 & cadical-alluip \\
+   & 4265.6 & 126 & cadical-trail \\
+   & 4368.6 & 130 & CaDiCaL-sc2020 \\
+   & 4804.9 & 114 & Kissat-sc2020-unsat \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Main UNSAT}
+\label{tab:mainUNSAT}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+1  & 4315.1 & 124 & {\bf Kissat-sc2020-unsat} \\
+(1)& 4335.6 & 126 & Kissat-sc2020-default \\
+(1)& 4724.8 & 118 & Kissat-sc2020-sat \\
+ 2 & 4842.5 & 117 & {\bf cadical-trail} \\
+-- & 4846.7 & 116 & CaDiCaL-sc2020 \\
+(2)& 4947.8 & 115 & cadical-alluip-trail \\
+(2)& 4949.6 & 115 & cadical-alluip \\
+ 3 & 4991.4 & 110 & {\bf MapleLCMDistChronoBT-f2trc-s} \\
+(3)& 5051.4 & 109 & MapleLCMDistChronoBT-f2trc \\
+(3)& 5054.3 & 110 & MapleLCMDistChronoBT-DL-f2trc \\
+   & 5069.6 & 109 & Maple\_mix \\
+   & 5110.0 & 107 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\
+   & 5126.9 & 107 & Maple\_simp \\
+   & 5128.9 & 107 & MapleLCMDistChronoBT-DL-v3 \\
+   & 5142.2 & 106 & Undominated-LC-MapleLCMDiscChronoBT-DL \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Planning (ALL)}
+\label{tab:planning}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+ 1 & 6406.9 & 80 & {\bf cadical-alluip-trail} \\
+(1)& 6409.3 & 80 & cadical-alluip \\
+ 2 & 6466.9 & 79 & {\bf cryptominisat-ccnr-lsids} \\
+(2)& 6471.9 & 79 & cryptominisat-ccnr \\
+(2)& 6472.9 & 79 & cryptominisat-walksat \\
+ 3 & 6596.4 & 75 & {\bf Kissat-sc2020-unsat} \\
+   & 6650.1 & 79 & cadical-trail \\
+   & 6713.0 & 75 & Maple\_mix \\
+   & 6746.5 & 75 & MapleCOMSPS\_LRB\_VSIDS\_2\_\_LRB\_VSIDS\_2\_init \\
+   & 6754.3 & 73 & Maple\_simp \\
+   & 6773.0 & 73 & MapleCOMSPS\_LRB\_VSIDS\_2\_\_default\_drup \\
+   & 6773.9 & 73 & Kissat-sc2020-sat \\
+   & 6774.2 & 73 & Kissat-sc2020-default \\
+   & 7003.0 & 69 & optsat\_m20 \\
+   & 7025.5 & 68 & upGlucose-3.0\_PADC \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Parallel (ALL)}
+\label{tab:parallelALL}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+ 1 & 3316.6 & 283 & {\bf pmcompspsthirty} \\
+(1)& 3714.7 & 271 & pmcompspsixty \\
+ 2 & 3743.4 & 269 & {\bf plingeling} \\
+ 3 & 3985.3 & 260 & {\bf manyglucosethirty} \\
+   & 4022.7 & 262 & painlessmaplevone \\
+   & 4036.3 & 258 & manyglucosesixty \\
+   & 4103.3 & 260 & painlessmaplevtwo \\
+   & 4433.3 & 243 & syrupscavel \\
+   & 4903.4 & 225 & treengeling \\
+   & 5240.1 & 213 & abcdsatptwenty \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Parallel (SAT)}
+\label{tab:parallelSAT}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+ 1 & 2853.7 & 153 & {\bf pmcompspsthirty} \\
+ 2 & 2913.6 & 154 & {\bf painlessmaplevone} \\
+(2)& 3082.7 & 151 & painlessmaplevtwo \\
+(1)& 3196.9 & 148 & pmcompspsixty \\
+ 3 & 3805.9 & 133 & {\bf plingeling} \\
+   & 4048.3 & 130 & manyglucosesixty \\
+   & 4076.2 & 130 & manyglucosethirty \\
+   & 4675.4 & 119 & syrupscavel \\
+   & 4907.1 & 114 & treengeling \\
+   & 6337.5 & 85 & abcdsatptwenty \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Parallel (UNS)}
+\label{tab:parallelUNS}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+ 1 & 3680.8 & 136 & {\bf plingeling} \\
+ 2 & 3779.5 & 130 & {\bf pmcompspsthirty} \\
+ 3 & 3894.3 & 130 & {\bf manyglucosethirty} \\
+(3)& 4024.2 & 128 & manyglucosesixty \\
+   & 4142.8 & 128 & abcdsatptwenty \\
+   & 4191.1 & 124 & syrupscavel \\
+   & 4232.5 & 123 & pmcompspsixty \\
+   & 4899.8 & 111 & treengeling \\
+   & 5123.9 & 109 & painlessmaplevtwo \\
+   & 5131.9 & 108 & painlessmaplevone \\
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Claud (ALL)}
+\label{tab:claud}
+\begin{tabular}{cccl}
+place & PAR-2 score & num. solved & solver \\
+\hline
+ 1 & 2603.8 & 299 & {\bf mallobecs} \\
+ 2 & 3146.8 & 278 & {\bf toposat} \\
+ 3 & 4797.6 & 213 & {\bf slime} \\
+   & 6800.8 & 132 & paracooba \\
+   & 7299.0 & 110 & ctsat \\
+   & 8468.3 & 62 & paracoobamarch \\
+\end{tabular}
+\end{table}
+
 \todo{New Codebases}
@@
 
-\subsection{Planning Sub-Track}
+\subsection{Planning Track}
 % - 86 out of 100 biggest (number of clauses) are planning
@@
 % - all 200 above 90\% binary clauses and half have above 99%
-The instances of the planning sub-track are big compared to the rest of the
+The instances of the planning track are big compared to the rest of the
 main track. Using the number of clauses as a metric; out of the $100$ biggest
@@
 Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
-The variants including \emph{Stable AllUIP} were the most successful and won the first price in the Planning Sub-Track.
+The variants including \emph{Stable AllUIP} were the most successful and won the first price in the Planning Track.
 
@@
 
+\section{More detailed analysis of the Main track results (to be renamed)}
+
+In this section, we provide additional views on the Main track results,
+in particular focusing on metrics which help to highlight strengths
+
+\subsection{Contributions to VBS}
+
+Everything could be done separately for (ALL, SAT, UNSAT)
+
+3X VBS
+
+Greedy cover
+
+Fair split strategy
+
+Z3 strategy
+
+Maxent Nash
+
+Van Gelder ?
+
 \section{Conclusion and Prospects}

### 2021-01-08 paper/main.tex
one sentence

@@
 In this section, we provide additional views on the Main track results,
-in particular focusing on metrics which help to highlight strengths
+focusing on metrics complementing the PAR-2 score, 
+which we used for ranking the solvers in the actual competition.
 

### 2021-01-11 paper/main.tex
ranking robustness plot dump

@@
    & 4907.1 & 114 & treengeling \\
-   & 6337.5 & 85 & abcdsatptwenty \\
+   & 6337.5 & \phantom{0}85 & abcdsatptwenty \\
 \end{tabular}
@@
    & 7299.0 & 110 & ctsat \\
-   & 8468.3 & 62 & paracoobamarch \\
+   & 8468.3 & \phantom{0}62 & paracoobamarch \\
 \end{tabular}
@@
 
+\includegraphics[width=0.5\textwidth]{stability/50-50-sat-unsat_random_sampling_scores.png}%
+\includegraphics[width=0.5\textwidth]{stability/276_instances_random_sampling_scores.png}
+\includegraphics[width=0.5\textwidth]{stability/ALL_random_smpling_correlations.png}%
+\includegraphics[width=0.5\textwidth]{stability/SAT_randomSampling_correlations.png}
+\includegraphics[width=0.5\textwidth]{stability/UNSAT_randomSampling_correlations.png}
+
+\includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
+
 \subsection{Observations}
@@
 
-Kochemazov et al. improved three-tier clause-management by persting \todo{Please check "persting"!}
+Kochemazov et al. improved three-tier clause-management by persisting
 additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
@@
 
-\multirow{3}{*}{Zhang, Cai}
-    & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
- &  & \solbert{Rel. noTimeParam} & \\
+\multirow{2}{*}{Zhang, Cai}
+    & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
+% &  & \solbert{Rel. noTimeParam} & \\
  &  & \solbert{Rel. newTech} & \secondo, \firsts\\
@@
 The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
-\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{GlucoseSyrup}~\cite{ManySat}.
+\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
 
@@
 
-\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSAT}. 
+\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
 \solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
@@
 Each node performs a three-way merge of its local export and the two incoming buffers. 
-The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{}.
+The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{Schreiber:SC2020}.
 
@@
 Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
-Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{}.
+Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{Schreiber:SC2020}.
 
@@
 
-\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Glucose3,Toposat2}. 
-\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and MPI \todo{Please spell out MPI once.}
-to share clauses between machines~\cite{ManySat,Proceedings}.
-
+\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
+\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
 \solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
-\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting.
+\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.
 
@@
 
-\solver{Slime} is built from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{SlimeSATRace2019}. 
-The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{}. 
+\solver{Slime} is built from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{Riveros:SC2019}. 
+The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{Riveros:SC2020}. 
 Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} won the third price in the Cloud track.
@@
 
-\subsection{Contributions to VBS}
-
-Everything could be done separately for (ALL, SAT, UNSAT)
-
-3X VBS
-
-Greedy cover
-
-Fair split strategy
-
-Z3 strategy
-
-Maxent Nash
-
-Van Gelder ?
+\subsection{Contributions to the Virtual Best Solver}
+
+The Virtual Best Solver (VBS) is a fictitious solver consisting 
+of all the solvers that actually participated in the competition (or a specific track)
+and an oracle which, when given an input instance,
+invokes to run the actual solver which performed the best on that instance.
+In this way, the performance of the VBS highlights a certain upper bound 
+on performance achievable in principle by the technology 
+of the participating solvers (cf. the figures in Section~\ref{sec:results}).
+
+One can see that the VBS solves all the instances that
+were solved by at least one solver and solves each instance in the best observed time.
+By quantifying how much each participating solver contributes
+to the performance of the VBS, we may attempt to establish which
+technology (as represented by the solvers) is the most important
+(and to what degree) in the observed state of the art of SAT solving.
+We came up with the following three related metrics conceptually derived
+from the notion of VBS:
+\begin{description}
+\item[VBS1]
+``The fastest takes it all'':
+For each solver we count the number of times, it was the fastest to solve an instance.
+\item[VBS2]
+``Time aware, but proportional'':
+A solver $S$ solving an instance $I$ in time $T^S_I$ accrues 
+the following fraction of a point for solving $I$:
+$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
+\item[VBS3]
+``Split the point for solving'':
+We award each solver $S$ solving an instance $I$ the fraction $1/|\mathcal{S}_I|$ of points, where
+$\mathcal{S}_I$ is the set of solvers solving $I$.
+\end{description}
+We remark that the sum of VBS1 points, as well as VBS3 points, computed across all the solvers
+is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
+This is obvious for VBS1, as exactly one solver scores a point for solving an instance.
+In the case of VBS3, where we discard the information about the solution times, 
+we evenly split the one point reward for solving an instance to those solvers which were successful on it.
+
+In contrast, VBS2 does not have this property as it in general distributes more than one point per instance.
+Similarly to VBS1, it takes the solution time into account,
+and similarly to VBS3 it does not award just the best solver on an instance.
+For example, being twice as slow on an instance than the fastest solver results in a half point awarded.
+And, if all the solvers solve an instance with the same solution time,
+each solver scores a whole point for that instance.
+
+\begin{table}
+\caption{VBS metrics for the results of the Main track, all instances. 
+The total number of solved problems was 317. 
+There were 60 (non-disqualified) solvers (and their configurations).
+Each table shows the first ten solvers sorted according to the respective metric.}
+\label{tab:vbsMainALL}
+\begin{center}
+\begin{tabular}{ccl}
+VBS1 & percent total & solver \\
+\hline
+46 & 11.5 & Kissat-sc2020-unsat \\
+37 & \phantom{0}9.2 & Kissat-sc2020-sat \\
+22 & \phantom{0}5.5 & Kissat-sc2020-default \\
+14 & \phantom{0}3.5 & Maple\_CM+dist+sattime2s+- \\
+13 & \phantom{0}3.2 & cryptominisat-ccnr-lsids \\
+13 & \phantom{0}3.2 & Maple-LCM-Dist-alluip-trail \\
+12 & \phantom{0}3.0 & Relaxed\_LCMDCBDL \\
+11 & \phantom{0}2.8 & upGlucose-3.0\_PADC \\
+10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
+\phantom{0}9 & \phantom{0}2.2 & Maple\_CMused+dist \\
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{ccl}
+VBS2 & percent total & solver \\
+\hline
+129.8 & 32.4 & Kissat-sc2020-sat \\
+120.1 & 30.0 & Kissat-sc2020-default \\
+113.6 & 28.4 & Kissat-sc2020-unsat \\
+\phantom{0}91.0 & 22.7 & cryptominisat-ccnr-lsids \\
+\phantom{0}87.0 & 21.7 & cryptominisat-ccnr \\
+\phantom{0}82.0 & 20.5 & cadical-alluip-trail \\
+\phantom{0}81.9 & 20.5 & cadical-alluip \\
+\phantom{0}81.8 & 20.5 & CaDiCaL-sc2020 \\
+\phantom{0}81.0 & 20.2 & Relaxed\_LCMDCBDL\_newTech \\
+\phantom{0}80.5 & 20.1 & Relaxed\_LCMDCBDL \\
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{ccl}
+VBS3 & percent total & solver \\
+\hline
+11.7 & 2.9 & Kissat-sc2020-default \\
+10.8 & 2.7 & Kissat-sc2020-unsat \\
+10.4 & 2.6 & Relaxed\_LCMDCBDL\_newTech \\
+\phantom{0}9.9 & 2.5 & Kissat-sc2020-sat \\
+\phantom{0}9.8 & 2.4 & cadical-alluip \\
+\phantom{0}9.8 & 2.4 & cadical-alluip-trail \\
+\phantom{0}9.4 & 2.3 & Relaxed\_LCMDCBDL \\
+\phantom{0}9.4 & 2.3 & CaDiCaL-sc2020 \\
+\phantom{0}8.7 & 2.2 & cadical-trail \\
+\phantom{0}8.3 & 2.1 & cryptominisat-walksat \\
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}
+\caption{VBS metrics for the results of the Main track, SAT instances. 
+The total number of solved problems was 183. 
+There were 60 (non-disqualified) participating solvers.
+Each table always shows the first ten solvers sorted according to the respective metric.}
+\label{tab:vbsMainSAT}
+\begin{center}
+\begin{tabular}{ccl}
+VBS1 & percent total & solver \\
+\hline
+27 & 14.8 & Kissat-sc2020-sat \\
+14 & \phantom{0}7.7 & Maple\_CM+dist+sattime2s+- \\
+12 & \phantom{0}6.6 & Kissat-sc2020-default \\
+10 & \phantom{0}5.5 & Relaxed\_LCMDCBDL \\
+\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
+\phantom{0}8 & \phantom{0}4.4 & Kissat-sc2020-unsat \\
+\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids-nolimits \\
+\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids \\
+\phantom{0}6 & \phantom{0}3.3 & cadical-trail \\
+\phantom{0}6 & \phantom{0}3.3 & cryptominisat-ccnr-nolimits \\
+
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{ccl}
+VBS2 & percent total & solver \\
+\hline
+68.5 & 37.4 & Kissat-sc2020-sat \\
+46.3 & 25.3 & Kissat-sc2020-default \\
+44.1 & 24.1 & cryptominisat-ccnr-lsids \\
+42.2 & 23.0 & Relaxed\_LCMDCBDL\_newTech \\
+41.8 & 22.9 & cryptominisat-ccnr-lsids-nolimits \\
+40.9 & 22.3 & cryptominisat-ccnr \\
+40.6 & 22.2 & Relaxed\_LCMDCBDL \\
+39.4 & 21.5 & cryptominisat-ccnr-nolimits \\
+35.2 & 19.2 & cryptominisat-walksat-nolimits \\
+32.8 & 17.9 & cryptominisat-walksat \\
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{ccl}
+VBS3 & percent total & solver \\
+\hline
+8.0 & 4.4 & Relaxed\_LCMDCBDL\_newTech \\
+7.0 & 3.8 & Relaxed\_LCMDCBDL \\
+6.5 & 3.6 & cryptominisat-walksat-nolimits \\
+5.8 & 3.2 & cryptominisat-walksat \\
+5.6 & 3.0 & Kissat-sc2020-sat \\
+5.4 & 3.0 & cryptominisat-ccnr-lsids \\
+5.4 & 3.0 & Kissat-sc2020-default \\
+5.4 & 2.9 & cryptominisat-ccnr \\
+5.2 & 2.8 & cadical-alluip \\
+5.2 & 2.8 & cadical-alluip-trail \\
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}
+\caption{VBS metrics for the results of the Main track, UNSAT instances. 
+The total number of solved problems was 134. 
+There were 60 (non-disqualified) participating solvers.
+Each table always shows the first ten solvers sorted according to the respective metric.}
+\label{tab:vbsMainUNSAT}
+\begin{center}
+\begin{tabular}{ccl}
+VBS1 & percent total & solver \\
+\hline
+38 & 28.4 & Kissat-sc2020-unsat \\
+11 & \phantom{0}8.2 & Maple-LCM-Dist-alluip-trail \\
+10 & \phantom{0}7.5 & Kissat-sc2020-default \\
+10 & \phantom{0}7.5 & Kissat-sc2020-sat \\
+\phantom{0}8 & \phantom{0}6.0 & Maple\_CMused+dist \\
+\phantom{0}6 & \phantom{0}4.5 & cryptominisat-ccnr-lsids \\
+\phantom{0}6 & \phantom{0}4.5 & upGlucose-3.0\_PADC \\
+\phantom{0}3 & \phantom{0}2.2 & MapleLCMDistChronoBT-f2trc \\
+\phantom{0}3 & \phantom{0}2.2 & glucose3.0\_\_proofs \\
+\phantom{0}3 & \phantom{0}2.2 & DurianSat \\
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{ccl}
+VBS2 & percent total & solver \\
+\hline
+86.3 & 64.4 & Kissat-sc2020-unsat \\
+73.8 & 55.1 & Kissat-sc2020-default \\
+61.3 & 45.7 & Kissat-sc2020-sat \\
+55.4 & 41.3 & MapleLCMDistChronoBT-f2trc-s \\
+55.0 & 41.0 & DurianSat \\
+53.6 & 40.0 & Maple-LCM-Dist-alluip-trail \\
+53.3 & 39.8 & MapleLCMDistChronoBT-f2trc \\
+52.4 & 39.1 & MapleLCMDistChronoBT-DL-f2trc \\
+51.7 & 38.6 & Maple\_CMused+dist \\
+51.6 & 38.5 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\
+\end{tabular}
+\end{center}
+\begin{center}
+\begin{tabular}{ccl}
+VBS3 & percent total & solver \\
+\hline
+6.7 & 5.0 & Kissat-sc2020-unsat \\
+6.2 & 4.7 & Kissat-sc2020-default \\
+4.6 & 3.4 & cadical-trail \\
+4.6 & 3.4 & cadical-alluip \\
+4.6 & 3.4 & cadical-alluip-trail \\
+4.3 & 3.2 & Kissat-sc2020-sat \\
+4.2 & 3.1 & CaDiCaL-sc2020 \\
+3.4 & 2.5 & MapleLCMDistChronoBT-f2trc-s \\
+3.3 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
+3.0 & 2.3 & MapleLCMDistChronoBT-DL-f2trc \\
+\end{tabular}
+\end{center}
+\end{table}
+
+\todo{Probably hide tab:vbsMainSAT and tab:vbsMainUNSAT.}
+
+Table~\ref{tab:vbsMainALL} renders the just described three metrics applied 
+to the full results of the Main track. We can see that the respective leaderboards 
+are generally dominated by Kissat-sc2020 and its configurations.
+VBS1 tells us that Kissat-sc2020-unsat was most often the fastest solver,
+in particular on \SI{11.5}{\percent} of all the solved instances.
+
+VBS2 highlights as first Kissat-sc2020-sat. Its leading \SI{32.4}{\percent} of total is a bit harder to 
+interpret: A solver can score \SI{32.4}{\percent} of VBS2 total
+by solving \SI{32.4}{\percent} of the solved instances in the best observed time
+and no others. But we know, thanks to its VBS1, that Kissat-sc2020-sat solved \SI{9.2}{\percent}
+of the solved instances in the best observed time (and some others).
+A solver can also score \SI{32.4}{\percent} of VBS2 total by solving all the solved instances,
+but always being roughly 3 times slower than the VBS. 
+Kissat-sc2020-sat lies obviously somewhere between these two extremes.
+
+Finally, according to VBS3, the best solver is Kissat-sc2020-default with 11.7 points,
+which amounts to \SI{2.9}{\percent} of the distributed total score.
+The VBS3 metric is generally the most evenly distributed one,
+at least among the first 10 solvers.
+(The last solver got 0.5 points which is \SI{0.123}{\percent} of total.)
+One can conclude from this that most of the benchmarks are solved
+by most of the well performing solvers.
+
+\subsection{Greedy set cover}
+Another perspective on how much each solver contributes to the state of the art
+can be obtained by attempting to construct a sequential schedule of solvers 
+(rather then relying on an oracle to pick one for each instance, as with VBS)
+and looking at how big role each solvers plays in such a schedule. Since constructing 
+an optimal schedule tends to be computationally hard, we start here by 
+presenting a useful efficient alternative -- a greedy set cover approach.
+
+With greedy set cover, we start with an empty schedule and iteratively consider 
+each solver for the addition to the schedule obtained so far, picking the one
+with the highest ``marginal contribution'' in terms of the number of problems
+the new schedule will be able to solve. This is perhaps best demonstrated on
+the actual data from the competition, again taking the Main track results.
+
+\begin{table}
+\caption{A greedy set cover of the solved instances by solvers of the Main track.}
+\label{tab:gscMain}
+\begin{center}
+\begin{tabular}{clccc}
+Iteration & selected solver & (num. solved) & contributes & covered so far \\
+\hline
+\phantom{0}1 & Kissat-sc2020-sat & 264 & 264 & 264 \\
+\phantom{0}2 & cadical-alluip & 250 & \phantom{0}22 & 286 \\
+\phantom{0}3 & MapleLCMDistChronoBT-f2trc-s & 214 & \phantom{0}10 & 296 \\
+\phantom{0}4 & Relaxed\_LCMDCBDL\_newTech & 253 & \phantom{00}6 & 302 \\
+\phantom{0}5 & Kissat-sc2020-unsat & 238 & \phantom{00}4 & 306 \\
+\phantom{0}6 & cryptominisat-walksat & 243 & \phantom{00}3 & 309 \\
+\phantom{0}7 & Relaxed\_LCMDCBDL & 245 & \phantom{00}3 & 312 \\
+\phantom{0}8 & cryptominisat-ccnr-lsids & 248 & \phantom{00}1 & 313 \\
+\phantom{0}9 & exp\_V\_LGB\_MLD\_CBT\_DL & 194 & \phantom{00}1 & 314 \\
+10 & MapleLCMDistChronoBT-DL-f2trc & 220 & \phantom{00}1 & 315 \\
+11 & MapleLCMDistChronoBT-DL-v3 & 211 & \phantom{00}1 & 316 \\
+12 & cryptominisat-walksat-nolimits & 140 & \phantom{00}1 & 317 \\
+
+\end{tabular}
+\end{center}
+\end{table}
+
+A greedy set cover of the solved instances by solvers of the Main track is presented 
+in Table~\ref{tab:gscMain}. In the first iteration, the solver which solved the highest number 
+of instances is selected; in our case it was Kissat-sc2020-sat with 264 instances
+as we know already from Table~\ref{tab:mainALL}.
+Given those 264 instances as already covered, cadical-alluip was the best in further contributing
+to the set by additional 22 instances in iteration 2.
+We can see that the further iterations tend to add very little,
+with the final 5 iterations adding one instance each. Note that each solver
+that managed to solve an instance uniquely (i.e.~being the only solver to do so)
+is showing up in the table. This is, for example the case of last listed  
+cryptominisat-walksat-nolimits with otherwise relatively low number of solved instances (140).
+Highlighting unique solutions is a property of the greedy set cover metric
+which we believe is congruent with documenting contributions to the state of the art.
+
+\subsection{Time-limited schedules}
+
+The greedy set cover technique focuses only on solving the ``solvable'' instances,
+disregarding the time it would take to execute the obtained schedule. We can
+also look at schedules that would fit in a prescribed time budget. A natural choice
+of the budget seems to be the original time limit of \SI{5000}{\second}.
+
+\begin{table}
+\caption{``Uniform time split'' schedules %using $i$ solvers 
+to solve as many Main track instances as possible.}
+\label{tab:MainUniformTimeSplit}
+\begin{center}
+\begin{tabular}{cccl}
+\# solvers & time (s) & total solved & best schedule \\
+\hline
+1 & 5000 & 264 & Kissat-sc2020-sat \\
+2 & 2500 & 278 & Kissat-sc2020-unsat, \\
+             &&& Relaxed\_LCMDCBDL\_newTech \\
+3 & 1666 & 272 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
+			 &&& cryptominisat-ccnr-lsids \\
+4 & 1250 & 262 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
+			 &&& cryptominisat-ccnr-lsids, Maple-LCM-Dist-alluip-trail \\ 
+5 & 1000 & 253 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
+			&&& cryptominisat-ccnr-lsids, \\
+			&&& Maple-LCM-Dist-alluip-trail, cadical-alluip \\
+\end{tabular}
+\end{center}
+\end{table}
+
+By employing a brute-force approach we first constructed a sequences of schedules 
+where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
+$i$ solvers and solves the highest number of instances under these constraints.
+The results are presented in Table~\ref{tab:MainUniformTimeSplit}.
+We can see that the initial increase from 264 to 278 of ``covered'' instances 
+when using two solvers instead of one (although allowing each to only use half of the time)
+does not continue further with additional solvers allowed,
+although its still better to use three solvers in a fair time split 
+(and cover 272 instances) than just one.
+One could use this observation to conjecture that the really hard 
+problems that were solved actually require quite a large time to 
+get ``cracked'' by any solver and thus the advantage of adding more solvers to the schedule
+quickly diminishes.
+
+We complemented ...
+
+\newpage
 

### 2021-01-11 paper/main.tex

@@
 \newcommand{\thirdp}{\colorbox{cupper}{\texttt{P3}}}
+
+\definecolor{redorange}{rgb}{0.878431, 0.235294, 0.192157}
+\definecolor{lightblue}{rgb}{0.552941, 0.72549, 0.792157}
+\definecolor{clearyellow}{rgb}{0.964706, 0.745098, 0}
+\definecolor{clearorange}{rgb}{0.917647, 0.462745, 0}
+\definecolor{mildgray}{rgb}{0.54902, 0.509804, 0.47451}
+\definecolor{softblue}{rgb}{0.643137, 0.858824, 0.909804}
+\definecolor{bluegray}{rgb}{0.141176, 0.313725, 0.603922}
+\definecolor{lightgreen}{rgb}{0.709804, 0.741176, 0}
+\definecolor{redpurple}{rgb}{0.835294, 0, 0.196078}
+\definecolor{midblue}{rgb}{0, 0.592157, 0.662745}
+\definecolor{clearpurple}{rgb}{0.67451, 0.0784314, 0.352941}
+\definecolor{browngreen}{rgb}{0.333333, 0.313725, 0.145098}
+\definecolor{darkestpurple}{rgb}{0.396078, 0.113725, 0.196078}
+\definecolor{greypurple}{rgb}{0.294118, 0.219608, 0.298039}
+\definecolor{darktruqoise}{rgb}{0, 0.239216, 0.298039}
+\definecolor{darkbrown}{rgb}{0.305882, 0.211765, 0.160784}
+\definecolor{midgreen}{rgb}{0.560784, 0.6, 0.243137}
+\definecolor{darkred}{rgb}{0.576471, 0.152941, 0.172549}
+\definecolor{darkpurple}{rgb}{0.313725, 0.027451, 0.470588}
+\definecolor{darkestblue}{rgb}{0, 0.156863, 0.333333}
+\definecolor{lightpurple}{rgb}{0.776471, 0.690196, 0.737255}
+\definecolor{softgreen}{rgb}{0.733333, 0.772549, 0.572549}
+\definecolor{offwhite}{rgb}{0.839216, 0.823529, 0.768627}
 
@@
 
+\subsection{Best Tuples and Triples}
+
+When selecting solvers for instance-specific algorithm selection, it is interesting to know about the complementarity of the performance of solvers. 
+We created analyzed all pairs and triples of submitted solvers and calculated the PAR-2 score of the VBS of the resulting set of solvers.
+
+\begin{table}
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+Solver 1 & Solver 2 & VBS score \\
+\hline
+\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \\
+\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
+\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
+\solver{Kissat unsat} & \solver{CryptoMiniSat-CCAnr LSIDS} & \\
+\solver{Kissat} & \solver{Relaxed Maple newTech} & \\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\begin{tabular}{|l|l|l|l|}
+\hline
+Solver 1 & Solver 2 & Solver 3 & VBS score \\
+\hline
+\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-Walksat} & \\
+\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{MapleCOMSPS\_LRB\_VSIDS\_2 init} &  \\
+\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-CCAnr} & \\
+\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip\_trail} & \\
+\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip} & \\
+\hline
+\end{tabular}
+\end{table}
+
 \section{Conclusion and Prospects}

### 2021-01-11 paper/main.tex
z3 schedule

@@
 
-The greedy set cover technique focuses only on solving the ``solvable'' instances,
+The greedy set cover technique focuses only on solving instances,
 disregarding the time it would take to execute the obtained schedule. We can
@@
 
-We complemented ...
-
-\newpage
+We complemented this ``uniform time split'' schedule by formulating the schedule construction
+problem as a MaxSMT formula and using the Z3 SMT solver \cite{DBLP:conf/tacas/MouraB08} in its optimization mode \cite{DBLP:conf/sycss/BjornerP14} to solve it.
+For each solver (and its configuration) $S$ we introduced an integer variable $R^S$ denoting 
+the number of seconds $S$ will run in the new schedule. We then constructed a formula with the hard
+constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one 
+soft constraint for every instance $I$ of the form
+\[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
+where $\mathcal{S}_I$ is the set of solvers which solved the instance $I$ and $T^S_I$ is the time it took solver $S$ to solve $I$ here rounded up to the nearest integer.
+(Note that while $R^S$ are variables, i.e.~unknowns, the $T^S_I$ are known constants in the formula.)
+
+\begin{table}
+\caption{TODO}
+\label{tab:MainZ3Schedule}
+\begin{center}
+\begin{tabular}{lccc}
+solver & taking up (s) & solving & contributes \\
+\hline
+Kissat-sc2020-unsat & 2523 & 219 & 219 \\
+Relaxed\_LCMDCBDL\_newTech & 2180 & 234 & \phantom{0}59 \\
+Kissat-sc2020-sat & 103 & \phantom{0}72 & \phantom{00}2 \\
+MapleLCMDistChronoBT-DL-f2trc & \phantom{0}76 & \phantom{0}15 & \phantom{00}0 \\
+cadical-alluip & \phantom{0}58 & \phantom{0}26 & \phantom{00}2 \\
+Maple-LCM-Dist-alluip-trail & \phantom{0}34 & \phantom{0}12 & \phantom{00}1 \\
+Maple\_CM+dist+sattime2s+- & \phantom{0}18 & \phantom{0}18 & \phantom{00}1 \\
+CaDiCaL-sc2020 & \phantom{00}8 & \phantom{0}10 & \phantom{00}2 \\
+\hline 
+Total & 5000 & \phantom{0}-- & 286 \\ 
+\end{tabular}
+\end{center}
+\end{table}
+
+Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
+Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
+
+Its not clear how unique this is. Just take the total 286 and compare to uniform split -- that's the interesting bit, perhaps.
 

### 2021-01-11 paper/main.tex
variation

@@
 Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
-
-Its not clear how unique this is. Just take the total 286 and compare to uniform split -- that's the interesting bit, perhaps.
+The table is sorted by $R^S$, the time the schedule allocates to individual solvers, and skips the zero entries.
+It is not clear to what degree is the obtained schedule unique and how much it relies on each solver being present and for how long.
+Nevertheless, it is interesting to observe the total number of problems covered, here 286,
+and compare it to the 278 achieved in Table~\ref{tab:MainUniformTimeSplit} with the uniform split and two solvers.
+
+Amusingly, as can be seen from the ``contributes'' column, the presence of MapleLCMDistChronoBT-DL-f2trc in the schedule
+is not necessary.
+% The following three lines could be skipped without much harm:
+All the 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
+This result, however, does not signify a bug, as Z3 was not asked to produce a schedule with a minimal number of
+participating solvers.
+Indeed, allowing any other solver to run for the 76 ``wasted'' seconds would not increase the overall total.
 

### 2021-01-12 paper/main.tex
refined table of solvers

@@
 \newcommand{\solver}[1]{\texttt{#1}}
+\newcommand{\solbert}[1]{\underline{\solver{#1}}}
 
@@
 \hline
-1  & 3926.2 & 264 & {\bf Kissat-sc2020-sat} \\
-(1)& 4083.1 & 260 & Kissat-sc2020-default \\
-2  & 4179.3 & 253 & {\bf Relaxed\_LCMDCBDL\_newTech} \\
-3  & 4266.7 & 248 & {\bf cryptominisat-ccnr-lsids} \\
-(3)& 4278.0 & 250 & cryptominisat-ccnr \\
-   & 4428.1 & 250 & cadical-alluip-trail \\
-   & 4429.6 & 250 & cadical-alluip \\
-   & 4436.5 & 245 & Relaxed\_LCMDCBDL \\
-   & 4501.2 & 243 & cryptominisat-walksat \\
-   & 4554.0 & 243 & cadical-trail \\
-   & 4560.0 & 238 & Kissat-sc2020-unsat \\
+1     & 3926.2 & 264 & {\bf Kissat-sat} \\
+(1)   & 4083.1 & 260 & Kissat \\
+2     & 4179.3 & 253 & {\bf Relaxed\_newTech} \\
+3     & 4266.7 & 248 & {\bf CMS-ccnr-lsids} \\
+(3)   & 4278.0 & 250 & CMS-ccnr \\
+      & 4428.1 & 250 & CaDiCaL-alluip-trail \\
+      & 4429.6 & 250 & CaDiCaL-alluip \\
+      & 4436.5 & 245 & Relaxed \\
+      & 4501.2 & 243 & CMS-walksat \\
+      & 4554.0 & 243 & CaDiCaL-trail \\
+      & 4560.0 & 238 & Kissat-unsat \\
       & 4607.6 & 246 & CaDiCaL-sc2020 \\
-   & 5157.7 & 216 & Undominated-LC-MapleLCMDiscChronoBT-DL \\
-   & 5159.6 & 220 & MapleLCMDistChronoBT-DL-f2trc \\
-   & 5177.0 & 214 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\   
+      & 5157.7 & 216 & Undominated \\
+      & 5159.6 & 220 & f2trc-DL \\
+      & 5177.0 & 214 & PADC\_DL \\   
 \end{tabular}
@@
 \hline
- 1 & 2997.4 & 150 & {\bf Relaxed\_LCMDCBDL\_newTech} \\
- 2 & 3127.6 & 146 & {\bf Kissat-sc2020-sat} \\
- 3 & 3263.0 & 144 & {\bf cryptominisat-ccnr-lsids} \\
-(3)& 3317.4 & 145 & cryptominisat-ccnr \\
-   & 3355.5 & 143 & Relaxed\_LCMDCBDL \\
-   & 3524.7 & 140 & cryptominisat-ccnr-nolimits \\
-   & 3622.4 & 138 & cryptominisat-ccnr-lsids-nolimits \\
-   & 3703.7 & 140 & cryptominisat-walksat-nolimits \\
-   & 3721.2 & 139 & cryptominisat-walksat \\
-   & 3830.5 & 134 & Kissat-sc2020-default \\
-   & 3908.5 & 135 & cadical-alluip-trail \\
-   & 3909.6 & 135 & cadical-alluip \\
-   & 4265.6 & 126 & cadical-trail \\
+ 1    & 2997.4 & 150 & {\bf Relaxed\_newTech} \\
+ 2    & 3127.6 & 146 & {\bf Kissat-sat} \\
+ 3    & 3263.0 & 144 & {\bf CMS-ccnr-lsids} \\
+(3)   & 3317.4 & 145 & CMS-ccnr \\
+      & 3355.5 & 143 & Relaxed \\
+      & 3721.2 & 139 & CMS-walksat \\
+      & 3830.5 & 134 & Kissat \\
+      & 3908.5 & 135 & CaDiCaL-alluip-trail \\
+      & 3909.6 & 135 & CaDiCaL-alluip \\
+      & 4265.6 & 126 & CaDiCaL-trail \\
       & 4368.6 & 130 & CaDiCaL-sc2020 \\
-   & 4804.9 & 114 & Kissat-sc2020-unsat \\
+      & 4804.9 & 114 & Kissat-unsat \\
+      & 5173.2 & 110 & Undominated \\
+      & 5206.0 & 110 & abcdsat\_n20 \\
+      & 5244.1 & 107 & PADC\_DL \\   
 \end{tabular}
@@
 \hline   
-1  & 4315.1 & 124 & {\bf Kissat-sc2020-unsat} \\
-(1)& 4335.6 & 126 & Kissat-sc2020-default \\
-(1)& 4724.8 & 118 & Kissat-sc2020-sat \\
- 2 & 4842.5 & 117 & {\bf cadical-trail} \\
+1     & 4315.1 & 124 & {\bf Kissat-unsat} \\
+(1)   & 4335.6 & 126 & Kissat \\
+(1)   & 4724.8 & 118 & Kissat-sat \\
+ 2    & 4842.5 & 117 & {\bf CaDiCaL-trail} \\
 --    & 4846.7 & 116 & CaDiCaL-sc2020 \\
-(2)& 4947.8 & 115 & cadical-alluip-trail \\
-(2)& 4949.6 & 115 & cadical-alluip \\
- 3 & 4991.4 & 110 & {\bf MapleLCMDistChronoBT-f2trc-s} \\
-(3)& 5051.4 & 109 & MapleLCMDistChronoBT-f2trc \\
-(3)& 5054.3 & 110 & MapleLCMDistChronoBT-DL-f2trc \\
-   & 5069.6 & 109 & Maple\_mix \\
-   & 5110.0 & 107 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\
-   & 5126.9 & 107 & Maple\_simp \\
-   & 5128.9 & 107 & MapleLCMDistChronoBT-DL-v3 \\
-   & 5142.2 & 106 & Undominated-LC-MapleLCMDiscChronoBT-DL \\
+(2)   & 4947.8 & 115 & CaDiCaL-alluip-trail \\
+(2)   & 4949.6 & 115 & CaDiCaL-alluip \\
+ 3    & 4991.4 & 110 & {\bf f2trc-s} \\
+(3)   & 5051.4 & 109 & f2trc \\
+(3)   & 5054.3 & 110 & f2trc-DL \\
+      & 5069.6 & 109 & Maple\_Mix \\
+      & 5110.0 & 107 & PADC\_DL \\
+      & 5126.9 & 107 & Maple\_Simp \\
+      & 5128.9 & 107 & MapleCBT-DL-v3 \\
+      & 5142.2 & 106 & Undominated \\
 \end{tabular}
@@
 \hline   
- 1 & 6406.9 & 80 & {\bf cadical-alluip-trail} \\
-(1)& 6409.3 & 80 & cadical-alluip \\
- 2 & 6466.9 & 79 & {\bf cryptominisat-ccnr-lsids} \\
-(2)& 6471.9 & 79 & cryptominisat-ccnr \\
-(2)& 6472.9 & 79 & cryptominisat-walksat \\
- 3 & 6596.4 & 75 & {\bf Kissat-sc2020-unsat} \\
-   & 6650.1 & 79 & cadical-trail \\
-   & 6713.0 & 75 & Maple\_mix \\
-   & 6746.5 & 75 & MapleCOMSPS\_LRB\_VSIDS\_2\_\_LRB\_VSIDS\_2\_init \\
-   & 6754.3 & 73 & Maple\_simp \\
-   & 6773.0 & 73 & MapleCOMSPS\_LRB\_VSIDS\_2\_\_default\_drup \\
-   & 6773.9 & 73 & Kissat-sc2020-sat \\
-   & 6774.2 & 73 & Kissat-sc2020-default \\
+ 1    & 6406.9 & 80 & {\bf CaDiCaL-alluip-trail} \\
+(1)   & 6409.3 & 80 & CaDiCaL-alluip \\
+ 2    & 6466.9 & 79 & {\bf CMS-ccnr-lsids} \\
+(2)   & 6471.9 & 79 & CMS-ccnr \\
+(2)   & 6472.9 & 79 & CMS-walksat \\
+ 3    & 6596.4 & 75 & {\bf Kissat-unsat} \\
+      & 6650.1 & 79 & CaDiCaL-trail \\
+      & 6713.0 & 75 & Maple\_Mix \\
+      & 6746.5 & 75 & MapleCOMSPS\_init \\
+      & 6754.3 & 73 & Maple\_Simp \\
+      & 6773.0 & 73 & MapleCOMSPS\_drup \\
+      & 6773.9 & 73 & Kissat-sat \\
+      & 6774.2 & 73 & Kissat \\
       & 7003.0 & 69 & optsat\_m20 \\
-   & 7025.5 & 68 & upGlucose-3.0\_PADC \\
+      & 7025.5 & 68 & upGlucose3.0\_PADC \\
 \end{tabular}
@@
 
-\renewcommand{\solver}[1]{\underline{\texttt{#1}}}
-\newcommand{\solbert}[1]{\texttt{#1}}
-
 \begin{table}[ht!]
+\setlength\tabcolsep{4.5pt}
 \smaller
-\arrayrulecolor{gray}
 \centering
-\begin{tabular}{|l|l|l|l|}
-\hline
-\bf Team & \bf Base Solver & \bf Variant / Name & \bf Award \\
-\hline
-
-\multirow{3}{*}{Biere} & \multirow{3}{*}{\solver{Kissat}} &  -- & \firsto, \firstu\\
- &  &  \solbert{sat} & \firsto, \firstu, \seconds\\
- &  &  \solbert{unsat} & \firstu, \thirdp\\
-\hline
- Biere, Fleury &  \solbert{Cadical} & \solver{SC2020} & \\
+\begin{tabular}{lllcccc}
+\bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
+\hline
+\arrayrulecolor{lightgray}
+
+\multirow{3}{*}{Biere} & \multirow{3}{*}{\solbert{Kissat}} &  -- & 1 & 1 & -- & --\\
+ &  &  \solver{sat} & 1 & 1 & 2 & --\\
+ &  &  \solver{unsat} & -- & 1 & -- & 3\\
+\hline
+ Biere, Fleury &  \solver{Cadical} & \solbert{SC2020} & -- & -- & -- & --\\
 \hline
@@
 \multirow{2}{*}{Zhang, Cai}
-    & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
-% &  & \solbert{Rel. noTimeParam} & \\
- &  & \solbert{Rel. newTech} & \secondo, \firsts\\
+    & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Relaxed} & -- & -- & -- & --\\
+% &  & \solver{Rel. noTimeParam} & \\
+ &  & \solver{Rel. newTech} & 2 & -- & 1 & --\\
 \hline
@@
 \multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
- &  \multirow{2}{*}{\solbert{CryptoMiniSat-CCAnr}} &  -- & \thirdo, \thirds, \secondp\\
- &  &  \solbert{lsids} & \thirdo, \thirds, \secondp\\
-\hline
-
-\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solbert{CryptoMiniSat-WalkSAT} & -- & \\
+ &  \multirow{2}{*}{\solver{CryptoMiniSat-CCAnr}} &  -- & 3 & -- & 3 & 2\\
+ &  &  \solver{lsids} & 3 & -- & 3 & 2\\
+\hline
+
+\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solver{CryptoMiniSat-WalkSAT} & -- & -- & -- & -- & --\\
 \hline
@@
 \multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
- &  &  \solbert{trail} & \secondu\\
- &  &  \solbert{alluip} & \secondu, \firstp\\
- & \multirow{-3}{*}{\solbert{CaDiCaL}} &  \solver{alluip-trail} & \secondu, \firstp\\
- \cline{2-4}
- & \solbert{MapleLCMDist} & \solbert{alluip-trail} & \\
-\hline
-
-\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solbert{MapleLCMDistCBT}} & \solver{f2trc} & \thirdu\\
- & & \solbert{f2trc-s} & \thirdu\\
- \cline{2-4}
- & \solbert{MapleLCMDistCBT-DL} & \solbert{f2trc} & \thirdu\\
-\hline
-
-\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solver{MapleLCMDistCBT-DL-v3} & -- & \\
+ &  &  \solver{trail} & -- & 2 & -- & --\\
+ &  &  \solver{alluip} & -- & 2 & -- & 1\\
+ & \multirow{-3}{*}{\solver{CaDiCaL}} &  \solbert{alluip-trail} & -- & 2 & -- & 1\\
+ \cline{2-7}
+ & \solver{MapleLCMDist} & \solver{alluip-trail} & -- & -- & -- & -- \\
+\hline
+
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solver{MapleLCMDistCBT}} & \solbert{f2trc} & -- & 3 & -- & --\\
+ & & \solver{f2trc-s} & -- & 3 & -- & --\\
+ \cline{2-7}
+ & \solver{MapleLCMDistCBT-DL} & \solver{f2trc} & -- & 3 & -- & --\\
+\hline
+
+\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solbert{MapleLCMDistCBT-DL-v3} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
- & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v3}} & \solver{Undominated} & \\
- &  & \solbert{Undom. Top16} & \\
- &  & \solbert{Undom. Top24} & \\
- &  & \solbert{Undom. Top36} & \\
+ & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v3}} & \solbert{Undominated} & -- & -- & -- & -- \\
+ &  & \solver{Undom. Top16} & -- & -- & -- & -- \\
+ &  & \solver{Undom. Top24} & -- & -- & -- & -- \\
+ &  & \solver{Undom. Top36} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{\solver{Ex}\solbert{MapleLCMDistCBT}} & \solbert{padc\_dl} & \\
- &  & \solbert{padc\_dl\_ovau\_lin} & \\
- &  & \solbert{padc\_dl\_ovau\_exp} & \\
- &  & \solbert{psids\_dl} & \\
+ & \multirow{4}{*}{\solbert{Ex}\solver{MapleLCMDistCBT}} & \solver{padc\_dl} & -- & -- & -- & -- \\
+ &  & \solver{padc\_dl\_ovau\_lin} & -- & -- & -- & -- \\
+ &  & \solver{padc\_dl\_ovau\_exp} & -- & -- & -- & -- \\
+ &  & \solver{psids\_dl} & -- & -- & -- & -- \\
 % \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
@@
 
-Shaw, Meel & \solbert{MapleLCMDistCBT-DL-v3} & \solver{DurianSat} & \\
+Shaw, Meel & \solver{MapleLCMDistCBT-DL-v3} & \solbert{DurianSat} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{2}{*}{Chen}
- & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Maple\_Mix} & \\
- &  & \solver{Maple\_Simp} & \\
-\hline
-
-Riveros & \solbert{MapleLCMDistCBT} & \solver{SLIME} & \\
+ & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Maple\_Mix} & -- & -- & -- & -- \\
+ &  & \solbert{Maple\_Simp} & -- & -- & -- & -- \\
+\hline
+
+Riveros & \solver{MapleLCMDistCBT} & \solbert{SLIME} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{3}{*}{Li, Wu, Xu, Chen}
- & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Scavel} & \\
- &  & \solbert{Scavel01} & \\
- &  & \solbert{Scavel02} & \\
+ & \multirow{3}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Scavel} & -- & -- & -- & -- \\
+ &  & \solver{Scavel01} & -- & -- & -- & -- \\
+ &  & \solver{Scavel02} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
- & \multirow{2}{*}{\solver{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & \\
- &  & \solbert{init} & \\
+ & \multirow{2}{*}{\solbert{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & -- & -- & -- & -- \\
+ &  & \solver{init} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
- & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v2.2}} & \solver{exp}\solbert{-V-LGB} & \\
- &  & \solbert{exp-V-L} & \\
- &  & \solbert{exp-L} & \\
- &  & \solbert{exp-V} & \\
+ & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v2.2}} & \solbert{exp}\solver{-V-LGB} & -- & -- & -- & -- \\
+ &  & \solver{exp-V-L} & -- & -- & -- & -- \\
+ &  & \solver{exp-L} & -- & -- & -- & -- \\
+ &  & \solver{exp-V} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
- & \multirow{4}{*}{\solver{MapleCM}} & \solver{+dist} & \\
- &  & \solbert{+dist+sattime2s+-} & \\
- &  & \solbert{+dist+simp2--} & \\
- &  & \solbert{used+dist} & \\
-\hline
-
-Kaiser, Hartung & \solbert{MapleLCMDist} & \solver{PauSat} & \\
+ & \multirow{4}{*}{\solbert{MapleCM}} & \solbert{+dist} & -- & -- & -- & -- \\
+ &  & \solver{+dist+sattime2s+-} & -- & -- & -- & -- \\
+ &  & \solver{+dist+simp2--} & -- & -- & -- & -- \\
+ &  & \solver{used+dist} & -- & -- & -- & -- \\
+\hline
+
+Kaiser, Hartung & \solver{MapleLCMDist} & \solbert{PauSat} & -- & -- & -- & -- \\
 \hline
@@
 \multirow{2}{*}{Osama, Wijs} 
- & \multirow{2}{*}{\solver{ParaFROST}} & -- & \\
- &  & \solbert{CBT} & \\
-\hline
+ & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- \\
+ &  & \solver{CBT} & -- & -- & -- & -- 
 \end{tabular}
 \caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks.
-We partially \solver{underlined} submission names.
+We partially \solbert{underlined} submission names.
 Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$.
@@
 \end{table}
-
-\renewcommand{\solver}[1]{\texttt{#1}} % sorry ;)
 
@@
 on performance achievable in principle by the technology 
-of the participating solvers (cf. the figures in Section~\ref{sec:results}).
+of the participating solvers (cf.~the figures in Section~\ref{sec:results}).
 
@@
 \caption{VBS metrics for the results of the Main track, all instances. 
-The total number of solved problems was 317. 
-There were 60 (non-disqualified) solvers (and their configurations).
+The total number of solved problems was 316. 
+There were 54 (non-disqualified) solvers (and their configurations).
 Each table shows the first ten solvers sorted according to the respective metric.}
@@
 \hline
-46 & 11.5 & Kissat-sc2020-unsat \\
-37 & \phantom{0}9.2 & Kissat-sc2020-sat \\
-22 & \phantom{0}5.5 & Kissat-sc2020-default \\
-14 & \phantom{0}3.5 & Maple\_CM+dist+sattime2s+- \\
-13 & \phantom{0}3.2 & cryptominisat-ccnr-lsids \\
-13 & \phantom{0}3.2 & Maple-LCM-Dist-alluip-trail \\
-12 & \phantom{0}3.0 & Relaxed\_LCMDCBDL \\
-11 & \phantom{0}2.8 & upGlucose-3.0\_PADC \\
+46 & 11.5 & Kissat-unsat \\
+37 & \phantom{0}9.2 & Kissat-sat \\
+24 & \phantom{0}6.0 & Kissat \\
+18 & \phantom{0}4.5 & CMS-ccnr-lsids \\
+14 & \phantom{0}3.5 & MapleCM+dist+sat2s \\
+13 & \phantom{0}3.2 & Maple-alluip-trail \\
+12 & \phantom{0}3.0 & Relaxed \\
+11 & \phantom{0}2.8 & upGlucose3.0\_PADC \\
 10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
-\phantom{0}9 & \phantom{0}2.2 & Maple\_CMused+dist \\
+\phantom{0}9 & \phantom{0}2.2 & CMS-ccnr \\
 \end{tabular}
@@
 \hline
-129.8 & 32.4 & Kissat-sc2020-sat \\
-120.1 & 30.0 & Kissat-sc2020-default \\
-113.6 & 28.4 & Kissat-sc2020-unsat \\
-\phantom{0}91.0 & 22.7 & cryptominisat-ccnr-lsids \\
-\phantom{0}87.0 & 21.7 & cryptominisat-ccnr \\
-\phantom{0}82.0 & 20.5 & cadical-alluip-trail \\
-\phantom{0}81.9 & 20.5 & cadical-alluip \\
-\phantom{0}81.8 & 20.5 & CaDiCaL-sc2020 \\
-\phantom{0}81.0 & 20.2 & Relaxed\_LCMDCBDL\_newTech \\
-\phantom{0}80.5 & 20.1 & Relaxed\_LCMDCBDL \\
+130.3 & 32.6 & Kissat-sat \\
+120.7 & 30.2 & Kissat \\
+114.0 & 28.5 & Kissat-unsat \\
+\phantom{0}91.5 & 22.9 & CMS-ccnr-lsids \\
+\phantom{0}87.8 & 22.0 & CMS-ccnr \\
+\phantom{0}82.3 & 20.6 & CaDiCaL-alluip-trail \\
+\phantom{0}82.2 & 20.5 & CaDiCaL-alluip \\
+\phantom{0}81.9 & 20.5 & CaDiCaL-sc2020 \\
+\phantom{0}81.4 & 20.4 & Relaxed\_newTech \\
+\phantom{0}80.8 & 20.2 & Relaxed \\
 \end{tabular}
@@
 \hline
-11.7 & 2.9 & Kissat-sc2020-default \\
-10.8 & 2.7 & Kissat-sc2020-unsat \\
-10.4 & 2.6 & Relaxed\_LCMDCBDL\_newTech \\
-\phantom{0}9.9 & 2.5 & Kissat-sc2020-sat \\
-\phantom{0}9.8 & 2.4 & cadical-alluip \\
-\phantom{0}9.8 & 2.4 & cadical-alluip-trail \\
-\phantom{0}9.4 & 2.3 & Relaxed\_LCMDCBDL \\
-\phantom{0}9.4 & 2.3 & CaDiCaL-sc2020 \\
-\phantom{0}8.7 & 2.2 & cadical-trail \\
-\phantom{0}8.3 & 2.1 & cryptominisat-walksat \\
+12.4 & 3.1 & Kissat \\
+11.4 & 2.9 & Kissat-unsat \\
+11.4 & 2.8 & Relaxed\_newTech \\
+10.7 & 2.7 & Kissat-sat \\
+10.3 & 2.6 & CaDiCaL-alluip-trail \\
+10.3 & 2.6 & CaDiCaL-alluip \\
+10.0 & 2.5 & Relaxed \\
+\phantom{0}9.9 & 2.5 & CaDiCaL-sc2020 \\
+\phantom{0}9.7 & 2.4 & CMS-walksat \\
+\phantom{0}9.2 & 2.3 & CaDiCaL-trail \\
 \end{tabular}
@@
 \caption{VBS metrics for the results of the Main track, SAT instances. 
-The total number of solved problems was 183. 
-There were 60 (non-disqualified) participating solvers.
+The total number of solved problems was 182. 
+There were 54 (non-disqualified) participating solvers.
 Each table always shows the first ten solvers sorted according to the respective metric.}
@@
 \hline
-27 & 14.8 & Kissat-sc2020-sat \\
-14 & \phantom{0}7.7 & Maple\_CM+dist+sattime2s+- \\
-12 & \phantom{0}6.6 & Kissat-sc2020-default \\
-10 & \phantom{0}5.5 & Relaxed\_LCMDCBDL \\
+27 & 14.8 & Kissat-sat \\
+14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
+14 & \phantom{0}7.7 & Kissat \\
+12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
+10 & \phantom{0}5.5 & Relaxed \\
+\phantom{0}8 & \phantom{0}4.4 & CMS-ccnr \\
 \phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
-\phantom{0}8 & \phantom{0}4.4 & Kissat-sc2020-unsat \\
-\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids-nolimits \\
-\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids \\
-\phantom{0}6 & \phantom{0}3.3 & cadical-trail \\
-\phantom{0}6 & \phantom{0}3.3 & cryptominisat-ccnr-nolimits \\
-
+\phantom{0}8 & \phantom{0}4.4 & Kissat-unsat \\
+\phantom{0}6 & \phantom{0}3.3 & CaDiCaL-trail \\
+\phantom{0}5 & \phantom{0}2.7 & MapleCOMSPS\_drup \\
 \end{tabular}
@@
 \hline
-68.5 & 37.4 & Kissat-sc2020-sat \\
-46.3 & 25.3 & Kissat-sc2020-default \\
-44.1 & 24.1 & cryptominisat-ccnr-lsids \\
-42.2 & 23.0 & Relaxed\_LCMDCBDL\_newTech \\
-41.8 & 22.9 & cryptominisat-ccnr-lsids-nolimits \\
-40.9 & 22.3 & cryptominisat-ccnr \\
-40.6 & 22.2 & Relaxed\_LCMDCBDL \\
-39.4 & 21.5 & cryptominisat-ccnr-nolimits \\
-35.2 & 19.2 & cryptominisat-walksat-nolimits \\
-32.8 & 17.9 & cryptominisat-walksat \\
+69.0 & 37.9 & Kissat-sat \\
+46.9 & 25.7 & Kissat \\
+44.6 & 24.5 & CMS-ccnr-lsids \\
+42.6 & 23.4 & Relaxed\_newTech \\
+41.7 & 22.9 & CMS-ccnr \\
+41.0 & 22.5 & Relaxed \\
+33.1 & 18.2 & CMS-walksat \\
+32.9 & 18.1 & CaDiCaL-alluip-trail \\
+32.8 & 18.0 & CaDiCaL-alluip \\
+31.8 & 17.5 & CaDiCaL-sc2020 \\
 \end{tabular}
@@
 \hline
-8.0 & 4.4 & Relaxed\_LCMDCBDL\_newTech \\
-7.0 & 3.8 & Relaxed\_LCMDCBDL \\
-6.5 & 3.6 & cryptominisat-walksat-nolimits \\
-5.8 & 3.2 & cryptominisat-walksat \\
-5.6 & 3.0 & Kissat-sc2020-sat \\
-5.4 & 3.0 & cryptominisat-ccnr-lsids \\
-5.4 & 3.0 & Kissat-sc2020-default \\
-5.4 & 2.9 & cryptominisat-ccnr \\
-5.2 & 2.8 & cadical-alluip \\
-5.2 & 2.8 & cadical-alluip-trail \\
+9.0 & 4.9 & Relaxed\_newTech \\
+7.7 & 4.2 & Relaxed \\
+7.3 & 4.0 & CMS-walksat \\
+6.4 & 3.5 & Kissat-sat \\
+6.2 & 3.4 & CMS-ccnr-lsids \\
+6.2 & 3.4 & Kissat \\
+6.2 & 3.4 & CMS-ccnr \\
+5.7 & 3.2 & CaDiCaL-alluip-trail \\
+5.7 & 3.2 & CaDiCaL-alluip \\
+5.7 & 3.1 & CaDiCaL-sc2020 \\
 \end{tabular}
@@
 The total number of solved problems was 134. 
-There were 60 (non-disqualified) participating solvers.
+There were 49 (non-disqualified) participating solvers.
 Each table always shows the first ten solvers sorted according to the respective metric.}
@@
 \hline
-38 & 28.4 & Kissat-sc2020-unsat \\
-11 & \phantom{0}8.2 & Maple-LCM-Dist-alluip-trail \\
-10 & \phantom{0}7.5 & Kissat-sc2020-default \\
-10 & \phantom{0}7.5 & Kissat-sc2020-sat \\
-\phantom{0}8 & \phantom{0}6.0 & Maple\_CMused+dist \\
-\phantom{0}6 & \phantom{0}4.5 & cryptominisat-ccnr-lsids \\
-\phantom{0}6 & \phantom{0}4.5 & upGlucose-3.0\_PADC \\
-\phantom{0}3 & \phantom{0}2.2 & MapleLCMDistChronoBT-f2trc \\
-\phantom{0}3 & \phantom{0}2.2 & glucose3.0\_\_proofs \\
+38 & 28.4 & Kissat-unsat \\
+11 & \phantom{0}8.2 & Maple-alluip-trail \\
+10 & \phantom{0}7.5 & Kissat \\
+10 & \phantom{0}7.5 & Kissat-sat \\
+\phantom{0}8 & \phantom{0}6.0 & MapleCMused+dist \\
+\phantom{0}6 & \phantom{0}4.5 & CMS-ccnr-lsids \\
+\phantom{0}6 & \phantom{0}4.5 & upGlucose3.0\_PADC \\
+\phantom{0}3 & \phantom{0}2.2 & f2trc \\
+\phantom{0}3 & \phantom{0}2.2 & Glucose3.0\_proofs \\
 \phantom{0}3 & \phantom{0}2.2 & DurianSat \\
@@
 \hline
-86.3 & 64.4 & Kissat-sc2020-unsat \\
-73.8 & 55.1 & Kissat-sc2020-default \\
-61.3 & 45.7 & Kissat-sc2020-sat \\
-55.4 & 41.3 & MapleLCMDistChronoBT-f2trc-s \\
+86.3 & 64.4 & Kissat-unsat \\
+73.8 & 55.1 & Kissat \\
+61.3 & 45.7 & Kissat-sat \\
+55.4 & 41.3 & f2trc-s \\
 55.0 & 41.0 & DurianSat \\
-53.6 & 40.0 & Maple-LCM-Dist-alluip-trail \\
-53.3 & 39.8 & MapleLCMDistChronoBT-f2trc \\
-52.4 & 39.1 & MapleLCMDistChronoBT-DL-f2trc \\
-51.7 & 38.6 & Maple\_CMused+dist \\
-51.6 & 38.5 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\
+53.6 & 40.0 & Maple-alluip-trail \\
+53.3 & 39.8 & f2trc \\
+52.4 & 39.1 & f2trc-DL \\
+51.7 & 38.6 & MapleCMused+dist \\
+51.6 & 38.5 & PADC\_DL \\
 \end{tabular}
@@
 \hline
-6.7 & 5.0 & Kissat-sc2020-unsat \\
-6.2 & 4.7 & Kissat-sc2020-default \\
-4.6 & 3.4 & cadical-trail \\
-4.6 & 3.4 & cadical-alluip \\
-4.6 & 3.4 & cadical-alluip-trail \\
-4.3 & 3.2 & Kissat-sc2020-sat \\
+6.7 & 5.0 & Kissat-unsat \\
+6.2 & 4.7 & Kissat \\
+4.6 & 3.4 & CaDiCaL-trail \\
+4.6 & 3.4 & CaDiCaL-alluip-trail \\
+4.6 & 3.4 & CaDiCaL-alluip \\
+4.3 & 3.2 & Kissat-sat \\
 4.2 & 3.1 & CaDiCaL-sc2020 \\
-3.4 & 2.5 & MapleLCMDistChronoBT-f2trc-s \\
+3.4 & 2.5 & f2trc-s \\
 3.3 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
-3.0 & 2.3 & MapleLCMDistChronoBT-DL-f2trc \\
+3.0 & 2.3 & f2trc-DL \\
 \end{tabular}
@@
 to the full results of the Main track. We can see that the respective leaderboards 
-are generally dominated by Kissat-sc2020 and its configurations.
-VBS1 tells us that Kissat-sc2020-unsat was most often the fastest solver,
+are generally dominated by Kissat and its configurations.
+VBS1 tells us that Kissat-unsat was most often the fastest solver,
 in particular on \SI{11.5}{\percent} of all the solved instances.
 
-VBS2 highlights as first Kissat-sc2020-sat. Its leading \SI{32.4}{\percent} of total is a bit harder to 
-interpret: A solver can score \SI{32.4}{\percent} of VBS2 total
-by solving \SI{32.4}{\percent} of the solved instances in the best observed time
-and no others. But we know, thanks to its VBS1, that Kissat-sc2020-sat solved \SI{9.2}{\percent}
+VBS2 highlights as first Kissat-sat. Its leading \SI{32.6}{\percent} of total is a bit harder to 
+interpret: A solver can score \SI{32.6}{\percent} of VBS2 total
+by solving \SI{32.6}{\percent} of the solved instances in the best observed time
+and no others. But we know, thanks to its VBS1, that Kissat-sat solved \SI{9.2}{\percent}
 of the solved instances in the best observed time (and some others).
-A solver can also score \SI{32.4}{\percent} of VBS2 total by solving all the solved instances,
+A solver can also score \SI{32.6}{\percent} of VBS2 total by solving all the solved instances,
 but always being roughly 3 times slower than the VBS. 
-Kissat-sc2020-sat lies obviously somewhere between these two extremes.
-
-Finally, according to VBS3, the best solver is Kissat-sc2020-default with 11.7 points,
-which amounts to \SI{2.9}{\percent} of the distributed total score.
+Kissat-sat lies obviously somewhere between these two extremes.
+
+Finally, according to VBS3, the best solver is Kissat with 12.4 points,
+which amounts to \SI{3.1}{\percent} of the distributed total score.
 The VBS3 metric is generally the most evenly distributed one,
 at least among the first 10 solvers. 
-(The last solver got 0.5 points which is \SI{0.123}{\percent} of total.)
+(The last solver got 1.0 points which is \SI{0.256}{\percent} of the total.)
 One can conclude from this that most of the benchmarks are solved
@@
 \begin{tabular}{clccc}
-Iteration & selected solver & (num. solved) & contributes & covered so far \\
-\hline
-\phantom{0}1 & Kissat-sc2020-sat & 264 & 264 & 264 \\
-\phantom{0}2 & cadical-alluip & 250 & \phantom{0}22 & 286 \\
-\phantom{0}3 & MapleLCMDistChronoBT-f2trc-s & 214 & \phantom{0}10 & 296 \\
-\phantom{0}4 & Relaxed\_LCMDCBDL\_newTech & 253 & \phantom{00}6 & 302 \\
-\phantom{0}5 & Kissat-sc2020-unsat & 238 & \phantom{00}4 & 306 \\
-\phantom{0}6 & cryptominisat-walksat & 243 & \phantom{00}3 & 309 \\
-\phantom{0}7 & Relaxed\_LCMDCBDL & 245 & \phantom{00}3 & 312 \\
-\phantom{0}8 & cryptominisat-ccnr-lsids & 248 & \phantom{00}1 & 313 \\
-\phantom{0}9 & exp\_V\_LGB\_MLD\_CBT\_DL & 194 & \phantom{00}1 & 314 \\
-10 & MapleLCMDistChronoBT-DL-f2trc & 220 & \phantom{00}1 & 315 \\
-11 & MapleLCMDistChronoBT-DL-v3 & 211 & \phantom{00}1 & 316 \\
-12 & cryptominisat-walksat-nolimits & 140 & \phantom{00}1 & 317 \\
-
+Iteration & selected solver & (num. solved) & contributes \\ % & covered so far \\
+\hline
+\phantom{0}1 & Kissat-sat & 264 & 264 \\ % & 264 \\
+\phantom{0}2 & CaDiCaL-alluip & 250 & \phantom{0}22 \\ % & 286 \\
+\phantom{0}3 & f2trc-s & 214 & \phantom{0}10 \\ % & 296 \\
+\phantom{0}4 & Relaxed\_newTech & 253 & \phantom{00}6 \\ % & 302 \\
+\phantom{0}5 & Kissat-unsat & 238 & \phantom{00}4 \\ % & 306 \\
+\phantom{0}6 & Relaxed & 245 & \phantom{00}3 \\ % & 309 \\
+\phantom{0}7 & CMS-walksat & 243 & \phantom{00}3 \\ % & 312 \\
+\phantom{0}8 & CMS-ccnr-lsids & 248 & \phantom{00}1 \\ % & 313 \\
+\phantom{0}9 & MapleCBT-DL-v3 & 211 & \phantom{00}1 \\ % & 314 \\
+10 & DurianSat & 210 & \phantom{00}1 \\ % & 315 \\
+11 & exp\_V\_LGB\_MLD\_CBT\_DL & 194 & \phantom{00}1 \\ % & 316 \\
+\hline
+ & Total & -- & 316 \\
 \end{tabular}
@@
 in Table~\ref{tab:gscMain}. In the first iteration, the solver which solved the highest number 
-of instances is selected; in our case it was Kissat-sc2020-sat with 264 instances
+of instances is selected; in our case it was Kissat-sat with 264 instances
 as we know already from Table~\ref{tab:mainALL}.
-Given those 264 instances as already covered, cadical-alluip was the best in further contributing
+Given those 264 instances as already covered, CaDiCaL-alluip was the best in further contributing
 to the set by additional 22 instances in iteration 2.
 We can see that the further iterations tend to add very little,
-with the final 5 iterations adding one instance each. Note that each solver
+with the final four iterations adding one instance each. Note that each solver
 that managed to solve an instance uniquely (i.e.~being the only solver to do so)
-is showing up in the table. This is, for example the case of last listed  
-cryptominisat-walksat-nolimits with otherwise relatively low number of solved instances (140).
+is showing up in the table. This is, for example the case of the last listed  
+exp\_V\_LGB\_MLD\_CBT\_DL.
 Highlighting unique solutions is a property of the greedy set cover metric
@@
 \begin{tabular}{cccl}
-\# solvers & time (s) & total solved & best schedule \\
-\hline
-1 & 5000 & 264 & Kissat-sc2020-sat \\
-2 & 2500 & 278 & Kissat-sc2020-unsat, \\
-             &&& Relaxed\_LCMDCBDL\_newTech \\
-3 & 1666 & 272 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
-			 &&& cryptominisat-ccnr-lsids \\
-4 & 1250 & 262 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
-			 &&& cryptominisat-ccnr-lsids, Maple-LCM-Dist-alluip-trail \\ 
-5 & 1000 & 253 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
-			&&& cryptominisat-ccnr-lsids, \\
-			&&& Maple-LCM-Dist-alluip-trail, cadical-alluip \\
+\# solvers & time (s) & total solved & the best schedule \\
+\hline
+1 & 5000 & 264 & \{Kissat-sat\} \\
+2 & 2500 & 278 & \{Kissat-unsat, Relaxed\_newTech\} \\
+3 & 1666 & 272 & \{Kissat-unsat, Kissat-sat, \\
+			 &&& CMS-ccnr-lsids\} \\
+4 & 1250 & 262 & \{Kissat-unsat, Kissat-sat, \\
+			 &&& CMS-ccnr-lsids, Maple-alluip-trail\} \\ 
+5 & 1000 & 253 & \{Kissat-unsat, Kissat-sat, \\
+			&&& CMS-ccnr-lsids, Maple-alluip-trail, \\ 
+			&&& CaDiCaL-alluip \}\\
 \end{tabular}
@@
 \hline
-Kissat-sc2020-unsat & 2523 & 219 & 219 \\
-Relaxed\_LCMDCBDL\_newTech & 2180 & 234 & \phantom{0}59 \\
-Kissat-sc2020-sat & 103 & \phantom{0}72 & \phantom{00}2 \\
-MapleLCMDistChronoBT-DL-f2trc & \phantom{0}76 & \phantom{0}15 & \phantom{00}0 \\
-cadical-alluip & \phantom{0}58 & \phantom{0}26 & \phantom{00}2 \\
-Maple-LCM-Dist-alluip-trail & \phantom{0}34 & \phantom{0}12 & \phantom{00}1 \\
-Maple\_CM+dist+sattime2s+- & \phantom{0}18 & \phantom{0}18 & \phantom{00}1 \\
-CaDiCaL-sc2020 & \phantom{00}8 & \phantom{0}10 & \phantom{00}2 \\
+Kissat-unsat & 2523 & 219 & 219 \\
+Relaxed\_newTech & 2180 & 234 & \phantom{0}59 \\
+Kissat-sat & \phantom{0}103 & \phantom{0}72 & \phantom{00}2 \\
+f2trc-DL & \phantom{00}76 & \phantom{0}15 & \phantom{00}0 \\
+CaDiCaL-alluip & \phantom{00}58 & \phantom{0}26 & \phantom{00}2 \\
+Maple-alluip-trail & \phantom{00}34 & \phantom{0}12 & \phantom{00}1 \\
+MapleCM+dist+sat2s & \phantom{00}18 & \phantom{0}18 & \phantom{00}1 \\
+CaDiCaL-sc2020 & \phantom{000}8 & \phantom{0}10 & \phantom{00}2 \\
 \hline 
@@
 
-Amusingly, as can be seen from the ``contributes'' column, the presence of MapleLCMDistChronoBT-DL-f2trc in the schedule
+Amusingly, as can be seen from the ``contributes'' column, the presence of f2trc-DL in the schedule
 is not necessary.

### 2021-01-15 paper/main.tex
results update

@@
 
-Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
-Despite its complexity, there is an ongoing progress in solving methods and their implementations in SAT solvers. 
-The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
-Today, SAT solvers are used for verification of hard- and software, product configuration, cryptography, planning and scheduling, to name a few. 
-In mathematics, SAT solvers were recently even used to generate a record sized proof (200 TB) for an until then unsolved problem in Ramsey theory.
-
-SAT Competitions are organized regularly since 1992 in order to drive progress and to serve as a public assessment of the state-of-the-art in SAT solving. 
-For each SAT Competition, a set of new benchmark instances is compiled which reflects the various applications of interest to the community.
-
-In this competition, we initiated a new application-specific track. 
-The idea is to provide a large amount of benchmark instances of a specific application and to evaluate all solvers with respect to these instance in a special track. 
-In this competition, we used 200 instances of the planning domain to run a planning track.
-
-Faster networks, distributed systems, and the increasing number of processors in modern computers show that the trend of increasing parallelism is about to continue.  
-In the new cloud track, for the first time, solver authors could compete in SAT technologies that allow hundreds of SAT solvers to cooperate in solving a SAT instance.
-
-\todo{Present some important pointers for SAT and CDCL}
-
 In Section~\ref{sec:overview}, we start with an overview of the competition,
@@
 A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.
-
-\todo{maybe mention \url{https://satcompetition.github.io/2020/}}
-
-\todo{Maybe mention proceedings \cite{SC2020}}
 
@@
 
-Instead of using or extending the DIMACS input format, we realize the Incremental track
+Instead of using or extending the DIMACS input format, we realize the Incremental Library track
 by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
@@
 a proof and {\tt cake\_lpr} would later disagree with the verdict.
+
+\todo{on wrong certificate (but still correct result) followed the demotion of the solver to the no-limits track}
 
@@
 
-For selection of benchmark instances in this competition, we used GBD Tools.%
-\footnote{\url{https://pypi.org/project/gbd-tools/}} 
+Benchmark instances selection in this competition was realized using GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which is a tool-chain for maintenance and distribution of benchmark instances and instance attributes~\cite{Iser:2018:GBD}.
 Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
-The association of instance-id and instance attributes is maintained in publicly available databases.%
-\footnote{\url{https://gbd.iti.kit.edu}}
-
-GBD Tools is a tool-chain for maintenance and distribution of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
-Its databases provide information about all instances used in SAT competitive events dating back to 2006. 
-In GBD Server, each instance also has an URL, such that instances can be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.
+Instance attributes are maintained in publicly available databases, which provide information about all instances used in SAT Competitions since 2006.\footnote{\url{https://gbd.iti.kit.edu}} 
+Benchmark instance identification also simplifies the distribution of instances via the GBD Server.\footnote{\url{https://gbd.iti.kit.edu/file/<gbd-hash>}}
 
@@
 \KwResult{$S$ : Set of Selected Instances}
-\SetKwFunction{rand}{$\mathsf{random.choice}$}
+\SetKwFunction{rand}{$\mathsf{random}$}
 \BlankLine
@@
 \For {$a \in A$} {
-	$I_a^+ \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$, $k=7$}\;	
-	$I_a^- \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$, $k=7$}\;	
+	$I_a^+ \leftarrow$ \rand{$7$, $\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{sat} \}$}\;	
+	$I_a^- \leftarrow$ \rand{$7$, $\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unsat} \}$}\;	
 	\If {$|I_a^+|+|I_a^-| < 14$}{
-		$l \leftarrow 14 - (|I_a^+|+|I_a^-|)$\;
-		$I_a^? \leftarrow$ \rand{$\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$, $k=l$}\;
+		$l \leftarrow 14 - |I_a^+| - |I_a^-|$\;
+		$I_a^? \leftarrow$ \rand{$l$, $\{ e \in I \mid \alpha(e) = a \land \sigma(e) = \mathsf{unknown} \}$}\;
 	}
@@
 \centering
-\begin{tabular}{|l|l||rr|}
-\hline
-Family & Author & Submitted & Selected\\
-\hline\hline
-0-1 Integer Programming & Riveros & 6 & 2 \\
+\begin{tabular}{llrr}
+\bf Family & \bf Author & \bf Submitted & \bf Selected\\
+\hline
+\arrayrulecolor{lightgray}
+0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
+Fermat &  & 8 & 5 \\
+Schur Coloring &  & 4 & 2 \\
+Sum Subset &  & 5 & 2 \\
+\hline
 Anti-Bandwidth & Biere & 187 & 14 \\
@@
 Cover & Gacek & 18 & 13 \\
-Cryptography & Paxian, Shaw, Soos & 106 & 34 \\
+\hline
+\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
+ & Shaw &  &  \\
+ & Soos &  &  \\
+\hline
 Discrete Logarithm & Jingchao & 20 & 7 \\
 Edge Matching & Holten & 58 & 7 \\
-Fermat & Riveros & 8 & 5 \\
 Flood-It Puzzle & Stiphout & 40 & 0 \\
@@
 Polynomial Multiplication & Maoluo & 20 & 8 \\
-Schur Coloring & Riveros & 4 & 2 \\
 Station Repacking & Newman & 20 & 12 \\
 Stedman Triples & Johnson & 23 & 7 \\
-Sum Subset & Riveros & 5 & 2 \\
 Tensors & Savicky & 20 & 14 \\
-Termination & Yolcu & 12 & 7 \\
+Termination Analysis & Yolcu & 12 & 7 \\
 Timetable & Djamegni & 20 & 14 \\
@@
 Vlsat & Bouvier & 36 & 14 \\
-\hline
-\multicolumn{2}{|r||}{$\Sigma$} & 1260 & 300 \\
-\hline
+\arrayrulecolor{black}
+\hline
+\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
 \end{tabular}
@@
 
-As can be seen in Table~\ref{tab:families}, a total of $28$ authors followed our calls for participation and benchmark instances, thus contributing a set of $1260$ previously unseen benchmark instances in a large variety of different instance families.
-
-By filtering out instances with could be solved by Minisat in less than $10$ minutes, we obtained an initial set of $1012$ instances. 
-In order to compile a balanced set of $300$ benchmark instances, we considered a maximum of $14$ submissions per author and used the procedure which is depicted in Algorithm~\ref{algo:select}. 
-Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (lines~3 and~4). 
-If this did not yield a total of $14$ instances, we added instances of yet unknown outcome (lines~5--7). 
+As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances of a large variety of different instance families. 
+In order to compile a balanced set of $300$ benchmark instances, we first removed those instances solved by \solver{Minisat} in less than $10$ minutes, thus obtaining a reduced set of $1012$ instances.
+We considered a maximum of $14$ submissions per author using the procedure which is depicted in Algorithm~\ref{algo:select}. 
+Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (Lines~3 and~4). 
+If this did not yield a total of $14$ instances, we added instances of yet unknown result (Lines~5--7). 
 Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
@@
 
-Table~\ref{tab:families} displays the numbers of submitted and selected instances grouped by problem family and author.
-
 \begin{table}[t]
 \centering
-\begin{tabular}{|r|ccc|c|}
-\hline
+\begin{tabular}{rcccc}
  & SAT & UNSAT & UNKNOWN & $\Sigma$\\
-\hline\hline
+\hline
 New Instances & 114 & 78 & 108 & 300 \\
@@
 \hline
-$\Sigma$ & 135 & 135 & 130 & 400\\
-\hline
+$\Sigma$ & 135 & 135 & 130 & 400
 \end{tabular}
@@
    & 5173.2 & 110 & Undominated \\
-      & 5206.0 & 110 & abcdsat\_n20 \\
    & 5244.1 & 107 & PADC\_DL \\
+   & 5264.9 & 110 & f2trc-DL \\           
 \end{tabular}
@@
       & 6774.2 & 73 & Kissat \\
-      & 7003.0 & 69 & optsat\_m20 \\
       & 7025.5 & 68 & upGlucose3.0\_PADC \\
+      & 7044.7 & 66 & Glucose3.0\_proofs \\
 \end{tabular}
@@
 
-\subsection{Best Tuples and Triples}
-
-When selecting solvers for instance-specific algorithm selection, it is interesting to know about the complementarity of the performance of solvers. 
-We created analyzed all pairs and triples of submitted solvers and calculated the PAR-2 score of the VBS of the resulting set of solvers.
-
-\begin{table}
+\subsection{Small Portfolios}
+
+\begin{table}[tb]
 \centering
-\begin{tabular}{|l|l|l|}
-\hline
-Solver 1 & Solver 2 & VBS score \\
-\hline
-\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \\
-\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
-\solver{Kissat} & \solver{CryptoMiniSat-CCAnr} & \\
-\solver{Kissat unsat} & \solver{CryptoMiniSat-CCAnr LSIDS} & \\
-\solver{Kissat} & \solver{Relaxed Maple newTech} & \\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\begin{tabular}{|l|l|l|l|}
-\hline
-Solver 1 & Solver 2 & Solver 3 & VBS score \\
-\hline
-\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-Walksat} & \\
-\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{MapleCOMSPS\_LRB\_VSIDS\_2 init} &  \\
-\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{CryptoMiniSat-CCAnr} & \\
-\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip\_trail} & \\
-\solver{Kissat unsat} & \solver{Relaxed Maple newTech} & \solver{cadical\_alluip} & \\
-\hline
-\end{tabular}
-\end{table}
+\begin{tabular}{lll}
+\bf Solver 1 & \bf Solver 2 & \bf VBS\\
+\hline\arrayrulecolor{lightgray}
+\multirow{3}{*}{\solver{Kissat}} & \solver{CMS-CCAnr} & $3028.0$\\
+ & \solver{CMS-CCAnr lsids} & $3052.8$\\
+ & \solver{CMS-Walksat} & $3127.7$\\
+\hline
+\solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-CCAnr}} & $3128.0$\\
+\solver{CaDiCaL-alluip-trail} &  & $3128.0$\\
+\solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-Walksat}} & $3152.8$\\
+\solver{CaDiCaL-alluip-trail} &  & $3152.9$\\
+\hline
+\solver{Kissat} & \multirow{2}{*}{\solver{Relaxed-newTech}} & $3177.7$\\
+\solver{Kissat-unsat} &  & $3177.8$
+\end{tabular}
+\caption{The $9$ best performing tuples of solvers in terms of their VBS' PAR-2 score.}
+\label{tab:best-tuples}
+\end{table}
+
+\begin{table}[tb]
+\centering
+\begin{tabular}{llll}
+\bf Solver 1 & \bf Solver 2 & \bf Solver 3 & \bf VBS\\
+\hline\arrayrulecolor{lightgray}
+\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{f2trc-DL} & $2827.7$\\
+\hline
+\multirow{3}{*}{\solver{Kissat}} & \multirow{3}{*}{\solver{CMS-CCAnr}} & \solver{Scavel01} & $2852.7$\\
+ &  & \solver{f2trc-DL} & $2852.8$\\
+ &  & \solver{DurianSat} & $2852.8$\\
+\hline
+\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{Scavel01}& $2877.6$\\
+%\solver{Kissat-unsat} & \solver{CryptoMiniSat-Walksat} & \solver{f2trc-DL} & $2877.8$\\
+%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-Walksat} & \solver{DurianSat} & $2877.8$\\
+%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-Walksat} & \solver{f2trc-DL} & $2877.8$\\
+%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-CCAnr} & \solver{Kissat} & $2877.8$\\
+\end{tabular}
+\caption{The $5$ best performing triples of solvers in terms of their VBS' PAR-2 score.}
+\label{tab:best-triples}
+\end{table}
+
+\begin{table}[tb]
+\centering
+\setlength\tabcolsep{4.5pt}
+\begin{tabular}{lllll}
+\bf Solver 1 & \bf Solver 2 & \bf Solver 3 & \bf Solver 4 & \bf VBS\\
+\hline\arrayrulecolor{lightgray}
+\multirow{2}{*}{\solver{Kissat}} & \multirow{2}{*}{\solver{CMS-CCAnr}} & \multirow{2}{*}{\solver{Scavel01}} & \solver{CaDiCaL-alluip} & 2727.7\\
+ &  &  & \solver{CaDiCaL-alluip-trail} & 2727.7\\
+\hline
+\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{f2trc-DL} & \solver{exp-V-LGB} & 2752.5\\
+\hline
+\solver{Kissat} & \solver{CaDiCaL-2020} & \solver{Scavel01} & \solver{Relaxed-newTech} & 2752.6\\
+% & \solver{CMS-CCAnr lsids} & \solver{Scavel01} & \solver{f2trc-DL} & 2752.6
+\end{tabular}
+\caption{The $4$ best performing quatruples of solvers in terms of their VBS' PAR-2 score.}
+\label{tab:best-quatruples}
+\end{table}
+
+The PAR-2 score of the VBS of all $48$ submitted solvers is $2701$. 
+This is much better than the PAR-2 score of the single best solver (SBS) $3926$. 
+In order to further analyze the contribution of solvers to the VBS, we calculated the PAR-2 score of the VBS of fixed-size subsets of the submitted solvers. 
+In the following, we report on the best scores achieved by tuples, triples and quatruples of solvers in terms of their VBS's PAR-2 score.
+
+The best scoring solver tuple is \solver{Kissat} and \solver{CryptoMiniSat-CCAnr}. 
+The VBS of those two solvers achieved a PAR-2 score of $3028$. 
+Further well performing solver tuples can be created from combinations of \solver{CaDiCaL-alluip} and \solver{CryptoMiniSat-CCAnr} or \solver{Kissat} and \solver{Relaxed-newTech}. 
+A detailed report on the exact variants and scores of those solver tuples can be seen in Table~\ref{tab:best-tuples}.
+
+The best triple of solvers is \solver{Kissat}, \solver{CryptoMiniSat-CCAnr lsids} and \solver{f2trc-DL}. 
+In combination their VBS achieves a PAR-2 score of $2827.7$. 
+Other combinations of \solver{Kissat} and \solver{CryptoMiniSat-CCAnr} with \solver{Scavel01} or \solver{DurianSat} achieved runner-up scores as can be seen in Table~\ref{tab:best-triples}.
+
+With a PAR-2 score of $2727.7$ the solver quatruple \solver{Kissat}, \solver{CryptoMiniSat-CCAnr}, \solver{Scavel01} and \solver{CaDiCaL-alluip} is very close to the overall VBS. 
+Runner-up and further best performing quatruples can be seen in Table~\ref{tab:best-quatruples}.
 

### 2021-01-18 paper/main.tex
updated plots

@@
 
-The incremental library track was first introduced in SAT~Race~2015 and 
-then took place again in SAT~Competitions 2016 and 2017. 
-Benchmarks for the incremental track are divided into two parts: 
-Applications which implement and use an incremental SAT solver in their backend and benchmark instances which serve as input to these applications. 
-For evaluating the incremental library track of this competition, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning.
+The incremental library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017. 
+Benchmarks for the Incremental Library track constist of \emph{benchmark applications} which implement and use the incremental SAT solver in their backend as well as \emph{benchmark instances} which serve as input to these applications.
+For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
 For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.
@@
 
-The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding of the given instance~\cite{Balyo:2015:SATRace}.
-Backbone variables have the same value in all models of a formula~\cite{Janota:2015:Backbones}. 
+Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Janota:2015:Backbones}. 
+The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
 We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.
@@
 
+Essential variables are defined to be those variables which have to be assigned in all partial models of a formula (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
 The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
-Essential variables have to be assigned in all partial models of a formula~\cite{Bryant:1987:Essentials}. 
 We used the same $50$ easy satisfiable instances as in backbone detection to evaluate solver performance with this application.
@@
 
-The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are then input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
+The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
 The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
@@
 
-\todo{New Codebases}
-
-\todo{Winners and Runtime Plots for all the tracks}
-
 \subsection{Planning Track}
@@
 % - all 200 above 90\% binary clauses and half have above 99%
-The instances of the planning track are big compared to the rest of the
+The instances of the Planning track are big compared to the rest of the
 main track. Using the number of clauses as a metric; out of the $100$ biggest
@@
 % of the main-track
-$86$ belong to the planning track. The large size can mainly be attributed to
+$86$ belong to the Planning track. The large size can mainly be attributed to
 binary clauses. On average, more than $98$\% of the clauses are binary for
 planning instances, where the average for the rest of the instances from the
-main track is below $60$\%.
+Main track is below $60$\%.
 
@@
 
-\includegraphics[width=0.5\textwidth]{stability/50-50-sat-unsat_random_sampling_scores.png}%
-\includegraphics[width=0.5\textwidth]{stability/276_instances_random_sampling_scores.png}
-\includegraphics[width=0.5\textwidth]{stability/ALL_random_smpling_correlations.png}%
-\includegraphics[width=0.5\textwidth]{stability/SAT_randomSampling_correlations.png}
-\includegraphics[width=0.5\textwidth]{stability/UNSAT_randomSampling_correlations.png}
-
+\includegraphics[width=\textwidth]{stability/ALL_random_smpling_correlations.png}
 \includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
@@
 We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
-Our survey of the winning strategies in this competition starts with sequential (including incremental) SAT solving in Section~\ref{sec:part:seq}, then we continue with parallel SAT solving in Section~\ref{sec:part:par} and conclude with solvers in the cloud track in Section~\ref{sec:part:cloud}.
+Our review of the winning strategies in this competition starts with sequential (including incremental) SAT solving in Section~\ref{sec:part:seq}, then we continue with parallel SAT solving in Section~\ref{sec:part:par} and conclude with solvers in the cloud track in Section~\ref{sec:part:cloud}.
 
@@
 
-Progress in SAT solvers is usually recorded based on successful evaluations of  modifications of existing code-bases. 
+Progress in SAT solvers is often based on successful modifications of existing code-bases. 
 One well-known tree of development is rooted in the code-base of \solver{Minisat} by Eén and Sörenson~\cite{Niklas:2003:Minisat}. 
@@
 The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
-The then award winning variant \solver{MapleCOMSPS} is an implementation of a hybrid branching heuristic of classic Variable-State Independent Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+The then award winning variant \solver{MapleCOMSPS} by Liang et al.
+is an implementation of a hybrid branching heuristic of classic Variable-State Independent Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
 
@@
 Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
-They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} to SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
+They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
 
 Kochemazov et al. improved three-tier clause-management by persisting
-additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
-As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning \solver{Maple} solver.
-
-Starting as a \solver{Minisat}-fork and the integration of special xor treatment~\cite{Soos:2009:Crypto}, \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver.
+additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
+As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning descendants of \solver{Maple}-based solver.
+
+Starting as a fork of \solver{Minisat} and the integration of special xor treatment~\cite{Soos:2009:Crypto}, \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver.
 One highlight of \solver{CryptoMinisat} is its advanced data-logging capabilities for statistical analysis of SAT solver behavior~\cite{Soos:2019:ChrystalBall}.
-In its new version~5, \solver{CryptoMinisat} has once again been award winning in SAT Competition~2020 (see Section~\ref{sec:cryptominisat}).
-
-Many independent and award-winning code-bases can be found among the state-of-the-art SAT solvers written by Biere. 
+
+Many independent and award-winning code-bases can be found among the SAT solvers written by Biere. 
 The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
 As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
-by Biere is another independent award winning and structured implementation of the state-of-the-art in SAT solving. 
+by Biere is another independent, award winning and structured implementation of the state-of-the-art in SAT solving. 
 Its improved reimplementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.
@@
 
-Sequential SAT solvers have been evaluated in the Main tracks as well as in the Incremental track of SAT Competition~2020. 
+Sequential SAT solvers have been evaluated in the Main, Planning and Incremental Library track of SAT Competition~2020. 
 A total of $18$ teams submitted correct solvers to the Main track of the competition. 
@@
 
-Four submissions made it to participate in the Incremental Library track, some of which, e.g, \solver{CryptoMinisat-5}, have also been evaluated and awarded in the Main sequential track. 
+Four submissions made it to participate in the Incremental Library track, some of which, e.g, \solver{CryptoMiniSat-5}, have also been evaluated and awarded in the Main track. 
 Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
@@
 \centering
-\begin{tabular}{|l|l|c|}
-\hline
+\begin{tabular}{llc}
 \bf Team & \bf Solver & \bf Score\\
-\hline
-\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
-\hline
-\stack{Biere, Fleury}~ & CaDiCaL-sc2020 & 1 \\
-\hline
-Chen & abcdsat-i20 & 1 \\
-\hline
-Manthey & Riss-7.1.2 & 1 \\
-\hline
+\hline\arrayrulecolor{lightgray}
+\stack{Soos, Cai, Devriendt, Gocht, }{Shaw, Meel}~ & \solver{CryptoMiniSat 5} & 3 \\
+\hline
+\stack{Biere, Fleury}~ & \solver{CaDiCaL 2020} & 1 \\
+Chen & \solver{abcdsat-i20} & 1 \\
+Manthey & \solver{Riss 7.1.2} & 1 
 \end{tabular}
@@
 
-Three major configurations of \solver{Kissat} were evaluated in this competition. 
-That includes one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively. 
-\solver{Kissat} won \emph{four awards}, by achieving first place in the Main track, first place in the Unsat track, second place in the Sat track and third place in the Planning track.
-
-\solver{Kissat} is a reimplementation of \solver{CaDiCaL} in C,
-but comes with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
+Three configurations of \solver{Kissat} were evaluated in this competition, including one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively.
+\solver{Kissat} received \emph{four awards}, by achieving first place in the Main track, best score on unsatisfiable instances, second best score on satisfiable instances and third place in the Planning track.
+
+\solver{Kissat} is a low-level reimplementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}.
 Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.
 
-\solver{Kissat} uses a new unit (``ticks'') to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses, after conflict-rate has been observed to be too unstable for the use-case~\cite{Biere:SC2020}.
-
-\solver{Kissat} also exploits an innovative use-case for autarkies to account for saved phases. 
+Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses the new unit ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.
+
+Furthermore, \solver{Kissat} exploits autarkies to account for saved phases. 
 In order to keep valuable information of saved phases, before each rephasing step, \solver{Kissat} computes the largest autarky for the assignment implied by the current saved phases~\cite{Kiesl:2019:Autarkies}.
@@
 
-\solver{CryptoMinisat} won \emph{four awards}, two third places in the Main and Sat tracks, one second place in the Planning track, and first place in the Incremental Library track. 
+\solver{CryptoMiniSat} received \emph{four awards}, first place in the Incremental Library track, second place in the Planning track, third place in the Main track, and third best score on satisfiable instances.
 Two submitted variants \solver{default} and \solver{LSIDS} scored mostly adjacent ranks in the evaluation of tracks. 
-The \solver{LSIDS} variant of \solver{CryptoMinisat} comes with a new hybrid phase selection approach~\cite{Shaw:2020:LSIDS,Soos:SC2020}.
-
-\solver{CryptoMinisat} comes with an independent implementation of the recent hybrid branching heuristic which alternates between classic phase saving and target phase selection~\cite{Biere:SC2019}.
-
-\solver{CryptoMiniSat-CCAnr} integrates stochastic local search (SLS) in a unique way~\cite{Cai:2015:CCAnr}. 
-\solver{CryptoMiniSat-CCAnr} regularly schedules short periods of local search and imports the best assignment found by the SLS solver for phase selection -- a procedure which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
+The \solver{LSIDS} variant of \solver{CryptoMiniSat} comes with a new hybrid phase selection approach~\cite{Shaw:2020:LSIDS,Soos:SC2020}.
+
+\solver{CryptoMiniSat} comes with an independent implementation of state-of-the-art hybrid branching heuristics which alternate between classic phase saving and target phase selection~\cite{Biere:SC2019}.
+\solver{CryptoMiniSat-CCAnr} regularly schedules short periods of local search and imports the best assignment for phase selection -- a procedure which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
 In addition, \solver{CryptoMiniSat-CCAnr} bumps the VSIDS scores of the first 100 variables in those clauses which the SLS solver weighs most hard to satisfy~\cite{Soos:SC2020}.
@@
 Inprocessing has been extended to include ternary resolution and more vivification~\cite{ChuMinLi:2020:Vivification}. 
-All the new features are fully supported in \emph{incremental} mode. 
 \solver{CryptoMinisat} alternates decay factors of its branching heuristics, thus avoiding the restriction to a ``single best'' configuration~\cite{Soos:SC2020}. 
@@
 
-Based on \solver{CaDiCaL}, its variants \solver{Trail} and \solver{AllUip} present implementations of a new \emph{Trail Saving} approach~\cite{Hickey:2020:TrailSaving} and improved clause-learing based on the notion of \emph{Stable AllUIP}~\cite{Bacchus:SC2020}.
+Based on \solver{CaDiCaL}, its variants \solver{Trail} and \solver{AllUip} present implementations of a new \emph{Trail Saving} approach~\cite{Hickey:2020:TrailSaving} and improved clause-learning \emph{Stable AllUIP}~\cite{Bacchus:SC2020}.
 Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
-The variants including \emph{Stable AllUIP} were the most successful and won the first price in the Planning Track.
-
-The \emph{Stable AllUip} variants resolve additional clauses beyond the 1st Unit Implication Point (1-UIP) and keep them if they are of smaller size or LBD than the 1-UIP clause. 
-By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
+The variants including \emph{Stable AllUIP} were the most successful and won the first price in the Planning track.
+
+\emph{Stable AllUip} resolves additional clauses beyond the 1st Unit Implication Point (1-UIP) and keeps them if they are of smaller size or LBD than the 1-UIP clause. 
+By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of such extended learning attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
 The \emph{Trail Saving} variant caches backtracked portions of the trail and uses them to restore decision levels during search if possible~\cite{Hickey:2020:TrailSaving}.
@@
 
-The \solver{Relaxed} fork of \solver{MapleLCMDistCBT-DL} was first presented to the community in SAT Race 2019~\cite{Xindi:SC2019}. 
-In SAT Competition~2020, its new variant \solver{newTech} showed a good performance especially on satisfiable instances. 
-The solver won two awards, the second price in the Main track and the first price in the Sat track.
-
-The \solver{Relaxed} fork integrates short runs of the local search solver \solver{CCAnr} through periodic export and import of assignments~\cite{Xindi:SC2019}. 
-The submitted versions of \solver{Relaxed Maple} use a probabilistic schedule for switching between $10$ phase selection modes. 
-The award winning variant \solver{newTech} uses occurrence counts of variables in unsatisfied clauses during SLS runs to recalculate variable priorities for their modified branching heuristic~\cite{Xindi:SC2020}.
+The \solver{Relaxed} fork of \solver{MapleLCMDistCBT-DL} was first presented in SAT Race 2019~\cite{Xindi:SC2019}. 
+In SAT Competition~2020, its variant \solver{newTech} showed a good performance especially on satisfiable instances. 
+The solver achieved two awards, the second price in the Main track and the best score on satisfiable instances.
+
+\solver{Relaxed} integrates short runs of the local search solver \solver{CCAnr} through periodic export and import of assignments~\cite{Xindi:SC2019} and uses a probabilistic schedule for switching between $10$ phase selection modes.
+The \solver{Relaxed newTech} variant uses occurrence counts of variables in unsatisfied clauses during SLS runs to recalculate variable priorities for their modified branching heuristic~\cite{Xindi:SC2020}.
 
@@
 
-The \solver{F2TRC} fork of \solver{MapleLCMDistCBT} won the third price in the Unsat track. 
-\solver{F2TRC} comes with a deterministic reimplementations of former winning strategies, e.g., by replacing time intervals by conflict intervals~\cite{Kochemazov:SC2020}.
-
-\solver{F2TRC} introduces an improved management of learned clauses in the tree tiers \emph{core}, \emph{tier2} and \emph{local} which are inherited from \solver{CoMinisatPS}~\cite{Oh:2015:satunsat}.
+The \solver{F2TRC} fork of \solver{MapleLCMDistCBT} achieved the third best score on unsatisfiable instances. 
+\solver{F2TRC} comes with deterministic reimplementations of former winning strategies in \solver{Maple}, e.g., by replacing time-based intervals through conflict-based intervals~\cite{Kochemazov:SC2020}.
+
+\solver{F2TRC} introduces improved management of learned clauses in the tree tiers \emph{core}, \emph{tier2} and \emph{local} which are inherited from \solver{CoMinisatPS}~\cite{Oh:2015:satunsat}.
 A dynamic size limit for the \emph{core} tier triggers the reassignment of inactive clauses from \emph{core} to \emph{tier2}. 
@@
 \centering
-\begin{tabular}{|l|l|l|}
-\hline
-\bf Team & \bf Solver & \bf Awards\\
-\hline
+\begin{tabular}{llccc}
+\bf Team & \bf Solver & \bf M & \bf U & \bf S \\
+\hline\arrayrulecolor{lightgray}
 \multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
- & \solver{Painless-MCOMSPS-STR-32} & \firsto \firsts \secondu \\
- & \solver{Painless-MCOMSPS-STR-64} & \firsto \\
+ & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
+ & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
 \hline
 \multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
- & \solver{Plingeling} & \secondo \thirds \firstu \\
- & \solver{Treengeling} & \\
+ & \solver{Plingeling} & 2 & 1 & 3 \\
+ & \solver{Treengeling} & --& --& --\\
 \hline
 \multirow{2}{*}{Nabeshima, Inoue}
- & \solver{ManyGlucose-32} & \thirdo \thirdu \\
- & \solver{ManyGlucose-64} & \thirdu \\
+ & \solver{ManyGlucose-32} & 3 & 3 & -- \\
+ & \solver{ManyGlucose-64} & -- & 3 & --\\
 \hline
 \multirow{2}{*}{Tchinda, Djamegni}
- & \solver{painlessmaplevone} & \seconds \\
- & \solver{painlessmaplevtwo} & \seconds \\
-\hline
-Li, Wu, Xu, Chen & \solver{syrupscavel} & \\
-\hline
-Chen & \solver{abcdsatptwenty} & \\
-\hline
+ & \solver{painlessmaplevone} & --& --& 2 \\
+ & \solver{painlessmaplevtwo} & --& --& 2 \\
+\hline
+Li, Wu, Xu, Chen & \solver{syrupscavel} & --& --& --\\
+\hline
+Chen & \solver{abcdsatptwenty} & --& --& --
 \end{tabular}
@@
 
-\subsubsection{Painless Maple-CoMinisatPS STR}
+\subsubsection{Painless MCOMSPS STR}
 
 \solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32 core} and a \solver{64 core} variant and were awarded three prices: first place in the Main track, first place in the Sat track and second in the Unsat track. 
+The authors submitted a \solver{32 core} and a \solver{64 core} variant and won three awards: first place in the Main track, best score on satisfiable and second best score on unsatisfiable instances.
 The \solver{32 core} variant achieved slightly better scores than the \solver{64 core} variant. 
-The differentiated evaluation of the Sat and Unsat tracks shows the \solver{32 core} variant performed much better, such that the follow-up solvers outperformed the \solver{64 core} variant.
-
-\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrent data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies.
-
-\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random initialization of variable polarities~\cite{Balyo:2015:Hordesat}.
+The \solver{32 core} variant performed much better, such that the runner-up solvers on satisfiable and unsatisfiable instances outperformed the \solver{64 core} variant.
+
+\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrent data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies~\cite{Frioux:2017:Painless}.
+
+\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}.
 However, a special solver instance performs concurrent clause strengthening~\cite{Wieringa:2013:CCS}. 
 Another special solver instance is configured to perform Gaussian elimination during preprocessing. 
-\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit.
+\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
 
@@
 
-\solver{Plingeling} got three awards: first place in the Unsat track, second place in the Main track, third place in the Sat track. 
+\solver{Plingeling} achieved the best score on unsatisfiable instances, second place in the Main track, and the third best score on satisfiable instances. 
 \solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
 In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
-\solver{Plingeling} uses random seeds for diversification via default polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.
+\solver{Plingeling} uses random seeds for diversification via polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.
 
@@
 \solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
-The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
+The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third best score on unsatisfiable instances. 
 \solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
@@
 \solver{Painless Maple} received the award for the second best performance in the Sat track but scored last in the Unsat track. 
-\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT}, which is a modified \solver{MapleLCMDistChronoBT} (see Main track), in the \solver{Painless} parallelization framework.
+\solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}.
 
@@
 \solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
-\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics.
+\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics~\cite{SC2020}.
 
@@
 \centering
-\begin{tabular}{|l|l|l|}
-\hline
+\begin{tabular}{llc}
 \bf Team & \bf Solver & \bf Rank\\
-\hline
+\hline\arrayrulecolor{lightgray}
 Schreiber & \solver{mallob-mono} & 1\\
@@
 \hline
-\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & \solver{Paracooba} & -\\
-& \solver{Paracooba-March} & -\\
-\hline
-Hartung & \solver{CTSat} & -\\
-\hline
+\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & \solver{Paracooba}, & --\\
+& \solver{Paracooba-March} & --\\
+\hline
+Hartung & \solver{CTSat} & --
 \end{tabular}
@@
 \solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
-Each node performs a three-way merge of its local export and the two incoming buffers. 
+Each node performs a three-way merge of its local export buffer and the two incoming buffers. 
 The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{Schreiber:SC2020}.
@@
 Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
-Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{Schreiber:SC2020}.
+Duplicates are avoided by using a bloom filter which is cleared periodically~\cite{Schreiber:SC2020}.
 
@@
 
-\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
+\solver{TopoSAT~2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
 \solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
@@
 The total number of solved problems was 316. 
-There were 54 (non-disqualified) solvers (and their configurations).
+There were 48 (non-disqualified) solvers (and their configurations).
 Each table shows the first ten solvers sorted according to the respective metric.}
@@
 46 & 11.5 & Kissat-unsat \\
-37 & \phantom{0}9.2 & Kissat-sat \\
-24 & \phantom{0}6.0 & Kissat \\
+39 & \phantom{0}9.8 & Kissat-sat \\
+26 & \phantom{0}6.5 & Kissat \\
 18 & \phantom{0}4.5 & CMS-ccnr-lsids \\
 14 & \phantom{0}3.5 & MapleCM+dist+sat2s \\
+13 & \phantom{0}3.2 & Relaxed \\
 13 & \phantom{0}3.2 & Maple-alluip-trail \\
-12 & \phantom{0}3.0 & Relaxed \\
-11 & \phantom{0}2.8 & upGlucose3.0\_PADC \\
+12 & \phantom{0}3.0 & upGlucose3.0\_PADC \\
+10 & \phantom{0}2.5 & CMS-ccnr \\
 10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
-\phantom{0}9 & \phantom{0}2.2 & CMS-ccnr \\
 \end{tabular}
@@
 \hline
-130.3 & 32.6 & Kissat-sat \\
-120.7 & 30.2 & Kissat \\
-114.0 & 28.5 & Kissat-unsat \\
-\phantom{0}91.5 & 22.9 & CMS-ccnr-lsids \\
-\phantom{0}87.8 & 22.0 & CMS-ccnr \\
-\phantom{0}82.3 & 20.6 & CaDiCaL-alluip-trail \\
-\phantom{0}82.2 & 20.5 & CaDiCaL-alluip \\
-\phantom{0}81.9 & 20.5 & CaDiCaL-sc2020 \\
-\phantom{0}81.4 & 20.4 & Relaxed\_newTech \\
-\phantom{0}80.8 & 20.2 & Relaxed \\
+131.5 & 32.9 & Kissat-sat \\
+122.6 & 30.6 & Kissat \\
+115.4 & 28.9 & Kissat-unsat \\
+\phantom{0}92.3 & 23.1 & CMS-ccnr-lsids \\
+\phantom{0}88.8 & 22.2 & CMS-ccnr \\
+\phantom{0}84.1 & 21.0 & CaDiCaL-alluip-trail \\
+\phantom{0}84.0 & 21.0 & CaDiCaL-alluip \\
+\phantom{0}83.0 & 20.7 & CaDiCaL-sc2020 \\
+\phantom{0}82.3 & 20.6 & Relaxed\_newTech \\
+\phantom{0}81.5 & 20.4 & Relaxed \\
 \end{tabular}
@@
 \hline
-12.4 & 3.1 & Kissat \\
-11.4 & 2.9 & Kissat-unsat \\
-11.4 & 2.8 & Relaxed\_newTech \\
-10.7 & 2.7 & Kissat-sat \\
-10.3 & 2.6 & CaDiCaL-alluip-trail \\
-10.3 & 2.6 & CaDiCaL-alluip \\
-10.0 & 2.5 & Relaxed \\
-\phantom{0}9.9 & 2.5 & CaDiCaL-sc2020 \\
-\phantom{0}9.7 & 2.4 & CMS-walksat \\
-\phantom{0}9.2 & 2.3 & CaDiCaL-trail \\
+13.0 & 3.3 & Kissat \\
+11.9 & 3.0 & Kissat-unsat \\
+11.7 & 2.9 & Relaxed\_newTech \\
+11.4 & 2.8 & Kissat-sat \\
+10.8 & 2.7 & CaDiCaL-alluip-trail \\
+10.8 & 2.7 & CaDiCaL-alluip \\
+10.5 & 2.6 & Relaxed \\
+10.4 & 2.6 & CaDiCaL-sc2020 \\
+10.3 & 2.6 & CMS-walksat \\
+\phantom{0}9.6 & 2.4 & CaDiCaL-trail \\
 \end{tabular}
@@
 The total number of solved problems was 182. 
-There were 54 (non-disqualified) participating solvers.
+There were 48 (non-disqualified) participating solvers.
 Each table always shows the first ten solvers sorted according to the respective metric.}
@@
 \hline
-27 & 14.8 & Kissat-sat \\
+29 & 15.9 & Kissat-sat \\
+16 & \phantom{0}8.8 & Kissat \\
 14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
-14 & \phantom{0}7.7 & Kissat \\
 12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
@@
 \hline
-69.0 & 37.9 & Kissat-sat \\
-46.9 & 25.7 & Kissat \\
-44.6 & 24.5 & CMS-ccnr-lsids \\
-42.6 & 23.4 & Relaxed\_newTech \\
-41.7 & 22.9 & CMS-ccnr \\
-41.0 & 22.5 & Relaxed \\
-33.1 & 18.2 & CMS-walksat \\
-32.9 & 18.1 & CaDiCaL-alluip-trail \\
-32.8 & 18.0 & CaDiCaL-alluip \\
-31.8 & 17.5 & CaDiCaL-sc2020 \\
+70.1 & 38.5 & Kissat-sat \\
+48.6 & 26.7 & Kissat \\
+45.2 & 24.8 & CMS-ccnr-lsids \\
+43.4 & 23.8 & Relaxed\_newTech \\
+42.4 & 23.3 & CMS-ccnr \\
+41.6 & 22.8 & Relaxed \\
+34.7 & 19.0 & CaDiCaL-alluip-trail \\
+34.6 & 19.0 & CaDiCaL-alluip \\
+33.7 & 18.5 & CMS-walksat \\
+32.8 & 18.0 & CaDiCaL-sc2020 \\
 \end{tabular}
@@
 \hline
-9.0 & 4.9 & Relaxed\_newTech \\
-7.7 & 4.2 & Relaxed \\
-7.3 & 4.0 & CMS-walksat \\
-6.4 & 3.5 & Kissat-sat \\
-6.2 & 3.4 & CMS-ccnr-lsids \\
-6.2 & 3.4 & Kissat \\
-6.2 & 3.4 & CMS-ccnr \\
-5.7 & 3.2 & CaDiCaL-alluip-trail \\
-5.7 & 3.2 & CaDiCaL-alluip \\
-5.7 & 3.1 & CaDiCaL-sc2020 \\
+9.3 & 5.1 & Relaxed\_newTech \\
+8.1 & 4.4 & Relaxed \\
+7.8 & 4.3 & CMS-walksat \\
+7.0 & 3.8 & Kissat-sat \\
+6.7 & 3.7 & Kissat \\
+6.7 & 3.7 & CMS-ccnr \\
+6.6 & 3.6 & CMS-ccnr-lsids \\
+6.2 & 3.4 & CaDiCaL-sc2020 \\
+6.2 & 3.4 & CaDiCaL-alluip-trail \\
+6.2 & 3.4 & CaDiCaL-alluip \\
 \end{tabular}
@@
 The total number of solved problems was 134. 
-There were 49 (non-disqualified) participating solvers.
+There were 48 (non-disqualified) participating solvers.
 Each table always shows the first ten solvers sorted according to the respective metric.}
@@
 \phantom{0}8 & \phantom{0}6.0 & MapleCMused+dist \\
+\phantom{0}7 & \phantom{0}5.2 & upGlucose3.0\_PADC \\
 \phantom{0}6 & \phantom{0}4.5 & CMS-ccnr-lsids \\
-\phantom{0}6 & \phantom{0}4.5 & upGlucose3.0\_PADC \\
 \phantom{0}3 & \phantom{0}2.2 & f2trc \\
+\phantom{0}3 & \phantom{0}2.2 & Relaxed \\
 \phantom{0}3 & \phantom{0}2.2 & Glucose3.0\_proofs \\
-\phantom{0}3 & \phantom{0}2.2 & DurianSat \\
 \end{tabular}
@@
 \hline
-86.3 & 64.4 & Kissat-unsat \\
-73.8 & 55.1 & Kissat \\
-61.3 & 45.7 & Kissat-sat \\
-55.4 & 41.3 & f2trc-s \\
-55.0 & 41.0 & DurianSat \\
+86.5 & 64.6 & Kissat-unsat \\
+74.0 & 55.2 & Kissat \\
+61.4 & 45.8 & Kissat-sat \\
+55.4 & 41.4 & f2trc-s \\
+55.2 & 41.2 & DurianSat \\
 53.6 & 40.0 & Maple-alluip-trail \\
-53.3 & 39.8 & f2trc \\
+53.4 & 39.8 & f2trc \\
 52.4 & 39.1 & f2trc-DL \\
-51.7 & 38.6 & MapleCMused+dist \\
-51.6 & 38.5 & PADC\_DL \\
+51.8 & 38.6 & MapleCMused+dist \\
+51.7 & 38.6 & PADC\_DL \\
 \end{tabular}
@@
 6.7 & 5.0 & Kissat-unsat \\
-6.2 & 4.7 & Kissat \\
-4.6 & 3.4 & CaDiCaL-trail \\
-4.6 & 3.4 & CaDiCaL-alluip-trail \\
-4.6 & 3.4 & CaDiCaL-alluip \\
-4.3 & 3.2 & Kissat-sat \\
-4.2 & 3.1 & CaDiCaL-sc2020 \\
-3.4 & 2.5 & f2trc-s \\
-3.3 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
-3.0 & 2.3 & f2trc-DL \\
+6.3 & 4.7 & Kissat \\
+4.7 & 3.5 & CaDiCaL-trail \\
+4.6 & 3.5 & CaDiCaL-alluip-trail \\
+4.6 & 3.5 & CaDiCaL-alluip \\
+4.4 & 3.3 & Kissat-sat \\
+4.3 & 3.2 & CaDiCaL-sc2020 \\
+3.5 & 2.6 & f2trc-s \\
+3.4 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
+3.1 & 2.3 & f2trc-DL \\
 \end{tabular}
@@
 
-VBS2 highlights as first Kissat-sat. Its leading \SI{32.6}{\percent} of total is a bit harder to 
-interpret: A solver can score \SI{32.6}{\percent} of VBS2 total
-by solving \SI{32.6}{\percent} of the solved instances in the best observed time
-and no others. But we know, thanks to its VBS1, that Kissat-sat solved \SI{9.2}{\percent}
+VBS2 highlights as first Kissat-sat. Its leading \SI{32.9}{\percent} of total is a bit harder to 
+interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
+by solving \SI{32.9}{\percent} of the solved instances in the best observed time
+and no others. But we know, thanks to its VBS1, that Kissat-sat solved \SI{9.8}{\percent}
 of the solved instances in the best observed time (and some others).
-A solver can also score \SI{32.6}{\percent} of VBS2 total by solving all the solved instances,
+A solver can also score \SI{32.9}{\percent} of VBS2 total by solving all the solved instances,
 but always being roughly 3 times slower than the VBS. 
@@
 
-Finally, according to VBS3, the best solver is Kissat with 12.4 points,
-which amounts to \SI{3.1}{\percent} of the distributed total score.
+Finally, according to VBS3, the best solver is Kissat with 13.0 points,
+which amounts to \SI{3.3}{\percent} of the distributed total score.
 The VBS3 metric is generally the most evenly distributed one,
 at least among the first 10 solvers. 
-(The last solver got 1.0 points which is \SI{0.256}{\percent} of the total.)
+(The last solver got 0.9 points which is \SI{0.221}{\percent} of the total.)
 One can conclude from this that most of the benchmarks are solved
@@
 \begin{table}
-\caption{TODO}
+\caption{An optimal \SI{5000}{\second} schedule for the Main track
+constructed using Z3.}
 \label{tab:MainZ3Schedule}
@@
 \begin{tabular}{lccc}
-solver & taking up (s) & solving & contributes \\
+solver & taking up (s) & solving under limit & contributes \\
 \hline

### 2021-01-18 paper/main.tex
table and solver-name formatting

@@
 \begin{abstract}
-The SAT Competitions constitute a well-established series of yearly open international competitive algorithm implementation competitions
+The SAT Competitions constitute a well-established series of yearly open international algorithm implementation competitions
 focusing on the Boolean satisfiability (or propositional satisfiability, SAT) problem. 
@@
 In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
-on the SAT competition webpages (\url{https://satcompetition.github.io/2020/}). Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.
-
-The rest of this article is organized as follows. TODO -MJ
-
-===
-
-OLD:
-
-In Section~\ref{sec:overview}, we start with an overview of the competition,
-including detailed description of the competition tracks and their purpose,
-the general rules and the used computing environment.
-Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
-In Section~\ref{sec:results}, we present the competition results alongside a survey on the winning strategies of the award winning solvers. 
-A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.
-
-OLD END ===
-
-\section{Overview of the Competition}
+on the SAT competition webpages (\url{https://satcompetition.github.io/2020/}). 
+Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.
+
+The rest of this article is organized as follows. 
+We start by providing an overview on the competition, including details on and motivations for the several
+competition tracks, the rules and other technical requirements of the competition, the ranking schemes used
+in evaluating the competing solvers, 
+and the computing environments used for executing the competition
+(Section~\ref{sec:overview}).
+We then provide an overview of the benchmark sets used in evaluating the solvers, including their origins and the selection
+process used for constructing the sets (Section~\ref{sec:instances}).
+In Section~\ref{sec:results} we provide an overview of the competition results together with  a survey on the
+the solving strategies implemented distinctly in  top-ranking  solvers. 
+Going considerably beyond the plain competition rankings, we provide more in-depth analysis of the competition 
+data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
+of individual solvers to the ``virtual best solver'' and 
+portfolios constructed from the competing solvers,  (Section~\ref{sec:analysis}.
+The article is concluded with future prospects in Section~\ref{sec:conclusion}.
+\todo{Need to decide on final structure regardign the results overview and analysis}
+
+\section{Overview of SAT Competition 2020}
 \label{sec:overview}
@@
 
-\section{Description of Benchmark Instances}
+\section{Benchmarks}
 \label{sec:instances}
@@
 The ``Bring Your Own Benchmarks'' (BYOB) rule is established since SAT Competition 2017~\cite{SC2017}. 
-By this rule solver authors are required to submit $20$ new benchmark instances in order to participate in the competition.
+By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition.
 At least $10$ of these instances are required to be ``interesting'', meaning that Minisat must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.
@@
 To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
-We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable and $130$ instances of unknown result. 
-Furthermore, we made sure not to select instances of a family which is already represented in the set of newly submitted instances and excluded random, agile and planning instances (due to the planning track).
+We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result. 
+Furthermore, we made sure not to select instances of families which are already represented in the set of newly submitted instances and moreover excluded random, agile and planning instances (due to the Planning track).
 
@@
 \begin{table}
+\centering
+\begin{tabular}{cccl}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline
+1     & 3926.2 & 264 & \solbert{Kissat-sat} \\
+(1)   & 4083.1 & 260 & \solver{Kissat} \\
+2     & 4179.3 & 253 & \solbert{Relaxed-newTech} \\
+3     & 4266.7 & 248 & \solbert{CMS-ccnr-lsids} \\
+(3)   & 4278.0 & 250 & \solver{CMS-ccnr} \\
+      & 4428.1 & 250 & \solver{CaDiCaL-alluip-trail} \\
+      & 4429.6 & 250 & \solver{CaDiCaL-alluip} \\
+      & 4436.5 & 245 & \solver{Relaxed} \\
+      & 4501.2 & 243 & \solver{CMS-walksat} \\
+      & 4554.0 & 243 & \solver{CaDiCaL-trail} \\
+      & 4560.0 & 238 & \solver{Kissat-unsat} \\
+      & 4607.6 & 246 & \solver{CaDiCaL-sc2020} \\
+      & 5157.7 & 216 & \solver{Undominated} \\
+      & 5159.6 & 220 & \solver{f2trc-DL} \\
+      & 5177.0 & 214 & \solver{PADC-DL} \\              
+\end{tabular}
 \caption{Main ALL}
 \label{tab:mainALL}
+\end{table}
+
+\begin{table}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline
-1     & 3926.2 & 264 & {\bf Kissat-sat} \\
-(1)   & 4083.1 & 260 & Kissat \\
-2     & 4179.3 & 253 & {\bf Relaxed\_newTech} \\
-3     & 4266.7 & 248 & {\bf CMS-ccnr-lsids} \\
-(3)   & 4278.0 & 250 & CMS-ccnr \\
-      & 4428.1 & 250 & CaDiCaL-alluip-trail \\
-      & 4429.6 & 250 & CaDiCaL-alluip \\
-      & 4436.5 & 245 & Relaxed \\
-      & 4501.2 & 243 & CMS-walksat \\
-      & 4554.0 & 243 & CaDiCaL-trail \\
-      & 4560.0 & 238 & Kissat-unsat \\
-      & 4607.6 & 246 & CaDiCaL-sc2020 \\
-      & 5157.7 & 216 & Undominated \\
-      & 5159.6 & 220 & f2trc-DL \\
-      & 5177.0 & 214 & PADC\_DL \\              
-\end{tabular}
-\end{table}
-
-\begin{table}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline
+ 1    & 2997.4 & 150 & \solbert{Relaxed\_newTech} \\
+ 2    & 3127.6 & 146 & \solbert{Kissat-sat} \\
+ 3    & 3263.0 & 144 & \solbert{CMS-ccnr-lsids} \\
+(3)   & 3317.4 & 145 & \solver{CMS-ccnr} \\
+      & 3355.5 & 143 & \solver{Relaxed} \\
+      & 3721.2 & 139 & \solver{CMS-walksat} \\
+      & 3830.5 & 134 & \solver{Kissat} \\
+      & 3908.5 & 135 & \solver{CaDiCaL-alluip-trail} \\
+      & 3909.6 & 135 & \solver{CaDiCaL-alluip} \\
+      & 4265.6 & 126 & \solver{CaDiCaL-trail} \\
+      & 4368.6 & 130 & \solver{CaDiCaL-sc2020} \\
+   & 4804.9 & 114 & \solver{Kissat-unsat} \\
+   & 5173.2 & 110 & \solver{Undominated} \\
+   & 5244.1 & 107 & \solver{PADC-DL} \\
+   & 5264.9 & 110 & \solver{f2trc-DL} \\           
+\end{tabular}
 \caption{Main SAT}
 \label{tab:mainSAT}
+\end{table}
+
+\begin{table}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline
- 1    & 2997.4 & 150 & {\bf Relaxed\_newTech} \\
- 2    & 3127.6 & 146 & {\bf Kissat-sat} \\
- 3    & 3263.0 & 144 & {\bf CMS-ccnr-lsids} \\
-(3)   & 3317.4 & 145 & CMS-ccnr \\
-      & 3355.5 & 143 & Relaxed \\
-      & 3721.2 & 139 & CMS-walksat \\
-      & 3830.5 & 134 & Kissat \\
-      & 3908.5 & 135 & CaDiCaL-alluip-trail \\
-      & 3909.6 & 135 & CaDiCaL-alluip \\
-      & 4265.6 & 126 & CaDiCaL-trail \\
-      & 4368.6 & 130 & CaDiCaL-sc2020 \\
-   & 4804.9 & 114 & Kissat-unsat \\
-   & 5173.2 & 110 & Undominated \\
-   & 5244.1 & 107 & PADC\_DL \\
-   & 5264.9 & 110 & f2trc-DL \\           
-\end{tabular}
-\end{table}
-
-\begin{table}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline   
+1     & 4315.1 & 124 & \solbert{Kissat-unsat} \\
+(1)   & 4335.6 & 126 & \solver{Kissat} \\
+(1)   & 4724.8 & 118 & \solver{Kissat-sat} \\
+ 2    & 4842.5 & 117 & \solbert{CaDiCaL-trail} \\
+--    & 4846.7 & 116 & \solver{CaDiCaL-sc2020} \\
+(2)   & 4947.8 & 115 & \solver{CaDiCaL-alluip-trail} \\
+(2)   & 4949.6 & 115 & \solver{CaDiCaL-alluip} \\
+ 3    & 4991.4 & 110 & \solbert{f2trc-s} \\
+(3)   & 5051.4 & 109 & \solver{f2trc} \\
+(3)   & 5054.3 & 110 & \solver{f2trc-DL} \\
+      & 5069.6 & 109 & \solver{Maple-Mix} \\
+      & 5110.0 & 107 & \solver{PADC-DL} \\
+      & 5126.9 & 107 & \solver{Maple-Simp} \\
+      & 5128.9 & 107 & \solver{MapleCBT-DL-v3} \\
+      & 5142.2 & 106 & \solver{Undominated} \\      
+\end{tabular}
 \caption{Main UNSAT}
 \label{tab:mainUNSAT}
+\end{table}
+
+\begin{table}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline   
-1     & 4315.1 & 124 & {\bf Kissat-unsat} \\
-(1)   & 4335.6 & 126 & Kissat \\
-(1)   & 4724.8 & 118 & Kissat-sat \\
- 2    & 4842.5 & 117 & {\bf CaDiCaL-trail} \\
---    & 4846.7 & 116 & CaDiCaL-sc2020 \\
-(2)   & 4947.8 & 115 & CaDiCaL-alluip-trail \\
-(2)   & 4949.6 & 115 & CaDiCaL-alluip \\
- 3    & 4991.4 & 110 & {\bf f2trc-s} \\
-(3)   & 5051.4 & 109 & f2trc \\
-(3)   & 5054.3 & 110 & f2trc-DL \\
-      & 5069.6 & 109 & Maple\_Mix \\
-      & 5110.0 & 107 & PADC\_DL \\
-      & 5126.9 & 107 & Maple\_Simp \\
-      & 5128.9 & 107 & MapleCBT-DL-v3 \\
-      & 5142.2 & 106 & Undominated \\      
-\end{tabular}
-\end{table}
-
-\begin{table}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline   
+ 1    & 6406.9 & 80 & \solbert{CaDiCaL-alluip-trail} \\
+(1)   & 6409.3 & 80 & \solver{CaDiCaL-alluip} \\
+ 2    & 6466.9 & 79 & \solbert{CMS-ccnr-lsids} \\
+(2)   & 6471.9 & 79 & \solver{CMS-ccnr} \\
+(2)   & 6472.9 & 79 & \solver{CMS-walksat} \\
+ 3    & 6596.4 & 75 & \solbert{Kissat-unsat} \\
+      & 6650.1 & 79 & \solver{CaDiCaL-trail} \\
+      & 6713.0 & 75 & \solver{Maple-Mix} \\
+      & 6746.5 & 75 & \solver{MapleCOMSPS-init} \\
+      & 6754.3 & 73 & \solver{Maple-Simp} \\
+      & 6773.0 & 73 & \solver{MapleCOMSPS-drup} \\
+      & 6773.9 & 73 & \solver{Kissat-sat} \\
+      & 6774.2 & 73 & \solver{Kissat} \\
+      & 7025.5 & 68 & \solver{upGlucose3.0-PADC} \\
+      & 7044.7 & 66 & \solver{Glucose3.0-proofs} \\
+\end{tabular}
 \caption{Planning (ALL)}
 \label{tab:planning}
+\end{table}
+
+\begin{table}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline   
- 1    & 6406.9 & 80 & {\bf CaDiCaL-alluip-trail} \\
-(1)   & 6409.3 & 80 & CaDiCaL-alluip \\
- 2    & 6466.9 & 79 & {\bf CMS-ccnr-lsids} \\
-(2)   & 6471.9 & 79 & CMS-ccnr \\
-(2)   & 6472.9 & 79 & CMS-walksat \\
- 3    & 6596.4 & 75 & {\bf Kissat-unsat} \\
-      & 6650.1 & 79 & CaDiCaL-trail \\
-      & 6713.0 & 75 & Maple\_Mix \\
-      & 6746.5 & 75 & MapleCOMSPS\_init \\
-      & 6754.3 & 73 & Maple\_Simp \\
-      & 6773.0 & 73 & MapleCOMSPS\_drup \\
-      & 6773.9 & 73 & Kissat-sat \\
-      & 6774.2 & 73 & Kissat \\
-      & 7025.5 & 68 & upGlucose3.0\_PADC \\
-      & 7044.7 & 66 & Glucose3.0\_proofs \\
-\end{tabular}
-\end{table}
-
-\begin{table}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline
+ 1 & 3316.6 & 283 & \solbert{Painless-MCOMSPS-STR-32} \\
+(1)& 3714.7 & 271 & \solver{Painless-MCOMSPS-STR-64} \\
+ 2 & 3743.4 & 269 & \solbert{Plingeling} \\
+ 3 & 3985.3 & 260 & \solbert{ManyGlucose-32} \\
+   & 4022.7 & 262 & \solver{Painless-Maple-v1} \\
+   & 4036.3 & 258 & \solver{ManyGlucose-64} \\
+   & 4103.3 & 260 & \solver{Painless-Maple-v2} \\
+   & 4433.3 & 243 & \solver{Syrup-Scavel} \\
+   & 4903.4 & 225 & \solver{Treengeling} \\
+   & 5240.1 & 213 & \solver{abcdsat-p20} \\
+\end{tabular}
 \caption{Parallel (ALL)}
 \label{tab:parallelALL}
+\end{table}
+
+\begin{table}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline
- 1 & 3316.6 & 283 & {\bf pmcompspsthirty} \\
-(1)& 3714.7 & 271 & pmcompspsixty \\
- 2 & 3743.4 & 269 & {\bf plingeling} \\
- 3 & 3985.3 & 260 & {\bf manyglucosethirty} \\
-   & 4022.7 & 262 & painlessmaplevone \\
-   & 4036.3 & 258 & manyglucosesixty \\
-   & 4103.3 & 260 & painlessmaplevtwo \\
-   & 4433.3 & 243 & syrupscavel \\
-   & 4903.4 & 225 & treengeling \\
-   & 5240.1 & 213 & abcdsatptwenty \\
-\end{tabular}
-\end{table}
-
-\begin{table}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline
+ 1 & 2853.7 & 153 & \solbert{Painless-MCOMSPS-STR-32} \\
+ 2 & 2913.6 & 154 & \solbert{Painless-Maple-v1} \\
+(2)& 3082.7 & 151 & \solver{Painless-Maple-v2} \\
+-- & 3196.9 & 148 & \solver{Painless-MCOMSPS-STR-64} \\
+ 3 & 3805.9 & 133 & \solbert{Plingeling} \\
+   & 4048.3 & 130 & \solver{ManyGlucose-64} \\
+   & 4076.2 & 130 & \solver{ManyGlucose-32} \\
+   & 4675.4 & 119 & \solver{Syrup-Scavel} \\
+   & 4907.1 & 114 & \solver{Treengeling} \\
+   & 6337.5 & \phantom{0}85 & \solver{abcdsat-p20} \\
+\end{tabular}
 \caption{Parallel (SAT)}
 \label{tab:parallelSAT}
+\end{table}
+
+\begin{table}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline
- 1 & 2853.7 & 153 & {\bf pmcompspsthirty} \\
- 2 & 2913.6 & 154 & {\bf painlessmaplevone} \\
-(2)& 3082.7 & 151 & painlessmaplevtwo \\
-(1)& 3196.9 & 148 & pmcompspsixty \\
- 3 & 3805.9 & 133 & {\bf plingeling} \\
-   & 4048.3 & 130 & manyglucosesixty \\
-   & 4076.2 & 130 & manyglucosethirty \\
-   & 4675.4 & 119 & syrupscavel \\
-   & 4907.1 & 114 & treengeling \\
-   & 6337.5 & \phantom{0}85 & abcdsatptwenty \\
-\end{tabular}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline
+ 1 & 3680.8 & 136 & \solbert{Plingeling} \\
+ 2 & 3779.5 & 130 & \solbert{Painless-MCOMSPS-STR-32} \\
+ 3 & 3894.3 & 130 & \solbert{ManyGlucose-32} \\
+(3)& 4024.2 & 128 & \solver{ManyGlucose-64} \\
+   & 4142.8 & 128 & \solver{abcdsat-p20} \\
+   & 4191.1 & 124 & \solver{Syrup-Scavel} \\
+   & 4232.5 & 123 & \solver{Painless-MCOMSPS-STR-64} \\
+   & 4899.8 & 111 & \solver{Treengeling} \\
+   & 5123.9 & 109 & \solver{Painless-Maple-v2} \\
+   & 5131.9 & 108 & \solver{Painless-Maple-v1} \\
+\end{tabular}
+\caption{Parallel (UNSAT)}
+\label{tab:parallelUNS}
 \end{table}
@@
 \begin{table}
-\caption{Parallel (UNS)}
-\label{tab:parallelUNS}
+\centering
 \begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline
- 1 & 3680.8 & 136 & {\bf plingeling} \\
- 2 & 3779.5 & 130 & {\bf pmcompspsthirty} \\
- 3 & 3894.3 & 130 & {\bf manyglucosethirty} \\
-(3)& 4024.2 & 128 & manyglucosesixty \\
-   & 4142.8 & 128 & abcdsatptwenty \\
-   & 4191.1 & 124 & syrupscavel \\
-   & 4232.5 & 123 & pmcompspsixty \\
-   & 4899.8 & 111 & treengeling \\
-   & 5123.9 & 109 & painlessmaplevtwo \\
-   & 5131.9 & 108 & painlessmaplevone \\
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{Claud (ALL)}
-\label{tab:claud}
-\begin{tabular}{cccl}
-place & PAR-2 score & num. solved & solver \\
-\hline
- 1 & 2603.8 & 299 & {\bf mallobecs} \\
- 2 & 3146.8 & 278 & {\bf toposat} \\
- 3 & 4797.6 & 213 & {\bf slime} \\
-   & 6800.8 & 132 & paracooba \\
-   & 7299.0 & 110 & ctsat \\
-   & 8468.3 & \phantom{0}62 & paracoobamarch \\
-\end{tabular}
+\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
+\hline
+ 1 & 2603.8 & 299 & \solbert{Mallob-Mono} \\
+ 2 & 3146.8 & 278 & \solbert{TopoSAT 2} \\
+ 3 & 4797.6 & 213 & \solbert{Slime} \\
+   & 6800.8 & 132 & \solver{Paracooba} \\
+   & 7299.0 & 110 & \solver{CTsat} \\
+   & 8468.3 & \phantom{0}62 & \solver{Paracooba-March} \\
+\end{tabular}
+\caption{Cloud (ALL)}
+\label{tab:cloud}
 \end{table}
@@
 \includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
-
-\subsection{Observations}
-
-\paragraph{Marginal Contributions to VBS} Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth''~\cite{} or ``timetable''~\cite{}.
 
@@
 \begin{table}
+\centering
+\begin{tabular}{ccl}
+\bf VBS1 & \bf Percent Total & \bf Solver \\
+\hline
+46 & 11.5 & \solver{Kissat-unsat} \\
+39 & \phantom{0}9.8 & \solver{Kissat-sat} \\
+26 & \phantom{0}6.5 & \solver{Kissat} \\
+18 & \phantom{0}4.5 & \solver{CMS-ccnr-lsids} \\
+14 & \phantom{0}3.5 & \solver{MapleCM+dist+sat2s} \\
+13 & \phantom{0}3.2 & \solver{Relaxed} \\
+13 & \phantom{0}3.2 & \solver{Maple-alluip-trail} \\
+12 & \phantom{0}3.0 & \solver{upGlucose3.0-PADC} \\
+10 & \phantom{0}2.5 & \solver{CMS-ccnr} \\
+10 & \phantom{0}2.5 & \solver{CaDiCaL-sc2020} \\
+\end{tabular}
+~\\[1em]
+\begin{tabular}{ccl}
+\bf VBS2 & \bf Percent Total & \bf Solver \\
+\hline
+131.5 & 32.9 & \solver{Kissat-sat} \\
+122.6 & 30.6 & \solver{Kissat} \\
+115.4 & 28.9 & \solver{Kissat-unsat} \\
+\phantom{0}92.3 & 23.1 & \solver{CMS-ccnr-lsids} \\
+\phantom{0}88.8 & 22.2 & \solver{CMS-ccnr} \\
+\phantom{0}84.1 & 21.0 & \solver{CaDiCaL-alluip-trail} \\
+\phantom{0}84.0 & 21.0 & \solver{CaDiCaL-alluip} \\
+\phantom{0}83.0 & 20.7 & \solver{CaDiCaL-sc2020} \\
+\phantom{0}82.3 & 20.6 & \solver{Relaxed-newTech} \\
+\phantom{0}81.5 & 20.4 & \solver{Relaxed} \\
+\end{tabular}
+~\\[1em]
+\begin{tabular}{ccl}
+\bf VBS3 & \bf Percent Total & \bf Solver \\
+\hline
+13.0 & 3.3 & \solver{Kissat} \\
+11.9 & 3.0 & \solver{Kissat-unsat} \\
+11.7 & 2.9 & \solver{Relaxed-newTech} \\
+11.4 & 2.8 & \solver{Kissat-sat} \\
+10.8 & 2.7 & \solver{CaDiCaL-alluip-trail} \\
+10.8 & 2.7 & \solver{CaDiCaL-alluip} \\
+10.5 & 2.6 & \solver{Relaxed} \\
+10.4 & 2.6 & \solver{CaDiCaL-sc2020} \\
+10.3 & 2.6 & \solver{CMS-walksat} \\
+\phantom{0}9.6 & 2.4 & \solver{CaDiCaL-trail} \\
+\end{tabular}
 \caption{VBS metrics for the results of the Main track, all instances. 
@@
 \label{tab:vbsMainALL}
-\begin{center}
-\begin{tabular}{ccl}
-VBS1 & percent total & solver \\
-\hline
-46 & 11.5 & Kissat-unsat \\
-39 & \phantom{0}9.8 & Kissat-sat \\
-26 & \phantom{0}6.5 & Kissat \\
-18 & \phantom{0}4.5 & CMS-ccnr-lsids \\
-14 & \phantom{0}3.5 & MapleCM+dist+sat2s \\
-13 & \phantom{0}3.2 & Relaxed \\
-13 & \phantom{0}3.2 & Maple-alluip-trail \\
-12 & \phantom{0}3.0 & upGlucose3.0\_PADC \\
-10 & \phantom{0}2.5 & CMS-ccnr \\
-10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
-\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{ccl}
-VBS2 & percent total & solver \\
-\hline
-131.5 & 32.9 & Kissat-sat \\
-122.6 & 30.6 & Kissat \\
-115.4 & 28.9 & Kissat-unsat \\
-\phantom{0}92.3 & 23.1 & CMS-ccnr-lsids \\
-\phantom{0}88.8 & 22.2 & CMS-ccnr \\
-\phantom{0}84.1 & 21.0 & CaDiCaL-alluip-trail \\
-\phantom{0}84.0 & 21.0 & CaDiCaL-alluip \\
-\phantom{0}83.0 & 20.7 & CaDiCaL-sc2020 \\
-\phantom{0}82.3 & 20.6 & Relaxed\_newTech \\
-\phantom{0}81.5 & 20.4 & Relaxed \\
-\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{ccl}
-VBS3 & percent total & solver \\
-\hline
-13.0 & 3.3 & Kissat \\
-11.9 & 3.0 & Kissat-unsat \\
-11.7 & 2.9 & Relaxed\_newTech \\
-11.4 & 2.8 & Kissat-sat \\
-10.8 & 2.7 & CaDiCaL-alluip-trail \\
-10.8 & 2.7 & CaDiCaL-alluip \\
-10.5 & 2.6 & Relaxed \\
-10.4 & 2.6 & CaDiCaL-sc2020 \\
-10.3 & 2.6 & CMS-walksat \\
-\phantom{0}9.6 & 2.4 & CaDiCaL-trail \\
-\end{tabular}
-\end{center}
-\end{table}
-
-\begin{table}
-\caption{VBS metrics for the results of the Main track, SAT instances. 
-The total number of solved problems was 182. 
-There were 48 (non-disqualified) participating solvers.
-Each table always shows the first ten solvers sorted according to the respective metric.}
-\label{tab:vbsMainSAT}
-\begin{center}
-\begin{tabular}{ccl}
-VBS1 & percent total & solver \\
-\hline
-29 & 15.9 & Kissat-sat \\
-16 & \phantom{0}8.8 & Kissat \\
-14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
-12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
-10 & \phantom{0}5.5 & Relaxed \\
-\phantom{0}8 & \phantom{0}4.4 & CMS-ccnr \\
-\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
-\phantom{0}8 & \phantom{0}4.4 & Kissat-unsat \\
-\phantom{0}6 & \phantom{0}3.3 & CaDiCaL-trail \\
-\phantom{0}5 & \phantom{0}2.7 & MapleCOMSPS\_drup \\
-\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{ccl}
-VBS2 & percent total & solver \\
-\hline
-70.1 & 38.5 & Kissat-sat \\
-48.6 & 26.7 & Kissat \\
-45.2 & 24.8 & CMS-ccnr-lsids \\
-43.4 & 23.8 & Relaxed\_newTech \\
-42.4 & 23.3 & CMS-ccnr \\
-41.6 & 22.8 & Relaxed \\
-34.7 & 19.0 & CaDiCaL-alluip-trail \\
-34.6 & 19.0 & CaDiCaL-alluip \\
-33.7 & 18.5 & CMS-walksat \\
-32.8 & 18.0 & CaDiCaL-sc2020 \\
-\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{ccl}
-VBS3 & percent total & solver \\
-\hline
-9.3 & 5.1 & Relaxed\_newTech \\
-8.1 & 4.4 & Relaxed \\
-7.8 & 4.3 & CMS-walksat \\
-7.0 & 3.8 & Kissat-sat \\
-6.7 & 3.7 & Kissat \\
-6.7 & 3.7 & CMS-ccnr \\
-6.6 & 3.6 & CMS-ccnr-lsids \\
-6.2 & 3.4 & CaDiCaL-sc2020 \\
-6.2 & 3.4 & CaDiCaL-alluip-trail \\
-6.2 & 3.4 & CaDiCaL-alluip \\
-\end{tabular}
-\end{center}
-\end{table}
-
-\begin{table}
-\caption{VBS metrics for the results of the Main track, UNSAT instances. 
-The total number of solved problems was 134. 
-There were 48 (non-disqualified) participating solvers.
-Each table always shows the first ten solvers sorted according to the respective metric.}
-\label{tab:vbsMainUNSAT}
-\begin{center}
-\begin{tabular}{ccl}
-VBS1 & percent total & solver \\
-\hline
-38 & 28.4 & Kissat-unsat \\
-11 & \phantom{0}8.2 & Maple-alluip-trail \\
-10 & \phantom{0}7.5 & Kissat \\
-10 & \phantom{0}7.5 & Kissat-sat \\
-\phantom{0}8 & \phantom{0}6.0 & MapleCMused+dist \\
-\phantom{0}7 & \phantom{0}5.2 & upGlucose3.0\_PADC \\
-\phantom{0}6 & \phantom{0}4.5 & CMS-ccnr-lsids \\
-\phantom{0}3 & \phantom{0}2.2 & f2trc \\
-\phantom{0}3 & \phantom{0}2.2 & Relaxed \\
-\phantom{0}3 & \phantom{0}2.2 & Glucose3.0\_proofs \\
-\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{ccl}
-VBS2 & percent total & solver \\
-\hline
-86.5 & 64.6 & Kissat-unsat \\
-74.0 & 55.2 & Kissat \\
-61.4 & 45.8 & Kissat-sat \\
-55.4 & 41.4 & f2trc-s \\
-55.2 & 41.2 & DurianSat \\
-53.6 & 40.0 & Maple-alluip-trail \\
-53.4 & 39.8 & f2trc \\
-52.4 & 39.1 & f2trc-DL \\
-51.8 & 38.6 & MapleCMused+dist \\
-51.7 & 38.6 & PADC\_DL \\
-\end{tabular}
-\end{center}
-\begin{center}
-\begin{tabular}{ccl}
-VBS3 & percent total & solver \\
-\hline
-6.7 & 5.0 & Kissat-unsat \\
-6.3 & 4.7 & Kissat \\
-4.7 & 3.5 & CaDiCaL-trail \\
-4.6 & 3.5 & CaDiCaL-alluip-trail \\
-4.6 & 3.5 & CaDiCaL-alluip \\
-4.4 & 3.3 & Kissat-sat \\
-4.3 & 3.2 & CaDiCaL-sc2020 \\
-3.5 & 2.6 & f2trc-s \\
-3.4 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
-3.1 & 2.3 & f2trc-DL \\
-\end{tabular}
-\end{center}
-\end{table}
-
-\todo{Probably hide tab:vbsMainSAT and tab:vbsMainUNSAT.}
+\end{table}
+
+%\begin{table}
+%\caption{VBS metrics for the results of the Main track, SAT instances. 
+%The total number of solved problems was 182. 
+%There were 48 (non-disqualified) participating solvers.
+%Each table always shows the first ten solvers sorted according to the respective metric.}
+%\label{tab:vbsMainSAT}
+%\begin{center}
+%\begin{tabular}{ccl}
+%VBS1 & percent total & solver \\
+%\hline
+%29 & 15.9 & Kissat-sat \\
+%16 & \phantom{0}8.8 & Kissat \\
+%14 & \phantom{0}7.7 & MapleCM+dist+sat2s \\
+%12 & \phantom{0}6.6 & CMS-ccnr-lsids \\
+%10 & \phantom{0}5.5 & Relaxed \\
+%\phantom{0}8 & \phantom{0}4.4 & CMS-ccnr \\
+%\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
+%\phantom{0}8 & \phantom{0}4.4 & Kissat-unsat \\
+%\phantom{0}6 & \phantom{0}3.3 & CaDiCaL-trail \\
+%\phantom{0}5 & \phantom{0}2.7 & MapleCOMSPS\_drup \\
+%\end{tabular}
+%\end{center}
+%\begin{center}
+%\begin{tabular}{ccl}
+%VBS2 & percent total & solver \\
+%\hline
+%70.1 & 38.5 & Kissat-sat \\
+%48.6 & 26.7 & Kissat \\
+%45.2 & 24.8 & CMS-ccnr-lsids \\
+%43.4 & 23.8 & Relaxed\_newTech \\
+%42.4 & 23.3 & CMS-ccnr \\
+%41.6 & 22.8 & Relaxed \\
+%34.7 & 19.0 & CaDiCaL-alluip-trail \\
+%34.6 & 19.0 & CaDiCaL-alluip \\
+%33.7 & 18.5 & CMS-walksat \\
+%32.8 & 18.0 & CaDiCaL-sc2020 \\
+%\end{tabular}
+%\end{center}
+%\begin{center}
+%\begin{tabular}{ccl}
+%VBS3 & percent total & solver \\
+%\hline
+%9.3 & 5.1 & Relaxed\_newTech \\
+%8.1 & 4.4 & Relaxed \\
+%7.8 & 4.3 & CMS-walksat \\
+%7.0 & 3.8 & Kissat-sat \\
+%6.7 & 3.7 & Kissat \\
+%6.7 & 3.7 & CMS-ccnr \\
+%6.6 & 3.6 & CMS-ccnr-lsids \\
+%6.2 & 3.4 & CaDiCaL-sc2020 \\
+%6.2 & 3.4 & CaDiCaL-alluip-trail \\
+%6.2 & 3.4 & CaDiCaL-alluip \\
+%\end{tabular}
+%\end{center}
+%\end{table}
+
+%\begin{table}
+%\caption{VBS metrics for the results of the Main track, UNSAT instances. 
+%The total number of solved problems was 134. 
+%There were 48 (non-disqualified) participating solvers.
+%Each table always shows the first ten solvers sorted according to the respective metric.}
+%\label{tab:vbsMainUNSAT}
+%\begin{center}
+%\begin{tabular}{ccl}
+%VBS1 & percent total & solver \\
+%\hline
+%38 & 28.4 & Kissat-unsat \\
+%11 & \phantom{0}8.2 & Maple-alluip-trail \\
+%10 & \phantom{0}7.5 & Kissat \\
+%10 & \phantom{0}7.5 & Kissat-sat \\
+%\phantom{0}8 & \phantom{0}6.0 & MapleCMused+dist \\
+%\phantom{0}7 & \phantom{0}5.2 & upGlucose3.0\_PADC \\
+%\phantom{0}6 & \phantom{0}4.5 & CMS-ccnr-lsids \\
+%\phantom{0}3 & \phantom{0}2.2 & f2trc \\
+%\phantom{0}3 & \phantom{0}2.2 & Relaxed \\
+%\phantom{0}3 & \phantom{0}2.2 & Glucose3.0\_proofs \\
+%\end{tabular}
+%\end{center}
+%\begin{center}
+%\begin{tabular}{ccl}
+%VBS2 & percent total & solver \\
+%\hline
+%86.5 & 64.6 & Kissat-unsat \\
+%74.0 & 55.2 & Kissat \\
+%61.4 & 45.8 & Kissat-sat \\
+%55.4 & 41.4 & f2trc-s \\
+%55.2 & 41.2 & DurianSat \\
+%53.6 & 40.0 & Maple-alluip-trail \\
+%53.4 & 39.8 & f2trc \\
+%52.4 & 39.1 & f2trc-DL \\
+%51.8 & 38.6 & MapleCMused+dist \\
+%51.7 & 38.6 & PADC\_DL \\
+%\end{tabular}
+%\end{center}
+%\begin{center}
+%\begin{tabular}{ccl}
+%VBS3 & percent total & solver \\
+%\hline
+%6.7 & 5.0 & Kissat-unsat \\
+%6.3 & 4.7 & Kissat \\
+%4.7 & 3.5 & CaDiCaL-trail \\
+%4.6 & 3.5 & CaDiCaL-alluip-trail \\
+%4.6 & 3.5 & CaDiCaL-alluip \\
+%4.4 & 3.3 & Kissat-sat \\
+%4.3 & 3.2 & CaDiCaL-sc2020 \\
+%3.5 & 2.6 & f2trc-s \\
+%3.4 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
+%3.1 & 2.3 & f2trc-DL \\
+%\end{tabular}
+%\end{center}
+%\end{table}
+%\todo{Probably hide tab:vbsMainSAT and tab:vbsMainUNSAT.}
 
@@
 to the full results of the Main track. We can see that the respective leaderboards 
-are generally dominated by Kissat and its configurations.
-VBS1 tells us that Kissat-unsat was most often the fastest solver,
+are generally dominated by \solver{Kissat} and its configurations.
+VBS1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
 in particular on \SI{11.5}{\percent} of all the solved instances.
 
-VBS2 highlights as first Kissat-sat. Its leading \SI{32.9}{\percent} of total is a bit harder to 
+VBS2 highlights as first \solver{Kissat-sat}. Its leading \SI{32.9}{\percent} of total is a bit harder to 
 interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
 by solving \SI{32.9}{\percent} of the solved instances in the best observed time
-and no others. But we know, thanks to its VBS1, that Kissat-sat solved \SI{9.8}{\percent}
+and no others. But we know, thanks to its VBS1, that \solver{Kissat-sat} solved \SI{9.8}{\percent}
 of the solved instances in the best observed time (and some others).
@@
 but always being roughly 3 times slower than the VBS. 
-Kissat-sat lies obviously somewhere between these two extremes.
-
-Finally, according to VBS3, the best solver is Kissat with 13.0 points,
+\solver{Kissat-sat} lies obviously somewhere between these two extremes.
+
+Finally, according to VBS3, the best solver is \solver{Kissat} with 13.0 points,
 which amounts to \SI{3.3}{\percent} of the distributed total score.
@@
 \begin{table}
+\centering
+\begin{tabular}{clccc}
+\bf Iteration & \bf Selected Solver & \bf Num. Solved & \bf Contributes \\ % & covered so far \\
+\hline
+\phantom{0}1 & \solver{Kissat-sat} & 264 & 264 \\ % & 264 \\
+\phantom{0}2 & \solver{CaDiCaL-alluip} & 250 & \phantom{0}22 \\ % & 286 \\
+\phantom{0}3 & \solver{f2trc-s} & 214 & \phantom{0}10 \\ % & 296 \\
+\phantom{0}4 & \solver{Relaxed-newTech} & 253 & \phantom{00}6 \\ % & 302 \\
+\phantom{0}5 & \solver{Kissat-unsat} & 238 & \phantom{00}4 \\ % & 306 \\
+\phantom{0}6 & \solver{Relaxed} & 245 & \phantom{00}3 \\ % & 309 \\
+\phantom{0}7 & \solver{CMS-walksat} & 243 & \phantom{00}3 \\ % & 312 \\
+\phantom{0}8 & \solver{CMS-ccnr-lsids} & 248 & \phantom{00}1 \\ % & 313 \\
+\phantom{0}9 & \solver{MapleCBT-DL-v3} & 211 & \phantom{00}1 \\ % & 314 \\
+10 & \solver{DurianSat} & 210 & \phantom{00}1 \\ % & 315 \\
+11 & \solver{exp-V-LGB-MLD-CBT-DL} & 194 & \phantom{00}1 \\ % & 316 \\
+\hline
+ & Total & -- & 316 \\
+\end{tabular}
 \caption{A greedy set cover of the solved instances by solvers of the Main track.}
 \label{tab:gscMain}
-\begin{center}
-\begin{tabular}{clccc}
-Iteration & selected solver & (num. solved) & contributes \\ % & covered so far \\
-\hline
-\phantom{0}1 & Kissat-sat & 264 & 264 \\ % & 264 \\
-\phantom{0}2 & CaDiCaL-alluip & 250 & \phantom{0}22 \\ % & 286 \\
-\phantom{0}3 & f2trc-s & 214 & \phantom{0}10 \\ % & 296 \\
-\phantom{0}4 & Relaxed\_newTech & 253 & \phantom{00}6 \\ % & 302 \\
-\phantom{0}5 & Kissat-unsat & 238 & \phantom{00}4 \\ % & 306 \\
-\phantom{0}6 & Relaxed & 245 & \phantom{00}3 \\ % & 309 \\
-\phantom{0}7 & CMS-walksat & 243 & \phantom{00}3 \\ % & 312 \\
-\phantom{0}8 & CMS-ccnr-lsids & 248 & \phantom{00}1 \\ % & 313 \\
-\phantom{0}9 & MapleCBT-DL-v3 & 211 & \phantom{00}1 \\ % & 314 \\
-10 & DurianSat & 210 & \phantom{00}1 \\ % & 315 \\
-11 & exp\_V\_LGB\_MLD\_CBT\_DL & 194 & \phantom{00}1 \\ % & 316 \\
-\hline
- & Total & -- & 316 \\
-\end{tabular}
-\end{center}
-\end{table}
-
-A greedy set cover of the solved instances by solvers of the Main track is presented 
-in Table~\ref{tab:gscMain}. In the first iteration, the solver which solved the highest number 
-of instances is selected; in our case it was Kissat-sat with 264 instances
-as we know already from Table~\ref{tab:mainALL}.
-Given those 264 instances as already covered, CaDiCaL-alluip was the best in further contributing
-to the set by additional 22 instances in iteration 2.
+\end{table}
+
+A greedy set cover of the solved instances by solvers of the Main track is presented in Table~\ref{tab:gscMain}. 
+In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:mainALL}.
+Given those 264 instances as already covered, \solver{CaDiCaL-alluip} was the best in further contributing to the set by additional $22$ instances in iteration $2$.
 We can see that the further iterations tend to add very little,
@@
 is showing up in the table. This is, for example the case of the last listed  
-exp\_V\_LGB\_MLD\_CBT\_DL.
+\solver{exp-V-LGB-MLD-CBT-DL}.
 Highlighting unique solutions is a property of the greedy set cover metric
@@
 \begin{table}
+\centering
+\begin{tabular}{cccl}
+\bf \#Solvers & \bf Time (s) & \bf Num. Solved & \bf Best Schedule \\
+\hline
+1 & 5000 & 264 & \solver{\{Kissat-sat\}} \\
+2 & 2500 & 278 & \solver{\{Kissat-unsat, Relaxed\_newTech\}} \\
+3 & 1666 & 272 & \solver{\{Kissat-unsat, Kissat-sat, }\\
+			 &&& \solver{CMS-ccnr-lsids\}} \\
+4 & 1250 & 262 & \solver{\{Kissat-unsat, Kissat-sat, }\\
+			 &&& \solver{CMS-ccnr-lsids, Maple-alluip-trail\}} \\ 
+5 & 1000 & 253 & \solver{\{Kissat-unsat, Kissat-sat, }\\
+			&&& \solver{CMS-ccnr-lsids, Maple-alluip-trail, }\\ 
+			&&& \solver{CaDiCaL-alluip \}}\\
+\end{tabular}
 \caption{``Uniform time split'' schedules %using $i$ solvers 
@@
 \label{tab:MainUniformTimeSplit}
-\begin{center}
-\begin{tabular}{cccl}
-\# solvers & time (s) & total solved & the best schedule \\
-\hline
-1 & 5000 & 264 & \{Kissat-sat\} \\
-2 & 2500 & 278 & \{Kissat-unsat, Relaxed\_newTech\} \\
-3 & 1666 & 272 & \{Kissat-unsat, Kissat-sat, \\
-			 &&& CMS-ccnr-lsids\} \\
-4 & 1250 & 262 & \{Kissat-unsat, Kissat-sat, \\
-			 &&& CMS-ccnr-lsids, Maple-alluip-trail\} \\ 
-5 & 1000 & 253 & \{Kissat-unsat, Kissat-sat, \\
-			&&& CMS-ccnr-lsids, Maple-alluip-trail, \\ 
-			&&& CaDiCaL-alluip \}\\
-\end{tabular}
-\end{center}
 \end{table}
@@
 \begin{table}
+\centering
+\begin{tabular}{lccc}
+\bf Solver & \bf Taking Up (s) & \bf Solving Under Limit & \bf Contributes \\
+\hline
+\solver{Kissat-unsat} & 2523 & 219 & 219 \\
+\solver{Relaxed-newTech} & 2180 & 234 & \phantom{0}59 \\
+\solver{Kissat-sat} & \phantom{0}103 & \phantom{0}72 & \phantom{00}2 \\
+\solver{f2trc-DL} & \phantom{00}76 & \phantom{0}15 & \phantom{00}0 \\
+\solver{CaDiCaL-alluip} & \phantom{00}58 & \phantom{0}26 & \phantom{00}2 \\
+\solver{Maple-alluip-trail} & \phantom{00}34 & \phantom{0}12 & \phantom{00}1 \\
+\solver{MapleCM+dist+sat2s} & \phantom{00}18 & \phantom{0}18 & \phantom{00}1 \\
+\solver{CaDiCaL-sc2020} & \phantom{000}8 & \phantom{0}10 & \phantom{00}2 \\
+\hline 
+Total & 5000 & \phantom{0}-- & 286 \\ 
+\end{tabular}
 \caption{An optimal \SI{5000}{\second} schedule for the Main track
@@
 \label{tab:MainZ3Schedule}
-\begin{center}
-\begin{tabular}{lccc}
-solver & taking up (s) & solving under limit & contributes \\
-\hline
-Kissat-unsat & 2523 & 219 & 219 \\
-Relaxed\_newTech & 2180 & 234 & \phantom{0}59 \\
-Kissat-sat & \phantom{0}103 & \phantom{0}72 & \phantom{00}2 \\
-f2trc-DL & \phantom{00}76 & \phantom{0}15 & \phantom{00}0 \\
-CaDiCaL-alluip & \phantom{00}58 & \phantom{0}26 & \phantom{00}2 \\
-Maple-alluip-trail & \phantom{00}34 & \phantom{0}12 & \phantom{00}1 \\
-MapleCM+dist+sat2s & \phantom{00}18 & \phantom{0}18 & \phantom{00}1 \\
-CaDiCaL-sc2020 & \phantom{000}8 & \phantom{0}10 & \phantom{00}2 \\
-\hline 
-Total & 5000 & \phantom{0}-- & 286 \\ 
-\end{tabular}
-\end{center}
 \end{table}
@@
 
-Amusingly, as can be seen from the ``contributes'' column, the presence of f2trc-DL in the schedule
-is not necessary.
+Amusingly, as can be seen from the ``contributes'' column, the presence of \solver{f2trc-DL} in the schedule is not necessary.
 % The following three lines could be skipped without much harm:
@@
 \subsection{Small Portfolios}
+
+\paragraph{Marginal Contributions to VBS} Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth''~\cite{} or ``timetable''~\cite{}.
 
@@
 \solver{CaDiCaL-alluip-trail} &  & $3128.0$\\
+\hline
 \solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-Walksat}} & $3152.8$\\

### 2021-01-18 paper/vbs/vbs.py
added PauSAT_noproof to names, vbs script and csv

@@ -1,0 +1,85 @@
+#!/usr/bin/env python3
+
+import pandas as pd
+
+
+def pl(args):
+    for e in args:
+        print("- " + e)
+
+
+def getVbs(outputAllSolvers=True, removePlanning=False):
+    pResults = "../../downloads/results.csv"
+    pNames = "../solver_names_final.txt"
+
+    d = pd.read_csv(pResults)
+    d["n"] = d["solver"] + "__" + d["configuration"]
+    o = d
+    print("\n" + str(len(o.n.unique())) + " original solvers")
+
+    # withdrawn
+    withdrawn = d[d["solver"] == "Relaxed_LCMDCBDL_noTimePara"].n.unique()
+    d = d[~d["n"].isin(withdrawn)]
+    print("Removed withdrawn solver:")
+    pl(withdrawn)
+
+    # disqualified
+    dis = d[d["verifier-result"].isin(["SAT-INCORRECT", "UNSAT-INCORRECT"])][
+        "n"
+    ].unique()
+    d = d[~d["n"].isin(dis)]
+    print("Removed disqualified solver:")
+    pl(dis)
+
+    # competed in no limits
+    np = d[d["drat"] == "NOPROOF"]["n"].unique()
+    d = d[~d["n"].isin(np)]
+    print("Removed NoLimits solver:")
+    pl(np)
+
+    # demoted to no limits
+    dem = d[d["drat"] == "NOT_VERIFIED"]["n"].unique()
+    d = d[~d["n"].isin(dem)]
+    print("Removed demoted solver:")
+    pl(dem)
+
+    solverInMain = len(d["n"].unique())
+    print(str(solverInMain) + " solvers participated in main track")
+
+    d = d.set_index(["n", "benchmark"])
+    s = d[d["result"].isin(["SAT", "UNSAT"])]
+    print(str(len(s.reset_index().benchmark.unique())) + " benchmarks have been solved")
+    vbsRows = s.groupby("benchmark").time.idxmin()
+
+    if outputAllSolvers:
+        d = o.set_index(["n", "benchmark"])
+
+    d["VBS_Origin"] = False
+    d.loc[vbsRows, "VBS_Origin"] = True
+    d = d.reset_index()
+
+    # adding short names
+    nameDict = pd.read_csv(pNames, sep=" ", names=["n", "name"])
+    nameDict["name"] = nameDict["name"].str.replace("\\", "")
[…]

### 2021-01-19 paper/vbs/vbs.py
Yet a bit more verbose

@@ -72,7 +72,9 @@ def getVbs(outputAllSolvers=True, removePlanning=False):
     d = d.append(v)
 
     if removePlanning:
+        print("removed " + str(len(d[d["benchmark"].apply(lambda x: "ddl_" in x)].benchmark.unique())) + " planning bechmarks")
         d = d[~d["benchmark"].apply(lambda x: "ddl_" in x)]
+        print(str(len(d[d.result.isin(["SAT", "UNSAT"])].benchmark.unique())) + " solved benchmarks are left")
     d = d.drop("n", axis=1)
     return d
 

### 2021-01-21 paper/similarity/makeCross.py
Updated scripts and plots

@@ -1,0 +1,108 @@
+#!/usr/bin/env python3
+
+from tabulate import tabulate
+import pandas as pd
+
+
+def pl(args):
+    for e in args:
+        print("- " + e)
+
+
+pResults = "../../downloads/results.csv"
+pNames = "../solver_names_final.txt"
+numSolvers = 30
+
+d = pd.read_csv(pResults)
+d["n"] = d["solver"] + "__" + d["configuration"]
+print(str(len(d.n.unique())) + " original solvers")
+
+# withdrawn
+withdrawn = d[d["solver"] == "Relaxed_LCMDCBDL_noTimePara"].n.unique()
+d = d[~d["n"].isin(withdrawn)]
+print("Removed withdrawn solver:")
+pl(withdrawn)
+
+# disqualified
+dis = d[d["verifier-result"].isin(["SAT-INCORRECT", "UNSAT-INCORRECT"])]["n"].unique()
+d = d[~d["n"].isin(dis)]
+print("Removed disqualified solver:")
+pl(dis)
+
+# competed in no limits
+np = d[d["drat"] == "NOPROOF"]["n"].unique()
+d = d[~d["n"].isin(np)]
+print("Removed NoLimits solver:")
+pl(np)
+
+# demoted to no limits
+dem = d[d["drat"] == "NOT_VERIFIED"]["n"].unique()
+d = d[~d["n"].isin(dem)]
+print("Removed demoted solver:")
+pl(dem)
+
+solverInMain = len(d["n"].unique())
+print(str(solverInMain) + " solvers participated in main track")
+
+# only main track (-> no planning)
+print(
+    "removed "
+    + str(len(d[d["benchmark"].apply(lambda x: "ddl_" in x)].benchmark.unique()))
+    + " planning bechmarks"
+)
+d = d[~d["benchmark"].apply(lambda x: "ddl_" in x)]
+print(
+    str(len(d[d.result.isin(["SAT", "UNSAT"])].benchmark.unique()))
+    + " solved benchmarks are left"
+)
+
+# remove fully unsolved benchmarks
+d["s"] = d["result"].isin(["SAT", "UNSAT"])
+count = d.groupby("benchmark").sum()["s"].reset_index()
+unsolved = count[count["s"] == 0]["benchmark"].unique()
+d = d[~d["benchmark"].isin(unsolved)]
+
+# PAR2
+d.loc[d["s"] == 0, "time"] = 10000
+d = d[["n", "benchmark", "time"]]
+
[…]

### 2021-01-21 paper/stability/benchfeatures/family_and_SAT_random_sampling_plots.py

@@ -1,0 +1,380 @@
+#! /usr/bin/env python3
+import pandas as pd
+import numpy as np
+from scipy import stats
+import matplotlib.pyplot as plt
+import random
+
+in_path = "par2scores.csv"
+families = "benchmark_families.csv"
+sat_answers = "instance_answers.csv"
+
+def clean_features(data):
+    mean = data.mean()
+    idx = [i for i in range(data.shape[1]) if mean[i] != 10000]
+    X_new = data.iloc[:,idx]
+    return X_new
+
+def read_csv_data(path):
+    raw_data = pd.read_csv(path)
+    data = raw_data.drop('solver', 1)
+    solver = raw_data['solver']
+    return solver, data
+
+def calc_par2score(data2):
+    value = data2.sum(axis=1)
+    return value
+
+def ranking(data1, score1):
+    return [x for _,x in sorted(zip(score1, data1))]
+
+
+def ranking_mat(ranks, solv):
+    l = []
+    for i in solv:
+        l = l + [ranks.index(i)+1]
+    return l
+
+def spearman_vector(matrixr):
+     cor = np.empty([len(matrixr)-1])
+
+     for j in range(1,len(matrixr)):
+         cor[j-1] = stats.spearmanr(matrixr[0], matrixr[j])[0]
+     return cor
+
+def random_sample(data, num):
+    size = data.shape[1]
+    indices = random.sample(range(size),num)
+    subset = data.iloc[:,indices]
+    return subset
+
+def extract_sat_unsat(sat, data):
+   if(sat == 0): sat_set = sat_answ.loc[sat_answ['answer'] == 'SAT-VERIFIED']
+   else: sat_set = sat_answ.loc[sat_answ['answer'] == 'UNSAT']
+
+   sat_bench = sat_set['benchmark'].str.strip()
+   sat_bench = list("sat/"+sat_bench)
+   data_bench=list(data.columns.values)
+
+   intersect=list(set(sat_bench).intersection(data_bench))
+
+
+   return data[intersect]
+
+def get_sat_instances(sat, subset):
+    if(sat == 0): sat_set = sat_answ.loc[sat_answ['answer'] == 'SAT-VERIFIED']
+    else: sat_set = sat_answ.loc[sat_answ['answer'] == 'UNSAT']
+
+    sat_bench = sat_set['benchmark'].str.strip()
+    sat_bench = list("sat/"+sat_bench)
[…]

### 2021-01-21 paper/stability/benchfeatures/par2_generator.py

@@ -1,0 +1,74 @@
+#! /usr/bin/env python3
+import csv
+import pandas as pd
+
+penalty = 10000
+verifier_failed_markers = ['DRATmemout','DRATtimeout','TIMEOUT','RATcfoapp','Enc','ccbnd']
+solver2scores = {}
+header = True
+benchmark_set = set()
+
+answers = {}
+
+with open('main.csv','r') as main_input:
+    for line in main_input:
+        if header:
+            header = False
+            continue
+
+        cells = line.strip().split(',')
+        benchmark = cells[0]
+        benchmark_set.add(benchmark)
+        solver = cells[1] + '-' + cells[2] #solver-configuration
+        if benchmark[4:] not in answers: #remove prefix 'sat/'
+            answers[benchmark[4:]] = []
+        answers[benchmark[4:]].append(cells[5])
+        if cells[4] != 'complete' or cells[7] in verifier_failed_markers:
+            score = penalty
+        else:
+            score = cells[3]
+
+        if solver in solver2scores:
+            solver2scores[solver][benchmark] = score
+        else:
+            solver2scores[solver] = {}
+            solver2scores[solver]['solver'] = solver
+            solver2scores[solver][benchmark] = score
+
+#sorting is not relevant to the plots, it is here just to reproduce the used data-files exactly
+output_header = ['solver'] + sorted(list(benchmark_set), key=lambda s: s.lower().replace('_','!'))
+sorted_solvers_list = sorted(solver2scores.keys(), key=lambda s: s.lower().replace('+','.').replace('_','!'))
+
+output_file = 'par2scores.csv'
+try:
+    with open(output_file,'w') as output_csv:
+        for instance in output_header[:-1]:
+            output_csv.write(instance + ',')
+        output_csv.write(output_header[-1]+'\n')
+        for solver in sorted_solvers_list:
+            output_csv.write(solver+',')
+            for instance in output_header[1:-1]:
+                output_csv.write(str(solver2scores[solver][instance])+',')
+            output_csv.write(str(solver2scores[solver][output_header[-1]])+'\n')
+except IOError:
+    print("I/O error")
+
+
+output_file = 'instance_answers.csv'
+try:
+    with open(output_file,'w') as output_csv:
+        output_csv.write('benchmark,answer\n')
+        for instance,answer in sorted(answers.items()):
+            answer_set = set(answer)
+            assert  not (('SAT-VERIFIED' in answer_set) and ('UNSAT' in answer_set))
[…]

### 2021-01-21 paper/stability/benchfeatures/random_sampling_plots.py

@@ -1,0 +1,149 @@
+#! /usr/bin/env python3
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+
+def read_csv_data(path):
+    raw_data = pd.read_csv(path)
+    raw_data.rename(columns=lambda x: x[4:] if str(x).startswith('sat/') else x, inplace=True)
+    return raw_data
+
+def remove_unsolved_instances(df,penalty):
+    data = df.copy()
+    unsolved_instances = []
+    for col in data.columns[1:]: #columns[0] == 'solvers'
+        if data[col].eq(penalty).all(): # Penalty running time means that the instance was not solved, i.e. TO or MO happened during solving
+            unsolved_instances.append(col)
+
+    data.drop(unsolved_instances, axis=1, inplace=True)
+    print('Eliminating %d unsolved instances from the data.' %len(unsolved_instances))
+    return data
+
+def introduce_par2score_column(df):
+    data = df.copy()
+    data.insert(loc=len(data.columns),column='par2_score',value=data.iloc[:,:].sum(axis=1,numeric_only=True))
+    return data
+
+def sort_by_score(scores,solvers):
+    solver_score_pairs = zip(scores,solvers)
+    return sorted(solver_score_pairs)
+
+def get_position(solver,rank):
+    for (idx,r) in zip(range(len(rank)),rank):
+        (rank_score,rank_solver) = r
+        if rank_solver == solver:
+            return idx+1
+    assert False
+
+def spearman_correlation(rank1,rank2): #alternative: scipy.starts.spearmanr
+    assert (len(rank1) == len(rank2))
+    diff_square_sum = 0
+    for _,solver in rank1:
+        pos1 = get_position(solver,rank1)
+        pos2 = get_position(solver,rank2)
+        diff_square_sum += ((pos1-pos2)**2)
+    n = len(rank1)
+    nom = 6*diff_square_sum
+    dnom = n*((n**2)-1)
+    spc = 1. - nom/dnom
+
+    return spc
+
+def select_random_features(amount,times,feature_list):
+    assert amount <= len(feature_list)
+    selected_features = []
+    for t in range(times):
+        selected_features.append(np.random.choice(feature_list,amount,replace=False)) #random sampling without replacement - sample WITH replacement: random.choices
+
+    return selected_features
+
+
+def random_sampling(data_frame,original_rank,original_features,solver_names,repeat,ub,step):
[…]

### 2021-01-21 paper/stability/benchfeatures/run_all.sh

@@ -1,0 +1,10 @@
+#!/bin/sh
+
+echo 'Executing par2_generator.py:'
+python3 par2_generator.py
+
+echo 'Executing random_sampling_plots.py:'
+python3 random_sampling_plots.py
+
+echo 'Executing family_and_SAT_random_sampling_plots.py:'
+python3 family_and_SAT_random_sampling_plots.py

### 2021-01-21 paper/by-family/gen.sh
touched all tables, fixed k-tuples, added raw data for family-wise interpretation of results

@@ -1,0 +1,3 @@
+for family in $(gbd get "competition_track = main_2020" -r family | sort -k2 | uniq -s33 -c | sort -n | tail -n12 | head -n11 | cut -d" " -f8); do 
+  gbd eval par2 "competition_track = main_2020 and family = $family" -r cadical_sc2020 duriansat exmaple_padc_dl exmaple_padc_dl_ovau_exp exmaple_padc_dl_ovau_lin exmaple_psids_dl kissat kissat_sat kissat_unsat maple_scavel maple_alluip_trail maple_lrb_vsids_2_init maplecomsps_lrb_vsids_2 maple_scavel01 maple_scavel02 maple_dl_f2trc maplelcmdistchronobt_dl_v3 maple_f2trc maple_f2trc_s maple_cm_dist maple_cm_dist_sattime2s maple_cm_dist_simp2 maple_cmused_dist maple_mix maple_simp parafrost parafrost_cbt pausat relaxed relaxed_newtech relaxed_notimepara slime undominated_top16 undominated_top24 undominated_top36 undominated cadical_alluip cadical_alluip_trail cadical_trail cryptominisat_ccnr cryptominisat_ccnr_lsids cryptominisat_walksat exp_l_mld_cbt_dl exp_v_lgb_mld_cbt_dl exp_v_l_mld_cbt_dl exp_v_mld_cbt_dl glucose3 upglucose_3_padc | cut -d. -f1 | sort -k2 -t: -n > eval-$family.score
+done

### 2021-01-22 paper/main.tex
moved my sections around
compressed layout for results

@@
 \usepackage[ruled,linesnumbered,vlined]{algorithm2e}
-
+\usepackage{microtype}
 \usepackage{lscape} 
+\usepackage{tabularx} 
+\usepackage{tabulary} 
 \usepackage[binary-units=true]{siunitx}
-
-\definecolor{gold}{HTML}{FFF3D6}
-\definecolor{silver}{HTML}{F3F5F7}
-\definecolor{cupper}{HTML}{EAD9D7}
-\fboxsep0pt
-\newcommand{\firsto}{\colorbox{gold}{\texttt{M1}}}
-\newcommand{\firsts}{\colorbox{gold}{\texttt{s1}}}
-\newcommand{\firstu}{\colorbox{gold}{\texttt{u1}}}
-\newcommand{\firstp}{\colorbox{gold}{\texttt{P1}}}
-\newcommand{\secondo}{\colorbox{silver}{\texttt{M2}}}
-\newcommand{\seconds}{\colorbox{silver}{\texttt{s2}}}
-\newcommand{\secondu}{\colorbox{silver}{\texttt{u2}}}
-\newcommand{\secondp}{\colorbox{silver}{\texttt{P2}}}
-\newcommand{\thirdo}{\colorbox{cupper}{\texttt{M3}}}
-\newcommand{\thirds}{\colorbox{cupper}{\texttt{s3}}}
-\newcommand{\thirdu}{\colorbox{cupper}{\texttt{u3}}}
-\newcommand{\thirdp}{\colorbox{cupper}{\texttt{P3}}}
 
@@
 \newcommand{\solbert}[1]{\underline{\solver{#1}}}
+\newcommand{\solverine}[1]{\texttt{\textls*[-70]{#1}}}
 
@@
 \bf Family & \bf Author & \bf Submitted & \bf Selected\\
-\hline
-\arrayrulecolor{lightgray}
+\hline\arrayrulecolor{lightgray}
 0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
@@
  & SAT & UNSAT & UNKNOWN & $\Sigma$\\
-\hline
+\hline\arrayrulecolor{lightgray}
 New Instances & 114 & 78 & 108 & 300 \\
@@
 \begin{table}[h]
-  \caption{Number of benchmarks generated by each encoding.}
 \centering
-  \begin{tabular}{@{}|l@{\hspace{3pt}}|l|r|r|@{}}
-    % &Encoding& SAT & UNSAT\\
-    \hline
-    \multicolumn{2}{|@{}l|}{Encoding} & SAT & UNSAT\\
-    % \midrule
-    \hline
+\begin{tabular}{llrr}
+\multicolumn{2}{l}{Encoding} & SAT& UNSAT\\
+\hline\arrayrulecolor{lightgray}
 \textbf{H}  & Tree-REX & 15 & 11\\
@@
 \textbf{MS} & Madagascar sequential & 66 & 65\\
-    % \midrule
 \hline
 && 100 & 100\\
-    % \bottomrule
-    \hline
 \end{tabular}
 \label{tab:planningBenchmarkDist}
+\caption{Number of benchmarks generated by each encoding.}
 \end{table}
@@
 
-\subsection{Incremental Library Applications and Instances}
-
-The incremental library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017. 
-Benchmarks for the Incremental Library track constist of \emph{benchmark applications} which implement and use the incremental SAT solver in their backend as well as \emph{benchmark instances} which serve as input to these applications.
-For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
-For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.
-
-\paragraph{Backbone Variables}
-
-Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Janota:2015:Backbones}. 
-The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
-We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.
-
-\paragraph{Essential Variables}
-
-Essential variables are defined to be those variables which have to be assigned in all partial models of a formula (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
-The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
-We used the same $50$ easy satisfiable instances as in backbone detection to evaluate solver performance with this application.
-
-\paragraph{Longest Simple Paths (LSP)}
-
-The application \textsf{genipalsp} determines longest simple paths in a graph~\cite{Balyo:2019:LSP}. 
-We selected $50$ easy LSP instances for our evaluation.\footnote{\url{http://algo2.iti.kit.edu/kalp/}}
-
-\paragraph{Maximum Satisfiability (MaxSAT)}
-
-The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
-The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
-For this application, we selected $50$ instances from \texttt{MaxSAT Evaluation 2019}.\footnote{\url{https://maxsat-evaluations.github.io/2019/}}
-
-\paragraph{Quantified Boolean Formulas (QBF)}
-\textsf{Ijtihad} is a QBF solver which uses counter\-example-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
-Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}
-
-\paragraph{Planning (SAS+)}
-We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar} -- a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
-
-\section{Competition Results}
-\label{sec:results}
-
-\begin{figure}
-\centering
-\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
-\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
-\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
-\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
-\end{figure}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline
-1     & 3926.2 & 264 & \solbert{Kissat-sat} \\
-(1)   & 4083.1 & 260 & \solver{Kissat} \\
-2     & 4179.3 & 253 & \solbert{Relaxed-newTech} \\
-3     & 4266.7 & 248 & \solbert{CMS-ccnr-lsids} \\
-(3)   & 4278.0 & 250 & \solver{CMS-ccnr} \\
-      & 4428.1 & 250 & \solver{CaDiCaL-alluip-trail} \\
-      & 4429.6 & 250 & \solver{CaDiCaL-alluip} \\
-      & 4436.5 & 245 & \solver{Relaxed} \\
-      & 4501.2 & 243 & \solver{CMS-walksat} \\
-      & 4554.0 & 243 & \solver{CaDiCaL-trail} \\
-      & 4560.0 & 238 & \solver{Kissat-unsat} \\
-      & 4607.6 & 246 & \solver{CaDiCaL-sc2020} \\
-      & 5157.7 & 216 & \solver{Undominated} \\
-      & 5159.6 & 220 & \solver{f2trc-DL} \\
-      & 5177.0 & 214 & \solver{PADC-DL} \\              
-\end{tabular}
-\caption{Main ALL}
-\label{tab:mainALL}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline
- 1    & 2997.4 & 150 & \solbert{Relaxed\_newTech} \\
- 2    & 3127.6 & 146 & \solbert{Kissat-sat} \\
- 3    & 3263.0 & 144 & \solbert{CMS-ccnr-lsids} \\
-(3)   & 3317.4 & 145 & \solver{CMS-ccnr} \\
-      & 3355.5 & 143 & \solver{Relaxed} \\
-      & 3721.2 & 139 & \solver{CMS-walksat} \\
-      & 3830.5 & 134 & \solver{Kissat} \\
-      & 3908.5 & 135 & \solver{CaDiCaL-alluip-trail} \\
-      & 3909.6 & 135 & \solver{CaDiCaL-alluip} \\
-      & 4265.6 & 126 & \solver{CaDiCaL-trail} \\
-      & 4368.6 & 130 & \solver{CaDiCaL-sc2020} \\
-   & 4804.9 & 114 & \solver{Kissat-unsat} \\
-   & 5173.2 & 110 & \solver{Undominated} \\
-   & 5244.1 & 107 & \solver{PADC-DL} \\
-   & 5264.9 & 110 & \solver{f2trc-DL} \\           
-\end{tabular}
-\caption{Main SAT}
-\label{tab:mainSAT}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline   
-1     & 4315.1 & 124 & \solbert{Kissat-unsat} \\
-(1)   & 4335.6 & 126 & \solver{Kissat} \\
-(1)   & 4724.8 & 118 & \solver{Kissat-sat} \\
- 2    & 4842.5 & 117 & \solbert{CaDiCaL-trail} \\
---    & 4846.7 & 116 & \solver{CaDiCaL-sc2020} \\
-(2)   & 4947.8 & 115 & \solver{CaDiCaL-alluip-trail} \\
-(2)   & 4949.6 & 115 & \solver{CaDiCaL-alluip} \\
- 3    & 4991.4 & 110 & \solbert{f2trc-s} \\
-(3)   & 5051.4 & 109 & \solver{f2trc} \\
-(3)   & 5054.3 & 110 & \solver{f2trc-DL} \\
-      & 5069.6 & 109 & \solver{Maple-Mix} \\
-      & 5110.0 & 107 & \solver{PADC-DL} \\
-      & 5126.9 & 107 & \solver{Maple-Simp} \\
-      & 5128.9 & 107 & \solver{MapleCBT-DL-v3} \\
-      & 5142.2 & 106 & \solver{Undominated} \\      
-\end{tabular}
-\caption{Main UNSAT}
-\label{tab:mainUNSAT}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline   
- 1    & 6406.9 & 80 & \solbert{CaDiCaL-alluip-trail} \\
-(1)   & 6409.3 & 80 & \solver{CaDiCaL-alluip} \\
- 2    & 6466.9 & 79 & \solbert{CMS-ccnr-lsids} \\
-(2)   & 6471.9 & 79 & \solver{CMS-ccnr} \\
-(2)   & 6472.9 & 79 & \solver{CMS-walksat} \\
- 3    & 6596.4 & 75 & \solbert{Kissat-unsat} \\
-      & 6650.1 & 79 & \solver{CaDiCaL-trail} \\
-      & 6713.0 & 75 & \solver{Maple-Mix} \\
-      & 6746.5 & 75 & \solver{MapleCOMSPS-init} \\
-      & 6754.3 & 73 & \solver{Maple-Simp} \\
-      & 6773.0 & 73 & \solver{MapleCOMSPS-drup} \\
-      & 6773.9 & 73 & \solver{Kissat-sat} \\
-      & 6774.2 & 73 & \solver{Kissat} \\
-      & 7025.5 & 68 & \solver{upGlucose3.0-PADC} \\
-      & 7044.7 & 66 & \solver{Glucose3.0-proofs} \\
-\end{tabular}
-\caption{Planning (ALL)}
-\label{tab:planning}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline
- 1 & 3316.6 & 283 & \solbert{Painless-MCOMSPS-STR-32} \\
-(1)& 3714.7 & 271 & \solver{Painless-MCOMSPS-STR-64} \\
- 2 & 3743.4 & 269 & \solbert{Plingeling} \\
- 3 & 3985.3 & 260 & \solbert{ManyGlucose-32} \\
-   & 4022.7 & 262 & \solver{Painless-Maple-v1} \\
-   & 4036.3 & 258 & \solver{ManyGlucose-64} \\
-   & 4103.3 & 260 & \solver{Painless-Maple-v2} \\
-   & 4433.3 & 243 & \solver{Syrup-Scavel} \\
-   & 4903.4 & 225 & \solver{Treengeling} \\
-   & 5240.1 & 213 & \solver{abcdsat-p20} \\
-\end{tabular}
-\caption{Parallel (ALL)}
-\label{tab:parallelALL}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline
- 1 & 2853.7 & 153 & \solbert{Painless-MCOMSPS-STR-32} \\
- 2 & 2913.6 & 154 & \solbert{Painless-Maple-v1} \\
-(2)& 3082.7 & 151 & \solver{Painless-Maple-v2} \\
--- & 3196.9 & 148 & \solver{Painless-MCOMSPS-STR-64} \\
- 3 & 3805.9 & 133 & \solbert{Plingeling} \\
-   & 4048.3 & 130 & \solver{ManyGlucose-64} \\
-   & 4076.2 & 130 & \solver{ManyGlucose-32} \\
-   & 4675.4 & 119 & \solver{Syrup-Scavel} \\
-   & 4907.1 & 114 & \solver{Treengeling} \\
-   & 6337.5 & \phantom{0}85 & \solver{abcdsat-p20} \\
-\end{tabular}
-\caption{Parallel (SAT)}
-\label{tab:parallelSAT}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline
- 1 & 3680.8 & 136 & \solbert{Plingeling} \\
- 2 & 3779.5 & 130 & \solbert{Painless-MCOMSPS-STR-32} \\
- 3 & 3894.3 & 130 & \solbert{ManyGlucose-32} \\
-(3)& 4024.2 & 128 & \solver{ManyGlucose-64} \\
-   & 4142.8 & 128 & \solver{abcdsat-p20} \\
-   & 4191.1 & 124 & \solver{Syrup-Scavel} \\
-   & 4232.5 & 123 & \solver{Painless-MCOMSPS-STR-64} \\
-   & 4899.8 & 111 & \solver{Treengeling} \\
-   & 5123.9 & 109 & \solver{Painless-Maple-v2} \\
-   & 5131.9 & 108 & \solver{Painless-Maple-v1} \\
-\end{tabular}
-\caption{Parallel (UNSAT)}
-\label{tab:parallelUNS}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{cccl}
-\bf Place & \bf PAR-2 Score & \bf Num. Solved & \bf Solver \\
-\hline
- 1 & 2603.8 & 299 & \solbert{Mallob-Mono} \\
- 2 & 3146.8 & 278 & \solbert{TopoSAT 2} \\
- 3 & 4797.6 & 213 & \solbert{Slime} \\
-   & 6800.8 & 132 & \solver{Paracooba} \\
-   & 7299.0 & 110 & \solver{CTsat} \\
-   & 8468.3 & \phantom{0}62 & \solver{Paracooba-March} \\
-\end{tabular}
-\caption{Cloud (ALL)}
-\label{tab:cloud}
-\end{table}
-
-\subsection{Planning Track}
 % - 86 out of 100 biggest (number of clauses) are planning
@@
 
-\subsection{Similarity of Solvers}
-To investigate how similar the solvers of the Main track are to each other, we
-define a similarity metric based on the measured runtimes. For that we first
-remove $186$ benchmarks from the collected data that have not been solved by any
-solver. For the rest of the benchmarks we use the PAR-2 score,
-% based on the \num{5000}-second timeout
-i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
-This leaves us with $414$ floats
-$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
-and $B$, normalized to the interval $[0,1]$ is defined
-% as:
-by Equation~\ref{eq-similarity}.
-
-\begin{equation}
-\label{eq-similarity}
-	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{414 \cdot 10000}
-\end{equation}
-We calculated the \emph{similarity} between the $30$ solvers which achieved the
-best PAR-2 score in the main track. The results are displayed in
-Figure~\ref{fig-similarity-main} as a \emph{heat map}. Additionally the result
-of hierarchically clustering the solvers based on their similarity is
-illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
-are joined reflects how similar they are. For example
-enabling the \emph{trail saving} in \emph{CaDiCaL-alluip} has no impact on the
-runtime, resulting in a similarity above \num{0.999}. Thus the two solvers are joined very low in the dendrogram.
-% A similar visualization was used in the SAT Challenge 2012 \todo{cite}. They used
-
-One big cluster we can identify are the \emph{Mapel} decedents in the lower left
-corner, all of which are modifications of the winners of the SAT Competition
-2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
-  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
-has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
-family at the top right. With the exception of \emph{mergesat} and maybe
-\emph{DurianSat} we observe a high similarity within the cluster.
-
-The three \emph{Relaxed} solvers by \emph{Zhang} and \emph{Cai} are using the
-same code base as a lot of the solvers in the Maple-Cluster but their overall
-performance is better and closer to the CMS-Cluster.
-
-The CMS versions differ in their implementation of stochastic local search (SLS)
-but overall have a similar performance.
-
-The last big cluster in the center of the heat map is comprised of the solvers
-originally written by Biere. The three configurations of \emph{Kissat} form a
-sub-cluster, even though the configurations are fairly distinct from each other.
-% , specialized for satisfiable and unsatisfiable instances.
-% One targets satisfiable instances, while the other is focused on unsatisfiable
-% instances and a third alternating between them.
-
-The other sub-cluster consists of
-modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
-CaDiCaL-2020 has a worse overall performance than
-% has an overall worse per
-% is lacking behind
-the other solvers in this cluster.
-
-\begin{figure}[tp]
+\subsection{Incremental Library Applications and Instances}
+
+The incremental library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017. 
+Benchmarks for the Incremental Library track constist of \emph{benchmark applications} which implement and use the incremental SAT solver in their backend as well as \emph{benchmark instances} which serve as input to these applications.
+For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
+For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.
+
+\paragraph{Backbone Variables}
+
+Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Janota:2015:Backbones}. 
+The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
+We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.
+
+\paragraph{Essential Variables}
+
+Essential variables are defined to be those variables which have to be assigned in all partial models of a formula (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
+The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
+We used the same $50$ easy satisfiable instances as in backbone detection to evaluate solver performance with this application.
+
+\paragraph{Longest Simple Paths (LSP)}
+
+The application \textsf{genipalsp} determines longest simple paths in a graph~\cite{Balyo:2019:LSP}. 
+We selected $50$ easy LSP instances for our evaluation.\footnote{\url{http://algo2.iti.kit.edu/kalp/}}
+
+\paragraph{Maximum Satisfiability (MaxSAT)}
+
+The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
+The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
+For this application, we selected $50$ instances from \texttt{MaxSAT Evaluation 2019}.\footnote{\url{https://maxsat-evaluations.github.io/2019/}}
+
+\paragraph{Quantified Boolean Formulas (QBF)}
+\textsf{Ijtihad} is a QBF solver which uses counter\-example-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
+Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}
+
+\paragraph{Planning (SAS+)}
+We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar} -- a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
+
+\section{Competition Results}
+\label{sec:results}
+
+\begin{figure}
 \centering
-    \includegraphics[width=\linewidth]{similarity/cross.pdf}
-    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
-      % Similarity is defined as
-      % one minus the average taxicab distance normalized to the interval [0,1].
-      % Spearman's rank correlation coefficient.
-      Darker regions mean that the solvers are more similar.
-      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
-    }
-    \label{fig-similarity-main}
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
+\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
 \end{figure}
 
-% To estimate the similarity between the performance of the solvers of the Main
-% Track we define a similarity metric $s$.
-% identify each solver with a point in the 600-dimensional real vector
-% space. Each component describes the PAR-2 runtime on one instance. We map the
-% taxicab distance to the $[0, 1]$ interval and then to determine how similar two
-% solvers are.
-
-\includegraphics[width=\textwidth]{stability/ALL_random_smpling_correlations.png}
-\includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
+\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-UNSAT.pdf}
+\caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
+\end{figure}
+
+\begin{table}
+\centering\smaller
+\setlength\tabcolsep{3pt}
+%\begin{tabularx}{\linewidth}{X} \hline \end{tabularx}
+\begin{tabularx}{.47\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Main Track}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline
+1     & 3926.2 & 264 & \solbert{Kissat-sat} \\
+(1)   & 4083.1 & 260 & \solver{Kissat} \\
+2     & 4179.3 & 253 & \solbert{Relaxed-newTech} \\
+3     & 4266.7 & 248 & \solbert{CMS-ccnr-lsids} \\
+(3)   & 4278.0 & 250 & \solver{CMS-ccnr} \\
+      & 4428.1 & 250 & \solver{CaDiCaL-alluip-trail} \\
+      & 4429.6 & 250 & \solver{CaDiCaL-alluip} \\
+      & 4436.5 & 245 & \solver{Relaxed} \\
+      & 4501.2 & 243 & \solver{CMS-walksat} \\
+      & 4554.0 & 243 & \solver{CaDiCaL-trail}%
+%      & 4560.0 & 238 & \solver{Kissat-unsat} \\
+%      & 4607.6 & 246 & \solver{CaDiCaL-sc2020} \\
+%      & 5157.7 & 216 & \solver{Undominated} \\
+%      & 5159.6 & 220 & \solver{f2trc-DL} \\
+%      & 5177.0 & 214 & \solver{PADC-DL} \\  
+\end{tabularx}\quad%
+\begin{tabularx}{.5\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Parallel Track}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline
+ 1 & 3316.6 & 283 & \solbert{Painless-MCOMSPS-str32} \\
+(1)& 3714.7 & 271 & \solver{Painless-MCOMSPS-str64} \\
+ 2 & 3743.4 & 269 & \solbert{Plingeling} \\
+ 3 & 3985.3 & 260 & \solbert{ManyGlucose-32} \\
+   & 4022.7 & 262 & \solver{Painless-Maple-v1} \\
+   & 4036.3 & 258 & \solver{ManyGlucose-64} \\
+   & 4103.3 & 260 & \solver{Painless-Maple-v2} \\
+   & 4433.3 & 243 & \solver{Syrup-Scavel} \\
+   & 4903.4 & 225 & \solver{Treengeling} \\
+   & 5240.1 & 213 & \solver{abcdsat-p20} \\
+\end{tabularx}
+~\\[1em]
+\begin{tabularx}{.47\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Main Track, Satisfiable Instances}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline  
+ 1    & 2997.4 & 150 & \solbert{Relaxed-newTech} \\
+ 2    & 3127.6 & 146 & \solbert{Kissat-sat} \\
+ 3    & 3263.0 & 144 & \solbert{CMS-ccnr-lsids} \\
+(3)   & 3317.4 & 145 & \solver{CMS-ccnr} \\
+      & 3355.5 & 143 & \solver{Relaxed} \\
+      & 3721.2 & 139 & \solver{CMS-walksat} \\
+      & 3830.5 & 134 & \solver{Kissat} \\
+      & 3908.5 & 135 & \solver{CaDiCaL-alluip-trail} \\
+      & 3909.6 & 135 & \solver{CaDiCaL-alluip} \\
+      & 4265.6 & 126 & \solver{CaDiCaL-trail}%
+%      & 4368.6 & 130 & \solver{CaDiCaL-sc2020} \\
+%   & 4804.9 & 114 & \solver{Kissat-unsat} \\
+%   & 5173.2 & 110 & \solver{Undominated} \\
+%   & 5244.1 & 107 & \solver{PADC-DL} \\
+%   & 5264.9 & 110 & \solver{f2trc-DL} \\           
+\end{tabularx}\quad%
+\begin{tabularx}{.5\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Parallel Track, Satisfiable Instances}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline
+ 1 & 2853.7 & 153 & \solbert{Painless-MCOMSPS-str32} \\
+ 2 & 2913.6 & 154 & \solbert{Painless-Maple-v1} \\
+(2)& 3082.7 & 151 & \solver{Painless-Maple-v2} \\
+-- & 3196.9 & 148 & \solver{Painless-MCOMSPS-str64} \\
+ 3 & 3805.9 & 133 & \solbert{Plingeling} \\
+   & 4048.3 & 130 & \solver{ManyGlucose-64} \\
+   & 4076.2 & 130 & \solver{ManyGlucose-32} \\
+   & 4675.4 & 119 & \solver{Syrup-Scavel} \\
+   & 4907.1 & 114 & \solver{Treengeling} \\
+   & 6337.5 & \phantom{0}85 & \solver{abcdsat-p20} \\
+\end{tabularx}
+~\\[1em]
+\begin{tabularx}{.47\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Main Track, Unsatisfiable Instances}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline   
+1     & 4315.1 & 124 & \solbert{Kissat-unsat} \\
+(1)   & 4335.6 & 126 & \solver{Kissat} \\
+(1)   & 4724.8 & 118 & \solver{Kissat-sat} \\
+ 2    & 4842.5 & 117 & \solbert{CaDiCaL-trail} \\
+--    & 4846.7 & 116 & \solver{CaDiCaL-sc2020} \\
+(2)   & 4947.8 & 115 & \solver{CaDiCaL-alluip-trail} \\
+(2)   & 4949.6 & 115 & \solver{CaDiCaL-alluip} \\
+ 3    & 4991.4 & 110 & \solbert{f2trc-s} \\
+(3)   & 5051.4 & 109 & \solver{f2trc} \\
+(3)   & 5054.3 & 110 & \solver{f2trc-DL}%
+%      & 5069.6 & 109 & \solver{Maple-Mix} \\
+%      & 5110.0 & 107 & \solver{PADC-DL} \\
+%      & 5126.9 & 107 & \solver{Maple-Simp} \\
+%      & 5128.9 & 107 & \solver{MapleCBT-DL-v3} \\
+%      & 5142.2 & 106 & \solver{Undominated} \\  
+\end{tabularx}\quad%
+\begin{tabularx}{.5\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Parallel Track, Unsatisfiable Instances}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline
+ 1 & 3680.8 & 136 & \solbert{Plingeling} \\
+ 2 & 3779.5 & 130 & \solbert{Painless-MCOMSPS-str32} \\
+ 3 & 3894.3 & 130 & \solbert{ManyGlucose-32} \\
+(3)& 4024.2 & 128 & \solver{ManyGlucose-64} \\
+   & 4142.8 & 128 & \solver{abcdsat-p20} \\
+   & 4191.1 & 124 & \solver{Syrup-Scavel} \\
+   & 4232.5 & 123 & \solver{Painless-MCOMSPS-str64} \\
+   & 4899.8 & 111 & \solver{Treengeling} \\
+   & 5123.9 & 109 & \solver{Painless-Maple-v2} \\
+   & 5131.9 & 108 & \solver{Painless-Maple-v1}%
+\end{tabularx}
+~\\[1em]
+\begin{tabularx}{.47\linewidth}{cccX}
+\multicolumn{4}{l}{\bf Planning Track}\\
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\arrayrulecolor{lightgray}\hline   
+ 1    & 6406.9 & 80 & \solbert{CaDiCaL-alluip-trail} \\
+(1)   & 6409.3 & 80 & \solver{CaDiCaL-alluip} \\
+ 2    & 6466.9 & 79 & \solbert{CMS-ccnr-lsids} \\
+(2)   & 6471.9 & 79 & \solver{CMS-ccnr} \\
+(2)   & 6472.9 & 79 & \solver{CMS-walksat} \\
+ 3    & 6596.4 & 75 & \solbert{Kissat-unsat} \\
+      & 6650.1 & 79 & \solver{CaDiCaL-trail} \\
+      & 6713.0 & 75 & \solver{Maple-Mix} \\
+      & 6746.5 & 75 & \solver{MapleCOMSPS-init} \\
+      & 6754.3 & 73 & \solver{Maple-Simp}%
+%      & 6773.0 & 73 & \solver{MapleCOMSPS-drup} \\
+%      & 6773.9 & 73 & \solver{Kissat-sat} \\
+%      & 6774.2 & 73 & \solver{Kissat} \\
+%      & 7025.5 & 68 & \solver{upGlucose3.0-PADC} \\
+%      & 7044.7 & 66 & \solver{Glucose3.0-proofs} \\
+\end{tabularx}\quad%
+\begin{tabularx}{.5\linewidth}{cccX}
+\arrayrulecolor{lightgray}
+\multicolumn{4}{l}{\bf Cloud Track}\\
+%\hline
+\bf Pl. & \bf PAR-2 & \bf \# & \bf Solver \\
+\hline
+ 1 & 2603.8 & 299 & \solbert{Mallob-Mono} \\
+ 2 & 3146.8 & 278 & \solbert{TopoSAT 2} \\
+ 3 & 4797.6 & 213 & \solbert{Slime} \\
+   & 6800.8 & 132 & \solver{Paracooba} \\
+   & 7299.0 & 110 & \solver{CTsat} \\
+   & 8468.3 & \phantom{0}62 & \solver{Paracooba-March} \\
+\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}\\
+\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}\\
+\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}\\
+\phantom{0} & \phantom{0} & \phantom{0} & \phantom{0}
+\end{tabularx}
+\caption{Results of Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
+\label{tab:cloud}
+\end{table}
 
@@
 
-\begin{table}[ht!]
-\setlength\tabcolsep{4.5pt}
+\begin{table}[h!]
+\setlength\tabcolsep{4.5pt}%default: 6pt
+%\renewcommand{\arraystretch}{1.03}%default: 1
 \smaller
 \centering
-\begin{tabular}{lllcccc}
+\begin{tabularx}{\linewidth}{Xllcccc}
 \bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
@@
  &  & \solver{CBT} & -- & -- & -- & -- 
-\end{tabular}
-\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks.
-We partially \solbert{underlined} submission names.
-Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$.
-}
+\end{tabularx}
+\caption[Teams and Solvers in the Main Tracks]{\emph{Teams} and \emph{Solvers} in the Main Tracks.
+\emph{Base Solver} highlights solver genealogy while \emph{Variant} displays names of configurations and forks.
+Distinctive names are \solbert{underlined}.
+The rightmost columns indicate the awards given in the Main (\emph{M}) and Planning track (\emph{P}), and for performance on unsatisfiable (\emph{U}) and satisfiable (\emph{S}) instances.}
 \label{tab:solvers-main}
@@
 \begin{table}[ht]
-\smaller
-\arrayrulecolor{gray}
+%\smaller
 \centering
-\begin{tabular}{llc}
+\begin{tabularx}{\linewidth}{lXc}
 \bf Team & \bf Solver & \bf Score\\
-\hline\arrayrulecolor{lightgray}
-\stack{Soos, Cai, Devriendt, Gocht, }{Shaw, Meel}~ & \solver{CryptoMiniSat 5} & 3 \\
-\hline
+\hline
+Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 3 \\
 \stack{Biere, Fleury}~ & \solver{CaDiCaL 2020} & 1 \\
@@
 Manthey & \solver{Riss 7.1.2} & 1 
-\end{tabular}
+\end{tabularx}
 \caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
@@
 \begin{table}[b]
-\smaller
+%\smaller
 \centering
-\begin{tabular}{llccc}
+\begin{tabularx}{\linewidth}{Xlccc}
 \bf Team & \bf Solver & \bf M & \bf U & \bf S \\
@@
 \hline
-\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
+\multirow{2}{*}{Biere, Fazekas, Heisinger}
  & \solver{Plingeling} & 2 & 1 & 3 \\
@@
 Li, Wu, Xu, Chen & \solver{syrupscavel} & --& --& --\\
-\hline
+%\hline
 Chen & \solver{abcdsatptwenty} & --& --& --
-\end{tabular}
-\caption{Teams and Solvers participating in the parallel track.}
+\end{tabularx}
+\caption{Teams and Solvers participating in the Parallel track.}
 \end{table}
@@
 \begin{table}[t]
-\smaller
 \centering
-\begin{tabular}{llc}
+\begin{tabularx}{\linewidth}{Xlc}
 \bf Team & \bf Solver & \bf Rank\\
 \hline\arrayrulecolor{lightgray}
-Schreiber & \solver{mallob-mono} & 1\\
-\hline
-\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & \solver{TopoSAT2} & 2\\
-\hline
+Schreiber & \solver{Mallob Mono} & 1\\
+Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
 Riveros & \solver{Slime} & 3\\
 \hline
-\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & \solver{Paracooba}, & --\\
+\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
 & \solver{Paracooba-March} & --\\
@@
 Hartung & \solver{CTSat} & --
-\end{tabular}
-\caption{Teams and Solvers participating in the cloud track.}
+\end{tabularx}
+\caption{Teams and solvers participating in the Cloud track.}
 \end{table}
@@
 \begin{table}
-\centering
+%\setlength\tabcolsep{1.5pt}
+\smaller
+%\centering
 \begin{tabular}{ccl}
-\bf VBS1 & \bf Percent Total & \bf Solver \\
+\bf VBS-1 & \bf \% & \bf Solver \\
 \hline
@@
 13 & \phantom{0}3.2 & \solver{Relaxed} \\
-13 & \phantom{0}3.2 & \solver{Maple-alluip-trail} \\
+13 & \phantom{0}3.2 & \solver{Maple-alluip-tr.} \\
 12 & \phantom{0}3.0 & \solver{upGlucose3.0-PADC} \\
@@
 10 & \phantom{0}2.5 & \solver{CaDiCaL-sc2020} \\
-\end{tabular}
-~\\[1em]
+\end{tabular}\qquad%
+%~\\[1em]
 \begin{tabular}{ccl}
-\bf VBS2 & \bf Percent Total & \bf Solver \\
+\bf VBS-2 & \bf \% & \bf Solver \\
 \hline
@@
 \phantom{0}88.8 & 22.2 & \solver{CMS-ccnr} \\
-\phantom{0}84.1 & 21.0 & \solver{CaDiCaL-alluip-trail} \\
+\phantom{0}84.1 & 21.0 & \solver{CaDiCaL-alluip-tr.} \\
 \phantom{0}84.0 & 21.0 & \solver{CaDiCaL-alluip} \\
@@
 \phantom{0}81.5 & 20.4 & \solver{Relaxed} \\
-\end{tabular}
+\end{tabular}%
 ~\\[1em]
 \begin{tabular}{ccl}
-\bf VBS3 & \bf Percent Total & \bf Solver \\
+\bf VBS-3 & \bf \% & \bf Solver \\
 \hline
@@
 11.4 & 2.8 & \solver{Kissat-sat} \\
-10.8 & 2.7 & \solver{CaDiCaL-alluip-trail} \\
+10.8 & 2.7 & \solver{CaDiCaL-alluip-tr.} \\
 10.8 & 2.7 & \solver{CaDiCaL-alluip} \\
@@
 There were 48 (non-disqualified) solvers (and their configurations).
-Each table shows the first ten solvers sorted according to the respective metric.}
+Each table shows the first ten solvers sorted according to the respective metric.\todo{Maybe move classic PAR-2 ranking also to here for comparison}}
 \label{tab:vbsMainALL}
@@
 \centering
-\begin{tabular}{clccc}
-\bf Iteration & \bf Selected Solver & \bf Num. Solved & \bf Contributes \\ % & covered so far \\
-\hline
+\begin{tabularx}{\linewidth}{cXccc}
+\bf Iteration & \bf Selected Solver & \bf Solved & \bf Contributes \\ % & covered so far \\
+\hline\arrayrulecolor{lightgray}
 \phantom{0}1 & \solver{Kissat-sat} & 264 & 264 \\ % & 264 \\
@@
  & Total & -- & 316 \\
-\end{tabular}
+\end{tabularx}
 \caption{A greedy set cover of the solved instances by solvers of the Main track.}
@@
 \centering
-\begin{tabular}{cccl}
-\bf \#Solvers & \bf Time (s) & \bf Num. Solved & \bf Best Schedule \\
-\hline
-1 & 5000 & 264 & \solver{\{Kissat-sat\}} \\
-2 & 2500 & 278 & \solver{\{Kissat-unsat, Relaxed\_newTech\}} \\
-3 & 1666 & 272 & \solver{\{Kissat-unsat, Kissat-sat, }\\
-			 &&& \solver{CMS-ccnr-lsids\}} \\
-4 & 1250 & 262 & \solver{\{Kissat-unsat, Kissat-sat, }\\
-			 &&& \solver{CMS-ccnr-lsids, Maple-alluip-trail\}} \\ 
-5 & 1000 & 253 & \solver{\{Kissat-unsat, Kissat-sat, }\\
-			&&& \solver{CMS-ccnr-lsids, Maple-alluip-trail, }\\ 
-			&&& \solver{CaDiCaL-alluip \}}\\
-\end{tabular}
-\caption{``Uniform time split'' schedules %using $i$ solvers 
-to solve as many Main track instances as possible.}
+\begin{tabulary}{\linewidth}{cccL}
+\bf k & \bf Time (s) & \bf Solved & \bf Best Schedule \\
+\hline
+1 & 5000 & 264 & \{ \solver{Kissat-sat} \}\\
+2 & 2500 & 278 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \}\\
+3 & 1666 & 272 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \phantom{\{ }\solver{CMS-ccnr-lsids} \} \\
+4 & 1250 & 262 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \phantom{\{ }\solver{CMS-ccnr-lsids}, \solver{Maple-alluip-trail} \}\\ 
+5 & 1000 & 253 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \phantom{\{ }\solver{CMS-ccnr-lsids}, \solver{Maple-alluip-trail}, \phantom{\{ }\solver{CaDiCaL-alluip} \}\\
+\end{tabulary}
+\caption{Schedules that maximize the number of solved Main track instances for $k \in \{1, \dots, 5\}$ solvers among which $5000$ seconds are split uniformly.}
 \label{tab:MainUniformTimeSplit}
@@
 \centering
-\begin{tabular}{lccc}
-\bf Solver & \bf Taking Up (s) & \bf Solving Under Limit & \bf Contributes \\
-\hline
+\begin{tabularx}{\linewidth}{Xccc}
+\bf Solver & \bf Time (s) & \bf Solved & \bf Contributes \\
+\hline\arrayrulecolor{lightgray}
 \solver{Kissat-unsat} & 2523 & 219 & 219 \\
@@
 Total & 5000 & \phantom{0}-- & 286 \\ 
-\end{tabular}
+\end{tabularx}
 \caption{An optimal \SI{5000}{\second} schedule for the Main track
@@
 
-\paragraph{Marginal Contributions to VBS} Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth''~\cite{} or ``timetable''~\cite{}.
-
 \begin{table}[tb]
+%\setlength\tabcolsep{2.5pt}%default: 6pt
+%\renewcommand{\arraystretch}{1.03}%default: 1
+%\smaller
 \centering
-\begin{tabular}{lll}
-\bf Solver 1 & \bf Solver 2 & \bf VBS\\
+\begin{tabularx}{\linewidth}{rXl}
+\bf k & \bf k-Tuple & \bf Score\\ 
 \hline\arrayrulecolor{lightgray}
-\multirow{3}{*}{\solver{Kissat}} & \solver{CMS-CCAnr} & $3028.0$\\
- & \solver{CMS-CCAnr lsids} & $3052.8$\\
- & \solver{CMS-Walksat} & $3127.7$\\
-\hline
-\solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-CCAnr}} & $3128.0$\\
-\solver{CaDiCaL-alluip-trail} &  & $3128.0$\\
-\hline
-\solver{CaDiCaL-alluip} & \multirow{2}{*}{\solver{CMS-Walksat}} & $3152.8$\\
-\solver{CaDiCaL-alluip-trail} &  & $3152.9$\\
-\hline
-\solver{Kissat} & \multirow{2}{*}{\solver{Relaxed-newTech}} & $3177.7$\\
-\solver{Kissat-unsat} &  & $3177.8$
-\end{tabular}
-\caption{The $9$ best performing tuples of solvers in terms of their VBS' PAR-2 score.}
-\label{tab:best-tuples}
+1 & \{ \solver{Kissat-sat} \} & $3926.2$\\
+\hline
+2 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \} & $3160.5$\\
+3 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020} \} & $2986.4$\\
+4 & \{ \solver{Kissat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020}, \solver{Scavel01} \} & $2842.6$\\
+5 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-2020}, \solver{Scavel01}, \phantom{\{ }\solver{CMS-Walksat} \} & $2757.3$\\
+6 & \{ \solver{Kissat-sat}, \solver{Kissat-unsat}, \solver{Relaxed}, \solver{Relaxed-newTech}, \phantom{\{ }\solver{CaDiCaL-alluip-trail}, \solver{f2trc-s} \} & $2687.0$\\
+7 & \{ \solver{Kissat-sat}, \solver{Kissat-unsat}, \solver{Relaxed}, \solver{Relaxed-newTech}, \phantom{\{ }\solver{CaDiCaL-alluip-trail}, \solver{f2trc-s}, \solver{CMS-Walksat}\} & $2616.9$\\
+\hline
+48 & \emph{set of all solvers} & $2431.4$
+\end{tabularx}
+\caption{Best performing k-tuples in terms of their VBS's PAR-2 score.}
+\label{tab:tuples}
 \end{table}
 
-\begin{table}[tb]
+The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, 
+which is much better than that of the single best solver  \solver{Kissat-sat} with a PAR-2 score of $3926.2$. 
+We also calculated the PAR-2 score of the VBS of small subsets of the $48$ submitted solvers. 
+In Table~\ref{tab:tuples}, we report on the best performing sets of solvers of fixed size $k \in \{1, \dots, 7\}$.
+
+\subsection{Score per Instance Family}
+
+\todo{Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth'' or ``timetable''.
+}
+
+\subsection{Similarity of Solvers}
+To investigate how similar the solvers of the Main track are to each other, we
+define a similarity metric based on the measured runtimes. For that we first
+remove $186$ benchmarks from the collected data that have not been solved by any
+solver. For the rest of the benchmarks we use the PAR-2 score,
+% based on the \num{5000}-second timeout
+i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
+This leaves us with $414$ floats
+$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
+and $B$, normalized to the interval $[0,1]$ is defined
+% as:
+by Equation~\ref{eq-similarity}.
+
+\begin{equation}
+\label{eq-similarity}
+	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{414 \cdot 10000}
+\end{equation}
+We calculated the \emph{similarity} between the $30$ solvers which achieved the
+best PAR-2 score in the main track. The results are displayed in
+Figure~\ref{fig-similarity-main} as a \emph{heat map}. Additionally the result
+of hierarchically clustering the solvers based on their similarity is
+illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
+are joined reflects how similar they are. For example
+enabling the \emph{trail saving} in \emph{CaDiCaL-alluip} has no impact on the
+runtime, resulting in a similarity above \num{0.999}. Thus the two solvers are joined very low in the dendrogram.
+% A similar visualization was used in the SAT Challenge 2012 \todo{cite}. They used
+
+One big cluster we can identify are the \emph{Mapel} decedents in the lower left
+corner, all of which are modifications of the winners of the SAT Competition
+2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
+  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
+has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
+family at the top right. With the exception of \emph{mergesat} and maybe
+\emph{DurianSat} we observe a high similarity within the cluster.
+
+The three \emph{Relaxed} solvers by \emph{Zhang} and \emph{Cai} are using the
+same code base as a lot of the solvers in the Maple-Cluster but their overall
+performance is better and closer to the CMS-Cluster.
+
+The CMS versions differ in their implementation of stochastic local search (SLS)
+but overall have a similar performance.
+
+The last big cluster in the center of the heat map is comprised of the solvers
+originally written by Biere. The three configurations of \emph{Kissat} form a
+sub-cluster, even though the configurations are fairly distinct from each other.
+% , specialized for satisfiable and unsatisfiable instances.
+% One targets satisfiable instances, while the other is focused on unsatisfiable
+% instances and a third alternating between them.
+
+The other sub-cluster consists of
+modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
+CaDiCaL-2020 has a worse overall performance than
+% has an overall worse per
+% is lacking behind
+the other solvers in this cluster.
+
+\begin{figure}[tp]
     \centering
-\begin{tabular}{llll}
-\bf Solver 1 & \bf Solver 2 & \bf Solver 3 & \bf VBS\\
-\hline\arrayrulecolor{lightgray}
-\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{f2trc-DL} & $2827.7$\\
-\hline
-\multirow{3}{*}{\solver{Kissat}} & \multirow{3}{*}{\solver{CMS-CCAnr}} & \solver{Scavel01} & $2852.7$\\
- &  & \solver{f2trc-DL} & $2852.8$\\
- &  & \solver{DurianSat} & $2852.8$\\
-\hline
-\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{Scavel01}& $2877.6$\\
-%\solver{Kissat-unsat} & \solver{CryptoMiniSat-Walksat} & \solver{f2trc-DL} & $2877.8$\\
-%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-Walksat} & \solver{DurianSat} & $2877.8$\\
-%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-Walksat} & \solver{f2trc-DL} & $2877.8$\\
-%\solver{CaDiCaL-alluip} & \solver{CryptoMiniSat-CCAnr} & \solver{Kissat} & $2877.8$\\
-\end{tabular}
-\caption{The $5$ best performing triples of solvers in terms of their VBS' PAR-2 score.}
-\label{tab:best-triples}
-\end{table}
-
-\begin{table}[tb]
-\centering
-\setlength\tabcolsep{4.5pt}
-\begin{tabular}{lllll}
-\bf Solver 1 & \bf Solver 2 & \bf Solver 3 & \bf Solver 4 & \bf VBS\\
-\hline\arrayrulecolor{lightgray}
-\multirow{2}{*}{\solver{Kissat}} & \multirow{2}{*}{\solver{CMS-CCAnr}} & \multirow{2}{*}{\solver{Scavel01}} & \solver{CaDiCaL-alluip} & 2727.7\\
- &  &  & \solver{CaDiCaL-alluip-trail} & 2727.7\\
-\hline
-\solver{Kissat} & \solver{CMS-CCAnr lsids} & \solver{f2trc-DL} & \solver{exp-V-LGB} & 2752.5\\
-\hline
-\solver{Kissat} & \solver{CaDiCaL-2020} & \solver{Scavel01} & \solver{Relaxed-newTech} & 2752.6\\
-% & \solver{CMS-CCAnr lsids} & \solver{Scavel01} & \solver{f2trc-DL} & 2752.6
-\end{tabular}
-\caption{The $4$ best performing quatruples of solvers in terms of their VBS' PAR-2 score.}
-\label{tab:best-quatruples}
-\end{table}
-
-The PAR-2 score of the VBS of all $48$ submitted solvers is $2701$. 
-This is much better than the PAR-2 score of the single best solver (SBS) $3926$. 
-In order to further analyze the contribution of solvers to the VBS, we calculated the PAR-2 score of the VBS of fixed-size subsets of the submitted solvers. 
-In the following, we report on the best scores achieved by tuples, triples and quatruples of solvers in terms of their VBS's PAR-2 score.
-
-The best scoring solver tuple is \solver{Kissat} and \solver{CryptoMiniSat-CCAnr}. 
-The VBS of those two solvers achieved a PAR-2 score of $3028$. 
-Further well performing solver tuples can be created from combinations of \solver{CaDiCaL-alluip} and \solver{CryptoMiniSat-CCAnr} or \solver{Kissat} and \solver{Relaxed-newTech}. 
-A detailed report on the exact variants and scores of those solver tuples can be seen in Table~\ref{tab:best-tuples}.
-
-The best triple of solvers is \solver{Kissat}, \solver{CryptoMiniSat-CCAnr lsids} and \solver{f2trc-DL}. 
-In combination their VBS achieves a PAR-2 score of $2827.7$. 
-Other combinations of \solver{Kissat} and \solver{CryptoMiniSat-CCAnr} with \solver{Scavel01} or \solver{DurianSat} achieved runner-up scores as can be seen in Table~\ref{tab:best-triples}.
-
-With a PAR-2 score of $2727.7$ the solver quatruple \solver{Kissat}, \solver{CryptoMiniSat-CCAnr}, \solver{Scavel01} and \solver{CaDiCaL-alluip} is very close to the overall VBS. 
-Runner-up and further best performing quatruples can be seen in Table~\ref{tab:best-quatruples}.
+    \includegraphics[width=\linewidth]{similarity/cross.pdf}
+    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
+      % Similarity is defined as
+      % one minus the average taxicab distance normalized to the interval [0,1].
+      % Spearman's rank correlation coefficient.
+      Darker regions mean that the solvers are more similar.
+      A more precise relation between color and similarity-value together with a histogram of the values that appear is given at the bottom.
+    }
+    \label{fig-similarity-main}
+\end{figure}
+
+% To estimate the similarity between the performance of the solvers of the Main
+% Track we define a similarity metric $s$.
+% identify each solver with a point in the 600-dimensional real vector
+% space. Each component describes the PAR-2 runtime on one instance. We map the
+% taxicab distance to the $[0, 1]$ interval and then to determine how similar two
+% solvers are.
+
+\subsection{Sampling}
+\includegraphics[width=\textwidth]{stability/ALL_random_smpling_correlations.png}
+\includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
 

### 2021-01-22 paper/main.tex
few sentences about small portfolios

@@
 \end{tabularx}
-\caption{Results of Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
-\label{tab:cloud}
+\caption{Top 10 Solvers in Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
+\label{tab:results}
 \end{table}
@@
 
-\begin{table}[tb]
-%\setlength\tabcolsep{2.5pt}%default: 6pt
-%\renewcommand{\arraystretch}{1.03}%default: 1
-%\smaller
+\begin{table}[t]
 \centering
 \begin{tabularx}{\linewidth}{rXl}
-\bf k & \bf k-Tuple & \bf Score\\ 
+\bf k & \bf Best k-Tuple & \bf Score\\ 
 \hline\arrayrulecolor{lightgray}
@@
 \hline
-48 & \emph{set of all solvers} & $2431.4$
+48 & \emph{Set of all Solvers} & $2431.4$
 \end{tabularx}
@@
 
-The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, 
-which is much better than that of the single best solver  \solver{Kissat-sat} with a PAR-2 score of $3926.2$. 
-We also calculated the PAR-2 score of the VBS of small subsets of the $48$ submitted solvers. 
-In Table~\ref{tab:tuples}, we report on the best performing sets of solvers of fixed size $k \in \{1, \dots, 7\}$.
+The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, which is much better than the PAR-2 score of $3926.2$ of the single best solver \solver{Kissat-sat}. 
+Given the set of solvers $S$, the set of tuples of size $k$ is defined as follows $P_k := \{ T \mid T \in 2^S \land |T| = k\}$.
+We calculated the PAR-2 score for each VBS created from solver tuples in $P_k$. 
+In Table~\ref{tab:tuples}, we report on the single best performing $k$-tuple $T_k \in P_k$ ($1 \leq k \leq 7$).
+
+Interestingly, each of the first five tuples $T_{k \leq 5}$ contains exactly one of the three \solver{Kissat} variants. 
+For $i < 5$ the relation $T_{i} \subset T_{i+1}$ holds only under projection to base solvers due to the fluctuating variants of \solver{Kissat}. 
+The composition changes more strongly in $T_6$. 
+Interestingly, we now have both variants $\{ \solver{Kissat-sat}, \solver{Kissat-unsat} \} \subset T_6$, and moreover it holds that $T_6 \subset T_7$.
+With the only exception being $\solver{Scavel01} \in T_6 \cap T_7$, all solvers in $T_1, \dots, T_7$ belong the top performing solvers in the Main track (cf. Table~\ref{tab:results}).
 
 \subsection{Score per Instance Family} 
-
 \todo{Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth'' or ``timetable''.

### 2021-01-22 paper/by-family/pos.sh

@@ -1,0 +1,13 @@
+
+for file in $@; do
+	#echo " ### Positions of Best Main Track Solvers in $file"
+	grep -nH "kissat\|relaxed\|cryptominisat\|cadical\|scavel…\|f2trc" $file
+	#echo $(grep -n kissat_sat $file) $file
+	#echo $(grep -n relaxed_newtech $file) $file 
+	#echo $(grep -n cryptominisat_ccnr_lsids $file) $file
+	#echo
+	#grep -n kissat_unsat $file
+	#grep -n cadical_alluip $file
+	#grep -n f2trc $file
+	#echo
+done

### 2021-01-25 paper/by-family/gen.sh
added evaluation per family

@@ -1,3 +1,3 @@
 for family in $(gbd get "competition_track = main_2020" -r family | sort -k2 | uniq -s33 -c | sort -n | tail -n12 | head -n11 | cut -d" " -f8); do 
-  gbd eval par2 "competition_track = main_2020 and family = $family" -r cadical_sc2020 duriansat exmaple_padc_dl exmaple_padc_dl_ovau_exp exmaple_padc_dl_ovau_lin exmaple_psids_dl kissat kissat_sat kissat_unsat maple_scavel maple_alluip_trail maple_lrb_vsids_2_init maplecomsps_lrb_vsids_2 maple_scavel01 maple_scavel02 maple_dl_f2trc maplelcmdistchronobt_dl_v3 maple_f2trc maple_f2trc_s maple_cm_dist maple_cm_dist_sattime2s maple_cm_dist_simp2 maple_cmused_dist maple_mix maple_simp parafrost parafrost_cbt pausat relaxed relaxed_newtech relaxed_notimepara slime undominated_top16 undominated_top24 undominated_top36 undominated cadical_alluip cadical_alluip_trail cadical_trail cryptominisat_ccnr cryptominisat_ccnr_lsids cryptominisat_walksat exp_l_mld_cbt_dl exp_v_lgb_mld_cbt_dl exp_v_l_mld_cbt_dl exp_v_mld_cbt_dl glucose3 upglucose_3_padc | cut -d. -f1 | sort -k2 -t: -n > eval-$family.score
[…]

### 2021-01-25 paper/main.tex
took care of some todos

@@
 
-\todo{Should we have a discussion (maybe in later sections)
-about the future of the portfolio solver rule
-concerning the point raised by Mate Soos (in emails)?}
-
 \paragraph{Organizers}
@@
 in the Main track (besides the No Limits track).
+In some cases solvers output the correct result but the repective certificate was wrong. 
+Such solvers were demoted to the No-limits track of the competition.
 
@@
 a proof and {\tt cake\_lpr} would later disagree with the verdict.
-
-\todo{on wrong certificate (but still correct result) followed the demotion of the solver to the no-limits track}
 
@@
 \DontPrintSemicolon
-
+\small
 \KwData{$I$ : Set of Instances, $A$ : Set of Authors}
@@
 \begin{table}[t]
-\small
-\centering
+\centering\small
 \begin{tabular}{llrr}
@@
 \begin{table}[t]
-\centering
+\centering\small
 \begin{tabular}{rcccc}
@@
 
-Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
-by each encoding.
-
-\begin{table}[h]
-\centering
+\begin{table}[t]
+\centering\small
 \begin{tabular}{llrr}
@@
 \label{tab:planningBenchmarkDist}
-\caption{Number of benchmarks generated by each encoding.}
+\caption{Number of planning instances generated per encoding.}
 \end{table}
 
-The benchmarks of the planning track adhere to the naming convention below.
-For
-% more details and
-a complete list of the encoded planning tasks we refer to the
-generation script {\color{red}BROKEN LINK}.
-
+Table \ref{tab:planningBenchmarkDist} shows the number of benchmarks generated
+by each encoding. 
+For a complete list of the encoded planning tasks we refer to the
+generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/SAT2020_planning_generator.tar.xz}} 
+The benchmarks of the planning track adhere to the following naming convention:
 ${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
-  \texttt{pathToInstance} \rangle\_\langle \texttt{makespan}
+  \texttt{name} \rangle\_\langle \texttt{makespan}
   \rangle\text{.cnf}}$
@@
 \begin{table}[ht]
-%\smaller
-\centering
-\begin{tabularx}{\linewidth}{lXc}
-\bf Team & \bf Solver & \bf Score\\
-\hline
-Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 3 \\
-\stack{Biere, Fleury}~ & \solver{CaDiCaL 2020} & 1 \\
-Chen & \solver{abcdsat-i20} & 1 \\
-Manthey & \solver{Riss 7.1.2} & 1 
-\end{tabularx}
-\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
+\centering\small
+\begin{tabular}{llc}
+\bf Team & \bf Solver & \bf Place\\
+\hline
+Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 1 \\
+Biere, Fleury & \solver{CaDiCaL 2020} & -- \\
+Chen & \solver{abcdsat-i20} & -- \\
+Manthey & \solver{Riss 7.1.2} & -- 
+\end{tabular}
+\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track.}
 \label{tab:solvers-incremental}
@@
 
-\subsubsection{CryptoMiniSat-CCAnr and CryptoMiniSat5}
+\subsubsection{CryptoMiniSat}
 \label{sec:cryptominisat}
@@
 
-\subsubsection{Trail Saving and Stable AllUip in CaDiCaL}
+\subsubsection{CaDiCaL AllUip}
 
@@
 
-\subsubsection{Relaxed Maple newTech}
+\subsubsection{Relaxed newTech}
 
@@
 \begin{table}[b]
-%\smaller
-\centering
-\begin{tabularx}{\linewidth}{Xlccc}
-\bf Team & \bf Solver & \bf M & \bf U & \bf S \\
+\centering\small
+\begin{tabular}{llccc}
+\bf Team & \bf Solver & \bf U+S & \bf U & \bf S \\
 \hline\arrayrulecolor{lightgray}
@@
 \multirow{2}{*}{Tchinda, Djamegni}
- & \solver{painlessmaplevone} & --& --& 2 \\
- & \solver{painlessmaplevtwo} & --& --& 2 \\
-\hline
-Li, Wu, Xu, Chen & \solver{syrupscavel} & --& --& --\\
+ & \solver{Painless-Maple-v1} & --& --& 2 \\
+ & \solver{Painless-Maple-v2} & --& --& 2 \\
+\hline
+Li, Wu, Xu, Chen & \solver{Syrup Scavel} & --& --& --\\
 %\hline
-Chen & \solver{abcdsatptwenty} & --& --& --
-\end{tabularx}
+Chen & \solver{abcdSAT-p20} & --& --& --
+\end{tabular}
 \caption{Teams and Solvers participating in the Parallel track.}
@@
 
-\subsubsection{Painless MCOMSPS STR}
+\subsubsection{Painless MapleCOMSPS STR}
 
 \solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32 core} and a \solver{64 core} variant and won three awards: first place in the Main track, best score on satisfiable and second best score on unsatisfiable instances.
-The \solver{32 core} variant achieved slightly better scores than the \solver{64 core} variant. 
-The \solver{32 core} variant performed much better, such that the runner-up solvers on satisfiable and unsatisfiable instances outperformed the \solver{64 core} variant.
+The authors submitted a \solver{32} and a \solver{64} threaded variant and won three awards: first place overall, best score on satisfiable and second best score on unsatisfiable instances. 
+In the overall evaluation, the \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant. 
+However, in the separate evaluations on satisfiable and unsatisfiable variants the \solver{32} threaded variants performed much better, such that the runner-up solvers outperformed the \solver{64} threaded variant.
 
@@
 
-\solver{Painless-MCOMSPS-STR} diversifies mainly via diverse fixed configurations of the branching strategies LRB and VSIDS, and sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}.
-However, a special solver instance performs concurrent clause strengthening~\cite{Wieringa:2013:CCS}. 
-Another special solver instance is configured to perform Gaussian elimination during preprocessing. 
+\solver{Painless-MCOMSPS-STR} diversifies mainly via hard-coded configurations of the branching strategies LRB and VSIDS, and via sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}.
+Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} Gaussian elimination, respectively. 
 \solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
@@
 
-\solver{Plingeling} achieved the best score on unsatisfiable instances, second place in the Main track, and the third best score on satisfiable instances. 
+\solver{Plingeling} achieved the best score on unsatisfiable instances, second place in the overall evaluation, and the third best score on satisfiable instances. 
 \solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
 In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
-\solver{Plingeling} uses random seeds for diversification via polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.
+\solver{Plingeling} uses random seeds for diversification via variable polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.
 
@@
 
-\solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
-The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third best score on unsatisfiable instances. 
+\solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
+The \solver{32} threaded variant received two awards in this competition: the overall third place and third best score on unsatisfiable instances. 
 \solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
@@
 
-\solver{Painless Maple} received the award for the second best performance in the Sat track but scored last in the Unsat track. 
+\solver{Painless Maple} received the award for the second best performance on satisfiable instances but had the worst performance on unsatisfiable instances. 
 \solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
-
 \solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
@@
 \begin{table}[t]
-\centering
-\begin{tabularx}{\linewidth}{Xlc}
-\bf Team & \bf Solver & \bf Rank\\
+\centering\small
+\begin{tabular}{llc}
+\bf Team & \bf Solver & \bf Place\\
 \hline\arrayrulecolor{lightgray}
@@
 Hartung & \solver{CTSat} & --
-\end{tabularx}
+\end{tabular}
 \caption{Teams and solvers participating in the Cloud track.}
@@
 This functionality is disabled in the submitted variant \solver{Mallob Mono}. 
-
-\solver{Mallob} mainly uses \solver{Lingeling-bcj} and diversifies via randomized sparse initialization of branching scores. 
-However, as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
-
-\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
+\solver{Mallob} uses \solver{Lingeling-bcj} and as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
+Diversification is done via randomized sparse initialization of branching scores.
+
+\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from its leafs to the root. 
 Each node performs a three-way merge of its local export buffer and the two incoming buffers. 
@@
 
-\solver{Mallob} uses a global clause size limit and a dynamic limit for the sharing buffer, which depends on the position in the binary tree and grows while getting closer to the root. 
+\solver{Mallob} uses a global clause size limit and a dynamic size limit for the sharing buffer, which depends on its position in the binary tree and is larger the closer we get to the root. 
 Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
@@
 \solver{TopoSAT~2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
-\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
+\solver{TopoSAT~2} uses lock-free clause-exchange for solvers on the same machine, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
 \solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
-\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.
+\solver{Toposat~2} diversifies via strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.
 
@@
 
-\section{More detailed analysis of the Main track results (to be renamed)}
+\section{Differentiated Analysis of Main Track Results}
 
@@
 There were 48 (non-disqualified) solvers (and their configurations).
-Each table shows the first ten solvers sorted according to the respective metric.\todo{Maybe move classic PAR-2 ranking also to here for comparison}}
+Each table shows the first ten solvers sorted according to the respective metric.}
 \label{tab:vbsMainALL}
@@
 \begin{table}
-\centering
+\centering\small
 \begin{tabularx}{\linewidth}{cXccc}
@@
 \begin{table}
-\centering
+\centering\small
 \begin{tabulary}{\linewidth}{cccL}
@@
 2 & 2500 & 278 & \{ \solver{Kissat-unsat}, \solver{Relaxed-newTech} \}\\
-3 & 1666 & 272 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \phantom{\{ }\solver{CMS-ccnr-lsids} \} \\
-4 & 1250 & 262 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \phantom{\{ }\solver{CMS-ccnr-lsids}, \solver{Maple-alluip-trail} \}\\ 
-5 & 1000 & 253 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \phantom{\{ }\solver{CMS-ccnr-lsids}, \solver{Maple-alluip-trail}, \phantom{\{ }\solver{CaDiCaL-alluip} \}\\
+3 & 1666 & 272 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids} \} \\
+4 & 1250 & 262 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids}, \phantom{\{ }\solver{Maple-alluip-trail} \}\\ 
+5 & 1000 & 253 & \{ \solver{Kissat-unsat}, \solver{Kissat-sat}, \solver{CMS-ccnr-lsids}, \phantom{\{ }\solver{Maple-alluip-trail}, \solver{CaDiCaL-alluip} \}\\
 \end{tabulary}
@@
 \begin{table}
-\centering
+\centering\small
 \begin{tabularx}{\linewidth}{Xccc}
@@
 \begin{table}[t]
-\centering
-\begin{tabularx}{\linewidth}{rXl}
+\centering\small
+\begin{tabulary}{\linewidth}{rLl}
 \bf k & \bf Best k-Tuple & \bf Score\\ 
@@
 48 & \emph{Set of all Solvers} & $2431.4$
-\end{tabularx}
+\end{tabulary}
 \caption{Best performing k-tuples in terms of their VBS's PAR-2 score.}
@@
 
-The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, which is much better than the PAR-2 score of $3926.2$ of the single best solver \solver{Kissat-sat}. 
+The PAR-2 score of the VBS of all $48$ submitted solvers in the Main track is $2431.4$, which is close to 40\% better than the PAR-2 score of $3926.2$ of the single best solver \solver{Kissat-sat}. 
 Given the set of solvers $S$, the set of tuples of size $k$ is defined as follows $P_k := \{ T \mid T \in 2^S \land |T| = k\}$.
@@
 Interestingly, we now have both variants $\{ \solver{Kissat-sat}, \solver{Kissat-unsat} \} \subset T_6$, and moreover it holds that $T_6 \subset T_7$.
-With the only exception being $\solver{Scavel01} \in T_6 \cap T_7$, all solvers in $T_1, \dots, T_7$ belong the top performing solvers in the Main track (cf. Table~\ref{tab:results}).
+All solvers in $T_1, \dots, T_7$ belong the top performing solvers in the Main track, with the only exception being $\solver{Scavel01} \in T_6 \cap T_7$ (cf. Table~\ref{tab:results}).
 
 \subsection{Score per Instance Family}
-\todo{Interestingly, the second (Relaxed-Maple-newTech) and the third (CryptoMinisat-lsids) ranked solver both outperform the winning solver (Kissat-sat) when we project only on the instance families ``antibandwidth'' or ``timetable''.
-}
+
+Contributions to the VBS can be well capatured by clustering the instance space into instance families. 
+We evaluated the runtimes of the three winning solvers of the Main track on the all families represented by at least $14$ instances (cf.
+Table~\ref{tab:families}) and report on their place and score in Table~\ref{tab:eval-by-family}.
+
+Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on a few instance families by a large margin, namely \emph{Anti-Bandwidth}, \emph{Vlsat}, \emph{Hypertree Decomposition}, \emph{Influence Maximization} and \emph{Tournament}.
+
+\begin{table}
+\small
+\begin{tabularx}{\linewidth}{X|rrrrrr}
+ & \multicolumn{2}{l}{\solver{Kissat-sat}} & \multicolumn{2}{l}{\solver{Relaxed-newTech}} & \multicolumn{2}{l}{\solver{CMS-ccnr-lsids}} \\
+\bf Family & \bf Pl. & \bf PAR-2 & \bf Pl. & \bf PAR-2 & \bf Pl. & \bf PAR-2 \\
+\hline
+Anti-Bandwidth 			& 26 & 7435.6 &  2 & 5863.2 &  \bf 1 & 4958.7\\
+Bit-Vector 				&  \bf 7 & 8310.2 & 22 & 8772.4 & 42 & 9005.9\\
+Coloring 				&  \bf 2 & 5357.1 & 11 & 7589.3 & 13 & 7910.1\\
+Core-Based Generator 	&  \bf 3 & 1217.0 & 29 & 3170.7 &  4 & 1253.3\\
+Cryptography 			&  \bf 4 & 3451.4 &  6 & 3526.9 & 10 & 4124.2\\
+Hypertree Decomposition & 21 & 1173.3 &  \bf 8 & 1016.0 & 38 & 3188.0\\
+Influence Maximization 	& 22 & 2350.4 &  \bf 3 & 1838.9 & 11 & 2035.8\\
+Tensors 				&  \bf 2 & 1412.4 &  7 & 4411.2 & 11 & 7414.2\\
+Timetable 				& 41 & 7889.0 & 21 & 5103.8 & \bf 19 & 5092.4\\
+Tournament 				& 20 & 10000.0&  \bf 2 & 8715.0 &  9 & 10000.0\\
+Vlsat 					& 27 & 7149.7 &  5 & 5307.5 &  \bf 1 & 5026.4\\
+\end{tabularx}
+\caption{Place and PAR-2 of Winning Solvers in the Main Track per Instance Family}
+\label{tab:eval-by-family}
+\end{table}
 
@@
 
-One big cluster we can identify are the \emph{Mapel} decedents in the lower left
+One big cluster we can identify are the \emph{Maple} decedents in the lower left
 corner, all of which are modifications of the winners of the SAT Competition
-2018 and the SAT Race 2019. \todo{I think... also race vs competition? Sorry I am new
-  here NF} The solver \emph{mergesat} does not quite fit into the cluster and
-has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS})
-family at the top right. With the exception of \emph{mergesat} and maybe
-\emph{DurianSat} we observe a high similarity within the cluster.
+2018 and the SAT Race 2019. 
+%The solver \emph{mergesat} does not quite fit into the cluster and has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS}) family at the top right.
+With the exception of \emph{mergesat} and maybe \emph{DurianSat} we observe a high similarity within the cluster.
 
@@
 
-\todo{Summarize Winning Strategies}
-
-\todo{Ideas for Future Competitions}
+All winning solvers of the Main track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul runs to reconfigure weights in their branching heuristics.
+
+From the results in the Parallel track, we can learn that it is still hard to scale from $32$ to $64$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart.
+However, from the winner in the massively parallel Cloud track, we could learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated architecture.
+
+\todo{Should we have a discussion (maybe in later sections)
+about the future of the portfolio solver rule
+concerning the point raised by Mate Soos (in emails)?}
 

### 2021-01-25 paper/main.tex
fixed minor details

@@
 For a complete list of the encoded planning tasks we refer to the
-generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/SAT2020_planning_generator.tar.xz}} 
+generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}} 
 The benchmarks of the planning track adhere to the following naming convention:
@@
 Interestingly, we now have both variants $\{ \solver{Kissat-sat}, \solver{Kissat-unsat} \} \subset T_6$, and moreover it holds that $T_6 \subset T_7$.
-All solvers in $T_1, \dots, T_7$ belong the top performing solvers in the Main track, with the only exception being $\solver{Scavel01} \in T_6 \cap T_7$ (cf. Table~\ref{tab:results}).
+All solvers in $T_{k \leq 7}$ belong the top performing solvers which received an award in the Main track, with the only exception being $\solver{Scavel01} \in T_4 \cap T_5$ (cf.~Table~\ref{tab:results}).
 
@@
 
-Contributions to the VBS can be well capatured by clustering the instance space into instance families. 
-We evaluated the runtimes of the three winning solvers of the Main track on the all families represented by at least $14$ instances (cf.
-Table~\ref{tab:families}) and report on their place and score in Table~\ref{tab:eval-by-family}.
-
-Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on a few instance families by a large margin, namely \emph{Anti-Bandwidth}, \emph{Vlsat}, \emph{Hypertree Decomposition}, \emph{Influence Maximization} and \emph{Tournament}.
-
-\begin{table}
+\begin{table}[b]
 \small
@@
 Timetable 				& 41 & 7889.0 & 21 & 5103.8 & \bf 19 & 5092.4\\
-Tournament 				& 20 & 10000.0&  \bf 2 & 8715.0 &  9 & 10000.0\\
+Tournament 				& 4 & 10000.0&  \bf 2 & 8715.0 &  4 & 10000.0\\
 Vlsat 					& 27 & 7149.7 &  5 & 5307.5 &  \bf 1 & 5026.4\\
@@
 \end{table}
+
+Contributions to the VBS can be well capatured by clustering the instance space into instance families. 
+We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.
+Table~\ref{tab:families}) and report on their place and score in Table~\ref{tab:eval-by-family}.
+Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.
 

### 2021-01-25 paper/main.tex
conclusion

@@
 
-All winning solvers of the Main track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul runs to reconfigure weights in their branching heuristics.
-
-From the results in the Parallel track, we can learn that it is still hard to scale from $32$ to $64$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart.
-However, from the winner in the massively parallel Cloud track, we could learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated architecture.
-
-\todo{Should we have a discussion (maybe in later sections)
-about the future of the portfolio solver rule
-concerning the point raised by Mate Soos (in emails)?}
+All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul SLS runs to reconfigure weights in their branching heuristics.
+
+As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart.
+However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture.
+
+It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
+The winner of the \emph{Incremental Library} track showed that it is worth integrating full solver functionality in the incremental use-case.
+
+\subsection*{Future Competitions}
+
+The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolio and to stimulate development of new code-bases.
+This rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.
+
+Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
+The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
 

### 2021-01-25 paper/main.tex
more conclusion

@@
 
-The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolio and to stimulate development of new code-bases.
-This rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.
+The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolios and to stimulate development of new code-bases. 
+The rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.
+Therefore, the \emph{Portfolio rule} will receive some refinement in future competitions.
 
 Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
+Those incremental use-cases impose additional challenges on solver authors. 
 The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
+
+The results of the \emph{Planning} track as well as our differentiated analysis of results highlight the individual contributions of many submissions. 
+Our plan for future competitions is, to always run a special track for varying applications alongside the Main track.
 

### 2021-01-26 paper/main.tex
fix tabel reference

@@
 that transforms the world from some initial state to a goal state. In 1992 Kautz
-and Selman
-\cite{Kautz1992} proposed to encode planning as satisfiability. In their
-encoding the problem of finding a plan of length $i$ (\textit{i.e.,} the
+and Selman \cite{Kautz1992} proposed to encode planning as satisfiability. In
+their encoding the problem of finding a plan of length $i$ (\textit{i.e.,} the
 \emph{makespan}) is translated into a Boolean formula $F_i$ that is satisfiable
-exactly if a plan of length $i$ \emph{or less} exists. In later encodings
-multiple actions can be executed \emph{in parallel} allowing longer plans to be
-found by solving smaller formulas \cite{Rintanen2006, Rintanen2007, Balyo2013}.
+if a plan of length $i$ \emph{or less} exists. In later encodings multiple
+actions can be executed \emph{in parallel} allowing longer plans to be found by
+solving smaller formulas \cite{Rintanen2006, Rintanen2007, Balyo2013}.
 
@@
 encoding. The hardest formulas that a SAT-based planner has to solve are usually
-the last unsatisfiable $F_i$ before the next higher makespan becomes satisfiable
+the last unsatisfiable $F_i$ before the next higher makespan $i$ is satisfiable
 \cite{Rintanen2006}. Therefore we preferably pick the last unsatisfiable
@@
 
+% - 86 out of 100 biggest (number of clauses) are planning
+% - 109 / 200 in the planning track are not solved by any solver
+% - 186 / 600 in total
+% - all 200 above 90\% binary clauses and half have above 99%
+The instances of the Planning track are big compared to the main track
+instances. Using the number of clauses as a metric; out of the $100$ biggest
+instances of both tracks
+% of the main-track
+$86$ belong to the Planning track. The large size can mainly be attributed to
+binary clauses. On average, more than $98$\% of the clauses are binary for
+planning instances. The average for the Main track instances is below $60$\%.
+
 \begin{table}[t]
@@
   \rangle\text{.cnf}}$
-
-% - 86 out of 100 biggest (number of clauses) are planning
-% - 109 / 200 in the planning track are not solved by any solver
-    % - 186 / 600 in total
-% - all 200 above 90\% binary clauses and half have above 99%
-The instances of the Planning track are big compared to the rest of the
-main track. Using the number of clauses as a metric; out of the $100$ biggest
-instances
-% of the main-track
-$86$ belong to the Planning track. The large size can mainly be attributed to
-binary clauses. On average, more than $98$\% of the clauses are binary for
-planning instances, where the average for the rest of the instances from the
-Main track is below $60$\%.
-
-Despite the large size, only a few instances directly caused memory problems for
-more than just a few solvers. In most cases the \SI{128}{\giga\byte} of RAM
-available were sufficient.
-% The saving grace might have been
-% This can be attributed to
-% the \SI{128}{\giga\byte} of RAM available to each solver.
-However, the three biggest instances from the \emph{childsnack} family of
-planning problems encoded with the \emph{hierarchical} planner \emph{Tree-REX}
-caused over half of the solvers to abort with some error message related to
-memory. Other solvers were still able to solve the same instances within $300$
-seconds.
 
@@
 A greedy set cover of the solved instances by solvers of the Main track is presented in Table~\ref{tab:gscMain}. 
-In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:mainALL}.
+In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
 Given those 264 instances as already covered, \solver{CaDiCaL-alluip} was the best in further contributing to the set by additional $22$ instances in iteration $2$.
@@
 define a similarity metric based on the measured runtimes. For that we first
-remove $186$ benchmarks from the collected data that have not been solved by any
-solver. For the rest of the benchmarks we use the PAR-2 score,
+remove $84$ benchmarks that have not been solved by any solver. For the rest of
+the benchmarks we use the PAR-2 score,
 % based on the \num{5000}-second timeout
 i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
-This leaves us with $414$ floats
-$S_{1},\dots,S_{n}$ for each solver $S$. The similarity for two solvers $A$
+This leaves us with $316$ floats
+$S_{1},\dots,S_{n}$ for each solver $S$. The \emph{similarity} of two solvers $A$
 and $B$, normalized to the interval $[0,1]$ is defined
-% as:
-by Equation~\ref{eq-similarity}.
-
-\begin{equation}
-\label{eq-similarity}
-	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{414 \cdot 10000}
-\end{equation}
+as:
+% by Equation~\ref{eq-similarity}.
+
+% \begin{equation}
+% \label{eq-similarity}
+\[
+	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{316 \cdot \num{10000}}
+\]
+% \end{equation}
 We calculated the \emph{similarity} between the $30$ solvers which achieved the
@@
 illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
-are joined reflects how similar they are. For example
-enabling the \emph{trail saving} in \emph{CaDiCaL-alluip} has no impact on the
-runtime, resulting in a similarity above \num{0.999}. Thus the two solvers are joined very low in the dendrogram.
-% A similar visualization was used in the SAT Challenge 2012 \todo{cite}. They used
-
-One big cluster we can identify are the \emph{Maple} decedents in the lower left
-corner, all of which are modifications of the winners of the SAT Competition
-2018 and the SAT Race 2019. 
-%The solver \emph{mergesat} does not quite fit into the cluster and has a comparatively high similarity to the \emph{CryptoMiniSat} (\emph{CMS}) family at the top right.
-With the exception of \emph{mergesat} and maybe \emph{DurianSat} we observe a high similarity within the cluster.
-
-The three \emph{Relaxed} solvers by \emph{Zhang} and \emph{Cai} are using the
-same code base as a lot of the solvers in the Maple-Cluster but their overall
-performance is better and closer to the CMS-Cluster.
-
-The CMS versions differ in their implementation of stochastic local search (SLS)
-but overall have a similar performance.
-
-The last big cluster in the center of the heat map is comprised of the solvers
-originally written by Biere. The three configurations of \emph{Kissat} form a
+are joined reflects how similar they are. For example enabling the \emph{trail
+  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
+a similarity above \num{0.999}. Thus the two solvers are joined low in the
+dendrogram.
+A similar visualization was used to visualize the results of the SAT Race \cite{Balyo:2015:SATRace}.
+
+One big cluster we can identify are the \solver{Maple}-decedents to the right,
+all of which are modifications of the winners of the SAT Competition 2018 and
+the SAT Race 2019.
+With the exception of \solver{mergesat} and
+maybe \solver{DurianSat} we observe a high similarity within the cluster.
+% * 0.9645726159423101, 'exp_V_MLD_CBT_DL', 'Scavel' second highest similarity of all (not 2 configurations of the same solver)
+% ** both based on MapleLCMDistChronoBT-dl-v2.2
+% ** suggesting that the changes they made are either very similar or both do not have a high impact on the performance of the base solver in this test set.
+
+% The two configurations of the \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
+use the same code base as a lot of the solvers in the Maple-Cluster but their
+overall performance is better and closer to the CMS-Cluster.
+
+The three CMS versions differ in their implementation of stochastic local search
+(SLS) but overall have a similar performance.
+
+The last cluster to the left of the heat map is comprised of the solvers
+originally written by Biere. The three configurations of \solver{Kissat} form a
 sub-cluster, even though the configurations are fairly distinct from each other.
@@
 
-The other sub-cluster consists of
-modifications to the 2019 version of \emph{\mbox{CaDiCaL}}. The new version
-CaDiCaL-2020 has a worse overall performance than
-% has an overall worse per
-% is lacking behind
-the other solvers in this cluster.
+The other sub-cluster consists of modifications to the 2019 version of
+\solver{CaDiCaL}. The new version CaDiCaL-2020 has a worse overall performance
+than the solvers in this cluster and a comparatively high similarty to the
+Maple-Cluster.
 
@@
     \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
-      % Similarity is defined as
-      % one minus the average taxicab distance normalized to the interval [0,1].
-      % Spearman's rank correlation coefficient.
       Darker regions mean that the solvers are more similar.
@@
 
-% To estimate the similarity between the performance of the solvers of the Main
-% Track we define a similarity metric $s$.
-% identify each solver with a point in the 600-dimensional real vector
-% space. Each component describes the PAR-2 runtime on one instance. We map the
-% taxicab distance to the $[0, 1]$ interval and then to determine how similar two
-% solvers are.
-
-\subsection{Sampling}
+% \subsection{Solver Ranking Robustness}
+\subsection{Influence of Benchmark Selection on Solver Ranking}
+The main result of the competition is the ranking of the solvers participating
+in the main track, according to their average PAR-2 score. To evaluate the impact
+of benchmark selection on the solver ranking, we follow the experiments
+described in the tool suite
+\texttt{benchfeature}\cite{benchfeature}.
+% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
+% by Fazekas, Kaufmann and Biere.
+% performed the following
+% experiment:
+
+We use random sampling to select a subset of benchmarks used in the Main track.
+We start with $316$ benchmarks that have been solved by at least one solver in
+the Main track and remove a number of benchmarks randomly.
+
+The solvers are assigned a new rank in ascending order of their PAR-2 score on
+each random sample. Note that we never encounter a tie. This ranking can be
+seen as an estimate of the original ranking.
+If even relatively small random samples result in a good estimate, we can draw a
+positive conclusion about the robustness of the ranking.
+% We draw a positive conclusion about the robustness of the original ranking, if
+% even the resulting estimate from relatively small random samples
+% are good approximations.
+To determine how similar the estimate is to the original ranking, we calculate
+the \emph{Spearman's rank correlation coefficient} of the two rankings. For each
+possible subset size (1--316) we generate 50 random samples.
+% and compute the correlation coefficient.
+
+Spearman's rank correlation coefficient
+for two rankings $r_{1}$ and $r_{2}$
+is defined by the following equation:
+% \begin{equation}
+% \label{eq-spearman}
+\[
+    \rho = 1 - \frac{6\cdot\sum_{s}{(r_{1}(s) - r_{2}(s))^2}}{n(n^2-1)},
+\]
+% \end{equation}
+where $n$ is the number of solvers in the Main track ($48$), and the rankings
+$r_{\{1,2\}}(s)$ map a solver $s$ to its rank, \emph{i.e.,} $1$ for the best
+performing solver, whereas $48$ is assigned to the solver
+with the highest average PAR-2 score.
+
+The coefficient $\rho$ is in the interval $[-1, 1]$, where a rank correlation of
+$1$ means that the two rankings are equal and $-1$ means that one ranking is the
+reverse of the other. To give a better intuition for $\rho$, we list a few
+modifications to the original ranking together with the resulting rank
+correlation coefficient: The smallest change we can make is to switch the rank
+of two adjacent solvers, resulting in a high rank correlation $\rho = 0.9999$.
+Several small changes also result in a high rank correlation; repeating the same
+modification as before $n/2$ times to switch every two adjacent solvers in rank
+still gives a value of $\rho = 0.9974$. On the other hand, switching the highest
+ranked solver (\solver{Kissat-sat}) with the lowest ranked solver, results in a
+rank correlation of $\rho = 0.7602$. Moving \solver{Kissat-sat} to the bottom of
+the ranking and moving every other solver up one rank gives a higher
+$\rho = 0.8776$. Doing the same to all three \solver{Kissat} configurations
+(with ranks 1, 2 and 11, now 46, 47 and 48) results in $\rho = 0.6839$.
+
+The mean and standard deviation of the computed correlation coefficients are
+depicted in Figure~\ref{fig:sampleAll}.
+
+\begin{figure}[h]
+  \label{fig:sampleAll}
   \includegraphics[width=\textwidth]{stability/ALL_random_smpling_correlations.png}
+  \caption{Mean and standard deviation of rank correlation under removal of random instances, 50 samples for each size}
+\end{figure}
+
+The rank correlation is high even for relatively small samples.
+The average rank correlation drops below $0.99$ only after randomly removing at least $95$ benchmarks, which is $30\%$ of the considered benchmark set.
+Accordingly, removing fewer benchmarks randomly has almost no effect on the ranking of the solvers.
+Furthermore, removing fewer than $200$ ($63\%$) benchmarks, results in an average rank correlation above $0.96$
+
+This suggest that the influence of the random selection in Algorithm~\ref{algo:select} on the solver ranking is limited.
+% \ref{sec:byob}
+
+The collected data cannot show, whether all of the benchmarks originally
+submitted by the solver authors, have a systematic bias. Since each newly
+submitted benchmark family originates from a different domain and is often the
+result of current research, we can assume that the submitted families together
+are representative. Figure~\ref{fig:sampleFamily} shows the rank correlation
+coefficient resulting from removing a complete benchmark family instead of a
+random subset. As expected removing a non random subset can have a higher impact
+on the ranking even if it is small. Removing the 13 benchmarks from the
+\emph{hgen}-family results in a (still high) rank correlation of $0.9895$. Additionally, the ranking of the top five solvers stays the same.
+
+\begin{figure}[h]
+  \label{fig:sampleFamily}
   \includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
+  \caption{Change of rank correlation under removal of individual benchmark families}
+\end{figure}
 

### 2021-01-27 paper/main.tex
track description

@@
 
-\todo{MH?}
+The Parallel track evaluates solver performance in wallclock time on multiple cores.
+The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
+Each solver run in this track was on a m4.16xlarge machine from Amazon Web Services.
+These machines have 64 virtual cores and 256GB of memory. In contrast to the 
+Main track, there is no proof logging for unsatisfiable benchmarks in the Parallel track.
 
@@
 
-\todo{MH?}
+New this year was the Cloud track to evaluated distributed solvers. Similar to the
+Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
+type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
+Communication between the machines is possible using MPI and SSH.
+The wallclock timeout is 1000 seconds and the same benchmarks were used as in
+the Main and Parallel track.
 
@@
 This leaves us with $316$ floats
-$S_{1},\dots,S_{n}$ for each solver $S$. The \emph{similarity} of two solvers $A$
-and $B$, normalized to the interval $[0,1]$ is defined
+$S_{1},\dots,S_{n}$ for each solver $S$. The \emph{similarity} of two solvers $S$
+and $S'$, normalized to the interval $[0,1]$ is defined
 as:
@@
 \[
-	similarity(A, B) =\quad 1 - \frac{\sum{|A_{i} - B_{i}|}}{316 \cdot \num{10000}}
+	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
 \]
@@
 a similarity above \num{0.999}. Thus the two solvers are joined low in the
-dendrogram.
-A similar visualization was used to visualize the results of the SAT Race \cite{Balyo:2015:SATRace}.
+dendrogram. A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.
 
@@
 the SAT Race 2019.
-With the exception of \solver{mergesat} and
-maybe \solver{DurianSat} we observe a high similarity within the cluster.
-% * 0.9645726159423101, 'exp_V_MLD_CBT_DL', 'Scavel' second highest similarity of all (not 2 configurations of the same solver)
-% ** both based on MapleLCMDistChronoBT-dl-v2.2
-% ** suggesting that the changes they made are either very similar or both do not have a high impact on the performance of the base solver in this test set.
-
-% The two configurations of the \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
+The similarity within the cluster is high, with the exception of
+\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
+They form a subcluster
+with a lower similarity to the rest, but a high similarity within. In fact the highest measured similarity,
+ % of $0.96$
+besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
+The two solvers are both based on
+\solver{MapleLCMDistChronoBT-dl-v2.2} but have different authors.
+The high similarity suggest that the
+changes they made either result in very similar behavior or do not have a
+significant impact on the runtime performance.
+
+The two configurations of the \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
 use the same code base as a lot of the solvers in the Maple-Cluster but their
@@
 
-The three CMS versions differ in their implementation of stochastic local search
-(SLS) but overall have a similar performance.
-
-The last cluster to the left of the heat map is comprised of the solvers
-originally written by Biere. The three configurations of \solver{Kissat} form a
-sub-cluster, even though the configurations are fairly distinct from each other.
-% , specialized for satisfiable and unsatisfiable instances.
-% One targets satisfiable instances, while the other is focused on unsatisfiable
-% instances and a third alternating between them.
-
-The other sub-cluster consists of modifications to the 2019 version of
-\solver{CaDiCaL}. The new version CaDiCaL-2020 has a worse overall performance
-than the solvers in this cluster and a comparatively high similarty to the
-Maple-Cluster.
+Close to them are the three \solver{CMS} versions. They differ in their implementation of stochastic local search
+(SLS) and have similar performance.
+The 2020 version of \solver{CaDiCaL}
+performed worse than the modifications based on the 2019 version and
+does not quite fit into any cluster.
+
+The last cluster to the left of the heat map is comprised of the other solvers
+originally written by \emph{Biere}. Interesting to note is that the
+\solver{Kissat} configuration specialized for unsatisfiable instances joins the
+others in the cluster high in the dendrogram. In fact \solver{Kissat-unsat} has
+the lowest average similarity to all other solvers in the top 30. This hints at
+its importance for the use in an optimal portfolio.
+% Average similarity
+% | Kissat-unsat         |  21.75012381941168 |
+% | Kissat               | 22.591060319234913 |
+% | CaDiCaL-alluip       |  22.93588211785061 |
+% | CaDiCaL-alluip-trail |  22.93631201417939 |
+% | Kissat-sat           |  22.99738644487821 |
+
+% The other sub-cluster consists of modifications to the 2019 version of
+% \solver{CaDiCaL}.
+% The new version CaDiCaL-2020 has a worse overall performance
+% than the solvers in this cluster and a comparatively high similarty to the
+% Maple-Cluster.
 
@@
 Several small changes also result in a high rank correlation; repeating the same
-modification as before $n/2$ times to switch every two adjacent solvers in rank
-still gives a value of $\rho = 0.9974$. On the other hand, switching the highest
-ranked solver (\solver{Kissat-sat}) with the lowest ranked solver, results in a
-rank correlation of $\rho = 0.7602$. Moving \solver{Kissat-sat} to the bottom of
-the ranking and moving every other solver up one rank gives a higher
-$\rho = 0.8776$. Doing the same to all three \solver{Kissat} configurations
-(with ranks 1, 2 and 11, now 46, 47 and 48) results in $\rho = 0.6839$.
+modification as before $n/2$ times to switch all pairs of adjacent solvers in
+rank still gives a value of $\rho = 0.9974$. On the other hand, switching the
+highest ranked solver (\solver{Kissat-sat}) with the lowest ranked solver,
+results in a rank correlation of $\rho = 0.7602$. Moving \solver{Kissat-sat} to
+the bottom of the ranking and moving every other solver up one rank gives a
+higher $\rho = 0.8776$. Doing the same to all three \solver{Kissat}
+configurations (with ranks 1, 2 and 11, now 46, 47 and 48) results in
+$\rho = 0.6839$.
 
@@
 depicted in Figure~\ref{fig:sampleAll}.
-
 \begin{figure}[h]
@@
 \end{figure}
-
 The rank correlation is high even for relatively small samples.
@@
 Accordingly, removing fewer benchmarks randomly has almost no effect on the ranking of the solvers.
-Furthermore, removing fewer than $200$ ($63\%$) benchmarks, results in an average rank correlation above $0.96$
+Furthermore, removing fewer than $200$ ($63\%$) benchmarks, still results in an average rank correlation above $0.96$
 
@@
 % \ref{sec:byob}
-
 The collected data cannot show, whether all of the benchmarks originally
-submitted by the solver authors, have a systematic bias. Since each newly
-submitted benchmark family originates from a different domain and is often the
-result of current research, we can assume that the submitted families together
-are representative. Figure~\ref{fig:sampleFamily} shows the rank correlation
-coefficient resulting from removing a complete benchmark family instead of a
-random subset. As expected removing a non random subset can have a higher impact
-on the ranking even if it is small. Removing the 13 benchmarks from the
-\emph{hgen}-family results in a (still high) rank correlation of $0.9895$. Additionally, the ranking of the top five solvers stays the same.
+submitted by the solver authors, have a systematic bias. However since each
+newly submitted benchmark family originates from a different domain and is often
+the result of current research, we can assume that the submitted families
+together are representative.
 
@@
 
+Figure~\ref{fig:sampleFamily} shows the rank
+correlation coefficient resulting from removing a complete benchmark family
+instead of a random subset. As expected removing a non random subset can have a
+higher impact on the ranking even if it is small. Removing the 13 benchmarks
+from the \emph{hgen}-family results in a (still high) rank correlation of
+$0.9895$. Additionally, the ranking of the top five solvers stays the same.
+The individual removal of all other benchmarks families results in a rank correlation over $0.99$.
+
 \section{Conclusion and Prospects}

### 2021-01-27 paper/main.tex
parallel & cloud

@@
 The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
-Each solver run in this track was on a m4.16xlarge machine from Amazon Web Services.
+Each solver run in this track was on a m4.16xlarge machine from Amazon Web Services (AWS).
 These machines have 64 virtual cores and 256GB of memory. In contrast to the 
@@
 
-In all tracks it was required to output a model to certify recognising a satisfiable instance.
+In all tracks it was required to output a model to certify recognizing a satisfiable instance.
 On the other hand, certificates for unsatisfiable instances (proofs) were required only 
 in the Main track (besides the No Limits track).
-In some cases solvers output the correct result but the repective certificate was wrong. 
+In some cases solvers output the correct result but the respective certificate was wrong. 
 Such solvers were demoted to the No-limits track of the competition.
@@
 
-\todo{Parallel / Cloud}
+As noted above, the Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
+of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
+memory. These tracks used wallclock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/parallel-ALL.pdf}
+\caption{Performance of the solvers in the Parallel track.}
+\end{figure}
+
 \subsubsection{Painless MapleCOMSPS STR}
@@
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/cloud-ALL.pdf}
+\caption{Performance of the solvers in the Cloud track.}
+\end{figure}
 

### 2021-01-28 paper/stability/benchfeatures/family_and_SAT_random_sampling_plots.py
updated plots

@@ -194,54 +194,83 @@ def multiple_samples_num(data, runs, target, sc, solv):
    return corr
 
 def fam_leave_one_out(data, target, sc, solv):
-   selected = []
-   init = ranking_mat(target, solv)
-   rankm = np.array([init])
-   plot_d = np.array([sc])
-   corr = []
-   name = []
+    selected = []
+    init = ranking_mat(target, solv)
+    rankm = np.array([init])
+    plot_d = np.array([sc])
+    corr = []
+    name = []
+    trans = {
+        "stedman-triples": "stedman-triples",
+        "cnf-miter": "cnf-miter",
+        "lam-discrete-geometry": "lam-discrete-geom.",
+        "discrete-logarithm": "discrete-logarithm",
+        "station-repacking": "station-repacking",
+        "antibandwidth": "antibandwidth",
+        "fermat": "fermat",
+        "hgen": "hgen",
+        "core-based-generator": "core-based-gen.",
+        "vlsat": "vlsat",
+        "baseball-lineup": "baseball-lineup",
+        "schur-coloring": "schur-coloring",
+        "cellular-automata": "cellular-automata",
+        "bitvector": "bitvector",
+        "cryptography": "cryptography",
+        "edge-matching": "edge-matching",
+        "cover": "cover",
+        "ssp-0": "ssp-0",
+        "hypertree-decomposition": "hypertree-decomp.",
+        "coloring": "coloring",
+        "polynomial-multiplication": "polynomial-multiply.",
+        "tensors": "tensors",
+        "termination": "termination",
+        "tournament": "tournament",
+        "influence-maximization": "influence-max.",
+        "01-integer-programming": "01-integer-prog.",
+        "timetable": "timetable",
+    }
+    for i in set(fam["family_name"]):
 
-   for i in set(fam['family_name']):
+        subset = fam.loc[fam["family_name"] == i]
 
-       subset = fam.loc[fam['family_name'] == i]
+        subset = subset.replace("\n", "", regex=True)
+        bench = subset["benchmark_name"].str.strip()
+        bench = list("sat/" + bench)
+        X_new = data.drop(bench, 1)
 
-       subset = subset.replace('\n','', regex=True)
-       bench = subset['benchmark_name'].str.strip()
[…]

### 2021-01-28 paper/stability/benchfeatures/random_sampling_plots.py

@@ -90,11 +90,13 @@ def random_sampling_plot(data_frame,original_ranks,original_instances,solver_nam
 
     plt.figure()
     fig = plt.figure()
-    fig.set_size_inches(9.6, 6.8)
-    plt.title(title,fontsize=18)
+    # fig.set_size_inches(9.6, 6.8)
+    # plt.title(title,fontsize=18)
     plt.yticks(np.arange(0.,1.09,0.1))
-    plt.ylabel('Spearman\'s correlation',fontsize=16)
-    plt.xlabel('Number of randomly removed instances',fontsize=16)
+    # plt.ylabel('Spearman\'s correlation',fontsize=16)
+    # plt.xlabel('Number of randomly removed instances',fontsize=16)
+    plt.ylabel('Spearman\'s correlation')
+    plt.xlabel('Number of randomly removed instances')
     plt.errorbar(number_of_removed, correlation_mean, correlation_std, linestyle='None', marker='^',elinewidth=1)
     plt.hlines([0.8,0.99,0.6,0.4,0.2],0,max(number_of_removed)+5,linestyle='dashed',color='m')
     plt.grid(True)
@@ -143,7 +145,7 @@ print('Found %d SAT and %d UNSAT problems from %d problems.' % (len(sat_original
 
 title = 'Mean and standard deviation of\n ranking correlations at random problem instance removals\n(repeated 50x each simple random sampling)'
 random_sampling_plot(data,original_rank,original_instances,solver_names,title,'plots/ALL_random_smpling_correlations.png')
-title = 'Mean and standard deviation of ranking correlations\n at random problem instance removals considering only SAT instances\n(repeated 50x each simple random sampling)'
-random_sampling_plot(sat_data,sat_original_rank,sat_original_instances,solver_names,title,'plots/SAT_randomSampling_correlations.png')
-title = 'Mean and standard deviation of ranking correlations\n at random problem instance removals considering only UNSAT instances\n(repeated 50x each simple random sampling)'
-random_sampling_plot(unsat_data,unsat_original_rank,unsat_original_instances,solver_names,title,'plots/UNSAT_randomSampling_correlations.png')
+# title = 'Mean and standard deviation of ranking correlations\n at random problem instance removals considering only SAT instances\n(repeated 50x each simple random sampling)'
+# random_sampling_plot(sat_data,sat_original_rank,sat_original_instances,solver_names,title,'plots/SAT_randomSampling_correlations.png')
[…]

### 2021-01-28 paper/main.tex
updated plots
resized my figures

@@
 \subsection{Similarity of Solvers}
-To investigate how similar the solvers of the Main track are to each other, we
-define a similarity metric based on the measured runtimes. For that we first
-remove $84$ benchmarks that have not been solved by any solver. For the rest of
-the benchmarks we use the PAR-2 score,
+To investigate the similarity of solvers from the Main track, we define a
+similarity metric based on measured runtimes. We start by removing $84$
+benchmarks that have not been solved by any solver. For the rest, a PAR-2 score
+is assigned to each instance for every solver,
 % based on the \num{5000}-second timeout
-i.\,e., for each solver we set a score of \num{10000} for unsolved instances.
-This leaves us with $316$ floats
-$S_{1},\dots,S_{n}$ for each solver $S$. The \emph{similarity} of two solvers $S$
+\emph{i.e.}, we set a score of \num{10000} for unsolved instances.
+Each solver $S$ thus is associated with the PAR-2 scores $S_{1},\dots,S_{316}$.
+% This leaves us with $316$ floats
+% $S_{1},\dots,S_{316}$ for each solver $S$.
+The \emph{similarity} of two solvers $S$
 and $S'$, normalized to the interval $[0,1]$ is defined
@@
 % \end{equation}
-We calculated the \emph{similarity} between the $30$ solvers which achieved the
-best PAR-2 score in the main track. The results are displayed in
-Figure~\ref{fig-similarity-main} as a \emph{heat map}. Additionally the result
+We calculated the \emph{similarity} of the $30$ solvers with the
+best average PAR-2 score in the main track. The results are displayed in
+Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRACE}. Additionally, the result
 of hierarchically clustering the solvers based on their similarity is
 illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
-are joined reflects how similar they are. For example enabling the \emph{trail
+are joined reflects how similar they are. For example, enabling the \emph{trail
   saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
-a similarity above \num{0.999}. Thus the two solvers are joined low in the
-dendrogram. A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.
-
-One big cluster we can identify are the \solver{Maple}-decedents to the right,
-all of which are modifications of the winners of the SAT Competition 2018 and
+a similarity above \num{0.999}. Therefore the two solvers are joined low in the
+dendrogram.
+% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.
+
+One big cluster that we identify consists of the \solver{Maple}-decedents,
+all of which are modifications of the winners in the SAT Competition 2018 and
 the SAT Race 2019.
@@
 They form a subcluster
-with a lower similarity to the rest, but a high similarity within. In fact the highest measured similarity,
+with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
  % of $0.96$
@@
 The high similarity suggest that the
-changes they made either result in very similar behavior or do not have a
+changes they made either result in a very similar behavior or do not have a
 significant impact on the runtime performance.
 
-The two configurations of the \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
-use the same code base as a lot of the solvers in the Maple-Cluster but their
-overall performance is better and closer to the CMS-Cluster.
-
-Close to them are the three \solver{CMS} versions. They differ in their implementation of stochastic local search
+The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
+use the same codebase as a lot of solvers in the Maple-Cluster but their
+overall performance is better and closer to the \solver{CMS}-Cluster.
+The three \solver{CMS} configurations
+differ in their implementation of stochastic local search
 (SLS) and have similar performance.
@@
 others in the cluster high in the dendrogram. In fact \solver{Kissat-unsat} has
-the lowest average similarity to all other solvers in the top 30. This hints at
-its importance for the use in an optimal portfolio.
+the lowest average similarity to all other solvers in the top 30.
+This suggests its importance for an optimal
+portfolio.
 % Average similarity
@@
     \centering
-    \includegraphics[width=\linewidth]{similarity/cross.pdf}
+    \includegraphics[width=\textwidth]{similarity/cross.pdf}
     \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
@@
 
-We use random sampling to select a subset of benchmarks used in the Main track.
+We first use random sampling to select subsets of benchmarks used in the Main track.
 We start with $316$ benchmarks that have been solved by at least one solver in
-the Main track and remove a number of benchmarks randomly.
+the Main track and remove a number of benchmarks randomly. For each
+possible subset size (1--316) we generate 50 random samples.
 
@@
 seen as an estimate of the original ranking.
-If even relatively small random samples result in a good estimate, we can draw a
+If even relatively small random samples result in a good estimate, we draw a
 positive conclusion about the robustness of the ranking.
@@
 % are good approximations.
-To determine how similar the estimate is to the original ranking, we calculate
-the \emph{Spearman's rank correlation coefficient} of the two rankings. For each
-possible subset size (1--316) we generate 50 random samples.
+To determine how similar an estimate is to the original ranking, we calculate
+the \emph{Spearman's rank correlation coefficient} of the two rankings.
 % and compute the correlation coefficient.
@@
 \[
-    \rho = 1 - \frac{6\cdot\sum_{s}{(r_{1}(s) - r_{2}(s))^2}}{n(n^2-1)},
+    \rho = 1 - \frac{6\cdot\sum_{S}{(r_{1}(S) - r_{2}(S))^2}}{n(n^2-1)},
 \]
@@
 where $n$ is the number of solvers in the Main track ($48$), and the rankings
-$r_{\{1,2\}}(s)$ map a solver $s$ to its rank, \emph{i.e.,} $1$ for the best
+$r_{\{1,2\}}(S)$ map a solver $S$ to its rank, \emph{i.e.,} $1$ for the best
 performing solver, whereas $48$ is assigned to the solver
@@
 modifications to the original ranking together with the resulting rank
-correlation coefficient: The smallest change we can make is to switch the rank
+correlation coefficient. The smallest change we can make is to switch the rank
 of two adjacent solvers, resulting in a high rank correlation $\rho = 0.9999$.
@@
 rank still gives a value of $\rho = 0.9974$. On the other hand, switching the
-highest ranked solver (\solver{Kissat-sat}) with the lowest ranked solver,
+highest ranked solver (\solver{Kissat-sat}) with the lowest,
 results in a rank correlation of $\rho = 0.7602$. Moving \solver{Kissat-sat} to
-the bottom of the ranking and moving every other solver up one rank gives a
+the bottom of the ranking while moving every other solver up one rank gives a
 higher $\rho = 0.8776$. Doing the same to all three \solver{Kissat}
@@
   \label{fig:sampleAll}
-  \includegraphics[width=\textwidth]{stability/ALL_random_smpling_correlations.png}
-  \caption{Mean and standard deviation of rank correlation under removal of random instances, 50 samples for each size}
+  \centering
+  \includegraphics[width=0.8\textwidth]{stability/ALL_random_smpling_correlations.png}
+  \caption{Mean and standard deviation of rank correlation under removal of random instances over 50 samples for each size}
 \end{figure}
@@
 Accordingly, removing fewer benchmarks randomly has almost no effect on the ranking of the solvers.
-Furthermore, removing fewer than $200$ ($63\%$) benchmarks, still results in an average rank correlation above $0.96$
-
-This suggest that the influence of the random selection in Algorithm~\ref{algo:select} on the solver ranking is limited.
+Furthermore, removing fewer than $200$ ($63\%$) benchmarks, still results in an average rank correlation above $0.96$.
+
+This suggests that the impact of the random selection in Algorithm~\ref{algo:select} on the solver ranking is limited.
 % \ref{sec:byob}
-The collected data cannot show, whether all of the benchmarks originally
-submitted by the solver authors, have a systematic bias. However since each
+The collected data cannot show whether all of the benchmarks originally
+submitted by the solver authors have a systematic bias. However, since each
 newly submitted benchmark family originates from a different domain and is often
@@
   \label{fig:sampleFamily}
-  \includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}
+  \centering
+  \includegraphics[width=0.9\textwidth]{stability/fam_leave_one_out_corr.png}
   \caption{Change of rank correlation under removal of individual benchmark families}
@@
 correlation coefficient resulting from removing a complete benchmark family
-instead of a random subset. As expected removing a non random subset can have a
-higher impact on the ranking even if it is small. Removing the 13 benchmarks
+instead of a random subset. As expected, removing a non random subset can have a
+higher impact on the ranking even if it is small. Removing the $13$ benchmarks
 from the \emph{hgen}-family results in a (still high) rank correlation of
 $0.9895$. Additionally, the ranking of the top five solvers stays the same.
-The individual removal of all other benchmarks families results in a rank correlation over $0.99$.
+The individual removal of all other benchmarks families results in a rank correlation above $0.99$.
 

### 2021-01-28 paper/main.tex

@@
 best average PAR-2 score in the main track. The results are displayed in
-Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRACE}. Additionally, the result
+Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
 of hierarchically clustering the solvers based on their similarity is
@@
 Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.
+
 Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
@@
 
+Nils Froleyks is supported by the Austrian Science Fund (FWF) under projects
+W1255-N23, S11408-N23 and by the LIT AI Lab funded by the State of Upper
+Austria.
+
 \bibliographystyle{elsarticle-num}

### 2021-01-28 paper/main.tex
more on results

@@
 
+Some interesting results were observed in the 2020 SAT Competition.
+Four Main track solvers (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
+performed significantly better compared to the others, see Figure~\ref{main:all} and Table~\ref{tab:results}.
+These four top solvers all have a different code base, which is rare. In recent competitions, top solvers were much closer together.
+The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
+\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
+The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
+compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
+Since the SAT Competition started to rank based on PAR-2 score, such cases have been observed several times.
+
+The main reason for the separation between the top four solvers and the others is the enormous gap on satisfiable benchmarks, 
+see Figure~\ref{main:sat}. In recent years, several techniques have been added to SAT solvers to improve
+their performance on satisfiable instance. Examples of such techniques are the integration of a local search
+solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts,
+and variable-move-to-front). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by 
+\solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.
+
+The solver performances on unsatisfiable formulas was much closer,
+see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
+performed significantly better compared to all other participants. It is therefore not surprising
+that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver,
+which has been implemented in C, while most solvers are implemented in C++. Further 
+details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
+The solvers \solver{CaDiCaL-trial}
+and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.
+
 \begin{figure}
@@
 \caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
+\label{main:all}
 \end{figure}
@@
 \caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
+\label{main:sat}
 \end{figure}
@@
 \end{figure}
+\label{main:unsat}
 
@@
 \subsubsection{Kissat} 
+\label{sec:kissat}
 

### 2021-01-31 paper/main.tex
Section 4

@@
 The article is concluded with future prospects in Section~\ref{sec:conclusion}.
-\todo{Need to decide on final structure regardign the results overview and analysis}
+\todo{Need to decide on final structure regarding the results overview and analysis}
 
@@
 
-Some interesting results were observed in the 2020 SAT Competition.
-Four Main track solvers (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
-performed significantly better compared to the others, see Figure~\ref{main:all} and Table~\ref{tab:results}.
-These four top solvers all have a different code base, which is rare. In recent competitions, top solvers were much closer together.
+This section describes some high-level observations, including the winners, of the 2020 SAT Competition. 
+We focus on some interesting results. Details about the solvers, including the key and new solving techniques,
+are described in Section~\ref{sec:analysis}.
+
+Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
+performed significantly better compared to the others, see Table~\ref{tab:results}.
+Figure~\ref{main:all} shows the cumulative solved instances plot of the best performing solver of the strongest
+10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS).
+The four top solvers all have a different code base, which is rare and has not been observed in many years.
+Also, in recent competitions, the top solvers were much closer together.
 The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
@@
 compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
-Since the SAT Competition started to rank based on PAR-2 score, such cases have been observed several times.
+Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
+\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
+\label{main:all}
+\end{figure}
 
@@
 
-The solver performances on unsatisfiable formulas was much closer,
-see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
-performed significantly better compared to all other participants. It is therefore not surprising
-that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver,
-which has been implemented in C, while most solvers are implemented in C++. Further 
-details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
-The solvers \solver{CaDiCaL-trial}
-and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.
-
-\begin{figure}
-\centering
-\includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
-\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
-\label{main:all}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[ht]
 \centering
@@
 
-\begin{figure}
+The solver performances on unsatisfiable formulas was much closer,
+see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
+performed significantly better compared to all other participants. It is therefore not surprising
+that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
+details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
+The solvers \solver{CaDiCaL-trial}
+and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.
+
+\begin{figure}[ht]
 \centering
@@
 \label{main:unsat}
+
+The ranking in the Planning Track was closer. \solver{CaDiCaL-alliup-trial}, the winning solver, 
+solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. Their PAR-2 score is 
+quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but fast runtime
+on several instances resulted in a strong PAR-2 score. Notice that these solvers were also strong in the Main tracks. 
+Apparently none of the participating solvers was optimized for planning instances.
+
+The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the postfix denotes
+that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
+competitions that uses fewer threads than the number of virtual cores can be helpful as threads compete 
+for memory, which can reduce of the overall performance. The runner up is \solver{Plingeling}, while the
+third place is for \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
+all participating parallel solvers. Notice in Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR} solvers
+and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
+This shows that it is hard to beat sequential solvers with a parallel solver on the competition instances. 
+We will show later in the article (Table~\ref{tab:tuples}) that small sequential portfolios 
+perform better (in terms of PAR-2 score) than the parallel solvers.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=.9\textwidth]{img/parallel-ALL.pdf}
+\caption{Performance of the solvers in the Parallel track.}
+\label{fig:res-parallel}
+\end{figure}
+
+The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2},
+see Figure~\ref{fig:res-cloud}.
+\solver{Mallob-Mono} was able to solver more instances in 1000 seconds, compared to the 
+winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
+The other four participants performed significantly worse. This is likley due to the initial challenges
+to develop a distributed solver. This was the first year of this track. We expect that the gap will be 
+closer is future years.
+
+\begin{figure}
+\centering
+\includegraphics[width=.9\textwidth]{img/cloud-ALL.pdf}
+\caption{Performance of the solvers in the Cloud track.}
+\label{fig:res-cloud}
+\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.9\textwidth]{img/parallel-ALL.pdf}
-\caption{Performance of the solvers in the Parallel track.}
-\end{figure}
-
 \subsubsection{Painless MapleCOMSPS STR}
@@
 \end{table}
-
-\begin{figure}
-\centering
-\includegraphics[width=.9\textwidth]{img/cloud-ALL.pdf}
-\caption{Performance of the solvers in the Cloud track.}
-\end{figure}
 
@@
 \section*{Acknowledgements}
-Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.
-
-Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
-the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
+The authors thank StarExec for their support and resources to run the Main and the Planning tracks, and Amazon Web Services 
+for their support and resources to run the Parallel and Cloud tracks.
 
@@
 Austria.
+%
+Marijn Heule is supported by the National Science Foundation (NSF) under grant CCF-2010951. 
+%
+Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.
+%
+Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
+the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.
 

### 2021-02-01 paper/main.tex
aspell

@@
 participating solvers, benchmarks, and the empirical results from the competition.
-In terms of competition tracks, two new tracks, namely the cloud track and an application-specifc track, where introduced in 2020 
+In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020 
 in addition to the already earlier established main, parallel, and incremental tracks; we
@@
 In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
-on the SAT competition webpages (\url{https://satcompetition.github.io/2020/}). 
+on the SAT competition web pages (\url{https://satcompetition.github.io/2020/}). 
 Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.
@@
 of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
-was set to 1000 non-space character edit distance from the sources of Glucose provided by the organisers. 
+was set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
 Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
@@
 In the Incremental Library track we mimic scenarios
-where a SAT solver is used as a backend solver in a more complex tool
+where a SAT solver is used as a back-end solver in a more complex tool
 (typically solving a harder problem than SAT) and is called multiple times before 
-the enclosing tool reaches its final state. Incrementality means that
+the enclosing tool reaches its final state. Incremental means that
 the individual calls to the SAT solver are not independent, but may share 
@@
 
-The Parallel track evaluates solver performance in wallclock time on multiple cores.
+The Parallel track evaluates solver performance in wall-clock time on multiple cores.
 The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
@@
 Communication between the machines is possible using MPI and SSH.
-The wallclock timeout is 1000 seconds and the same benchmarks were used as in
+The wall-clock timeout is 1000 seconds and the same benchmarks were used as in
 the Main and Parallel track.
@@
 of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
-memory. These tracks used wallclock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.
+memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.
 
@@
 bounds\footnote{Bounds on plan length are available for some planning tasks from
-  the \emph{optimal track} that have \emph{unit cost} actions.} on the optimal
+  the \emph{Optimal track} that have \emph{unit cost} actions.} on the optimal
 plan length we can generate SAT formulas with predetermined satisfiability for
@@
 
-The classical planning benchmarks are selected from the \emph{satisficing} and
-\emph{optimal} tracks of the \emph{International Planning Competitions} 2014
+The classical planning benchmarks are selected from the \emph{satisfying} and
+\emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
 \footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
@@
 % - all 200 above 90\% binary clauses and half have above 99%
-The instances of the Planning track are big compared to the main track
+The instances of the Planning track are big compared to the Main track
 instances. Using the number of clauses as a metric; out of the $100$ biggest
@@
 generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}} 
-The benchmarks of the planning track adhere to the following naming convention:
+The benchmarks of the Planning track adhere to the following naming convention:
 ${\langle \texttt{SAT/UNSAT} \rangle\_\langle \texttt{encoding} \rangle\_\langle
@@
 
-The incremental library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017. 
-Benchmarks for the Incremental Library track constist of \emph{benchmark applications} which implement and use the incremental SAT solver in their backend as well as \emph{benchmark instances} which serve as input to these applications.
+The Incremental Library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
+Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications.
 For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
@@
 
-Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alliup-trial}, and \solver{CMS-ccnr-lsids}) 
+Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}) 
 performed significantly better compared to the others, see Table~\ref{tab:results}.
@@
 The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
-compared to \solver{CaDiCaL-alliup-trial}, but solved various formulas much more efficiently. 
+compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more efficiently. 
 Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.
@@
 
-The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the postfix denotes
+The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the post-fix denotes
 that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
@@
 winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
-The other four participants performed significantly worse. This is likley due to the initial challenges
+The other four participants performed significantly worse. This is likely due to the initial challenges
 to develop a distributed solver. This was the first year of this track. We expect that the gap will be 
@@
 In SAT Competition 2017, Luo et al.
-integrated learnt clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
+integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
 Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
@@
 by Biere is another independent, award winning and structured implementation of the state-of-the-art in SAT solving. 
-Its improved reimplementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.
+Its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.
 
@@
 
-\solver{Kissat} is a low-level reimplementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}.
+\solver{Kissat} is a low-level re-implementation of \solver{CaDiCaL} with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}.
 Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.
@@
 The \solver{F2TRC} fork of \solver{MapleLCMDistCBT} achieved the third best score on unsatisfiable instances. 
-\solver{F2TRC} comes with deterministic reimplementations of former winning strategies in \solver{Maple}, e.g., by replacing time-based intervals through conflict-based intervals~\cite{Kochemazov:SC2020}.
+\solver{F2TRC} comes with deterministic re-implementations of former winning strategies in \solver{Maple}, e.g., by replacing time-based intervals through conflict-based intervals~\cite{Kochemazov:SC2020}.
 
@@
 The \solver{32} threaded variant received two awards in this competition: the overall third place and third best score on unsatisfiable instances. 
-\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
+\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
 
@@
 \solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
-\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized intialization of branching heuristics~\cite{SC2020}.
+\solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized initialization of branching heuristics~\cite{SC2020}.
 
@@
 \solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
-\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
+\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priority. 
 This functionality is disabled in the submitted variant \solver{Mallob Mono}. 
@@
 
-Contributions to the VBS can be well capatured by clustering the instance space into instance families. 
+Contributions to the VBS can be well captured by clustering the instance space into instance families. 
 We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.
@@
 We calculated the \emph{similarity} of the $30$ solvers with the
-best average PAR-2 score in the main track. The results are displayed in
+best average PAR-2 score in the Main track. The results are displayed in
 Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
@@
 \solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
-They form a subcluster
+They form a sub-cluster
 with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
@@
 The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
-use the same codebase as a lot of solvers in the Maple-Cluster but their
+use the same code-base as a lot of solvers in the Maple-Cluster but their
 overall performance is better and closer to the \solver{CMS}-Cluster.
@@
     \includegraphics[width=\textwidth]{similarity/cross.pdf}
-    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the main track.
+    \caption{Heat-map and dendrogram (top) based on the runtime similarity of the solvers participating in the Main track.
       Darker regions mean that the solvers are more similar.
@@
 The main result of the competition is the ranking of the solvers participating
-in the main track, according to their average PAR-2 score. To evaluate the impact
+in the Main track, according to their average PAR-2 score. To evaluate the impact
 of benchmark selection on the solver ranking, we follow the experiments
@@
 
-All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul SLS runs to reconfigure weights in their branching heuristics.
-
-As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart.
+All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
+
+As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occasions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart.
 However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture.
@@
 
-Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
+Many prominent applications of SAT use an \emph{incremental} SAT solver in their back-end. 
 Those incremental use-cases impose additional challenges on solver authors. 
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 The authors thank StarExec for their support and resources to run the Main and the Planning tracks, and Amazon Web Services 

### 2021-02-02 paper/main.tex
removed redundant tables

@@
 additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
-As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning descendants of \solver{Maple}-based solver.
+As can be seen in Table~\ref{tab:solvers-main}, numerous submissions to SAT Competition~2020 are forks of some recently award winning descendants of \solver{Maple}-based solver.
 
@@
 
-\subsection{Sequential SAT Solving}
+\subsection{Sequential SAT Solvers}
 \label{sec:part:seq}
@@
 Sequential SAT solvers have been evaluated in the Main, Planning and Incremental Library track of SAT Competition~2020. 
-A total of $18$ teams submitted correct solvers to the Main track of the competition. 
+$18$ teams submitted a total of $48$ solvers and configurations to the Main track and the Planning track of the competition, and $4$ solvers participated the Incremental Library track. 
+%and were ranked by the number of application categories in which they won based on their PAR-2 score. 
+%Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
+%
 Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
-The recent genealogy of all submissions is highlighted by \emph{base solver} and \emph{variant} columns. 
-Underlined text is used to point out the important parts of the respective submissions name.
+In the following sections, we outline the technical reports of the award winning solvers.
 
@@
 \centering
-\begin{tabularx}{\linewidth}{Xllcccc}
-\bf Team & \bf Base Solver & \bf Variant / Name & \bf M & \bf U & \bf S & \bf P \\
+\begin{tabularx}{\linewidth}{Xllccccc}
+\bf Team & \bf Base Solver & \bf Variant Name & \bf M & \bf U & \bf S & \bf P & \bf I \\
 \hline
@@
 
-\multirow{3}{*}{Biere} & \multirow{3}{*}{\solbert{Kissat}} &  -- & 1 & 1 & -- & --\\
- &  &  \solver{sat} & 1 & 1 & 2 & --\\
- &  &  \solver{unsat} & -- & 1 & -- & 3\\
-\hline
- Biere, Fleury &  \solver{Cadical} & \solbert{SC2020} & -- & -- & -- & --\\
+\multirow{3}{*}{Biere} & \multirow{3}{*}{\solbert{Kissat}} &  -- & 1 & 1 & -- & -- & --\\
+ &  &  \solver{sat} & 1 & 1 & 2 & -- & --\\
+ &  &  \solver{unsat} & -- & 1 & -- & 3 & --\\
+\hline
+ Biere, Fleury &  \solver{Cadical} & \solbert{SC2020} & -- & -- & -- & -- & --\\
 \hline
@@
 \multirow{2}{*}{Zhang, Cai}
-    & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Relaxed} & -- & -- & -- & --\\
+    & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Relaxed} & -- & -- & -- & -- & --\\
 % &  & \solver{Rel. noTimeParam} & \\
- &  & \solver{Rel. newTech} & 2 & -- & 1 & --\\
+ &  & \solver{Rel. newTech} & 2 & -- & 1 & -- & --\\
 \hline
@@
 \multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
- &  \multirow{2}{*}{\solver{CryptoMiniSat-CCAnr}} &  -- & 3 & -- & 3 & 2\\
- &  &  \solver{lsids} & 3 & -- & 3 & 2\\
-\hline
-
-\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solver{CryptoMiniSat-WalkSAT} & -- & -- & -- & -- & --\\
+ &  \multirow{2}{*}{\solver{CryptoMiniSat-CCAnr}} &  -- & 3 & -- & 3 & 2 & 1 \\
+ &  &  \solver{lsids} & 3 & -- & 3 & 2 & --\\
+\hline
+
+\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solver{CryptoMiniSat-WalkSAT} & -- & -- & -- & -- & -- & --\\
 \hline
@@
 \multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
- &  &  \solver{trail} & -- & 2 & -- & --\\
- &  &  \solver{alluip} & -- & 2 & -- & 1\\
- & \multirow{-3}{*}{\solver{CaDiCaL}} &  \solbert{alluip-trail} & -- & 2 & -- & 1\\
- \cline{2-7}
- & \solver{MapleLCMDist} & \solver{alluip-trail} & -- & -- & -- & -- \\
-\hline
-
-\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solver{MapleLCMDistCBT}} & \solbert{f2trc} & -- & 3 & -- & --\\
- & & \solver{f2trc-s} & -- & 3 & -- & --\\
- \cline{2-7}
- & \solver{MapleLCMDistCBT-DL} & \solver{f2trc} & -- & 3 & -- & --\\
-\hline
-
-\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solbert{MapleLCMDistCBT-DL-v3} & -- & -- & -- & -- & -- \\
+ &  &  \solver{trail} & -- & 2 & -- & -- & --\\
+ &  &  \solver{alluip} & -- & 2 & -- & 1 & --\\
+ & \multirow{-3}{*}{\solver{CaDiCaL}} &  \solbert{alluip-trail} & -- & 2 & -- & 1 & --\\
+ \cline{2-8}
+ & \solver{MapleLCMDist} & \solver{alluip-trail} & -- & -- & -- & -- & -- \\
+\hline
+
+\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solver{MapleLCMDistCBT}} & \solbert{f2trc} & -- & 3 & -- & -- & --\\
+ & & \solver{f2trc-s} & -- & 3 & -- & -- & --\\
+ \cline{2-8}
+ & \solver{MapleLCMDistCBT-DL} & \solver{f2trc} & -- & 3 & -- & -- & --\\
+\hline
+
+\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solbert{MapleLCMDistCBT-DL-v3} & -- & -- & -- & -- & --  & --\\
 \hline
@@
 \multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
- & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v3}} & \solbert{Undominated} & -- & -- & -- & -- \\
- &  & \solver{Undom. Top16} & -- & -- & -- & -- \\
- &  & \solver{Undom. Top24} & -- & -- & -- & -- \\
- &  & \solver{Undom. Top36} & -- & -- & -- & -- \\
+ & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v3}} & \solbert{Undominated} & -- & -- & -- & -- & --\\
+ &  & \solver{Undom. Top16} & -- & -- & -- & -- & -- \\
+ &  & \solver{Undom. Top24} & -- & -- & -- & -- & -- \\
+ &  & \solver{Undom. Top36} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
- & \multirow{4}{*}{\solbert{Ex}\solver{MapleLCMDistCBT}} & \solver{padc\_dl} & -- & -- & -- & -- \\
- &  & \solver{padc\_dl\_ovau\_lin} & -- & -- & -- & -- \\
- &  & \solver{padc\_dl\_ovau\_exp} & -- & -- & -- & -- \\
- &  & \solver{psids\_dl} & -- & -- & -- & -- \\
+ & \multirow{4}{*}{\solbert{Ex}\solver{MapleLCMDistCBT}} & \solver{padc\_dl} & -- & -- & -- & -- & -- \\
+ &  & \solver{padc\_dl\_ovau\_lin} & -- & -- & -- & -- & -- \\
+ &  & \solver{padc\_dl\_ovau\_exp} & -- & -- & -- & -- & -- \\
+ &  & \solver{psids\_dl} & -- & -- & -- & -- & -- \\
 % \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
@@
 
-Shaw, Meel & \solver{MapleLCMDistCBT-DL-v3} & \solbert{DurianSat} & -- & -- & -- & -- \\
+Shaw, Meel & \solver{MapleLCMDistCBT-DL-v3} & \solbert{DurianSat} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{2}{*}{Chen}
- & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Maple\_Mix} & -- & -- & -- & -- \\
- &  & \solbert{Maple\_Simp} & -- & -- & -- & -- \\
-\hline
-
-Riveros & \solver{MapleLCMDistCBT} & \solbert{SLIME} & -- & -- & -- & -- \\
+ & \multirow{2}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Maple\_Mix} & -- & -- & -- & -- & -- \\
+ &  & \solbert{Maple\_Simp} & -- & -- & -- & -- & -- \\
+\hline
+
+Riveros & \solver{MapleLCMDistCBT} & \solbert{SLIME} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{3}{*}{Li, Wu, Xu, Chen}
- & \multirow{3}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Scavel} & -- & -- & -- & -- \\
- &  & \solver{Scavel01} & -- & -- & -- & -- \\
- &  & \solver{Scavel02} & -- & -- & -- & -- \\
+ & \multirow{3}{*}{\solver{MapleLCMDistCBT-DL}} & \solbert{Scavel} & -- & -- & -- & -- & -- \\
+ &  & \solver{Scavel01} & -- & -- & -- & -- & -- \\
+ &  & \solver{Scavel02} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
- & \multirow{2}{*}{\solbert{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & -- & -- & -- & -- \\
- &  & \solver{init} & -- & -- & -- & -- \\
+ & \multirow{2}{*}{\solbert{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & -- & -- & -- & -- & -- \\
+ &  & \solver{init} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
- & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v2.2}} & \solbert{exp}\solver{-V-LGB} & -- & -- & -- & -- \\
- &  & \solver{exp-V-L} & -- & -- & -- & -- \\
- &  & \solver{exp-L} & -- & -- & -- & -- \\
- &  & \solver{exp-V} & -- & -- & -- & -- \\
+ & \multirow{4}{*}{\solver{MapleLCMDistCBT-DL-v2.2}} & \solbert{exp}\solver{-V-LGB} & -- & -- & -- & -- & -- \\
+ &  & \solver{exp-V-L} & -- & -- & -- & -- & -- \\
+ &  & \solver{exp-L} & -- & -- & -- & -- & -- \\
+ &  & \solver{exp-V} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
- & \multirow{4}{*}{\solbert{MapleCM}} & \solbert{+dist} & -- & -- & -- & -- \\
- &  & \solver{+dist+sattime2s+-} & -- & -- & -- & -- \\
- &  & \solver{+dist+simp2--} & -- & -- & -- & -- \\
- &  & \solver{used+dist} & -- & -- & -- & -- \\
-\hline
-
-Kaiser, Hartung & \solver{MapleLCMDist} & \solbert{PauSat} & -- & -- & -- & -- \\
+ & \multirow{4}{*}{\solbert{MapleCM}} & \solbert{+dist} & -- & -- & -- & -- & -- \\
+ &  & \solver{+dist+sat2s} & -- & -- & -- & -- & -- \\
+ &  & \solver{+dist+simp2} & -- & -- & -- & -- & -- \\
+ &  & \solver{used+dist} & -- & -- & -- & -- & -- \\
+\hline
+
+Kaiser, Hartung & \solver{MapleLCMDist} & \solbert{PauSat} & -- & -- & -- & -- & -- \\
 \hline
@@
 \multirow{2}{*}{Osama, Wijs} 
- & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- \\
- &  & \solver{CBT} & -- & -- & -- & -- 
+ & \multirow{2}{*}{\solbert{ParaFROST}} & -- & -- & -- & -- & -- & -- \\
+ &  & \solver{CBT} & -- & -- & -- & -- & --
 \end{tabularx}
-\caption[Teams and Solvers in the Main Tracks]{\emph{Teams} and \emph{Solvers} in the Main Tracks.
-\emph{Base Solver} highlights solver genealogy while \emph{Variant} displays names of configurations and forks.
+\caption{\emph{Teams} and \emph{Solvers} in the Main, Planning and Incremental Library Track.
+Column \emph{Base Solver} highlights solver genealogy, and \emph{Variant Name} displays names of configurations and forks.
 Distinctive names are \solbert{underlined}.
-The rightmost columns indicate the awards given in the Main (\emph{M}) and Planning track (\emph{P}), and for performance on unsatisfiable (\emph{U}) and satisfiable (\emph{S}) instances.}
+The rightmost columns indicate the awards given in the Main (\emph{M}) track, for performance on unsatisfiable (\emph{U}) and satisfiable (\emph{S}) instances, and in the Planning (\emph{P}) and Incremental Library (\emph{I}) track.}
 \label{tab:solvers-main}
@@
 
-Four submissions made it to participate in the Incremental Library track, some of which, e.g, \solver{CryptoMiniSat-5}, have also been evaluated and awarded in the Main track. 
-Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
-Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers. 
-In this table, \emph{Score} denotes the number of application categories in which the solvers won based on their PAR-2 score.
-
-\begin{table}[ht]
-\centering\small
-\begin{tabular}{llc}
-\bf Team & \bf Solver & \bf Place\\
-\hline
-Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 1 \\
-Biere, Fleury & \solver{CaDiCaL 2020} & -- \\
-Chen & \solver{abcdsat-i20} & -- \\
-Manthey & \solver{Riss 7.1.2} & -- 
-\end{tabular}
-\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track.}
-\label{tab:solvers-incremental}
-\end{table}
+%\begin{table}[ht]
+%\centering\small
+%\begin{tabular}{llc}
+%\bf Team & \bf Solver & \bf Place\\
+%\hline
+%Soos, Cai, Devriendt, Gocht, Shaw, Meel & \solver{CryptoMiniSat 5} & 1 \\
+%Biere, Fleury & \solver{CaDiCaL 2020} & -- \\
+%Chen & \solver{abcdsat-i20} & -- \\
+%Manthey & \solver{Riss 7.1.2} & -- 
+%\end{tabular}
+%\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track.}
+%\label{tab:solvers-incremental}
+%\end{table}
 
@@
 Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-
 Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses the new unit ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.
@@
 
-\subsection{Parallel SAT Solving: Winners of the Parallel Track}
+\subsection{Parallel SAT Solvers}
 \label{sec:part:par}
 
-\begin{table}[b]
-\centering\small
-\begin{tabular}{llccc}
-\bf Team & \bf Solver & \bf U+S & \bf U & \bf S \\
-\hline\arrayrulecolor{lightgray}
-\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
- & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
- & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
-\hline
-\multirow{2}{*}{Biere, Fazekas, Heisinger}
- & \solver{Plingeling} & 2 & 1 & 3 \\
- & \solver{Treengeling} & --& --& --\\
-\hline
-\multirow{2}{*}{Nabeshima, Inoue}
- & \solver{ManyGlucose-32} & 3 & 3 & -- \\
- & \solver{ManyGlucose-64} & -- & 3 & --\\
-\hline
-\multirow{2}{*}{Tchinda, Djamegni}
- & \solver{Painless-Maple-v1} & --& --& 2 \\
- & \solver{Painless-Maple-v2} & --& --& 2 \\
-\hline
-Li, Wu, Xu, Chen & \solver{Syrup Scavel} & --& --& --\\
+Six Teams submitted a total of $10$ solvers and configurations in the Parallel track. 
+In the following, we outline the technical reports of the award winning parallel solvers.
+
+%\begin{table}[b]
+%\centering\small
+%\begin{tabular}{llccc}
+%\bf Team & \bf Solver & \bf U+S & \bf U & \bf S \\
+%\hline\arrayrulecolor{lightgray}
+%\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
+% & \solver{Painless-MCOMSPS-STR-32} & 1 & 2 & 1 \\
+% & \solver{Painless-MCOMSPS-STR-64} & 1 & --& --\\
 %\hline
-Chen & \solver{abcdSAT-p20} & --& --& --
-\end{tabular}
-\caption{Teams and Solvers participating in the Parallel track.}
-\end{table}
+%\multirow{2}{*}{Biere, Fazekas, Heisinger}
+% & \solver{Plingeling} & 2 & 1 & 3 \\
+% & \solver{Treengeling} & --& --& --\\
+%\hline
+%\multirow{2}{*}{Nabeshima, Inoue}
+% & \solver{ManyGlucose-32} & 3 & 3 & -- \\
+% & \solver{ManyGlucose-64} & -- & 3 & --\\
+%\hline
+%\multirow{2}{*}{Tchinda, Djamegni}
+% & \solver{Painless-Maple-v1} & --& --& 2 \\
+% & \solver{Painless-Maple-v2} & --& --& 2 \\
+%\hline
+%Li, Wu, Xu, Chen & \solver{Syrup Scavel} & --& --& --\\
+%\hline
+%Chen & \solver{abcdSAT-p20} & --& --& --
+%\end{tabular}
+%\caption{Teams and Solvers participating in the Parallel track.}
+%\end{table}
 
@@
 
-\subsection{Massively Parallel SAT Solving: Winners of the Cloud Track}
+\subsection{Massively Parallel SAT Solvers}
 \label{sec:part:cloud}
 
-\begin{table}[t]
-\centering\small
-\begin{tabular}{llc}
-\bf Team & \bf Solver & \bf Place\\
-\hline\arrayrulecolor{lightgray}
-Schreiber & \solver{Mallob Mono} & 1\\
-Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
-Riveros & \solver{Slime} & 3\\
-\hline
-\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
-& \solver{Paracooba-March} & --\\
-\hline
-Hartung & \solver{CTSat} & --
-\end{tabular}
-\caption{Teams and solvers participating in the Cloud track.}
-\end{table}
+Five teams submitted a total of $6$ solvers and configuration in the Cloud track. 
+In the following, we outline the technical reports of the award winning massively parallel solvers.
+
+%\begin{table}[t]
+%\centering\small
+%\begin{tabular}{llc}
+%\bf Team & \bf Solver & \bf Place\\
+%\hline\arrayrulecolor{lightgray}
+%Schreiber & \solver{Mallob Mono} & 1\\
+%Ehlers, Kulczynski, Nowotka, Sieweck & \solver{TopoSAT 2} & 2\\
+%Riveros & \solver{Slime} & 3\\
+%\hline
+%\multirow{2}{*}{Biere, Fazekas, Fleury, Heisinger} & \solver{Paracooba}, & --\\
+%& \solver{Paracooba-March} & --\\
+%\hline
+%Hartung & \solver{CTSat} & --
+%\end{tabular}
+%\caption{Teams and solvers participating in the Cloud track.}
+%\end{table}
 

### 2021-02-02 paper/main.tex
structure

@@
 In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
-on the SAT competition web pages (\url{https://satcompetition.github.io/2020/}). 
+on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}. 
 Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.
@@
 process used for constructing the sets (Section~\ref{sec:instances}).
-In Section~\ref{sec:results} we provide an overview of the competition results together with  a survey on the
-the solving strategies implemented distinctly in  top-ranking  solvers. 
-Going considerably beyond the plain competition rankings, we provide more in-depth analysis of the competition 
+In Section~\ref{sec:results} we provide an overview of the competition results %together with a survey on the
+followed by a survey on 
+the solving strategies implemented distinctly in top-ranking solvers in Section~\ref{sec:winners}. 
+Going considerably beyond the plain competition rankings, in Section~\ref{sec:analysis}, we provide more in-depth analysis of the competition 
 data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
 of individual solvers to the ``virtual best solver'' and 
-portfolios constructed from the competing solvers,  (Section~\ref{sec:analysis}.
+portfolios constructed from the competing solvers.
 The article is concluded with future prospects in Section~\ref{sec:conclusion}.
-\todo{Need to decide on final structure regarding the results overview and analysis}
 
@@
 
-\section{Code-Bases and Winning Strategies}
-\label{sec:analysis}
+\section{Winning Solvers}
+\label{sec:winners}
 
@@
 and summarize new strategies which are implemented in the award winning solvers of this competition. 
-
 We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
-Our review of the winning strategies in this competition starts with sequential (including incremental) SAT solving in Section~\ref{sec:part:seq}, then we continue with parallel SAT solving in Section~\ref{sec:part:par} and conclude with solvers in the cloud track in Section~\ref{sec:part:cloud}.
+Our review of the winning strategies in this competition starts with sequential solvers in the Main-, Planning-, and Incremental Library track in Section~\ref{sec:part:seq}, then we continue with winners of the Parallel track in Section~\ref{sec:part:par} and conclude with winning solvers in the Cloud track in Section~\ref{sec:part:cloud}.
 
@@
 \section{Differentiated Analysis of Main Track Results}
+\label{sec:analysis}
 

### 2021-02-02 paper/main.tex
checking, sect4

@@
 \begin{abstract}
-The SAT Competitions constitute a well-established series of yearly open international algorithm implementation competitions
+The SAT Competitions constitute a well-established series of yearly open international algorithm implementation competitions,
 focusing on the Boolean satisfiability (or propositional satisfiability, SAT) problem. 
@@
  new competition tracks and benchmark selection procedures, overview of solving strategies implemented in top-performing solvers, 
-and a more detailed analysis of the empirical data obtained from running the competition.
+and a detailed analysis of the empirical data obtained from running the competition.
 %SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
@@
 
-The success of SAT would not be without the persistent efforts of the SAT community to further develop the performance and robustness
-of SAT solvers. The SAT Competition series, which a history dating back to early 90s, aims to support and provide further incentives 
+The success of SAT would not be possible without the persistent efforts of the SAT community to further develop the performance and robustness
+of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
 for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
@@
 by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
-the competition invite through open calls submissions of benchmark instances representing in particular new interesting applications 
+the competition invites through open calls submissions of benchmark instances representing, in particular, new interesting applications 
 scenarios of SAT solvers. Indeed, in addition to evaluating recently developed solvers, an important aspect of the SAT competition series is
-to construct on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.
+to collect on a yearly basis new benchmark sets, consisting of instances from various different application settings, which together with benchmark sets from previous years constitute a standard dataset for use in research papers and SAT solver development.
 
@@
 participating solvers, benchmarks, and the empirical results from the competition.
-In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020 
+In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020,
 in addition to the already earlier established main, parallel, and incremental tracks; we
-provide motivation and the new organizational details for both of the tracks.
-In terms of solvers, we provide an overview of solving strategies and other details implemented in top-performing solvers
-from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings.
+provide motivation and the new organizational details for both of these new tracks.
+In terms of solvers, we provide an overview of solving strategies and other details implemented in the top-performing solvers
+from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings \cite{SC2020}.
  As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
@@
 In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
-on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}. 
+on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}
 Finally, we also provide a discussion on lessons learned and ideas for future editions of SAT competitions.
@@
 followed by a survey on 
-the solving strategies implemented distinctly in top-ranking solvers in Section~\ref{sec:winners}. 
-Going considerably beyond the plain competition rankings, in Section~\ref{sec:analysis}, we provide more in-depth analysis of the competition 
+the solving strategies implemented distinctly in the top-ranking solvers in Section~\ref{sec:winners}. 
+Going considerably beyond the plain competition rankings, in Section~\ref{sec:analysis}, we provide an in-depth analysis of the competition 
 data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
@@
 Solvers not complying with either of the above criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
-The No-Limits thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) 
+The No-Limits track thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) 
 as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
@@
 of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
-was set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
+was arbitrarily set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
 Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
@@
 (typically solving a harder problem than SAT) and is called multiple times before 
-the enclosing tool reaches its final state. Incremental means that
+the enclosing tool reaches its final state. ``Incremental'' means that
 the individual calls to the SAT solver are not independent, but may share 
@@
 enclosing tool on its own benchmark and communicate with the competing SAT solver 
-through this interface API. Not only does the SAT solver in this track
+through this interface API. 
+%
+Not only does the SAT solver in this track
 need to solve a sequence of related problems fast, but its answers to the early questions
@@
 The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
-Each solver run in this track was on a m4.16xlarge machine from Amazon Web Services (AWS).
+Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
 These machines have 64 virtual cores and 256GB of memory. In contrast to the 
-Main track, there is no proof logging for unsatisfiable benchmarks in the Parallel track.
+Main track, proof logging for unsatisfiable instances is not required in the Parallel track.
 
@@
 
-New this year was the Cloud track to evaluated distributed solvers. Similar to the
+New this year was the Cloud track, dedicated to evaluating distributed solvers. Similar to the
 Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
@@
 either in its textual version, which is also very similar to the DIMACS input format,
-or on a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
+or in a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
 %
@@
 in the Main track (besides the No Limits track).
-In some cases solvers output the correct result but the respective certificate was wrong. 
+In some cases, a solver output the correct result, but the respective certificate was wrong. 
 Such solvers were demoted to the No-limits track of the competition.
@@
 
-Four solver participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}) 
+Four solvers participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}) 
 performed significantly better compared to the others, see Table~\ref{tab:results}.
@@
 10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS).
-The four top solvers all have a different code base, which is rare and has not been observed in many years.
+The four top solvers all have a different code base, which is rare and has not been observed for many years.
 Also, in recent competitions, the top solvers were much closer together.
@@
 The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
-compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more efficiently. 
+compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more quickly. 
 Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.
@@
 
-The solver performances on unsatisfiable formulas was much closer,
+The solver performance on unsatisfiable formulas was much closer,
 see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
@@
 that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
-details about \solver{Kissat} are described in Section~\ref{sec:kissat}.
+details about \solver{Kissat} are given in Section~\ref{sec:kissat}.
 The solvers \solver{CaDiCaL-trial}
-and \solver{f2trc-s} won the second, respectively, third place in the Main UNSAT track.
+and \solver{f2trc-s} placed, respectively, second and third in the Main UNSAT track.
 
@@
 \caption{Performance of the top 10 solvers + VBS on Main track unsatisfiable benchmarks}
+\label{main:unsat}
 \end{figure}
-\label{main:unsat}
 
@@
 solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. Their PAR-2 score is 
-quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but fast runtime
-on several instances resulted in a strong PAR-2 score. Notice that these solvers were also strong in the Main tracks. 
+quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtime
+on several instances resulted in a strong PAR-2 score. Notice that these solvers were also strong in the Main track. 
 Apparently none of the participating solvers was optimized for planning instances.
 
-The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the post-fix denotes
+The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the suffix denotes
 that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
-competitions that uses fewer threads than the number of virtual cores can be helpful as threads compete 
+competitions that using fewer threads than the number of virtual cores can be helpful as threads compete 
 for memory, which can reduce of the overall performance. The runner up is \solver{Plingeling}, while the
-third place is for \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
+third place is taken by \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
 all participating parallel solvers. Notice in Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR} solvers
@@
 
-The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2},
-see Figure~\ref{fig:res-cloud}.
-\solver{Mallob-Mono} was able to solver more instances in 1000 seconds, compared to the 
+The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2}
+(see Figure~\ref{fig:res-cloud}).
+\solver{Mallob-Mono} was able to solver more instances in 1000 seconds than the 
 winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
 The other four participants performed significantly worse. This is likely due to the initial challenges
-to develop a distributed solver. This was the first year of this track. We expect that the gap will be 
-closer is future years.
+in developing a distributed solver. 2020 was the first year of this track. We expect that the gap will be 
+smaller in the future years.
 

### 2021-02-02 paper/main.tex
checking, rest

@@
 Figure~\ref{main:all} shows the cumulative solved instances plot of the best performing solver of the strongest
-10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS).
+10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS -- see also~\ref{subsec:vbs_explained}).
 The four top solvers all have a different code base, which is rare and has not been observed for many years.
@@
 We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
-Our review of the winning strategies in this competition starts with sequential solvers in the Main-, Planning-, and Incremental Library track in Section~\ref{sec:part:seq}, then we continue with winners of the Parallel track in Section~\ref{sec:part:par} and conclude with winning solvers in the Cloud track in Section~\ref{sec:part:cloud}.
+Our review of the winning strategies in this competition starts with sequential solvers in the Main, Planning, and Incremental Library tracks in Section~\ref{sec:part:seq},
+then we continue with winners of the Parallel track in Section~\ref{sec:part:par} and conclude with winning solvers in the Cloud track in Section~\ref{sec:part:cloud}.
 
@@
 
-Another more recent string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-management~\cite{Oh:2015:satunsat}. 
+Another, more recent, string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-management~\cite{Oh:2015:satunsat}. 
 The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
-The then award winning variant \solver{MapleCOMSPS} by Liang et al.
-is an implementation of a hybrid branching heuristic of classic Variable-State Independent Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
-
-In SAT Competition 2017, Luo et al.
-integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
+The then award winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic Variable-State Independent Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+
+In SAT Competition 2017, Luo et al.~integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM}, which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
 Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
@@
 
-Kochemazov et al. improved three-tier clause-management by persisting
+Kochemazov et al.~improved three-tier clause-management by persisting
 additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
-As can be seen in Table~\ref{tab:solvers-main}, numerous submissions to SAT Competition~2020 are forks of some recently award winning descendants of \solver{Maple}-based solver.
-
-Starting as a fork of \solver{Minisat} and the integration of special xor treatment~\cite{Soos:2009:Crypto}, \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver.
-One highlight of \solver{CryptoMinisat} is its advanced data-logging capabilities for statistical analysis of SAT solver behavior~\cite{Soos:2019:ChrystalBall}.
+As can be seen in Table~\ref{tab:solvers-main}, numerous submissions to SAT Competition~2020 are forks of some recent award winning descendants of a \solver{Maple}-based solver.
+
+Starting as a fork of \solver{Minisat} with the integration of special xor treatment~\cite{Soos:2009:Crypto},
+\solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver. 
+One highlight of \solver{CryptoMinisat} are its advanced data-logging capabilities for statistical analysis of SAT solver behavior~\cite{Soos:2019:ChrystalBall}.
 
@@
 Three configurations of \solver{Kissat} were evaluated in this competition, including one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively.
-\solver{Kissat} received \emph{four awards}, by achieving first place in the Main track, best score on unsatisfiable instances, second best score on satisfiable instances and third place in the Planning track.
+\solver{Kissat} received \emph{four awards}, by achieving the first place in the Main track, 
+the best score on unsatisfiable instances, the second best score on satisfiable instances and the third place in the Planning track.
 
@@
 Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses the new unit ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.
+Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses a new unit called ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.
 
@@
 
-\solver{CryptoMiniSat} received \emph{four awards}, first place in the Incremental Library track, second place in the Planning track, third place in the Main track, and third best score on satisfiable instances.
-Two submitted variants \solver{default} and \solver{LSIDS} scored mostly adjacent ranks in the evaluation of tracks. 
+\solver{CryptoMiniSat} received \emph{four awards}, the first place in the Incremental Library track,
+the second place in the Planning track, the third place in the Main track, and the third best score on satisfiable instances. 
+Two submitted variants, \solver{default} and \solver{LSIDS}, scored mostly adjacent ranks in the evaluation of the tracks. 
 The \solver{LSIDS} variant of \solver{CryptoMiniSat} comes with a new hybrid phase selection approach~\cite{Shaw:2020:LSIDS,Soos:SC2020}.
@@
 
-Based on \solver{CaDiCaL}, its variants \solver{Trail} and \solver{AllUip} present implementations of a new \emph{Trail Saving} approach~\cite{Hickey:2020:TrailSaving} and improved clause-learning \emph{Stable AllUIP}~\cite{Bacchus:SC2020}.
+Based on \solver{CaDiCaL}, its variants \solver{Trail} and \solver{AllUip} present implementations of a new \emph{Trail Saving} approach~\cite{Hickey:2020:TrailSaving} 
+and an improved clause-learning \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
 Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
@@
 
-\emph{Stable AllUip} resolves additional clauses beyond the 1st Unit Implication Point (1-UIP) and keeps them if they are of smaller size or LBD than the 1-UIP clause. 
+\emph{Stable AllUip} resolves additional clauses beyond the 1st Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size or LBD than the 1-UIP clause. 
 By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of such extended learning attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
@@
 
-\solver{F2TRC} introduces improved management of learned clauses in the tree tiers \emph{core}, \emph{tier2} and \emph{local} which are inherited from \solver{CoMinisatPS}~\cite{Oh:2015:satunsat}.
+\solver{F2TRC} introduces improved management of learned clauses in the tree tiers \emph{core}, \emph{tier2} and \emph{local}, which are inherited from \solver{CoMinisatPS}~\cite{Oh:2015:satunsat}.
 A dynamic size limit for the \emph{core} tier triggers the reassignment of inactive clauses from \emph{core} to \emph{tier2}. 
-To counter-act an observed starving of tier2, the conflict-based heuristic that controls demotion of clauses from \emph{tier2} to \emph{local} was replaced by a size based heuristic~\cite{Kochemazov:SC2020}.
+To counter-act an observed starving of tier2, the conflict-based heuristic that controls demotion of clauses from \emph{tier2} to \emph{local} was replaced by a size-based heuristic~\cite{Kochemazov:SC2020}.
 
@@
 \solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32} and a \solver{64} threaded variant and won three awards: first place overall, best score on satisfiable and second best score on unsatisfiable instances. 
+The authors submitted a \solver{32} and a \solver{64} threaded variant and won three awards: the first place overall, the best score on satisfiable and the second best score on unsatisfiable instances.
 In the overall evaluation, the \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant. 
@@
 \solver{Painless-MCOMSPS-STR} diversifies mainly via hard-coded configurations of the branching strategies LRB and VSIDS, and via sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}.
-Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} Gaussian elimination, respectively. 
-\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
+Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} and Gaussian elimination, respectively. 
+\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed-size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
 
@@
 
-\solver{Plingeling} achieved the best score on unsatisfiable instances, second place in the overall evaluation, and the third best score on satisfiable instances. 
+\solver{Plingeling} achieved the best score on unsatisfiable instances, the second place in the overall evaluation, and the third best score on satisfiable instances. 
 \solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
@@
 \solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
-The \solver{32} threaded variant received two awards in this competition: the overall third place and third best score on unsatisfiable instances. 
+The \solver{32} threaded variant received two awards in this competition: the overall third place and the third best score on unsatisfiable instances. 
 \solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
@@
 
-Five teams submitted a total of $6$ solvers and configuration in the Cloud track. 
+Five teams submitted a total of $6$ solvers and configurations in the Cloud track. 
 In the following, we outline the technical reports of the award winning massively parallel solvers.
@@
 
-\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
+\solver{Mallob} is a fork of the generic, massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
 \solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priority. 
@@
 
-\solver{TopoSAT~2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
+\solver{TopoSAT~2}~\cite{Ehlers:2018:Toposat2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}. 
 \solver{TopoSAT~2} uses lock-free clause-exchange for solvers on the same machine, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
 \solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
-\solver{Toposat~2} diversifies via strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.
+\solver{Toposat~2} diversifies via strategies used for branching, restarting, and clause forgetting~\cite{Ehlers:SC2020}.
 
@@
 \subsection{Contributions to the Virtual Best Solver}
+
+\label{subsec:vbs_explained}
 
@@
 can be obtained by attempting to construct a sequential schedule of solvers 
-(rather then relying on an oracle to pick one for each instance, as with VBS)
+(rather than relying on an oracle to pick one for each instance, as with VBS)
 and looking at how big role each solvers plays in such a schedule. Since constructing 
@@
 Contributions to the VBS can be well captured by clustering the instance space into instance families. 
-We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.
-Table~\ref{tab:families}) and report on their place and score in Table~\ref{tab:eval-by-family}.
+We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
+and report their place and score in Table~\ref{tab:eval-by-family}. 
 Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.
@@
 \emph{i.e.}, we set a score of \num{10000} for unsolved instances.
-Each solver $S$ thus is associated with the PAR-2 scores $S_{1},\dots,S_{316}$.
+Each solver $S$ is thus associated with the PAR-2 scores $S_{1},\dots,S_{316}$.
 % This leaves us with $316$ floats
@@
 
-One big cluster that we identify consists of the \solver{Maple}-decedents,
+One big cluster that we identify consists of the \solver{Maple}-decedants, 
 all of which are modifications of the winners in the SAT Competition 2018 and
@@
 The two solvers are both based on
-\solver{MapleLCMDistChronoBT-dl-v2.2} but have different authors.
+\solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
 The high similarity suggest that the
@@
 The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
-use the same code-base as a lot of solvers in the Maple-Cluster but their
-overall performance is better and closer to the \solver{CMS}-Cluster.
+use the same code-base as a lot of solvers in the \solver{Maple}-cluster, but their
+overall performance is better and closer to the \solver{CMS}-cluster.
 The three \solver{CMS} configurations
@@
 
-We first use random sampling to select subsets of benchmarks used in the Main track.
+We first use random sampling to select subsets of the benchmarks used in the Main track.
 We start with $316$ benchmarks that have been solved by at least one solver in
@@
 \begin{figure}[h]
-  \label{fig:sampleAll}
   \centering
@@
   \caption{Mean and standard deviation of rank correlation under removal of random instances over 50 samples for each size}
+   \label{fig:sampleAll}
 \end{figure}
@@
 \begin{figure}[h]
-  \label{fig:sampleFamily}
   \centering
@@
   \caption{Change of rank correlation under removal of individual benchmark families}
+  \label{fig:sampleFamily}
 \end{figure}
@@
 correlation coefficient resulting from removing a complete benchmark family
-instead of a random subset. As expected, removing a non random subset can have a
+instead of a random subset. As expected, removing a non-random subset can have a
 higher impact on the ranking even if it is small. Removing the $13$ benchmarks
@@
 
-All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
+All the winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
 
@@
 It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
-The winner of the \emph{Incremental Library} track showed that it is worth integrating full solver functionality in the incremental use-case.
+The winner of the \emph{Incremental Library} track showed that it is worth integrating a full solver functionality in the incremental use-case.
 
@@
 
-The results of the \emph{Planning} track as well as our differentiated analysis of results highlight the individual contributions of many submissions. 
-Our plan for future competitions is, to always run a special track for varying applications alongside the Main track.
+The results of the \emph{Planning} track as well as our differentiated analysis of the results highlight the individual contributions of many submissions. 
+Our plan for the future competitions is to always run a special track for varying applications alongside the Main track.
 

### 2021-02-02 paper/main.tex
sects 1-2, added some notes in red...

@@
 which all came from the same application domain -- automated planning. 
-Solver submitted to the Main track automatically participated in the Planning track.
+Solvers submitted to the Main track automatically participated in the Planning track.
 It is envisioned that also in the future there will be an ``application promotion'' track,
@@
 
-Finally, the Main Track also had the so-called ``Glucose hack'' sub-track. 
-Since in the past several advances in SAT solving required only a small modification of an established solver
+Finally, the Main Track also included the so-called ``Glucose hack'' sub-track. 
+As in the past several advances in SAT solving required only a small modification of an established solver
 to achieve a considerable contribution, this sub-track encouraged participation 
 of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
-was arbitrarily set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
+was---somewhat arbitrarily---set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
 Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
@@
 (typically solving a harder problem than SAT) and is called multiple times before 
-the enclosing tool reaches its final state. ``Incremental'' means that
+the enclosing tool reaches its final state. \textcolor{red}{Could mention concrete applications here?}
+``Incremental'' here refers to the 
+idea that
 the individual calls to the SAT solver are not independent, but may share 
@@
 
-The Parallel track evaluates solver performance in wall-clock time on multiple cores.
-The benchmarks and the timeout (5000 seconds) are the same as in the Main track. 
+The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of
+ multiple processor cores.
+The benchmarks and the timeout (5000 seconds) are the same as in the Main track \textcolor{red}{repetitive? also mentioned below?}. 
 Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
@@
 
-New this year was the Cloud track, dedicated to evaluating distributed solvers. Similar to the
+New this year was the Cloud track, dedicated to evaluating distributed solvers \textcolor{red}{Not sure
+if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. Similar to the
 Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
@@
 The wall-clock timeout is 1000 seconds and the same benchmarks were used as in
-the Main and Parallel track.
+the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
 
@@
 The following requirements were imposed for 
-the participation in the competition.
+participating in the competition.
 
@@
 %
-Details on certification are further discussed below in Section~\ref{sec:certif}.
-
-\paragraph{Number of submissions}
-
-Each participant was restricted to be an author of at most four different sequential solvers,
+Details on certification are further discussed in Section~\ref{sec:certif}.
+
+\paragraph{Number of Submissions}
+
+Each participant was allowed to be an author of at most four different sequential solvers,
 two different parallel solvers, and one ``Glucose hack'' sub-track solver.
@@
 
-In all tracks it was required to output a model to certify recognizing a satisfiable instance.
-On the other hand, certificates for unsatisfiable instances (proofs) were required only 
+In all tracks solvers were required to output a model to certify recognizing a satisfiable instance.
+On the other hand, 
+certificates for unsatisfiable instances (proofs) were required only 
 in the Main track (besides the No Limits track).
@@
 
-The proofs were validated in a two step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
+The proofs were validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
 was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
@@
 
-\subsection{Computing environments}
+\subsection{Computing Environments}
 
 \label{sec:computing}
-The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec},
-whose nodes are equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
+The Main, No-Limits, and Planning tracks were run on the StarExec cluster \cite{starexec}
+with computing nodes  equipped with Intel Xeon \SI{2.4}{\giga\hertz} processors 
 and \SI{128}{\giga\byte} of memory.
@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.8\textwidth]{stability/ALL_random_smpling_correlations.png}
+  \caption{Mean and standard deviation of rank correlation under removal of random instances over 50 samples for each size}
+   \label{fig:sampleAll}
+\end{figure}
 The coefficient $\rho$ is in the interval $[-1, 1]$, where a rank correlation of
@@
 depicted in Figure~\ref{fig:sampleAll}.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.8\textwidth]{stability/ALL_random_smpling_correlations.png}
-  \caption{Mean and standard deviation of rank correlation under removal of random instances over 50 samples for each size}
-   \label{fig:sampleAll}
-\end{figure}
 The rank correlation is high even for relatively small samples.
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
   \centering
@@
 Figure~\ref{fig:sampleFamily} shows the rank
-correlation coefficient resulting from removing a complete benchmark family
-instead of a random subset. As expected, removing a non-random subset can have a
-higher impact on the ranking even if it is small. Removing the $13$ benchmarks
-from the \emph{hgen}-family results in a (still high) rank correlation of
+correlation coefficient resulting from removing a complete benchmark family. As expected, removing a non-random subset can have a
+higher impact on the ranking even if it is small. Removing the $13$ \emph{hgen} benchmarks
+results in a (still high) rank correlation of
 $0.9895$. Additionally, the ranking of the top five solvers stays the same.

### 2021-02-02 paper/main.tex
fixed a note so the pdf compiles

@@
 
+\textcolor{red}{need to add refs to intro... none right now...}
+
 From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
@@
 
-Benchmark instances selection in this competition was realized using GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which is a tool-chain for maintenance and distribution of benchmark instances and instance attributes~\cite{Iser:2018:GBD}.
+Benchmark instances selection in SAT Competition  2020 was realized using GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which is a tool-chain for maintenance and distribution of benchmark instances and instance attributes~\cite{Iser:2018:GBD}.
 Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
@@
 
-The ``Bring Your Own Benchmarks'' (BYOB) rule is established since SAT Competition 2017~\cite{SC2017}. 
+The ``Bring Your Own Benchmarks'' (BYOB) rule, first  established in SAT Competition 2017~\cite{SC2017}, was again followed
+in 2020.
 By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition.
-At least $10$ of these instances are required to be ``interesting'', meaning that Minisat must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.
-
-As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances of a large variety of different instance families. 
-In order to compile a balanced set of $300$ benchmark instances, we first removed those instances solved by \solver{Minisat} in less than $10$ minutes, thus obtaining a reduced set of $1012$ instances.
-We considered a maximum of $14$ submissions per author using the procedure which is depicted in Algorithm~\ref{algo:select}. 
+At least $10$ of these instances are required to be ``interesting'', meaning that the standard Minisat SAT solver
+must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.
+
+As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from
+a wide range of different instance families. 
+In order to compile a balanced set of $300$ benchmark instances, we first removed  instances solved by \solver{Minisat} in less than $10$ minutes, thus obtaining a reduced set of $1012$ instances. 
+We considered a maximum of $14$ submissions per author using a procedure detailed as Algorithm~\ref{algo:select}. 
 Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (Lines~3 and~4). 
@@
 that transforms the world from some initial state to a goal state. In 1992 Kautz
-and Selman \cite{Kautz1992} proposed to encode planning as satisfiability. In
+and Selman \cite{Kautz1992} proposed to encode planning as satisfiability, constituting
+one of the hallmark early adoptations of SAT solving to solve real-world problems. In
 their encoding the problem of finding a plan of length $i$ (\textit{i.e.,} the
@@
 
-The encodings are generated by the two SAT-based planners \emph{Madagascar}
-\cite{Madagascar14} and \emph{Pasar} \cite{Pasar19}. We use Madagascar both in
+\textcolor{red}{global note: should try to be consistent with present/past tense...}
+
+The encodings were generated by the two SAT-based planners \emph{Madagascar}
+\cite{Madagascar14} and \emph{Pasar} \cite{Pasar19}. We used Madagascar both in
 its default configuration to generate a parallel encoding based on
@@
 
-The classical planning benchmarks are selected from the \emph{satisfying} and
+The classical planning benchmarks were selected from the \emph{satisfying} and
 \emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
@@
 
-In addition to the classical planning problems, we also include SAT formulas
+In addition to the classical planning problems, we also included SAT formulas
 generated by \emph{Tree-REX} \cite{TreeRex19}; a planner for \emph{Hierarchical
   Task-networks}. In HTN planning the planner is provided with additional domain
-knowledge besides the problem description. The HTN benchmarks are provided by
+knowledge besides the problem description. The HTN benchmarks were provided by
 the author of \emph{Tree-REX}.
@@
 % - all 200 above 90\% binary clauses and half have above 99%
-The instances of the Planning track are big compared to the Main track
-instances. Using the number of clauses as a metric; out of the $100$ biggest
+The instances of the Planning track are large compared to the Main track
+instances. Using the number of clauses as a metric: out of the $100$ biggest
 instances of both tracks
@@
 Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications.
-For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface -- ranging from determination of backbone variables to SAT-based planning. 
+For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface, ranging from determination of backbone variables to SAT-based planning. 
 For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.
@@
 \paragraph{Planning (SAS+)}
-We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar} -- a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
+We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
 
@@
 
-This section describes some high-level observations, including the winners, of the 2020 SAT Competition. 
-We focus on some interesting results. Details about the solvers, including the key and new solving techniques,
-are described in Section~\ref{sec:analysis}.
-
-Four solvers participating in the Main track (\solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}) 
-performed significantly better compared to the others, see Table~\ref{tab:results}.
-Figure~\ref{main:all} shows the cumulative solved instances plot of the best performing solver of the strongest
-10 teams (in short, the top 10 solvers)  together with the Virtual Best Solver (VBS -- see also~\ref{subsec:vbs_explained}).
+In this section we provide a high-level overview of the results of SAT Competition 2020
+%We focus on some interesting results.
+Later on, we give more details about the solvers, including the key and new solving techniques
+(Section~\ref{sec:winners}) and more in-depth analysis of the results (Section~\ref{sec:analysis}).
+
+Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}),
+performed significantly better that all other solvers submitted to the Main track, see Table~\ref{tab:results}.
+Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
+10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
 The four top solvers all have a different code base, which is rare and has not been observed for many years.
-Also, in recent competitions, the top solvers were much closer together.
+Also, in recent competitions, the top solvers were much closer to each other in terms of runtime performance.
 The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
-\solver{Relaxed-newTech} solved more instances within the 2000 seconds limit.
-The third place, based on the PAR-2 score, was for \solver{CMS-ccnr-lsids}. It solved two fewer instances
+\solver{Relaxed-newTech} solved more instances within the 2000-second limit.
+Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
 compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more quickly. 
-Since the SAT Competition started to rank based on the PAR-2 score, such cases have been observed several times.
+Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.
 
@@
 \includegraphics[width=.9\textwidth]{img/paper-main-top10-ALL.pdf}
-\caption{Performance of the top 10 solvers + VBS on all  Main track benchmarks}
+\caption{Performance of the top 10-solvers and the VBS on all  Main track benchmarks}
 \label{main:all}
@@
 
-The main reason for the separation between the top four solvers and the others is the enormous gap on satisfiable benchmarks, 
+The main reason for the separation between the top-4 solvers and the others is the noticeable gap on satisfiable benchmarks, 
 see Figure~\ref{main:sat}. In recent years, several techniques have been added to SAT solvers to improve
 their performance on satisfiable instance. Examples of such techniques are the integration of a local search
-solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts,
-and variable-move-to-front). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by 
+solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
+and variable-move-to-front \textcolor{red}{screams for a reference...}). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by
 \solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.
@@
 \includegraphics[width=.9\textwidth]{img/paper-main-top10-SAT.pdf}
-\caption{Performance of the top 10 solvers + VBS on Main track satisfiable benchmarks}
+\caption{Performance of the top-10 solvers and the VBS on Main track satisfiable benchmarks}
 \label{main:sat}
@@
 
-The solver performance on unsatisfiable formulas was much closer,
+Overall, solvers performed much more similarly on
+unsatisfiable formulas,
 see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
@@
 
-The ranking in the Planning Track was closer. \solver{CaDiCaL-alliup-trial}, the winning solver, 
+The competition in the Planning Track was more tight. \solver{CaDiCaL-alliup-trial}, the winning solver, 
 solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. Their PAR-2 score is 
-quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtime
-on several instances resulted in a strong PAR-2 score. Notice that these solvers were also strong in the Main track. 
+quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtimes
+on several instances resulted in a strong PAR-2 score. Notice that these three solvers were also strong in the Main track. 
 Apparently none of the participating solvers was optimized for planning instances.
@@
 and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
-This shows that it is hard to beat sequential solvers with a parallel solver on the competition instances. 
+This shows that it was hard to beat best-performing sequential solvers with a parallel solver on the competition instances. 
 We will show later in the article (Table~\ref{tab:tuples}) that small sequential portfolios 
@@
 (see Figure~\ref{fig:res-cloud}).
-\solver{Mallob-Mono} was able to solver more instances in 1000 seconds than the 
-winner of the Parallel Track in 5000 seconds, thereby showing the potential of distributed SAT solving. 
+\solver{Mallob-Mono} was able to solve more instances in 1000 seconds than the 
+winner of the Parallel Track in 5000 seconds, which shows the potential of distributed SAT solving. 
 The other four participants performed significantly worse. This is likely due to the initial challenges
-in developing a distributed solver. 2020 was the first year of this track. We expect that the gap will be 
-smaller in the future years.
+in developing a distributed solver. 2020 was the first year of this track. We expect this gap to turn smaller in 
+forthcoming SAT competitions.
 
@@
 In the following, we provide an overview of the participating teams and solvers, 
-and summarize new strategies which are implemented in the award winning solvers of this competition. 
+and summarize new strategies which are implemented in the award-winning solvers of this competition. 
 We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
@@
 Progress in SAT solvers is often based on successful modifications of existing code-bases. 
-One well-known tree of development is rooted in the code-base of \solver{Minisat} by Eén and Sörenson~\cite{Niklas:2003:Minisat}. 
-A well-known fork of \solver{Minisat} is \solver{Glucose} by Audemard and Simon~\cite{Audemard:2018:Glucose}, among others introducing Literal Block Distance (LBD) for weighing clauses in forgetting heuristics~\cite{Audemard:2009:Glucose}.
-The SAT solver \solver{RISS} by Manthey is a successful and award winning fork of \solver{Glucose} in combination with the state-of-the-art preprocessor \solver{Coprocessor}~\cite{Manthey:2012:Coprocessor2}.
-
-Another, more recent, string of development is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Chanseok Oh introducing three-tier clause-management~\cite{Oh:2015:satunsat}. 
+One well-known tree of development is rooted in the code-base of \solver{Minisat} by E\'en and S\"orensson~\cite{Niklas:2003:Minisat}. 
+A well-known fork of \solver{Minisat} is \solver{Glucose} by Audemard and Simon~\cite{Audemard:2018:Glucose} which introduced the influential literal block distance (LBD) for weighing clauses in forgetting heuristics~\cite{Audemard:2009:Glucose}.
+The SAT solver \solver{RISS} by Manthey is a successful and award-winning fork of \solver{Glucose} in combination with the \solver{Coprocessor}~\cite{Manthey:2012:Coprocessor2} preprocessor.
+
+Another, more recent line of development in SAT solvers
+is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Oh which introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
 The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
-The then award winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic Variable-State Independent Decaying Sum (VSIDS) and the new Learning-Rate based Branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
-
-In SAT Competition 2017, Luo et al.~integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM}, which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
+The then award-winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)\textcolor{red}{add ref} and the newer learning rate based branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+
+In SAT Competition 2017, Luo et al.~integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award-winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
 Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
-They presented their award winning \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
+They introduced their award-winning \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
 
 Kochemazov et al.~improved three-tier clause-management by persisting
-additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
-As can be seen in Table~\ref{tab:solvers-main}, numerous submissions to SAT Competition~2020 are forks of some recent award winning descendants of a \solver{Maple}-based solver.
-
-Starting as a fork of \solver{Minisat} with the integration of special xor treatment~\cite{Soos:2009:Crypto},
+additional clauses through hash-based detection of repeatedly learned clauses and presented their award-winning~\solver{MapleLCMDistChronoBT-DL} in SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}.
+As can be seen in Table~\ref{tab:solvers-main}, numerous submissions to SAT Competition~2020 are forks of some recent award-winning descendants of a \solver{Maple}-based solver.
+
+Starting as a fork of \solver{Minisat} with the integration of special treatment for XOR constraints ~\cite{Soos:2009:Crypto},
 \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver. 
@@
 Many independent and award-winning code-bases can be found among the SAT solvers written by Biere. 
-The sequential SAT solver \solver{Lingeling} has been award winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
+The sequential SAT solver \solver{Lingeling} has been award-winning since SAT Competition~2011 and is still competitive in its parallel version \solver{Plingeling}~\cite{Biere:2012:Lingeling}. 
 As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
-by Biere is another independent, award winning and structured implementation of the state-of-the-art in SAT solving. 
+by Biere is another independent, award-winning and structured implementation of the state-of-the-art in SAT solving. 
 Its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.
@@
 
-\solver{CryptoMiniSat} received \emph{four awards}, the first place in the Incremental Library track,
-the second place in the Planning track, the third place in the Main track, and the third best score on satisfiable instances. 
+\solver{CryptoMiniSat} received \emph{four awards}: the first place in the Incremental Library track,
+the second place in the Planning track, the third place in the Main track, and the third-best score on satisfiable instances. 
 Two submitted variants, \solver{default} and \solver{LSIDS}, scored mostly adjacent ranks in the evaluation of the tracks. 
@@
 \solver{CryptoMiniSat} comes with an independent implementation of state-of-the-art hybrid branching heuristics which alternate between classic phase saving and target phase selection~\cite{Biere:SC2019}.
-\solver{CryptoMiniSat-CCAnr} regularly schedules short periods of local search and imports the best assignment for phase selection -- a procedure which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
+\solver{CryptoMiniSat-CCAnr} regularly schedules short periods of local search and imports the best assignment for phase selection---a procedure which is known as ``rephasing'' from CaDiCaL~\cite{Biere:SC2019}.
 In addition, \solver{CryptoMiniSat-CCAnr} bumps the VSIDS scores of the first 100 variables in those clauses which the SLS solver weighs most hard to satisfy~\cite{Soos:SC2020}.
@@
 Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
-The variants including \emph{Stable AllUIP} were the most successful and won the first price in the Planning track.
+The variants including \emph{Stable AllUIP} were the most successful and won  first place in the Planning track.
 
@@
 In SAT Competition~2020, its variant \solver{newTech} showed a good performance especially on satisfiable instances. 
-The solver achieved two awards, the second price in the Main track and the best score on satisfiable instances.
+The solver received two awards: second place in the Main track and the best score on satisfiable instances.
 
 \solver{Relaxed} integrates short runs of the local search solver \solver{CCAnr} through periodic export and import of assignments~\cite{Xindi:SC2019} and uses a probabilistic schedule for switching between $10$ phase selection modes.
-The \solver{Relaxed newTech} variant uses occurrence counts of variables in unsatisfied clauses during SLS runs to recalculate variable priorities for their modified branching heuristic~\cite{Xindi:SC2020}.
+The \solver{Relaxed newTech} variant uses occurrence counts of variables in unsatisfied clauses during stochastic local search runs to recalculate variable priorities for their modified branching heuristic~\cite{Xindi:SC2020}.
 
@@
 
-Six Teams submitted a total of $10$ solvers and configurations in the Parallel track. 
-In the following, we outline the technical reports of the award winning parallel solvers.
+Six teams submitted a total of $10$ solvers and configurations in the Parallel track. 
+In the following, we outline the award-winning parallel solvers.
 
@@
 
-\solver{Plingeling} achieved the best score on unsatisfiable instances, the second place in the overall evaluation, and the third best score on satisfiable instances. 
+\solver{Plingeling} obtained the best score on unsatisfiable instances, the second place in the overall evaluation, and the third best score on satisfiable instances. 
 \solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
@@
 
-\solver{Painless Maple} received the award for the second best performance on satisfiable instances but had the worst performance on unsatisfiable instances. 
+\solver{Painless Maple} received the award for second-best performance on satisfiable instances. Interestingly, it 
+at the same time exhibited  worst performance on unsatisfiable instances. 
 \solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
@@
 Five teams submitted a total of $6$ solvers and configurations in the Cloud track. 
-In the following, we outline the technical reports of the award winning massively parallel solvers.
+In the following, we outline the award-winning massively parallel solvers.
 
@@
 
-\solver{Mallob} is a fork of the generic, massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
+\solver{Mallob} is a fork of the  massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
 \solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priority. 
 This functionality is disabled in the submitted variant \solver{Mallob Mono}. 
-\solver{Mallob} uses \solver{Lingeling-bcj} and as every 14th solver \solver{Mallob} spawns the SLS solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
+\solver{Mallob} uses \solver{Lingeling-bcj} and as every 14th solver \solver{Mallob} spawns the stochastic local search solver \solver{YalSAT}~\cite{Biere:2018:LingelingYalsat}.
 Diversification is done via randomized sparse initialization of branching scores.
@@
 \solver{TopoSAT~2}~\cite{Ehlers:2018:Toposat2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}. 
-\solver{TopoSAT~2} uses lock-free clause-exchange for solvers on the same machine, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
+\solver{TopoSAT~2} uses lock-free clause-exchange for solvers on the same machine and the message passing interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
 \solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
@@
 
-In this section, we provide additional views on the Main track results,
-focusing on metrics complementing the PAR-2 score, 
-which we used for ranking the solvers in the actual competition.
+In this section, we provide additional analysis of the Main track results, going beyond the rankings.
+In paricular, we focus on metrics complementing the PAR-2 score used for ranking the solvers in the actual competition.
 
@@
 and an oracle which, when given an input instance,
-invokes to run the actual solver which performed the best on that instance.
+invokes  the  solver which performed the best on that instance.
 In this way, the performance of the VBS highlights a certain upper bound 
-on performance achievable in principle by the technology 
-of the participating solvers (cf.~the figures in Section~\ref{sec:results}).
+on performance achievable in principle by the 
+ participating solvers (cf.~the figures in Section~\ref{sec:results}).
 

### 2021-02-02 paper/main.tex

@@
 
-All the winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
-
-As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occasions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart.
+The 2020 SAT Competition successfully continued the tradition of the SAT Competition series. In 2020, significant advances
+in SAT solver compared to previous years were observed. Some of the more interesting observations on the winning solving 
+strategies include the following.
+All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
+solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
+As can be seen in the \emph{Parallel} track, it appear difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$ threaded counterpart.
 However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
-
 It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
@@
 
-\subsection*{Future Competitions}
+\subsection*{Future Prospects}
 

### 2021-02-03 paper/main.tex
add comp refs

@@
 
-\textcolor{red}{need to add refs to intro... none right now...}
-
 From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
-(or Boolean satisfiability, SAT) has flourished in practice into a success story of modern computer science.
+(or Boolean satisfiability, SAT) has flourished in practice into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
 This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which form today a 
@@
 for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
-in the form of SAT Races and SAT Challenge) have a consistent track record of receiving tens of solver submissions yearly, submitted
+in the form of SAT Races and SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
+ have a consistent track record of receiving tens of solver submissions yearly, submitted
 by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
@@
 In terms of solvers, we provide an overview of solving strategies and other details implemented in the top-performing solvers
-from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings \cite{SC2020}.
+from the competition, complementing the individual solver descriptions available in the 2020 competition proceedings~\cite{SC2020}.
  As for benchmarks, we describe how the 2020 benchmark sets were constructed for each of the competition tracks, with 
@@
 (and to what degree) in the observed state of the art of SAT solving.
-We came up with the following three related metrics conceptually derived
-from the notion of VBS:
+We will here consider the following three related metrics conceptually derived
+from the notion of VBS.
 \begin{description}
@@
 
-Table~\ref{tab:vbsMainALL} renders the just described three metrics applied 
+Table~\ref{tab:vbsMainALL} renders the just-described three metrics applied 
 to the full results of the Main track. We can see that the respective leaderboards 
@@
 
-Amusingly, as can be seen from the ``contributes'' column, the presence of \solver{f2trc-DL} in the schedule is not necessary.
+As can be seen from the ``contributes'' column, the presence of \solver{f2trc-DL} in the schedule is not necessary.
 % The following three lines could be skipped without much harm:

### 2021-02-04 paper/main.tex
added examples for il track

@@
 (typically solving a harder problem than SAT) and is called multiple times before 
-the enclosing tool reaches its final state. \textcolor{red}{Could mention concrete applications here?}
-``Incremental'' here refers to the 
-idea that
-the individual calls to the SAT solver are not independent, but may share 
-a common subset of the input clauses or differ in the presence of additional 
-unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.
+the enclosing tool reaches its final state. 
+``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.
+Examples for applications of incremental SAT solving are Counter-Example Guided Abstraction Refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based Planning~\cite{Balyo:2017:IncrPlanning} or SAT Modulo Theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
 

### 2021-02-04 paper/main.tex
added some missing cites

@@
 
-The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of
- multiple processor cores.
-The benchmarks and the timeout (5000 seconds) are the same as in the Main track \textcolor{red}{repetitive? also mentioned below?}. 
-Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
-These machines have 64 virtual cores and 256GB of memory. In contrast to the 
-Main track, proof logging for unsatisfiable instances is not required in the Parallel track.
+The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of multiple processor cores.
+The benchmarks %and the timeout (5000 seconds) 
+are the same as in the Main track. 
+%\textcolor{red}{repetitive? also mentioned below?}. 
+%Each solver in this track was run on a m4.16xlarge machine from Amazon Web Services (AWS).
+%These machines have 64 virtual cores and 256GB of memory. 
+However, in contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.
 
@@
 
-New this year was the Cloud track, dedicated to evaluating distributed solvers \textcolor{red}{Not sure
-if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. Similar to the
-Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the
-type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
+New this year was the Cloud track, dedicated to evaluating distributed solvers running on multiple machines in a network. 
+%\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
+%Similar to the Parallel track, the solvers ran on the Amazon cloud, but using 100 machines of the type m4.4xlarge, which have 16 virtual cores and 64GB of memory. 
 Communication between the machines is possible using MPI and SSH.
-The wall-clock timeout is 1000 seconds and the same benchmarks were used as in
-the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
+%The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
 
@@
 in the competition.}
-
 The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
@@
 
-As noted above, the Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
+%As noted above, 
+The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
 of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
@@
 
-\textcolor{red}{global note: should try to be consistent with present/past tense...}
+%\textcolor{red}{global note: should try to be consistent with present/past tense...}
 
@@
 
-The classical planning benchmarks were selected from the \emph{satisfying} and
+The classical planning benchmarks were selected from the \emph{Satisfying} and
 \emph{Optimal} tracks of the \emph{International Planning Competitions} 2014
@@
 and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.
-
 In addition to the classical planning problems, we also included SAT formulas
@@
 solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
-and variable-move-to-front \textcolor{red}{screams for a reference...}). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by
+and variable-move-to-front~\cite{Ryan:2004:Thesis}). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by
 \solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.
@@
 The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
-The then award-winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)\textcolor{red}{add ref} and the newer learning rate based branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+The then award-winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
 

### 2021-05-06 paper/main.tex
one cite

@@
 The focus of the traditional Main track is on sequential SAT solvers and their evaluation on structured, non-random benchmarks coming from various application areas.
-To participate in the main track, solvers needed to output certificates both for the satisfiable and the unsatisfiable answer.
+To participate in the Main track, solvers needed to output certificates both for the satisfiable and the unsatisfiable answer.
 Moreover, the source code of the solver had to be made publicly available.
@@
 
-In this section we provide a high-level overview of the results of SAT Competition 2020
+In this section we provide a high-level overview of the results of SAT Competition 2020.
 %We focus on some interesting results.
@@
 
-Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids}),
+Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids},
 performed significantly better that all other solvers submitted to the Main track, see Table~\ref{tab:results}.
@@
 The \solver{32} threaded variant received two awards in this competition: the overall third place and the third best score on unsatisfiable instances. 
-\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.
+\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup,Audemard:2014:LazyClauseExchange,Hamadi:2009:ManySat}.
 
@@
 
-\solver{Painless Maple} received the award for second-best performance on satisfiable instances. Interestingly, it 
-at the same time exhibited  worst performance on unsatisfiable instances. 
+\solver{Painless Maple} received the award for second-best performance on satisfiable instances. 
+Interestingly, \solver{Painless Maple}  
+at the same time exhibits worst performance on unsatisfiable instances. 
 \solver{Painless Maple} integrates the solver \solver{ExMapleLCMDistChronoBT} into the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless}. 
-\solver{Painless Maple} uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses. 
-\solver{Painless Maple} was submitted in two variants \solver{v1} and \solver{v2}. 
+It uses a sharing strategy in which the solvers are divided into those which only export clauses and others which import \emph{and} export clauses and was submitted with two diversification variants \solver{v1} and \solver{v2}.
 \solver{Painless Maple v1} diversifies via hand-crafted heuristic configurations and \solver{Painless Maple v2} diversifies via randomized initialization of branching heuristics~\cite{SC2020}.
@@
 (and to what degree) in the observed state of the art of SAT solving.
-We will here consider the following three related metrics conceptually derived
+We consider here the following three related metrics conceptually derived
 from the notion of VBS.
+
 \begin{description}
-\item[VBS1]
+\item[VBS-1]
 ``The fastest takes it all'':
 For each solver we count the number of times, it was the fastest to solve an instance.
-\item[VBS2]
+\item[VBS-2]
 ``Time aware, but proportional'':
@@
 $T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
-\item[VBS3]
+\item[VBS-3]
 ``Split the point for solving'':
@@
 \end{description}
-We remark that the sum of VBS1 points, as well as VBS3 points, computed across all the solvers
+
+We remark that the sum of VBS-1 points, as well as VBS-3 points, computed across all the solvers
 is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
-This is obvious for VBS1, as exactly one solver scores a point for solving an instance.
-In the case of VBS3, where we discard the information about the solution times, 
+This is obvious for VBS-1, as exactly one solver scores a point for solving an instance.
+In the case of VBS-3, where we discard the information about the solution times, 
 we evenly split the one point reward for solving an instance to those solvers which were successful on it.
 
-In contrast, VBS2 does not have this property as it in general distributes more than one point per instance.
-Similarly to VBS1, it takes the solution time into account,
-and similarly to VBS3 it does not award just the best solver on an instance.
+In contrast, VBS-2 does not have this property as it in general distributes more than one point per instance.
+Similarly to VBS-1, it takes the solution time into account,
+and similarly to VBS-3 it does not award just the best solver on an instance.
 For example, being twice as slow on an instance than the fastest solver results in a half point awarded.
@@
 
-\subsection{Greedy set cover}
+\subsection{Greedy Set Cover}
 Another perspective on how much each solver contributes to the state of the art
@@
 (rather than relying on an oracle to pick one for each instance, as with VBS)
-and looking at how big role each solvers plays in such a schedule. Since constructing 
+and looking at how big a role each solvers plays in such a schedule. Since constructing 
 an optimal schedule tends to be computationally hard, we start here by 
@@
 with the highest ``marginal contribution'' in terms of the number of problems
-the new schedule will be able to solve. This is perhaps best demonstrated on
+the new schedule will be able to solve. We demonstrate this on
 the actual data from the competition, again taking the Main track results.
@@
 
-\subsection{Time-limited schedules}
+\subsection{Time-Limited Schedules}
 
@@
 
-By employing a brute-force approach we first constructed a sequences of schedules 
+By employing a brute-force approach, we first construct a sequences of schedules 
 where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
@@
 
-We complemented this ``uniform time split'' schedule by formulating the schedule construction
-problem as a MaxSMT formula and using the Z3 SMT solver \cite{DBLP:conf/tacas/MouraB08} in its optimization mode \cite{DBLP:conf/sycss/BjornerP14} to solve it.
-For each solver (and its configuration) $S$ we introduced an integer variable $R^S$ denoting 
-the number of seconds $S$ will run in the new schedule. We then constructed a formula with the hard
-constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one 
-soft constraint for every instance $I$ of the form
-\[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
+We complement this ``uniform time split'' schedule by formulating the schedule construction problem as a MaxSMT formula and using the Z3 SMT solver \cite{DBLP:conf/tacas/MouraB08} in its optimization mode \cite{DBLP:conf/sycss/BjornerP14} to solve it.
+For each solver (and its configuration) $S$ we introduce an integer variable $R^S$ denoting the number of seconds $S$ runs in the new schedule. 
+We then construct a formula with the hard constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one soft constraint for every instance $I$ of the form \[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
 where $\mathcal{S}_I$ is the set of solvers which solved the instance $I$ and $T^S_I$ is the time it took solver $S$ to solve $I$ here rounded up to the nearest integer.
@@
 Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
-Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
+Z3 comes up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
 The table is sorted by $R^S$, the time the schedule allocates to individual solvers, and skips the zero entries.
@@
 Given the set of solvers $S$, the set of tuples of size $k$ is defined as follows $P_k := \{ T \mid T \in 2^S \land |T| = k\}$.
-We calculated the PAR-2 score for each VBS created from solver tuples in $P_k$. 
+We calculate the PAR-2 score for each VBS created from solver tuples in $P_k$. 
 In Table~\ref{tab:tuples}, we report on the single best performing $k$-tuple $T_k \in P_k$ ($1 \leq k \leq 7$).
@@
 Contributions to the VBS can be well captured by clustering the instance space into instance families. 
-We evaluated the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
+We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
 and report their place and score in Table~\ref{tab:eval-by-family}. 
@@
 % \end{equation}
-We calculated the \emph{similarity} of the $30$ solvers with the
+We calculate the \emph{similarity} of the $30$ solvers with the
 best average PAR-2 score in the Main track. The results are displayed in
@@
 \solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
-The high similarity suggest that the
+The high similarity suggests that the
 changes they made either result in a very similar behavior or do not have a
@@
 The 2020 version of \solver{CaDiCaL}
-performed worse than the modifications based on the 2019 version and
+performs worse than the modifications based on the 2019 version and
 does not quite fit into any cluster.
@@
 described in the tool suite
-\texttt{benchfeature}\cite{benchfeature}.
+\texttt{benchfeature}~\cite{benchfeature}.
 % \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
@@
 
-The 2020 SAT Competition successfully continued the tradition of the SAT Competition series. In 2020, significant advances
-in SAT solver compared to previous years were observed. Some of the more interesting observations on the winning solving 
+The 2020 SAT Competition successfully continues the tradition of the SAT Competition series. In 2020, significant advances
+in SAT solvers compared to previous years are observed. Some of the more interesting observations on the winning solving 
 strategies include the following.
@@
 solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
-As can be seen in the \emph{Parallel} track, it appear difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$ threaded counterpart.
+As can be seen in the \emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart.
 However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
 It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
-The winner of the \emph{Incremental Library} track showed that it is worth integrating a full solver functionality in the incremental use-case.
+The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use-case.
 

### 2021-05-06 paper/main.tex
Explain table underline; beautify other table

@@
 \end{tabularx}
-\caption{Top 10 Solvers in Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver}
+\caption{Top 10 Solvers in Main, Planning, Parallel and Cloud Tracks: Place~(Pl.), Score (PAR-2) and Number of Solved Instances~(\#) per Solver.
+Three awardees per track underlined.}
 \label{tab:results}
@@
 
-VBS2 highlights as first \solver{Kissat-sat}. Its leading \SI{32.9}{\percent} of total is a bit harder to 
-interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
+The metric VBS2 identifies as the best solver \solver{Kissat-sat}. Its leading score of \SI{32.9}{\percent} of the total
+is a bit harder to interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
 by solving \SI{32.9}{\percent} of the solved instances in the best observed time
@@
 but always being roughly 3 times slower than the VBS. 
-\solver{Kissat-sat} lies obviously somewhere between these two extremes.
+\solver{Kissat-sat} lies (obviously) somewhere between these two extremes.
 
@@
 \begin{tabulary}{\linewidth}{cccL}
-\bf k & \bf Time (s) & \bf Solved & \bf Best Schedule \\
+\bf k & \bf Time\,(s) & \bf Solved & \bf Best Schedule \\
 \hline

### 2021-05-31 paper/stability/benchfeatures/random_sampling_plots.py
removed triangle form stability plot

@@ -97,7 +97,7 @@ def random_sampling_plot(data_frame,original_ranks,original_instances,solver_nam
     # plt.xlabel('Number of randomly removed instances',fontsize=16)
     plt.ylabel('Spearman\'s correlation')
     plt.xlabel('Number of randomly removed instances')
-    plt.errorbar(number_of_removed, correlation_mean, correlation_std, linestyle='None', marker='^',elinewidth=1)
+    plt.errorbar(number_of_removed, correlation_mean, correlation_std, marker='.',elinewidth=1)
     plt.hlines([0.8,0.99,0.6,0.4,0.2],0,max(number_of_removed)+5,linestyle='dashed',color='m')
     plt.grid(True)
 

### 2021-06-01 paper/main.tex
added more detailed planning description

@@
 From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
-(or Boolean satisfiability, SAT) has flourished in practice into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
-This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which form today a 
+(or Boolean satisfiability, SAT) has flourished, in practice, into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
+This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
 central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
@@
 and certified proof logging and checking capabilities, applications of SAT solver technology
-have branched from first breakthrough applications in automated planning, test pattern generation and hardware verification
+have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
 to thousands of different application settings.
@@
 The success of SAT would not be possible without the persistent efforts of the SAT community to further develop the performance and robustness
-of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
+of SAT solvers. The SAT Competition series, with a history dating back to the early 90s, aims to support and provide further incentives 
 for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
@@
 need to solve a sequence of related problems fast, but its answers to the early questions
-may in general influence which questions will follow next.
+may, in general, influence which questions will follow next.
 % E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!
@@
 that transforms the world from some initial state to a goal state. In 1992 Kautz
-and Selman \cite{Kautz1992} proposed to encode planning as satisfiability, constituting
-one of the hallmark early adoptations of SAT solving to solve real-world problems. In
-their encoding the problem of finding a plan of length $i$ (\textit{i.e.,} the
-\emph{makespan}) is translated into a Boolean formula $F_i$ that is satisfiable
-if a plan of length $i$ \emph{or less} exists. In later encodings multiple
-actions can be executed \emph{in parallel} allowing longer plans to be found by
-solving smaller formulas \cite{Rintanen2006, Rintanen2007, Balyo2013}.
-
+and Selman \cite{Kautz1992} proposed to encode planning as satisfiability,
+constituting one of the hallmark early adoptions of SAT solving to solve
+real-world problems. In their encoding the problem of finding a plan of length
+$i$ (\textit{i.e.,} the \emph{makespan}) is translated into a Boolean formula
+$F_i$ that is satisfiable if a plan of length $i$ or less exists.
+Their encoding is called sequential, whereas parallel encodings allow the execution
+of multiple actions in one step~\cite{Rintanen2006, Rintanen2007, Balyo2013}.
 Finding the minimal makespan $i$ for which $F_i$ is satisfiable is important for
 SAT-based planning in general and the generation of this benchmark set in
-particular. The minimal makespan depends on the planning task and the used
-encoding. The hardest formulas that a SAT-based planner has to solve are usually
-the last unsatisfiable $F_i$ before the next higher makespan $i$ is satisfiable
-\cite{Rintanen2006}. Therefore we preferably pick the last unsatisfiable
-makespan for each planning task to generate unsatisfiable instances. For
-planning tasks where this makespan cannot be determined with available
-computational resources, we use a \emph{sequential} encoding, where the minimal
-makespan equals the length of the shortest valid plan. Together with known
-bounds\footnote{Bounds on plan length are available for some planning tasks from
-  the \emph{Optimal track} that have \emph{unit cost} actions.} on the optimal
-plan length we can generate SAT formulas with predetermined satisfiability for
-hard planning problems.
-
+particular.
+% The minimal makespan depends on the planning task and the used
+% encoding.
+The hardest formulas that a SAT-based planner has to solve are usually
+the last unsatisfiable $F_i$ before the next higher makespan $i$ is
+satisfiable~\cite{Rintanen2006}.
+% Therefore we preferably pick the last
+% unsatisfiable makespan for each planning task to generate unsatisfiable
+% instances.
+
+The encodings were generated by two SAT-based planners
+\emph{Madagascar}~\cite{Madagascar14} and \emph{Pasar}~\cite{Pasar19}. We used
+Madagascar both in its default configuration to generate a parallel encoding
+based on $\exists$-step plans and to generate a sequential encoding. Pasar uses
+the \emph{grounding routine} deployed by the well-known planner \emph{Fast
+  Downward}~\cite{FastDownward06} to translate planning tasks into a different
+formalism and then encodes it to SAT using a parallel encoding.
+% For planning tasks where this makespan cannot be determined with
+% available computational resources, we use a \emph{sequential} encoding, where
+% the minimal makespan equals the length of the shortest valid plan. Together with
+% known bounds\footnote{Upper and lower bounds on plan length are available for
+% 	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
+% 	actions.} on the optimal plan length
+%   we can generate satisfiable and unsatisfiable SAT formulas
+%   for hard planning problems.
 %\textcolor{red}{global note: should try to be consistent with present/past tense...}
-
-The encodings were generated by the two SAT-based planners \emph{Madagascar}
-\cite{Madagascar14} and \emph{Pasar} \cite{Pasar19}. We used Madagascar both in
-its default configuration to generate a parallel encoding based on
-$\exists$-step plans and to generate the sequential encoding where needed. Pasar
-uses the \emph{grounding routine} deployed by the well known planner \emph{Fast
-  Downward} \cite{FastDownward06} to translate planning tasks into a different
-formalism and then encodes it to SAT using a parallel encoding.
-
 The classical planning benchmarks were selected from the \emph{Satisfying} and
@@
 \footnote{\url{https://helios.hud.ac.uk/scommv/IPC-14/repository/benchmarksV1.1.zip}}
-and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}.
+and 2018 \footnote{\url{https://bitbucket.org/ipc2018-classical/domains}}. We
+only selected planning domains with \emph{unit cost} and eliminated those that
+% are designed to be challenging for the grounding routine and
+take more than 100 GB of memory to encode into SAT. We ran both Pasar and
+Madagascars $\exists$-configuration with a timeout of 3 hours on the
+remaining instances to find the minimal makespans. For each planning task where
+this process did not timeout, we generated a pair of satisfiable and
+unsatisfiable SAT instances. A lot of instances from this set were not used
+as \solver{Minisat} could solve them in under $10$ minutes.
+% From those we discarded the SAT formulas that \solver{Minisat} can solve in
+% under $10$ minutes.
+We augmented the remaining domains with the last unsatisfiable formulas
+generated for planning task where the minimal makespan could not be found.
+To generate the missing benchmarks we use a \emph{sequential} encoding
+% , where the minimal makespan equals the length of the shortest valid plan
+together with known bounds\footnote{Upper and lower bounds on plan length are available for
+	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
+	actions.} on the optimal plan length.
+
 In addition to the classical planning problems, we also included SAT formulas
-generated by \emph{Tree-REX} \cite{TreeRex19}; a planner for \emph{Hierarchical
+generated by \emph{Tree-REX} \cite{TreeRex19}, a planner for \emph{Hierarchical
 	Task-networks}. In HTN planning the planner is provided with additional domain
 knowledge besides the problem description. The HTN benchmarks were provided by
-the author of \emph{Tree-REX}.
+the solver author.
 
@@
 	\begin{tabular}{llrr}
-\multicolumn{2}{l}{Encoding} & SAT& UNSAT\\
+		\multicolumn{2}{l}{Encoding} & SAT                       & UNSAT       \\
 		\hline\arrayrulecolor{lightgray}
-\textbf{H}  & Tree-REX & 15 & 11\\
-\textbf{P}  & PASAR & 14 & 14\\
-\textbf{ME} & Madagascar $\exists$-step & 5 & 10\\
-\textbf{MS} & Madagascar sequential & 66 & 65\\
-\hline
-&& 100 & 100\\
+		\textbf{H}                   & Tree-REX                  & 15    & 11  \\
+		\textbf{P}                   & Pasar                     & 14    & 14  \\
+		\textbf{ME}                  & Madagascar $\exists$-step & 5     & 10  \\
+		\textbf{MS}                  & Madagascar sequential     & 66    & 65  \\
+		\hline
+		                             &                           & 100   & 100 \\
 	\end{tabular}
@@
 For a complete list of the encoded planning tasks we refer to the
-generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}} 
+generation script\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}}.
 The benchmarks of the Planning track adhere to the following naming convention:
@@
 			\rangle\text{.cnf}}$
+
+The instances of the Planning track are large compared to the Main track
+instances. Using the number of clauses as a metric: out of the $100$ biggest
+instances of both tracks
+% of the main-track
+$86$ belong to the Planning track. The size can be attributed to
+binary clauses. On average, more than $98$\% are binary for
+planning instances. The average for the Main track instances is below $60$\%.
 
@@
 
-\emph{Stable AllUip} resolves additional clauses beyond the 1st Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size or LBD than the 1-UIP clause. 
+\emph{Stable AllUip} resolves additional clauses beyond the First Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size or LBD than the 1-UIP clause. 
 By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of such extended learning attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
@@
 to the full results of the Main track. We can see that the respective leaderboards 
-are generally dominated by \solver{Kissat} and its configurations.
-VBS1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
+are generally dominated by \solver{Kissat} in at least one of its configurations.
+VBS-1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
 in particular on \SI{11.5}{\percent} of all the solved instances.
 
-The metric VBS2 identifies as the best solver \solver{Kissat-sat}. Its leading score of \SI{32.9}{\percent} of the total
-is a bit harder to interpret: A solver can score \SI{32.9}{\percent} of VBS2 total
+The metric VBS-2 identifies as the best solver \solver{Kissat-sat}. Its leading score of \SI{32.9}{\percent} of the total
+is a bit harder to interpret: A solver can score \SI{32.9}{\percent} of VBS-2 total
 by solving \SI{32.9}{\percent} of the solved instances in the best observed time
-and no others. But we know, thanks to its VBS1, that \solver{Kissat-sat} solved \SI{9.8}{\percent}
+and no others. But we know, thanks to its VBS-1, that \solver{Kissat-sat} solved \SI{9.8}{\percent}
 of the solved instances in the best observed time (and some others).
-A solver can also score \SI{32.9}{\percent} of VBS2 total by solving all the solved instances,
+A solver can also score \SI{32.9}{\percent} of VBS-2 total by solving all the solved instances,
 but always being roughly 3 times slower than the VBS. 
@@
 
-Finally, according to VBS3, the best solver is \solver{Kissat} with 13.0 points,
+Finally, according to VBS-3, the best solver is \solver{Kissat} with 13.0 points,
 which amounts to \SI{3.3}{\percent} of the distributed total score.
-The VBS3 metric is generally the most evenly distributed one,
+The VBS-3 metric is generally the most evenly distributed one,
 at least among the first 10 solvers. 

### 2021-06-04 paper/main.tex
added individual amounts for crypto submissions

@@
 
+\newcommand{\curly}[1]{\multirow{3}{*}{$\hspace{-1em}\left\rbrace\begin{array}{r}~\\#1\\~\end{array}\right.$}}
+\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
 \begin{table}[t]
 \centering\small
-\begin{tabular}{llrr}
-\bf Family & \bf Author & \bf Submitted & \bf Selected\\
+\begin{tabularx}{.94\linewidth}{llRrRr}
+\bf Family & \bf Author & \multicolumn{2}{l}{\bf Submitted} & \multicolumn{2}{l}{\bf Selected}\\
 \hline\arrayrulecolor{lightgray}
-0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
-Fermat &  & 8 & 5 \\
-Schur Coloring &  & 4 & 2 \\
-Sum Subset &  & 5 & 2 \\
-\hline
-Anti-Bandwidth & Biere & 187 & 14 \\
-Baseball Lineup & Hickey & 40 & 13 \\
-Bit-Vector & Preiner & 393 & 14 \\
-Cellular Automata & Chowdhury & 20 & 12 \\
-CNF Miter & Manthey & 38 & 7 \\
-Coloring & Oostema & 14 & 14 \\
-Core-based Generator & Hartung & 20 & 14 \\
-Cover & Gacek & 18 & 13 \\
-\hline
-\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
- & Shaw &  &  \\
- & Soos &  &  \\
-\hline
-Discrete Logarithm & Jingchao & 20 & 7 \\
-Edge Matching & Holten & 58 & 7 \\
-Flood-It Puzzle & Stiphout & 40 & 0 \\
-HGen & Guanfeng & 20 & 13 \\
-Hypertree Decomposition & Schidler & 56 & 14 \\
-Influence Maximization & Kochemazov & 20 & 14 \\
-Lam Discrete Geometry & Nejati & 20 & 9 \\
-Polynomial Multiplication & Maoluo & 20 & 8 \\
-Station Repacking & Newman & 20 & 12 \\
-Stedman Triples & Johnson & 23 & 7 \\
-Tensors & Savicky & 20 & 14 \\
-Termination Analysis & Yolcu & 12 & 7 \\
-Timetable & Djamegni & 20 & 14 \\
-Tournament & Heule & 16 & 14 \\
-Vlsat & Bouvier & 36 & 14 \\
+0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & & 2 & \\
+Fermat &  & 8 & & 5 & \\
+Schur Coloring &  & 4 & & 2 & \\
+Sum Subset &  & 5 & & 2 & \\
+\hline
+Anti-Bandwidth & Biere & 187 & & 14 & \\
+Baseball Lineup & Hickey & 40 & & 13 & \\
+Bit-Vector & Preiner & 393 & & 14 & \\
+Cellular Automata & Chowdhury & 20 & & 12 & \\
+CNF Miter & Manthey & 38 & & 7 & \\
+Coloring & Oostema & 14 & & 14 & \\
+Core-based Generator & Hartung & 20 & & 14 & \\
+Cover & Gacek & 18 & & 13 & \\
+%\hline
+\multirow{3}{*}{Cryptography} & Paxian & 50 & \arraycolsep=1pt\curly{106} & 6 & \arraycolsep=1pt\curly{34} \\
+ & Shaw & 20 & & 14 & \\
+ & Soos & 36 & & 14 & \\
+%\hline
+Discrete Logarithm & Jingchao & 20 & & 7 & \\
+Edge Matching & Holten & 58 & & 7 & \\
+Flood-It Puzzle & Stiphout & 40 & & 0 & \\
+HGen & Guanfeng & 20 & & 13 & \\
+Hypertree Decomposition & Schidler & 56 & & 14 & \\
+Influence Maximization & Kochemazov & 20 & & 14 & \\
+Lam Discrete Geometry & Nejati & 20 & & 9 & \\
+Polynomial Multiplication & Maoluo & 20 & & 8 & \\
+Station Repacking & Newman & 20 & & 12 & \\
+Stedman Triples & Johnson & 23 & & 7 & \\
+Tensors & Savicky & 20 & & 14 & \\
+Termination Analysis & Yolcu & 12 & & 7 & \\
+Timetable & Djamegni & 20 & & 14 & \\
+Tournament & Heule & 16 & & 14 & \\
+Vlsat & Bouvier & 36 & & 14 & \\
 \arrayrulecolor{black}
 \hline
-\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
-\end{tabular}
+\multicolumn{2}{r}{$\Sigma$} & 1260 & & 300 & 
+\end{tabularx}
 \caption{Families and amounts of newly submitted instances}
@@
 
-Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Janota:2015:Backbones}. 
+Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Monasson:1999,Janota:2015:Backbones}. 
 The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.

### 2021-06-04 paper/main.tex
ipasir

@@
 
-As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from
-a wide range of different instance families. 
-In order to compile a balanced set of $300$ benchmark instances, we first removed  instances solved by \solver{Minisat} in less than $10$ minutes, thus obtaining a reduced set of $1012$ instances. 
-We considered a maximum of $14$ submissions per author using a procedure detailed as Algorithm~\ref{algo:select}. 
-Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (Lines~3 and~4). 
-If this did not yield a total of $14$ instances, we added instances of yet unknown result (Lines~5--7). 
+As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from a wide range of different instance families. 
+In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances seen in previous competitions, we executed the following steps of \emph{rule-based randomization}.
+
+To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than 10 minutes. 
+From the resulting 1012 instances, we randomly selected $k$ instances per author, with a minimum $k$ such that the result set contains at least 300 instances.
+Algorithm~\ref{algo:select} depicts the details. 
+We randomly selected $7$ satisfiable and $7$ unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of $14$ instances (Lines~5--7). 
 Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
 
-To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
-We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result. 
-Furthermore, we made sure not to select instances of families which are already represented in the set of newly submitted instances and moreover excluded random, agile and planning instances (due to the Planning track).
+We augmented this set with $100$ instances from previous competitions as follows. 
+In order to further balance the amount of satisfiable and unsatisfiable instances in the new benchmark set, we randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances. 
+With additional constraints, we made sure not to select instances of families which are already represented in the set of 300 new instances (cf. Table~\ref{tab:families}). 
+We also excluded random, agile and planning instances (due to the Planning track). 
+The final selection of benchmark instances contains $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result (cf.~Table~\ref{tab:final}).
 
@@
 Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications.
-For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface, ranging from determination of backbone variables to SAT-based planning. 
-For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.
+For evaluating the Incremental Library track, we used six available IPASIR applications, ranging from determination of backbone variables to SAT-based planning. 
+For each application, we individually selected 50 application instances as follows.
 
@@
 
+In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances was often counter-productive and did not lead to a more balanced overall selection of new instances. 
+Moreover, this practice discriminated against authors of purely satisfiable or unsatifiable sets of instances. 
+Also the hardness criterion of 10 \solver{Minisat} minutes was higher than the hardness criterion of 1 \solver{Minisat} minute of the BYOB rule. 
+In future competitions, we will not balance by \emph{satisfiablity} on the author level, we will be more consistent or clear with our \emph{hardness} criteria, and we will specify what it means for an instance to be counted as \emph{unknown}.
+
+The IPASIR interface facilitates the integration of SAT Solvers into incremental applications. 
+In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 
+This calls for the creation of a more diverse and organized repository of applications for incremental SAT solvers. 
+Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
+
 The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolios and to stimulate development of new code-bases. 
@@
 Therefore, the \emph{Portfolio rule} will receive some refinement in future competitions.
-
-Many prominent applications of SAT use an \emph{incremental} SAT solver in their back-end. 
-Those incremental use-cases impose additional challenges on solver authors. 
-The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
 

### 2021-06-04 paper/main.tex
minor things in intro

@@
 From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
-(or Boolean satisfiability, SAT) has flourished, in practice, into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
+(or Boolean satisfiability, SAT) has flourished into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
 This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
@@
 
-The success of SAT would not be possible without the persistent efforts of the SAT community to further develop the performance and robustness
-of SAT solvers. The SAT Competition series, with a history dating back to the early 90s, aims to support and provide further incentives 
-for maintaining and furthering this progress. Organized yearly as an international open event, the SAT competitions (and their variants
-in the form of SAT Races and SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
- have a consistent track record of receiving tens of solver submissions yearly, submitted
+The success of SAT would not be possible without the persistent efforts of the SAT community to further improve the performance and robustness
+of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
+for maintaining this progress. Organized yearly as an international open event, the SAT competitions (and their variants
+in the forms of SAT Races and a SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
+ have a consistent track record in receiving tens of solver submissions yearly, submitted
 by the community at large for obtaining a snapshot of the current state-of-the-art in practical SAT solving. Alongside participating solvers,
@@
 
-This article focuses on the 2020 instantiation of the SAT competitions. 
+This article focuses on the 2020 instantiation of the SAT Competitions. 
 To this end, we provide
@@
 an overview of the benchmarks contributed to the 2020 competition.
-In terms of empirical results we provide further analysis on the results going beyond the standard rankings provided
+In terms of empirical results we provide further analysis on the competition results, going beyond the standard rankings provided
 on the SAT competition web pages.\footnote{\url{https://satcompetition.github.io/2020/}}
@@
 the solving strategies implemented distinctly in the top-ranking solvers in Section~\ref{sec:winners}. 
-Going considerably beyond the plain competition rankings, in Section~\ref{sec:analysis}, we provide an in-depth analysis of the competition 
+Going considerably beyond the plain competition rankings, we provide in Section~\ref{sec:analysis}, an in-depth analysis of the competition 
 data from different perspectives, including correlation analysis of runtime performance of solvers and marginal contributions
@@
 
-Benchmark instances selection in SAT Competition  2020 was realized using GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which is a tool-chain for maintenance and distribution of benchmark instances and instance attributes~\cite{Iser:2018:GBD}.
-Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with desired properties, e.g., instance author, family and result.
-Instance attributes are maintained in publicly available databases, which provide information about all instances used in SAT Competitions since 2006.\footnote{\url{https://gbd.iti.kit.edu}} 
-Benchmark instance identification also simplifies the distribution of instances via the GBD Server.\footnote{\url{https://gbd.iti.kit.edu/file/<gbd-hash>}}
+For data-driven selection and distribution of benchmark instances, we use GBD~Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which facilitates querying for instances with desired properties, e.g., instance author, family, result or solver-runtime~\cite{Iser:2018:GBD}.
+We also run GBD~Tools on a server to distribute benchmark instances and attribute databases.\footnote{\url{https://gbd.iti.kit.edu}}
 
@@
 By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition.
-At least $10$ of these instances are required to be ``interesting'', meaning that the standard Minisat SAT solver
-must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.
+At least $10$ of these instances are required to be ``interesting'', meaning that \solver{Minisat} must not solve it in less than one minute.
 
 As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from a wide range of different instance families. 
-In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances seen in previous competitions, we executed the following steps of \emph{rule-based randomization}.
+In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances from previous competitions, we executed the following steps of \emph{rule-based randomization}.
 
@@
 
-Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Monasson:1999,Janota:2015:Backbones}. 
+Backbone variables~\cite{Monasson:1999,Janota:2015:Backbones} are variables which take the same value in all models of a given SAT instance.
 The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
@@
 
-The IPASIR interface facilitates the integration of SAT Solvers into incremental applications. 
+The IPASIR interface facilitates the integration of SAT solvers into incremental applications. 
 In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 

### 2021-06-04 paper/main.tex
cadical

--- 2021-06-04 paper/main.tex
@@
 
-Finally, the Main Track also included the so-called ``Glucose hack'' sub-track. 
-As in the past several advances in SAT solving required only a small modification of an established solver
-to achieve a considerable contribution, this sub-track encouraged participation 
-of small modifications of the Glucose 3.0 SAT solver. The limit for being considered a ``hack''
-was---somewhat arbitrarily---set to 1000 non-space character edit distance from the sources of Glucose provided by the organizers. 
-Unfortunately, in 2020 there were not enough participants in this sub-track and we do not report on it 
-in the results section.
+The traditional Hack track (est. 2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}. 
+In the past, several advances in SAT solving required only small modifications of an established solver to achieve a considerable contribution. 
+Hack tracks encourage participation of such small modifications. 
+The limit for being considered a ``hack'' was---somewhat arbitrarily---set to 1000 non-space character edit distance from the sources of \solver{Glucose 3}. 
+Unfortunately, in 2020 there were not enough participants in this sub-track such that we do not report on it in the results section.
 
@@
 Apart from the No-limits track, participants were not allowed to submit a portfolio of solvers,
-i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{
-In other words, a submission of a combination of solvers was only possible if all the authors of all the parts
+i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{In other words, a submission of a combination of solvers was only possible if all the authors of all the parts
 were explicitly listed. This means that all the authors had to be notified if such participation
@@
 in 2020.
-By this rule, solver authors are required to submit $20$ new benchmark instances in order to participate in the competition.
-At least $10$ of these instances are required to be ``interesting'', meaning that the standard Minisat SAT solver
-must need more than a minute to solve it and the authors own solver does not run into a timeout for the instance.
-
-As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from a wide range of different instance families. 
-In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances seen in previous competitions, we executed the following steps of \emph{rule-based randomization}.
+By this rule, solver authors are required to submit 20~new benchmark instances in order to participate in the competition.
+At least 10~of these instances are required to be ``interesting'', meaning that \solver{Minisat} must not solve it in less than one minute.
+
+As can be seen in Table~\ref{tab:families}, 27~authors contributed a set of 1260~previously unseen benchmark instances from a wide range of different instance families. 
+In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances from previous competitions, we executed the following steps of \emph{rule-based randomization}.
 
 To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than 10 minutes. 
-From the resulting 1012 instances, we randomly selected $k$ instances per author, with a minimum $k$ such that the result set contains at least 300 instances.
+From the resulting 1012 instances, we randomly selected $k$~instances per author, with a minimum $k$~such that the result set contains at least 300 instances.
 Algorithm~\ref{algo:select} depicts the details. 
-We randomly selected $7$ satisfiable and $7$ unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of $14$ instances (Lines~5--7). 
-Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.
-
-We augmented this set with $100$ instances from previous competitions as follows. 
-In order to further balance the amount of satisfiable and unsatisfiable instances in the new benchmark set, we randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances. 
-With additional constraints, we made sure not to select instances of families which are already represented in the set of 300 new instances (cf. Table~\ref{tab:families}). 
+We randomly selected 7~satisfiable and 7~unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of 14~instances (Lines~5--7). 
+Of the such obtained 308~instances, we randomly removed 8~satisfiable instances, yielding a total of 114~satisfiable, 78~unsatisfiable and 108~instances of unknown result.
+
+We augmented this set with 100 instances from previous competitions as follows. 
+In order to further balance the amount of satisfiable and unsatisfiable instances in the new benchmark set, we randomly selected 21~satisfiable, 57~unsatisfiable and 22~unknown instances. 
+With additional constraints, we made sure not to select instances of families which are already represented in the set of~300 new instances (cf. Table~\ref{tab:families}). 
 We also excluded random, agile and planning instances (due to the Planning track). 
-The final selection of benchmark instances contains $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result (cf.~Table~\ref{tab:final}).
+The final selection of benchmark instances contains 135~satisfiable, 135~unsatisfiable, and 130~instances of unknown result (cf.~Table~\ref{tab:final}).
 
@@
 Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
+
+This year the Hack track was organized for hacks of \solver{Glucose 3}. 
+In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
+The \solver{CaDiCaL-alluip} solver -- which is a modified \solver{CaDiCaL} -- has shown competitive performance in this competitition.
 

### 2021-06-04 paper/main.tex

@@
 explain the requirements for participation % input/output and proof formats,
-and the ranking criteria, as well as
+and the ranking criteria, as well as describe
 the computing infrastructure used for executing the competition.
@@
 The focus of the traditional Main track is on sequential SAT solvers and their evaluation on structured, non-random benchmarks coming from various application areas.
-To participate in the Main track, solvers needed to output certificates both for the satisfiable and the unsatisfiable answer.
-Moreover, the source code of the solver had to be made publicly available.
-
-Solvers not complying with either of the above criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
+
+To participate in the Main track, solvers needed to output certificates for both the satisfiable and the unsatisfiable instances. Moreover, the source code of the solver were required 
+to be made publicly available. 
+Solvers not complying with either of these two criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
 The No-Limits track thus enabled participation of closed-source solvers (not being able or willing to expose the source code for legal or other reasons) 
@@
 However, solvers in No-Limits still competed against all other solvers submitted to the Main Track.
-Thus, to deserve a mention, a No-Limits solver would need to beat all the Main Track participants.
-The No-Limits track was only evaluated with respect to the benchmarks instances which were \emph{newly} submitted to SAT Competition 2020.
-
-The same rules for participation as in Main track applied to the Planning track, in which we evaluated the solvers on 200 benchmarks 
-which all came from the same application domain -- automated planning. 
+Thus, to deserve a mention, a No-Limits solver would need rank among the best-performing solvers among the Main Track participants.
+The No-Limits track was only evaluated with respect  \emph{newly} submitted benchmark instances, i.e., on instances
+which were submitted to SAT Competition 2020.
+
+Complementing the generality advocated by the standard SAT Competition tracks, in which solvers are evaluated
+on a set of benchmarks including instances from various types of different problem domains, for 2020 
+the organizers aimed to experiment with the potential of a more application-specific track,
+each year highlighting a different problem domain where the SAT solving technology helps to advance the state of the art.
+In 2020, the Planning track represented the first trial instantiation of this idea.
+The focus of this track was specifically on efficiently solving
+instances arising from the domain of SAT-based automated planning.\textcolor{red}{Add references} 
+Automated planning was chosen as the target problem domain of this first instantiation of the domain-specific tracks
+due to its centrality as oneof the first breakthrough applications of SAT solvers.
+To this end, solvers participating in the Planning
+track were evaluated on 200 benchmark instances encoding planning problems.
+The same rules for participation as in the Main track applied to the Planning track.
 Solvers submitted to the Main track automatically participated in the Planning track.
-It is envisioned that also in the future there will be an ``application promotion'' track,
-each time highlighting a different area where the SAT solving technology helps to advance the state of the art.
-
-The traditional Hack track (est. 2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}. 
+
+The traditional Hack track (est. 2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}\textcolor{red}{Add reference}. 
 In the past, several advances in SAT solving required only small modifications of an established solver to achieve a considerable contribution. 
 Hack tracks encourage participation of such small modifications. 
-The limit for being considered a ``hack'' was---somewhat arbitrarily---set to 1000 non-space character edit distance from the sources of \solver{Glucose 3}. 
+The limit for being considered a ``hack'' was---somewhat arbitrarily\footnote{The specific threshold for edit distance is not central here; the idea is essentially to only allow relatively small changes to the Glucose
+code base, i.e., ``quick hacks'' to Glucose.}---set to 1000 non-space character edit distance from the sources of \solver{Glucose 3}. 
 Unfortunately, in 2020 there were not enough participants in this sub-track such that we do not report on it in the results section.

### 2021-06-05 paper/main.tex
fixed all solver-names reaching into margin

@@
 
-Four solvers participating in the Main track, namely \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trial}, and \solver{CMS-ccnr-lsids},
-performed significantly better that all other solvers submitted to the Main track, see Table~\ref{tab:results}.
+The four solvers \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trail}, and \solver{CMS-ccnr-lsids} performed significantly better that all other solvers submitted to the Main track (cf.
+Table~\ref{tab:results}).
 Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
@@
 Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
-compared to \solver{CaDiCaL-alluip-trial}, but solved various formulas much more quickly. 
+compared to \solver{CaDiCaL-alluip-trail}, but solved various formulas much more quickly. 
 Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.
@@
 details about \solver{Kissat} are given in Section~\ref{sec:kissat}.
-The solvers \solver{CaDiCaL-trial}
+The solvers \solver{CaDiCaL-trail}
 and \solver{f2trc-s} placed, respectively, second and third in the Main UNSAT track.
@@
 
-The competition in the Planning Track was more tight. \solver{CaDiCaL-alliup-trial}, the winning solver, 
-solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. Their PAR-2 score is 
+The competition in the Planning Track was more tight. The winning solver \solver{CaDiCaL-alliup-trail} solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. 
+Their PAR-2 score is 
 quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtimes
@@
 Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} and Gaussian elimination, respectively. 
-\solver{Painless-MCOMSPS-STR} uses an all-to-all strategy for clause sharing with a fixed-size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
+Regarding sharing, \solver{Painless-MCOMSPS-STR} uses an all-to-all strategy with a fixed-size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
 

### 2021-06-05 paper/main.tex
touched again kissat description in sec. 5

@@
 Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-Since conflict-rate has been observed to be too unstable for the use-case, \solver{Kissat} uses a new unit called ``ticks'', which is based on the approximate number of cache-line accesses, to measure the length of two alternating restart-modes~\cite{Biere:SC2020}.
-
-Furthermore, \solver{Kissat} exploits autarkies to account for saved phases. 
+Since conflict-number has been observed to be too unstable for measuring the length of two alternating restart-modes, \solver{Kissat} uses the new unit ``ticks'' which approximates the number of cache-line accesses in unit-propagation~\cite{Biere:SC2020}.
+
+\solver{Kissat} also exploits autarkies to account for saved phases. 
 In order to keep valuable information of saved phases, before each rephasing step, \solver{Kissat} computes the largest autarky for the assignment implied by the current saved phases~\cite{Kiesl:2019:Autarkies}.

### 2021-06-05 paper/main.tex
additional challenges in distributed sat solving

@@
 winner of the Parallel Track in 5000 seconds, which shows the potential of distributed SAT solving. 
-The other four participants performed significantly worse. This is likely due to the initial challenges
-in developing a distributed solver. 2020 was the first year of this track. We expect this gap to turn smaller in 
-forthcoming SAT competitions.
+The other four participants performed significantly worse. 
+The massive parallelism in distributed SAT solving imposes additional challanges on scalable information sharing and search diversification. 
+Since 2020 was the first year of this track, we expect a tighter competition in the future.
 

### 2021-06-05 paper/main.tex
disqulified solvers and further stats

@@
 
-To participate in the Main track, solvers needed to output certificates for both the satisfiable and the unsatisfiable instances. Moreover, the source code of the solver were required 
-to be made publicly available. 
+To participate in the Main track, solvers needed to output certificates for both the satisfiable and the unsatisfiable instances. 
+Moreover, the source code of the solver were required to be made publicly available. 
 Solvers not complying with either of these two criteria were only evaluated in a so-called No-Limits track and were not eligible for the Main track awards.
@@
 as well as portfolio solvers (combining two or more core SAT solvers developed by different groups of authors; c.f.~Sect.~\ref{sec:rules}).
+Without limit, submissions could be solvers that use a lookup table or similar to determine solutions. 
+Thus, the No-Limits track was only evaluated with respect to \emph{newly} submitted benchmark instances, i.e., on instances which were submitted to SAT Competition~2020.
+
 However, solvers in No-Limits still competed against all other solvers submitted to the Main Track.
 Thus, to deserve a mention, a No-Limits solver would need rank among the best-performing solvers among the Main Track participants.
-The No-Limits track was only evaluated with respect  \emph{newly} submitted benchmark instances, i.e., on instances
-which were submitted to SAT Competition 2020.
+The top ranked solvers in the No-Limits track were the same as in the Main track. 
+This also indicates the stability of results under the exclusion of old benchmark instances.
 
@@
 
+We evaluated all 64 submitted solver configurations of which eight have been explicitly submitted to the No-Limits track, and four configurations were demoted to the No-Limits track due to wrong certificates.
+A total of six configurations got disqualified due to wrong answers. 
+This left us with 46 configurations of 22 solvers inluding one Glucose hack.
+
 \subsubsection{Incremental Library Track}
@@
 
+In this competition, two of the six submissions got disqualified, such that we had only four solvers competing in the Incremental track.
+
 \subsubsection{Parallel Track}
@@
 
+In the Parallel track, we evaluated ten solvers (in 14 configurations) out of which three solvers got disqualified due to wrong answers.
+
 \subsubsection{Cloud Track}
@@
 %The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
+We evaluated six solvers in this track.
 
@@
 
+The first instantiation of an Application track has been a Planning track. 
+The results show that different solvers take the lead when we only evaluate for a single application. 
+We intend to run further instantiations of the Application track. 
+In the next competition, we will compile a set of 200 cryptographic benchmark instances for a Crypto track.
+
 The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolios and to stimulate development of new code-bases. 

### 2021-06-08 paper/main.tex
..

@@
 have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
-to thousands of different application settings.
+to thousands of different application settings. \textcolor{red}{Add various references to the several things in this sentence}
 
@@
 of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
-for maintaining this progress. Organized yearly as an international open event, the SAT competitions (and their variants
+for maintaining this progress. Organized yearly as an international open event, SAT Competitions (and their variants
 in the forms of SAT Races and a SAT Challenge)~\cite{DBLP:journals/amai/SimonBH05,DBLP:conf/sat/BerreS03,DBLP:conf/sat/BerreS04,DBLP:journals/aim/JarvisaloBRS12,DBLP:journals/ai/BalintBJS15,DBLP:conf/aaai/BalyoHJ17,DBLP:journals/jsat/HeuleJS19}
@@
 
-We evaluated all 64 submitted solver configurations of which eight have been explicitly submitted to the No-Limits track, and four configurations were demoted to the No-Limits track due to wrong certificates.
-A total of six configurations got disqualified due to wrong answers. 
-This left us with 46 configurations of 22 solvers inluding one Glucose hack.
+We evaluated all 64 solver submissions (including different configurations of specific solvers) 
+to the Main track. Out of the 64 solvers, eight were explicitly submitted to the No-Limits track. Four solvers
+ were demoted to the No-Limits track due to outputting invalid unsatisfiability proof certificates. 
+Six solvers were disqualified due to outputting truth assignments which did not satisfy the corresponding benchmark instance.
+This left us with 46 configurations of 22 solvers, inluding only one Glucose hack.
 
@@
 
-In the Incremental Library track we mimic scenarios
+In the Incremental Library track the underlying idea is to mimic scenarios
 where a SAT solver is used as a back-end solver in a more complex tool
@@
 the enclosing tool reaches its final state. 
-``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.
-Examples for applications of incremental SAT solving are Counter-Example Guided Abstraction Refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based Planning~\cite{Balyo:2017:IncrPlanning} or SAT Modulo Theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
-
-Instead of using or extending the DIMACS input format, we realize the Incremental Library track
-by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
-for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
+``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
+Examples for applications of incremental SAT solving are counterexample-guided eastraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning} and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
+
+Instead of using or extending the DIMACS input format, in the the Incremental Library track
+a general incremental interface called IPASIR (Re-entrant Incremental Solver API) 
+is employed~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
 enclosing tool on its own benchmark and communicate with the competing SAT solver 
@@
 %
-Not only does the SAT solver in this track
-need to solve a sequence of related problems fast, but its answers to the early questions
-may, in general, influence which questions will follow next.
+SAT solvers submitted to this track need hence implement the require interface.
+Furthermore, it should be noted that the solutions output by a solver may, in general, influence
+the fortchoming invocations of the solver.
 % E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!
 
-In this competition, two of the six submissions got disqualified, such that we had only four solvers competing in the Incremental track.
+Six solver were submitted to the Incremental Library track.
+Two of the six solvers were disqualified due to outputting wrong answers.
 
@@
 
-The Parallel track evaluates the runtime performance in wall-clock time of SAT solvers making use of multiple processor cores.
+The Parallel track evaluates the runtime performance of SAT solvers making use of multiple processor cores
+in terms of wall-clock time.
 The benchmarks %and the timeout (5000 seconds) 
@@
 %These machines have 64 virtual cores and 256GB of memory. 
-However, in contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.
-
-In the Parallel track, we evaluated ten solvers (in 14 configurations) out of which three solvers got disqualified due to wrong answers.
+In contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.
+
+A total of 14 solver configurations, based on 10 solvers, were submitted to the Parallel track.
+Three solver configurations were disqualified due to wrong answers.
 
@@
 
-New this year was the Cloud track, dedicated to evaluating distributed solvers running on multiple machines in a network. 
+The Cloud track was a new development in the SAT Competitions for 2020.
+The track focuses on  evaluating distributed solvers running on multiple machines in a network. 
 %\textcolor{red}{Not sure if terms ``distributed'' vs ``parallel'' are clear, could be more explicitly explained?}. 
@@
 %The wall-clock timeout is 1000 seconds and the same benchmarks were used as in the Main and Parallel track. \textcolor{red}{repetitive? also mentioned below?}
-We evaluated six solvers in this track.
+We received six solver submissions to the Cloud track.
 
@@
 The following requirements were imposed for 
-participating in the competition.
+participating in SAT Competition 2020.
 
@@
 A short system description was required for each solver submission,
-including a list of all the solver's authors and explaining any non-standard algorithmic
-techniques and data structures, as well as references to the relevant literature.
-These system descriptions have been collected and published in the competition
-proceedings \cite{SC2020}.
+including a list of all  authors involved in developing the solver,  description of any non-standard algorithmic
+techniques and data structures implemented in the sovler, as well as references to the relevant literature.
+These system descriptions have been collected and made available publically in the non-refereed competition
+proceedings~\cite{SC2020}.
 
 \paragraph{Benchmarks}
-To participate in the Main track, each team had to submit 20 new benchmark instances.
-This rule guaranteed that the competition could be run on instances mostly unseen to the solver
+The authors of solvers participating in the Main track were required 
+  to submit 20 ``new'' benchmark instances.
+The exact details of this rule are further explained in Section~\ref{sec:byob}.
+In short, this rule guaranteed that the competition could be run on instances mostly unseen to the solver
 developers prior to the competition. Moreover, by making these benchmarks publicly available
@@
 of diverse problems to target with the next developments.
-
-The exact details of this rule are further explained in Section~\ref{sec:byob}.
-Also the descriptions of the benchmarks have been published \cite{SC2020}.
+The descriptions of the submitted benchmarks are also made available in the competition proceedings~\cite{SC2020}.
 
@@
 The benchmark instances were presented to the solvers in the de facto standard
-DIMACS input format for propositional formulas in conjunctive normal form.
+DIMACS input format for propositional formulas in conjunctive normal form (CNF).
 A simple extension of this format was to be adhered to when printing 
@@
 
-Proofs of unsatisfiability were to be emitted in the DRAT format~\cite{DRATtrim},
-either in its textual version, which is also very similar to the DIMACS input format,
-or in a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
+Where required, proofs of unsatisfiability were to be output in the DRAT format~\cite{DRATtrim},
+either in its textual version---which is also very similar to the DIMACS input format---or 
+in a more compact binary version (for more details, see \cite{satComp2020www}, Unsat Certificates).
 %
@@
 
-Each participant was allowed to be an author of at most four different sequential solvers,
+Due to the shear number of participants in the SAT Competitions, in order to make it
+feasible to run the whole competition, specific limits were set on the number of submitted solvers.
+In particular, each solver author was allowed to be an author of at most four different sequential solvers,
 two different parallel solvers, and one ``Glucose hack'' sub-track solver.
@@
 as specified by the previous rule.}
-
 This rule is mainly meant to encourage the SAT community to invest more effort into developing new solver code bases.
 Moreover, while we acknowledge that research on solver selection tools that typically orchestrate portfolio solvers 
-is interesting, it is not the focus of the SAT competition.
+is interesting, it is not at present the focus of the SAT competitions.
 
@@
 to solve a particular instance and twice the time limit, i.e.~\num{10000} points,
-if the instance was not solved. This means that lowers scores are better.
-We generally report the \emph{average score} of each solver across a benchmark set.
-
-A SAT solver was disqualified if it produced a wrong answer. 
-Specifically, if a solver reported ``unsatisfiable'' on an instance that 
+if the instance was not solved. In particular, this mean that the lower the score a solver
+obtained, the better the solver performs.
+%We generally report the \emph{average score} of each solver across a benchmark set.
+
+A  solver was disqualified if it produced a wrong answer:
+specifically, if a solver reported ``unsatisfiable'' on an instance that 
 was proven to be satisfiable by some other solver, or reported ``satisfiable'' 
 but provided a wrong certificate. Solvers disqualified from the competition were
-not eligible to win any award.
+not eligible for awards.
 
@@
 
-In all tracks solvers were required to output a model to certify recognizing a satisfiable instance.
+In all tracks solvers were required to output a solution (a satisfying truth assignment, i.e., a model on the instance in question)
+ to certify recognizing a satisfiable instance.
 On the other hand, 
 certificates for unsatisfiable instances (proofs) were required only 
-in the Main track (besides the No Limits track).
+in the Main track (besides the No-Limits track).
 In some cases, a solver output the correct result, but the respective certificate was wrong. 
-Such solvers were demoted to the No-limits track of the competition.
+Such solvers were demoted to the No-Limits track of the competition.
 
@@
 was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
-Afterwards, an independent, formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}, 
+Afterwards, an independent formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}
 was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
-In the Main track, we only considered solved those unsatisfiable formulas that 
-could be validated by {\tt DRAT-trim}.
-There were several cases where {\tt cake\_lpr} ran out of resources before being able to 
-confirm after {\tt DRAT-trim}. However, there was no case where {\tt DRAT-trim} would accept
+In the Main track, only those unsatisfiable benchmark instances for which the proof emitted by a specific solver
+could be validated by {\tt DRAT-trim} were considered solved by the  solver.
+It should be noted that, while there were several cases where {\tt cake\_lpr} ran out of resources before 
+there was no case where {\tt DRAT-trim} would accept
 a proof and {\tt cake\_lpr} would later disagree with the verdict.
+\textcolor{red}{This is pretty vague... does not really say if there were proofs that could not be validated with DRAT-trim??}
 
@@
 The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
-(In the Main track, validation then continued for up to \SI{45000}{\second}.)
+In the Main track, proof validation was limited to \SI{45000}{\second} per proof.)
 The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
@@
 This could have resulted in some solvers not ``daring'' to use the full \SI{128}{\giga\byte}
-in the competition.}
+in the competition. We do not, however, have concrete evidence to support this possibility.}
+
 The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
 (4-Core) processors and \SI{24}{\giga\byte} of RAM.
-
-%As noted above, 
 The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
-of memory, while the Cloud track was run on AWS m4.4xlarge machines with 16 virtual CPUs and 64 GB of
+of memory, while the Cloud track was run on AWS\textcolor{red}{Was AWS spelled out a single time before this? I now notice that
+we do not really mention Amazon much, should we mention it more specifically?}
+ m4.4xlarge machines with 16 virtual CPUs and 64 GB of
 memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

### 2021-06-16 paper/main.tex
explain no proof rule for Parallel

@@
 The success of SAT would not be possible without the persistent efforts of the SAT community to further improve the performance and robustness
-of SAT solvers. The SAT Competition series, with a history dating back to early 90s, aims to support and provide further incentives 
+of SAT solvers. The SAT Competition series, with a history dating back to the early 90s, aims to support and provide further incentives 
 for maintaining this progress. Organized yearly as an international open event, SAT Competitions (and their variants
@@
 However, solvers in No-Limits still competed against all other solvers submitted to the Main Track.
-Thus, to deserve a mention, a No-Limits solver would need rank among the best-performing solvers among the Main Track participants.
-The top ranked solvers in the No-Limits track were the same as in the Main track. 
+Thus, to deserve a mention, a No-Limits solver would need to rank among the best-performing solvers among the Main Track participants.
+In 2020, the top ranked solvers in the No-Limits track were the same as in the Main track. 
 This also indicates the stability of results under the exclusion of old benchmark instances.
@@
 Automated planning was chosen as the target problem domain of this first instantiation of the domain-specific tracks
-due to its centrality as oneof the first breakthrough applications of SAT solvers.
+due to its centrality as one of the first breakthrough applications of SAT solvers.
 To this end, solvers participating in the Planning
@@
 code base, i.e., ``quick hacks'' to Glucose.}---set to 1000 non-space character edit distance from the sources of \solver{Glucose 3}. 
-Unfortunately, in 2020 there were not enough participants in this sub-track such that we do not report on it in the results section.
+Unfortunately, in 2020 there were not enough participants in this sub-track and so we do not report on it in the results section.
 
@@
 Six solvers were disqualified due to outputting truth assignments which did not satisfy the corresponding benchmark instance.
-This left us with 46 configurations of 22 solvers, inluding only one Glucose hack.
+This left us with 46 configurations of 22 solvers, including % only 
+one Glucose hack.
 
@@
 ``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
-Examples for applications of incremental SAT solving are counterexample-guided eastraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning} and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
+Examples for applications of incremental SAT solving are counterexample-guided eastraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
+multi-agent path finding~\cite{DBLP:conf/ijcai/Surynek19}, and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
 
@@
 Furthermore, it should be noted that the solutions output by a solver may, in general, influence
-the fortchoming invocations of the solver.
+the forthcoming invocations of the solver.
 % E.g. Smaller unsat cores may allow the enclosing tool to converge using fewer SAT calls!
@@
 %These machines have 64 virtual cores and 256GB of memory. 
-In contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.
+In contrast to the Main track, proof logging for unsatisfiable instances is not required in the Parallel track.\footnote{
+Although this would, of course, be desirable, for the same reasons as in the Main track, 
+currently there are no good solutions known for efficient proof logging of parallel solvers.}
 
@@
 
-For data-driven selection and distribution of benchmark instances, we use GBD~Tools\footnote{\url{https://pypi.org/project/gbd-tools/}} which facilitates querying for instances with desired properties, e.g., instance author, family, result or solver-runtime~\cite{Iser:2018:GBD}.
-We also run GBD~Tools on a server to distribute benchmark instances and attribute databases.\footnote{\url{https://gbd.iti.kit.edu}}
+For data-driven selection of benchmark instances, we used GBD~Tools\footnote{\url{See https://pypi.org/project/gbd-tools/}} which facilitates querying for instances with desired properties, e.g., by instance author, family, result or solver runtime~\cite{Iser:2018:GBD}.
+We also use GBD~Tools for distributing benchmark instances and their attributes to the general public.\footnote{See \url{https://gbd.iti.kit.edu}}
 
@@
 in 2020.
-By this rule, solver authors are required to submit 20~new benchmark instances in order to participate in the competition.
-At least 10~of these instances are required to be ``interesting'', meaning that \solver{Minisat} must not solve it in less than one minute.
-
-As can be seen in Table~\ref{tab:families}, 27~authors contributed a set of 1260~previously unseen benchmark instances from a wide range of different instance families. 
-In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances from previous competitions, we executed the following steps of \emph{rule-based randomization}.
-
-To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than 10 minutes. 
-From the resulting 1012 instances, we randomly selected $k$~instances per author, with a minimum $k$~such that the result set contains at least 300 instances.
-Algorithm~\ref{algo:select} depicts the details. 
-We randomly selected 7~satisfiable and 7~unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of 14~instances (Lines~5--7). 
-Of the such obtained 308~instances, we randomly removed 8~satisfiable instances, yielding a total of 114~satisfiable, 78~unsatisfiable and 108~instances of unknown result.
-
-We augmented this set with 100 instances from previous competitions as follows. 
-In order to further balance the amount of satisfiable and unsatisfiable instances in the new benchmark set, we randomly selected 21~satisfiable, 57~unsatisfiable and 22~unknown instances. 
-With additional constraints, we made sure not to select instances of families which are already represented in the set of~300 new instances (cf. Table~\ref{tab:families}). 
+By this rule, solver authors are required to submit 20 ``new'' benchmark instances to accompany a solver submission in order to participate in the competition. 
+New refers to the fact that instances contained in benchmark sets from earlier SAT Competitions are not allowed.
+Furthermore, a least 10 of the required 20 instances are required to be ``interesting'', interpreted in loose terms by
+ the standard \solver{Minisat} SAT solving needing at least one minute of runtime (on typical computing hardware) to solve an instance.
+It should be noted that new benchmarks could be submitted to the competition without needing to submit a solver.
+As a results, as detailed in Table~\ref{tab:families}, 27 authors contributed a set of 1260 new benchmark instances from a wide range of different instance families.
+
+We decided to include a total of 
+300 new benchmarks and a further 100 benchmarks from previous SAT Competitions to the main benchmark set of the 2020 competition.
+Key aims of benchmark selection is to ensure that (i) the benchmark set includes enough many relatively hard-to-solve instances
+in order to differentiate the overall runtime performances of the competing solvers (without actually running the competing solvers during benchmark selection); 
+(ii)~the number of benchmarks included in the benchmark set from different problem domains 
+is balanced across the problem domains, and that (iii) the benchmark set is also balanced in terms of the number of unsatisfiable and satisfiable instances included in the set.
+
+To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than 10 minutes.\footnote{We note that
+the limit of 10 minutes is again somewhat arbitrary.
+This 10-min runtime hardness filter essentially aims to make sure that enough instances are included in the final benchmark set which allow for distinguishing in terms of relative performance between the best-performing competing solvers.
+Unfortunately this time the 10-min limit enforced  was much greater that the requirements imposed for  ``interesting'' benchmark instances
+by the BYOB rule. It could be more sensible to impose the some 10-min limited also for an instance being ``interesting''. However, this would require more efforts
+at least in terms of computation times from the solver authors in order to construct a set of 20 interesting new benchmarks required by the BYOB rule.}
+
+From the resulting 1012 instances, in order to obtain a balanced benchmark set, 
+we randomly selected $k$~instances per author using the value  $k$ which ensured that  the resulting set contains at least 300 instances.
+This \emph{rule-based randomization} procedure is detailed as
+Algorithm~\ref{algo:select}. Specifically,
+we randomly selected 7~satisfiable and 7~unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of 14~instances (Lines~5--7). 
+Of the such obtained 308~instances, we randomly removed 8~satisfiable instances, yielding a total of 114~satisfiable, 78~unsatisfiable and 108~instances of unknown satisfiability
+status.
+
+We augmented the then obtained set of 300 new benchmarks with 100 instances from previous SAT competitions as follows. 
+In order to further balance the number of satisfiable and unsatisfiable instances in the new benchmark set, we randomly selected 21~satisfiable, 57~unsatisfiable and 22~unknown instances. 
+With additional constraints, we made sure not to select instances from benchmark 
+families which are already represented in the set of~300 new instances (cf. Table~\ref{tab:families}). 
 We also excluded random, agile and planning instances (due to the Planning track). 
-The final selection of benchmark instances contains 135~satisfiable, 135~unsatisfiable, and 130~instances of unknown result (cf.~Table~\ref{tab:final}).
+The final main benchmark set  contains 135~satisfiable, 135~unsatisfiable, and 130~instances of ``unknown'' status (cf.~Table~\ref{tab:final}).
 
@@
 \subsection{Planning Instances}
-Classical planning is the problem of finding a sequence of actions -- a plan --
-that transforms the world from some initial state to a goal state. In 1992 Kautz
+Classical planning is the problem of finding a sequence of actions---a plan---that 
+transforms the world from some initial state to a goal state. In 1992 Kautz
 and Selman \cite{Kautz1992} proposed to encode planning as satisfiability,
@@
 of multiple actions in one step~\cite{Rintanen2006, Rintanen2007, Balyo2013}.
-Finding the minimal makespan $i$ for which $F_i$ is satisfiable is important for
+Finding the smallest makespan $i$ for which $F_i$ is satisfiable is important for
 SAT-based planning in general and the generation of this benchmark set in
@@
 The hardest formulas that a SAT-based planner has to solve are usually
-the last unsatisfiable $F_i$ before the next higher makespan $i$ is
+the last unsatisfiable $F_i$ before the next higher makespan $i+1$ is
 satisfiable~\cite{Rintanen2006}.
@@
 
-The encodings were generated by two SAT-based planners
+For the Planning track,
+the benchmark instances were generated using two SAT-based planners
 \emph{Madagascar}~\cite{Madagascar14} and \emph{Pasar}~\cite{Pasar19}. We used
@@
 this process did not timeout, we generated a pair of satisfiable and
-unsatisfiable SAT instances. A lot of instances from this set were not used
+unsatisfiable SAT instances. A significant number of instances from this set were not used
 as \solver{Minisat} could solve them in under $10$ minutes.
@@
 
-In addition to the classical planning problems, we also included SAT formulas
+In addition to the classical planning problems, we also included SAT instances
 generated by \emph{Tree-REX} \cite{TreeRex19}, a planner for \emph{Hierarchical
-	Task-networks}. In HTN planning the planner is provided with additional domain
+	Task-networks} (HTN). In HTN planning the planner is provided with additional domain
 knowledge besides the problem description. The HTN benchmarks were provided by
@@
 % - all 200 above 90\% binary clauses and half have above 99%
-The instances of the Planning track are large compared to the Main track
-instances. Using the number of clauses as a metric: out of the $100$ biggest
-instances of both tracks
+The instances of the Planning track are large in size compared to the Main track
+instances. Using the number of clauses as a metric, out of the $100$ largest
+instances across both tracks,
 % of the main-track
-$86$ belong to the Planning track. The large size can mainly be attributed to
-binary clauses. On average, more than $98$\% of the clauses are binary for
+$86$ belong to the Planning track benchmark set. The large size of Planning track instances
+can mainly be attributed to large numbers of
+binary clauses that SAT encodings of planning problems naturally produce. 
+On average, more than $98$\% of the clauses are binary for
 planning instances. The average for the Main track instances is below $60$\%.
@@
 			\rangle\text{.cnf}}$
-
-The instances of the Planning track are large compared to the Main track
-instances. Using the number of clauses as a metric: out of the $100$ biggest
-instances of both tracks
-% of the main-track
-$86$ belong to the Planning track. The size can be attributed to
-binary clauses. On average, more than $98$\% are binary for
-planning instances. The average for the Main track instances is below $60$\%.
 

### 2021-06-17 paper/main.tex
results section

@@
 
-The traditional Hack track (est. 2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}\textcolor{red}{Add reference}. 
+The traditional Hack track (established 
+2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}\textcolor{red}{Add reference}. 
 In the past, several advances in SAT solving required only small modifications of an established solver to achieve a considerable contribution. 
@@
 
+The Incremental Library track was first introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
 In the Incremental Library track the underlying idea is to mimic scenarios
@@
 
-\subsection{Incremental Library Applications and Instances}
-
-The Incremental Library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
+\subsection{Incremental Library Track Benchmarks}
+
 Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications.
-For evaluating the Incremental Library track, we used six available IPASIR applications, ranging from determination of backbone variables to SAT-based planning. 
-For each application, we individually selected 50 application instances as follows.
-
-\paragraph{Backbone Variables}
+For evaluating solvers participating in the 
+the Incremental Library track, we used six available IPASIR applications.
+For each of the six applications, we individually selected 50 application instances as follows.
+
+\paragraph{Backbone Computation}
 
 Backbone variables~\cite{Monasson:1999,Janota:2015:Backbones} are variables which take the same value in all models of a given SAT instance.
-The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
+The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the so-called 
+dual rail encoding~\cite{Balyo:2015:SATRace}.
 We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.
@@
 
-Essential variables are defined to be those variables which have to be assigned in all partial models of a formula (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
+Variables which have to be assigned in all partial models of a formula as \emph{essential} (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
 The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
-We used the same $50$ easy satisfiable instances as in backbone detection to evaluate solver performance with this application.
+For this applicaiton, we used the same $50$  satisfiable instances as for  backbone computation.
 
@@
 The application \textsf{genipalsp} determines longest simple paths in a graph~\cite{Balyo:2019:LSP}. 
-We selected $50$ easy LSP instances for our evaluation.\footnote{\url{http://algo2.iti.kit.edu/kalp/}}
+We selected $50$ LSP instances for our evaluation.\footnote{\url{http://algo2.iti.kit.edu/kalp/}}
 
@@
 
-The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with activation literals which are input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
-The MaxSAT problem is then solved by incrementally minimizing the bound of that cardinality constraint. 
+The application \textsf{genipamax} solves partial MaxSAT problems by augmenting soft clauses with relaxation (or blocking) variables
+which are input to a cardinality constraint~\cite{Philipp:2015:PBLib}. 
+The MaxSAT problem is then solved by incrementally minimizing the bound of the cardinality constraint. 
 For this application, we selected $50$ instances from \texttt{MaxSAT Evaluation 2019}.\footnote{\url{https://maxsat-evaluations.github.io/2019/}}
@@
 \paragraph{Quantified Boolean Formulas (QBF)}
-\textsf{Ijtihad} is a QBF solver which uses counter\-example-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
+\textsf{Ijtihad} is a QBF solver which uses counterexample-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
 Here we used $50$ instances from \texttt{QBF Evaluation 2019}.\footnote{\url{http://www.qbflib.org/qbfeval19.php}}
@@
 \paragraph{Planning (SAS+)}
-We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counter\-example-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
+We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counterexample-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
 
@@
 %We focus on some interesting results.
-Later on, we give more details about the solvers, including the key and new solving techniques
-(Section~\ref{sec:winners}) and more in-depth analysis of the results (Section~\ref{sec:analysis}).
-
-The four solvers \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trail}, and \solver{CMS-ccnr-lsids} performed significantly better that all other solvers submitted to the Main track (cf.
-Table~\ref{tab:results}).
+Later on, we will provide overview of some of the key and new solving techniques implemented in best-performing solvers
+(Section~\ref{sec:winners}) and as well as more in-depth analysis of the competition results (Section~\ref{sec:analysis}).
+
+\section{Main Track}
+
+Starting with the Main track, 
 Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
 10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
-The four top solvers all have a different code base, which is rare and has not been observed for many years.
-Also, in recent competitions, the top solvers were much closer to each other in terms of runtime performance.
-The winning solver is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that 
+The best-performing  solver overall on the combination of satisfiable and unsatisfiable instances
+is \solver{Kissat-sat} and the runner-up is \solver{Relaxed-newTech}. Notice that
 \solver{Relaxed-newTech} solved more instances within the 2000-second limit.
-Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two fewer instances
-compared to \solver{CaDiCaL-alluip-trail}, but solved various formulas much more quickly. 
-Since the SAT Competition nowadays applies the PAR-2 score for ranking solvers, such cases have been observed several times.
+Third place, based on the PAR-2 score, went to \solver{CMS-ccnr-lsids}. It solved two  instances less than
+\solver{CaDiCaL-alluip-trail}, but on the other hand solved various formulas more quickly.
+Similar observations have been made also in earlier recent SAT competitions where 
+solvers were ranked based on the PAR-2 score.
+Furthermore, we observe more differences in overall runtime performance among the top solvers than what has been observed
+in the recent past competitions.
+
+The four solvers \solver{Kissat-sat}, \solver{Relaxed-newTech}, \solver{CaDiCaL-alluip-trail}, and \solver{CMS-ccnr-lsids} 
+performed significantly better that all other solvers submitted to the Main track (cf. Table~\ref{tab:results}).
+A very interesting observation is that these four top solvers all have a different code base. This has not been observed for many years; more typically
+many of the best-performing solver have been based on same code bases.
+
+The majority of the overall performance differences
+ between the top-4 solvers and the other solvers 
+is due to performance differences on satisfiable instances;
+see Figure~\ref{main:sat}. Indeed, in recent years, several techniques have been added to SAT solvers to improve
+their performance on satisfiable instance. Examples of such techniques are the integration of a local search
+solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
+and variable-move-to-front~\cite{Ryan:2004:Thesis}). The best-performing solver in  Main SAT track on satisfiable instances is \solver{Relaxed-newTech}, followed by
+\solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.
 
@@
 
-The main reason for the separation between the top-4 solvers and the others is the noticeable gap on satisfiable benchmarks, 
-see Figure~\ref{main:sat}. In recent years, several techniques have been added to SAT solvers to improve
-their performance on satisfiable instance. Examples of such techniques are the integration of a local search
-solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
-and variable-move-to-front~\cite{Ryan:2004:Thesis}). The 2020 winner of the Main SAT track is \solver{Relaxed-newTech}, followed by
-\solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.
-
 \begin{figure}[ht]
@@
 Overall, solvers performed much more similarly on
-unsatisfiable formulas,
-see Figure~\ref{main:unsat}. Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
-performed significantly better compared to all other participants. It is therefore not surprising
-that the VBS is reasonably close to \solver{Kissat-unsat}. \solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
-details about \solver{Kissat} are given in Section~\ref{sec:kissat}.
+unsatisfiable instances than on satisfiable instances;
+see Figure~\ref{main:unsat} for the runtime performance on unsatisfiable instances. 
+Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
+performed significantly than all other participating solvers. 
+It is therefore not surprising
+that the VBS is reasonably close to \solver{Kissat-unsat}. %\solver{Kissat} is a new solver that has been implemented in C, while most solvers are implemented in C++. Further 
+%details about \solver{Kissat} are given in Section~\ref{sec:kissat}.
 The solvers \solver{CaDiCaL-trail}
@@
 
-The competition in the Planning Track was more tight. The winning solver \solver{CaDiCaL-alliup-trail} solved only one instance more compared to the runner up \solver{CMS-ccnr-lsids}. 
-Their PAR-2 score is 
-quite close as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtimes
+\subsection{Planning Track}
+
+The competition in the Planning Track was more tight. 
+The best solver \solver{CaDiCaL-alliup-trail} solved only one instance more than  the runner up \solver{CMS-ccnr-lsids}. 
+The PAR-2 scores of these two solvers were
+quite similar as well. The third ranked solver, \solver{Kissat}, solved fewer instances, but its fast runtimes
 on several instances resulted in a strong PAR-2 score. Notice that these three solvers were also strong in the Main track. 
-Apparently none of the participating solvers was optimized for planning instances.
-
-The winning solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. The number in the suffix denotes
-that this solver used 32 threads on the 64 virtual cores that were available. It has been observed in earlier 
-competitions that using fewer threads than the number of virtual cores can be helpful as threads compete 
-for memory, which can reduce of the overall performance. The runner up is \solver{Plingeling}, while the
-third place is taken by \solver{ManyGlucose-32}. Figure~\ref{fig:res-parallel} shows the performance of
-all participating parallel solvers. Notice in Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR} solvers
+It should be noted that, somewhat disappointingly,  none of the participating solvers were actually optimized for planning instances.
+
+\textcolor{red}{Hmm we don't have any result tables or anything??}
+
+\subsection{Parallel Track}
+
+Turning to the Parallel track, Figure~\ref{fig:res-parallel} shows the performance of
+all participating parallel solvers. 
+The best solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. Interestingly,
+this solver used 32 threads on the 64 virtual cores that were available. In fact, it has been observed in already 
+recent earlier 
+SAT competitions that using fewer threads than the number of available virtual cores can be helpful; as threads compete 
+for memory, using all virtual cores may be detrimental to  overall performance. The runner up is \solver{Plingeling}, while the
+third place goes to \solver{ManyGlucose-32}. 
+Interestingly, one can observe from Table~\ref{tab:results} that only the \solver{Painless-MCOMSPS-STR*} solvers
 and \solver{Plingeling} had a lower PAR-2 score than the winner of the Main Track (\solver{Kissat-sat}). 
-This shows that it was hard to beat best-performing sequential solvers with a parallel solver on the competition instances. 
-We will show later in the article (Table~\ref{tab:tuples}) that small sequential portfolios 
-perform better (in terms of PAR-2 score) than the parallel solvers.
+It appears still to be challenging to beat the best-performing sequential solvers with
+with a parallel solver. (In fact, as we will show later on, sequential portfolios including only a few
+Main track solvers show  better performance than all of the parallel solvers.)
 
@@
 \end{figure}
+
+\subsection{Cloud Track}
 

### 2021-06-18 paper/main.tex
working on section 6...

@@
 
-In the following, we provide an overview of the participating teams and solvers, 
-and summarize new strategies which are implemented in the award-winning solvers of this competition. 
-We start with a few remarks on the evolution of code-bases of well known SAT solvers in Section~\ref{sec:codebases}. 
-Our review of the winning strategies in this competition starts with sequential solvers in the Main, Planning, and Incremental Library tracks in Section~\ref{sec:part:seq},
-then we continue with winners of the Parallel track in Section~\ref{sec:part:par} and conclude with winning solvers in the Cloud track in Section~\ref{sec:part:cloud}.
-
-\subsection{Code-Bases of SAT Solvers: ``On the Shoulders of Giants''}
+In this section we will provide an overview of the participating teams and solvers, 
+and summarize new strategies implemented in the best-performing solvers of the 2020 competition. 
+We start with a few remarks on the evolution of code-bases of well-known SAT solvers. % in Section~\ref{sec:codebases}. 
+%Our review of the winning strategies in this competition starts with sequential solvers in the Main, Planning, and Incremental Library tracks in Section~\ref{sec:part:seq},
+%then we continue with winners of the Parallel track in Section~\ref{sec:part:par} and conclude with winning solvers in the Cloud track in Section~\ref{sec:part:cloud}.
+
+\subsection{Evolution of SAT Solver Code-Bases: ``On the Shoulders of Giants''}
 \label{sec:codebases}
 
-Progress in SAT solvers is often based on successful modifications of existing code-bases. 
-One well-known tree of development is rooted in the code-base of \solver{Minisat} by E\'en and S\"orensson~\cite{Niklas:2003:Minisat}. 
-A well-known fork of \solver{Minisat} is \solver{Glucose} by Audemard and Simon~\cite{Audemard:2018:Glucose} which introduced the influential literal block distance (LBD) for weighing clauses in forgetting heuristics~\cite{Audemard:2009:Glucose}.
-The SAT solver \solver{RISS} by Manthey is a successful and award-winning fork of \solver{Glucose} in combination with the \solver{Coprocessor}~\cite{Manthey:2012:Coprocessor2} preprocessor.
-
-Another, more recent line of development in SAT solvers
-is rooted in the \solver{CoMinisatPS} fork of \solver{Minisat} by Oh which introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
+Progress in SAT solvers is often based on successful modifications of existing and openly available solver code-bases. 
+One well-known tree of code-base evaluation is rooted in the code-base of \solver{Minisat} by E\'en and S\"orensson~\cite{Niklas:2003:Minisat}. 
+A well-known fork of \solver{Minisat} is \solver{Glucose} by Audemard and Simon~\cite{Audemard:2018:Glucose}. 
+In particular, \solver{Glucose} introduced the influential literal block distance (LBD) heuristics for deciding which learned clauses to keep and which 
+ones to forget during search~\cite{Audemard:2009:Glucose}. 
+The SAT solver \solver{RISS} by Manthey is a further fork of \solver{Glucose}, combining \solver{Glucose}  with 
+ the \solver{Coprocessor}~\cite{Manthey:2012:Coprocessor2} preprocessor.
+
+A further, more recent line of evolution in SAT solvers
+is rooted in the \solver{CoMinisatPS} by Oh, which is itself a again a fork of \solver{Minisat}, introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
+Building on \solver{CoMinisatPS}, 
 The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
-The then award-winning variant \solver{MapleCOMSPS} by Liang et al.~is an implementation of a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) in \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
-
-In SAT Competition 2017, Luo et al.~integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award-winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
-Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}. 
-They introduced their award-winning \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
+The at-the-time award-winning variant \solver{MapleCOMSPS} by Liang et al.~implements a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) of \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+
+For SAT Competition 2017, Luo et al.~integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award-winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
+Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}, with
+the introduction of the award-winning solver \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
 
@@
 As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
-by Biere is another independent, award-winning and structured implementation of the state-of-the-art in SAT solving. 
-Its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} won in several of this competitions sequential tracks by a large margin.
-
-The sequential variant of the \emph{new code-base} \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
+by Biere is another independent representative of state-of-the-art SAT solvers.
+Its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} was quite successful in the 2020 competition.
+
+The sequential variant of the \emph{new code-base} \solver{ParaFrost} by Osama and Wijs was submitted for the first time to the 2020 SAT Competition,
+ introducing several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
 
@@
 Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
-In the following sections, we outline the technical reports of the award winning solvers.
+In the following, we provide a short overview of the best-performing solvers of 2020, based mainly on the solver descriptions submitted
+to the 2020 competition proceedings by the authors of the individual solvers.
 
@@
 
-Three configurations of \solver{Kissat} were evaluated in this competition, including one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively.
-\solver{Kissat} received \emph{four awards}, by achieving the first place in the Main track, 
-the best score on unsatisfiable instances, the second best score on satisfiable instances and the third place in the Planning track.
+Three configurations of \solver{Kissat} were submitted to the 2020  competition, including one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively.
+\solver{Kissat} received \emph{four awards},achieving the first place in the Main track, 
+the best score on unsatisfiable instances, the second-best score on satisfiable instances and the third place in the Planning track.
 
@@
 Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
-Since conflict-number has been observed to be too unstable for measuring the length of two alternating restart-modes, \solver{Kissat} uses the new unit ``ticks'' which approximates the number of cache-line accesses in unit-propagation~\cite{Biere:SC2020}.
-
+Since conflict number has been observed to be too unstable for measuring the length of two alternating restart modes, \solver{Kissat} uses the new unit ``ticks'' which approximates the number of cache-line accesses in unit-propagation~\cite{Biere:SC2020}.
 \solver{Kissat} also exploits autarkies to account for saved phases. 
-In order to keep valuable information of saved phases, before each rephasing step, \solver{Kissat} computes the largest autarky for the assignment implied by the current saved phases~\cite{Kiesl:2019:Autarkies}.
+In order to keep valuable information of saved phases, before each rephasing step \solver{Kissat} computes the largest autarky for the assignment implied by the current saved phases~\cite{Kiesl:2019:Autarkies}.
 As such an autarky might contain satisfying assignments which imply disconnected components, those variables are subject to subsequent variable elimination.
@@
 
-\solver{CryptoMiniSat} received \emph{four awards}: the first place in the Incremental Library track,
+\solver{CryptoMiniSat} received \emph{four awards}, achieving the first place in the Incremental Library track,
 the second place in the Planning track, the third place in the Main track, and the third-best score on satisfiable instances. 
-Two submitted variants, \solver{default} and \solver{LSIDS}, scored mostly adjacent ranks in the evaluation of the tracks. 
+Two submitted variants, \solver{default} and \solver{LSIDS}, scored mostly adjacent ranks in the individual competition tracks.
+
 The \solver{LSIDS} variant of \solver{CryptoMiniSat} comes with a new hybrid phase selection approach~\cite{Shaw:2020:LSIDS,Soos:SC2020}.
-
 \solver{CryptoMiniSat} comes with an independent implementation of state-of-the-art hybrid branching heuristics which alternate between classic phase saving and target phase selection~\cite{Biere:SC2019}.
@@
 In addition, \solver{CryptoMiniSat-CCAnr} bumps the VSIDS scores of the first 100 variables in those clauses which the SLS solver weighs most hard to satisfy~\cite{Soos:SC2020}.
-
 Inprocessing has been extended to include ternary resolution and more vivification~\cite{ChuMinLi:2020:Vivification}. 
@@
 Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
-The variants including \emph{Stable AllUIP} were the most successful and won  first place in the Planning track.
+The variants including \emph{Stable AllUIP} were the most successful in the 2020 competition, achieving in particular the  first place in the Planning track.
 
@@
 In SAT Competition~2020, its variant \solver{newTech} showed a good performance especially on satisfiable instances. 
-The solver received two awards: second place in the Main track and the best score on satisfiable instances.
+The solver received two awards, achieving the second place in the Main track and the best score on satisfiable instances.
 

### 2021-06-18 paper/main.tex
done with sect 6

@@
 
-Six teams submitted a total of $10$ solvers and configurations in the Parallel track. 
-In the following, we outline the award-winning parallel solvers.
+Six teams submitted a total of $10$ solvers and configurations to the Parallel track. 
+In the following, we outline  the best-performing parallel solver implementations.
 
@@
 \solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32} and a \solver{64} threaded variant and won three awards: the first place overall, the best score on satisfiable and the second best score on unsatisfiable instances.
-In the overall evaluation, the \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant. 
-However, in the separate evaluations on satisfiable and unsatisfiable variants the \solver{32} threaded variants performed much better, such that the runner-up solvers outperformed the \solver{64} threaded variant.
-
-\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrent data-structures, such that implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies~\cite{Frioux:2017:Painless}.
-
+The authors submitted a \solver{32} and a \solver{64} threaded variant, which alltogether won three awards, achieving
+ the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
+The \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant overall
+Furthermore, 
+ the \solver{32} threaded variants geared towards either satisfiable or unsatisfiable instances 
+showed much better  than the the \solver{64} threaded variants.
+\textcolor{red}{Not sure if I got this right: did the submit variants of the solver geared specifically towards SAT and UNSAT, resp.?
+The writing was really confusing here...}
+% such that the runner-up solvers outperformed the \solver{64} threaded variant.
+
+\solver{Painless} uses a generic interface to integrate a solver and abstracts away the implementation details of parallelism and concurrent data-structures.
+Due to this,  implementations in \solver{Painless} boil down to implementing parallelization and clause sharing strategies~\cite{Frioux:2017:Painless}.
 \solver{Painless-MCOMSPS-STR} diversifies mainly via hard-coded configurations of the branching strategies LRB and VSIDS, and via sparse random initialization of variable polarities~\cite{Balyo:2015:HordeSATs}.
@@
 
-\solver{Plingeling} obtained the best score on unsatisfiable instances, the second place in the overall evaluation, and the third best score on satisfiable instances. 
+The parallel solver 
+\solver{Plingeling} achieved the best score on unsatisfiable instances, the second place in the overall evaluation, and the third-best score on satisfiable instances. 
 \solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
@@
 \solver{ManyGlucose} was submitted in \solver{32} and \solver{64} threaded variants. 
-The \solver{32} threaded variant received two awards in this competition: the overall third place and the third best score on unsatisfiable instances. 
+The \solver{32} threaded variant won two awards in this competition, achieving the overall third place as well as the third-best score on unsatisfiable instances. 
 \solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behavior~\cite{Audemard:2018:GlucoseSyrup,Audemard:2014:LazyClauseExchange,Hamadi:2009:ManySat}.
@@
 
-\subsection{Massively Parallel SAT Solvers}
+\subsection{Massively Parallel SAT Solvers in the Cloud Track}
 \label{sec:part:cloud}
@@
 Five teams submitted a total of $6$ solvers and configurations in the Cloud track. 
-In the following, we outline the award-winning massively parallel solvers.
+In the following, we outline the best-performing massively parallel solver implementations.
 
@@
 Diversification is done via randomized sparse initialization of branching scores. 
-
 \solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from its leafs to the root. 
@@
 The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{Schreiber:SC2020}. 
-
 \solver{Mallob} uses a global clause size limit and a dynamic size limit for the sharing buffer, which depends on its position in the binary tree and is larger the closer we get to the root. 
 Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
-Duplicates are avoided by using a bloom filter which is cleared periodically~\cite{Schreiber:SC2020}.
+Duplicates are avoided by using a Bloom filter which is cleared periodically~\cite{Schreiber:SC2020}.
 
@@
 \solver{TopoSAT~2}~\cite{Ehlers:2018:Toposat2} is a massively parallel SAT solver using \solver{Glucose~3}~\cite{Audemard:2018:Glucose}. 
-\solver{TopoSAT~2} uses lock-free clause-exchange for solvers on the same machine and the message passing interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
-\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
-\solver{Toposat~2} diversifies via strategies used for branching, restarting, and clause forgetting~\cite{Ehlers:SC2020}.
+The solver
+ uses lock-free clause-exchange for solvers on the same machine and the message passing interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
+\solver{TopoSAT~2} also strengthens clauses before export and delays clause import until the trail-size reaches a local minimum, as well as
+diversifies via strategies used for branching, restarting, and clause forgetting~\cite{Ehlers:SC2020}.
 
@@
 \solver{Slime} is built from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{Riveros:SC2019}. 
-The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{Riveros:SC2020}. 
-Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} won the third price in the Cloud track.
+The new version of \solver{Slime} submitted to the 2020 competition came with periodic randomization in geometrically increasing intervals~\cite{Riveros:SC2020}. 
+Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} achieved the third place in the Cloud track.
 

### 2021-06-18 paper/main.tex
More...

@@
 technology (as represented by the solvers) is the most important
-(and to what degree) in the observed state of the art of SAT solving.
+(and to what degree) in the observed state of the art in SAT solving.
 We consider here the following three related metrics conceptually derived
@@
 ``The fastest takes it all'':
-For each solver we count the number of times, it was the fastest to solve an instance.
+For each solver, we count the number of times the solver was the fastest to solve an instance.
 \item[VBS-2]
@@
 the following fraction of a point for solving $I$:
-$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
+$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the runtime of the best solver on $I$.
 \item[VBS-3]
@@
 
-We remark that the sum of VBS-1 points, as well as VBS-3 points, computed across all the solvers
+We remark that the sum of VBS-1 points as well as the sum of VBS-3 points computed across all the solvers
 is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
@@
 In the case of VBS-3, where we discard the information about the solution times, 
-we evenly split the one point reward for solving an instance to those solvers which were successful on it.
-
+we evenly split the one point reward for solving an instance among those solvers which succeeded in solving the instance.
 In contrast, VBS-2 does not have this property as it in general distributes more than one point per instance.
-Similarly to VBS-1, it takes the solution time into account,
-and similarly to VBS-3 it does not award just the best solver on an instance.
-For example, being twice as slow on an instance than the fastest solver results in a half point awarded.
-And, if all the solvers solve an instance with the same solution time,
-each solver scores a whole point for that instance.
+Similarly as VBS-1, it takes the solution time into account.
+Similarly as VBS-3, it does not award just the best solver on an instance.
+For example, a solver that uses twice as much runtime as  the fastest solver on an instance received half a point.
+Further, if all the solvers solve an instance equally fast,
+each solver receives a whole point for the instance.
 
@@
 
-Table~\ref{tab:vbsMainALL} renders the just-described three metrics applied 
+Table~\ref{tab:vbsMainALL} provides the result of applying the just-described three metrics 
 to the full results of the Main track. We can see that the respective leaderboards 
@@
 
-The metric VBS-2 identifies as the best solver \solver{Kissat-sat}. Its leading score of \SI{32.9}{\percent} of the total
-is a bit harder to interpret: A solver can score \SI{32.9}{\percent} of VBS-2 total
+The metric VBS-2 identifies \solver{Kissat-sat} as the best solver. Its leading score of \SI{32.9}{\percent} of the total
+is somewhat more difficult to interpret, though: a solver can score \SI{32.9}{\percent} of VBS-2 total
 by solving \SI{32.9}{\percent} of the solved instances in the best observed time
-and no others. But we know, thanks to its VBS-1, that \solver{Kissat-sat} solved \SI{9.8}{\percent}
+and no others. Howeer,  we see from its VBS-1 score that \solver{Kissat-sat} solved \SI{9.8}{\percent}
 of the solved instances in the best observed time (and some others).
 A solver can also score \SI{32.9}{\percent} of VBS-2 total by solving all the solved instances,
-but always being roughly 3 times slower than the VBS. 
-\solver{Kissat-sat} lies (obviously) somewhere between these two extremes.
+but always being roughly three times slower than the VBS. 
+The performance of \solver{Kissat-sat} lies (obviously) somewhere between these two extremes.
 
@@
 at least among the first 10 solvers. 
-(The last solver got 0.9 points which is \SI{0.221}{\percent} of the total.)
+(The last solver receives 0.9 points which is \SI{0.221}{\percent} of the total.)
 One can conclude from this that most of the benchmarks are solved
-by most of the well performing solvers.
+by most of the well-performing solvers.
 
@@
 can be obtained by attempting to construct a sequential schedule of solvers 
-(rather than relying on an oracle to pick one for each instance, as with VBS)
-and looking at how big a role each solvers plays in such a schedule. Since constructing 
+(rather than relying on an oracle to pick one solver for each instance, as with VBS)
+and observing how big a role each solvers plays in such a schedule. Since constructing 
 an optimal schedule tends to be computationally hard, we start here by 
-presenting a useful efficient alternative -- a greedy set cover approach.
+presenting a a computationally more efficient alternative---a greedy set cover approach.
 
@@
 the new schedule will be able to solve. We demonstrate this on
-the actual data from the competition, again taking the Main track results.
+the actual data from the competition, again focusing in particular on the Main track results.
 
@@
 In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
-Given those 264 instances as already covered, \solver{CaDiCaL-alluip} was the best in further contributing to the set by additional $22$ instances in iteration $2$.
+With these
+ 264 instances already covered, \solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
 We can see that the further iterations tend to add very little,
 with the final four iterations adding one instance each. Note that each solver
-that managed to solve an instance uniquely (i.e.~being the only solver to do so)
-is showing up in the table. This is, for example the case of the last listed  
-\solver{exp-V-LGB-MLD-CBT-DL}.
-Highlighting unique solutions is a property of the greedy set cover metric
+that managed to solve an instance uniquely (i.e., being the only solver that solved a particular instance)
+showis up in the greedy set cover. 
+% for example the case of the last listed  
+%\solver{exp-V-LGB-MLD-CBT-DL}.
+Highlighting solvers that uniquely solve instance is a property of the greedy set cover metric
 which we believe is congruent with documenting contributions to the state of the art.
+\textcolor{red}{congruent...? maybe a better choice of words here?}
 
@@
 
-The greedy set cover technique focuses only on solving instances,
-disregarding the time it would take to execute the obtained schedule. We can
+The greedy set cover 
+disregards the time it would take to execute the obtained ``schedule'' of running the solvers covering instances. 
+However, we can
 also look at schedules that would fit in a prescribed time budget. A natural choice
@@
 
-By employing a brute-force approach, we first construct a sequences of schedules 
+To this end, by employing a brute-force approach, we first construct a sequences of schedules 
 where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
@@
 (and cover 272 instances) than just one.
-One could use this observation to conjecture that the really hard 
-problems that were solved actually require quite a large time to 
+Based on this observation, it is plausible  that the really hard 
+instance that were solved actually may require quite large runtime to 
 get ``cracked'' by any solver and thus the advantage of adding more solvers to the schedule
@@
 Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
-Z3 comes up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
-The table is sorted by $R^S$, the time the schedule allocates to individual solvers, and skips the zero entries.
+Z3 provided  the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
+The table is sorted by $R^S$, the time the schedule allocates to individual solvers, with zero entries ignored.
 It is not clear to what degree is the obtained schedule unique and how much it relies on each solver being present and for how long.
@@
 All the 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
-This result, however, does not signify a bug, as Z3 was not asked to produce a schedule with a minimal number of
+This result is due to the fact that Z3 was not asked to produce a schedule with a minimal number of
 participating solvers.
@@
 Interestingly, we now have both variants $\{ \solver{Kissat-sat}, \solver{Kissat-unsat} \} \subset T_6$, and moreover it holds that $T_6 \subset T_7$.
-All solvers in $T_{k \leq 7}$ belong the top performing solvers which received an award in the Main track, with the only exception being $\solver{Scavel01} \in T_4 \cap T_5$ (cf.~Table~\ref{tab:results}).
+All solvers in $T_{k \leq 7}$ are among the top-performing solvers which received awards in the Main track, with the only exception of $\solver{Scavel01} \in T_4 \cap T_5$ (cf.~Table~\ref{tab:results}).
 
@@
 
-Contributions to the VBS can be well captured by clustering the instance space into instance families. 
+Contributions to the VBS can becaptured by clustering the instance space into instance families. 
 We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
 and report their place and score in Table~\ref{tab:eval-by-family}. 
-Interestingly, the overall winning solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.
+Interestingly, the overall best solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.
 
@@
 We calculate the \emph{similarity} of the $30$ solvers with the
-best average PAR-2 score in the Main track. The results are displayed in
+best average PAR-2 score in the Main track. The results are shown in
 Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
@@
 
-One big cluster that we identify consists of the \solver{Maple}-decedants, 
+Interestingly, one identifiable large cluster consists of the \solver{Maple}-decedants, 
 all of which are modifications of the winners in the SAT Competition 2018 and
@@
 They form a sub-cluster
-with a lower similarity to the rest, but a high similarity within. In fact, the highest measured similarity,
+with a lower similarity compared to the rest, but a high similarity within. In fact, the highest measured similarity,
  % of $0.96$
@@
 \solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
-The high similarity suggests that the
+This high similarity suggests that the
 changes they made either result in a very similar behavior or do not have a
@@
 The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
-use the same code-base as a lot of solvers in the \solver{Maple}-cluster, but their
-overall performance is better and closer to the \solver{CMS}-cluster.
+use the same code-base as a lot of solvers in the \solver{Maple}-cluster. However, the
+overall performance of the solver is better and closer to the \solver{CMS}-cluster.
 The three \solver{CMS} configurations
@@
 The 2020 version of \solver{CaDiCaL}
-performs worse than the modifications based on the 2019 version and
+exhibit weaker performance than the modifications based on the 2019 version and
 does not quite fit into any cluster.
 
-The last cluster to the left of the heat map is comprised of the other solvers
-originally written by \emph{Biere}. Interesting to note is that the
+The leftmost cluster in the heat map is comprised of the other solvers
+originally written by \emph{Biere}. What is interesting to note is that the
 \solver{Kissat} configuration specialized for unsatisfiable instances joins the
-others in the cluster high in the dendrogram. In fact \solver{Kissat-unsat} has
+others configurations in the cluster high in the dendrogram. In fact \solver{Kissat-unsat} has
 the lowest average similarity to all other solvers in the top 30.

### 2021-06-22 paper/main.tex
bib revised, please do not screw this up again...

@@
 \paragraph{Planning (SAS+)}
-We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counterexample-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.
+We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counterexample-guided abstraction refinement (CEGAR)~\cite{Pasar19}.
 
@@
 (Section~\ref{sec:winners}) and as well as more in-depth analysis of the competition results (Section~\ref{sec:analysis}).
+
+An overview of the top-10 solvers in each of the competition tracks discussed in the following
+is provided in Table~\ref{tab:results}.
 
@@
 Building on \solver{CoMinisatPS}, 
-The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
+The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{MapleSAT}. 
 The at-the-time award-winning variant \solver{MapleCOMSPS} by Liang et al.~implements a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) of \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
@@
 \subsection{Influence of Benchmark Selection on Solver Ranking}
-The main result of the competition is the ranking of the solvers participating
-in the Main track, according to their average PAR-2 score. To evaluate the impact
+To evaluate the impact
 of benchmark selection on the solver ranking, we follow the experiments
@@
 % experiment:
-
-We first use random sampling to select subsets of the benchmarks used in the Main track.
+In particular, we first use random sampling to select subsets of the benchmarks used in the Main track.
 We start with $316$ benchmarks that have been solved by at least one solver in
@@
 possible subset size (1--316) we generate 50 random samples.
-
 The solvers are assigned a new rank in ascending order of their PAR-2 score on
@@
 % are good approximations.
+
 To determine how similar an estimate is to the original ranking, we calculate
@@
 % and compute the correlation coefficient.
-
 Spearman's rank correlation coefficient
@@
 Accordingly, removing fewer benchmarks randomly has almost no effect on the ranking of the solvers.
-Furthermore, removing fewer than $200$ ($63\%$) benchmarks, still results in an average rank correlation above $0.96$.
-
+Furthermore, removing fewer than $200$ ($63\%$) benchmarks still results in an average rank correlation above $0.96$.
 This suggests that the impact of the random selection in Algorithm~\ref{algo:select} on the solver ranking is limited.
@@
 The 2020 SAT Competition successfully continues the tradition of the SAT Competition series. In 2020, significant advances
-in SAT solvers compared to previous years are observed. Some of the more interesting observations on the winning solving 
+in SAT solvers compared to previous years were observed. Some of the more interesting observations on the winning solving 
 strategies include the following.
 All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
-solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.
-As can be seen in the \emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart.
+solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As observed
+from the results of the\emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart.
 However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
-It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
+It appear challenging to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
 The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use-case.
@@
 
-In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances was often counter-productive and did not lead to a more balanced overall selection of new instances. 
-Moreover, this practice discriminated against authors of purely satisfiable or unsatifiable sets of instances. 
-Also the hardness criterion of 10 \solver{Minisat} minutes was higher than the hardness criterion of 1 \solver{Minisat} minute of the BYOB rule. 
-In future competitions, we will not balance by \emph{satisfiablity} on the author level, we will be more consistent or clear with our \emph{hardness} criteria, and we will specify what it means for an instance to be counted as \emph{unknown}.
+In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances turned out often counter-productive as it 
+did not lead to a more balanced overall selection of new instances. 
+Moreover, this practice discriminated against authors who submitted solely satisfiable or unsatisfiable  instances. 
+The hardness criterion of 10 \solver{Minisat} minutes was set higher than the hardness criterion of 1 \solver{Minisat} minute of the ``bring your own benchmarks'' rule, 
+which can be viewed as problematic. As lessons learned
+in future competitions we will not aim balance by satisfiability status on the benchmarks author level. will aim to be more consistent with the imposed \emph{hardness} criteria
+for benchmark selection, and will also make sure to clearly communicate what it means for an instance to be counted as \emph{unknown}.
 
 The IPASIR interface facilitates the integration of SAT solvers into incremental applications. 
-In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 
-This calls for the creation of a more diverse and organized repository of applications for incremental SAT solvers. 
-Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
+In contrast to benchmarking with instances given in the 
+DIMACS CNF format, there are only few benchmark applications available for the Incremental track.
+This calls for more community-level efforts for constructing a more diverse and well-organized repository of applications for incremental SAT solvers. 
+Proper benchmarking and new tools for testing incremental SAT solvers may also help solver authors to deal with the more complex use-cases.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
 
@@
 In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
-The \solver{CaDiCaL-alluip} solver -- which is a modified \solver{CaDiCaL} -- has shown competitive performance in this competitition.
-
-The first instantiation of an Application track has been a Planning track. 
-The results show that different solvers take the lead when we only evaluate for a single application. 
+The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competitition.
+
+The first instantiation of an Application track was the Planning track organized as a one-time track in 2020.. 
+The results show that different solvers take the lead when we only evaluate for a single application, when compared to the overall Main track results.
 We intend to run further instantiations of the Application track. 
-In the next competition, we will compile a set of 200 cryptographic benchmark instances for a Crypto track.
-
-The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolios and to stimulate development of new code-bases. 
-The rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.
-Therefore, the \emph{Portfolio rule} will receive some refinement in future competitions.
-
-The results of the \emph{Planning} track as well as our differentiated analysis of the results highlight the individual contributions of many submissions. 
-Our plan for the future competitions is to always run a special track for varying applications alongside the Main track.
+While essentially none of the solvers that participated in the Planning track seemd particularly optimized for Planning instance, we hope
+in future iterations the community will pick up on the challenge of optimizing SAT solvers towards different focus applications, as a complementary
+challenge when compared to the generality of the Main track.
+In the next competition, the  planned focus of Application track will be on SAT solver applications in cryptology.
+
+The portfolio rule has been established to prohibit participation of pure solver portfolios, in order to stimulate development of new code-bases and
+to ensure fair competition among  sequential solvers.
+The rule was challenged in this competition as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.
+We aim to revisit and refine the portfolio rule in future instantiations of the competition in order to ensure that the rule does not unnecessarily hinder interesting 
+algorithmic developments in SAT solving.
 

### 2021-06-22 paper/stability/benchfeatures/random_sampling_plots.py
plot colors

@@ -97,7 +97,7 @@ def random_sampling_plot(data_frame,original_ranks,original_instances,solver_nam
     # plt.xlabel('Number of randomly removed instances',fontsize=16)
     plt.ylabel('Spearman\'s correlation')
     plt.xlabel('Number of randomly removed instances')
-    plt.errorbar(number_of_removed, correlation_mean, correlation_std, marker='.',elinewidth=1)
+    plt.errorbar(number_of_removed, correlation_mean, correlation_std, marker='', color='C1', ecolor='C0', elinewidth=1)
     plt.hlines([0.8,0.99,0.6,0.4,0.2],0,max(number_of_removed)+5,linestyle='dashed',color='m')
     plt.grid(True)
 

### 2021-06-22 paper/main.tex
typos

@@
 ``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
-Examples for applications of incremental SAT solving are counterexample-guided eastraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
+Examples for applications of incremental SAT solving are counterexample-guided abstraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
 multi-agent path finding~\cite{DBLP:conf/ijcai/Surynek19}, and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
@@
 including a list of all  authors involved in developing the solver,  description of any non-standard algorithmic
-techniques and data structures implemented in the sovler, as well as references to the relevant literature.
-These system descriptions have been collected and made available publically in the non-refereed competition
+techniques and data structures implemented in the solver, as well as references to the relevant literature.
+These system descriptions have been collected and made available publicly in the non-refereed competition
 proceedings~\cite{SC2020}.
@@
 The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
-For this applicaiton, we used the same $50$  satisfiable instances as for  backbone computation.
+For this application, we used the same $50$  satisfiable instances as for  backbone computation.
 
@@
 The other four participants performed significantly worse. 
-The massive parallelism in distributed SAT solving imposes additional challanges on scalable information sharing and search diversification. 
+The massive parallelism in distributed SAT solving imposes additional challenges on scalable information sharing and search diversification.
 Since 2020 was the first year of this track, we expect a tighter competition in the future.
@@
 \solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32} and a \solver{64} threaded variant, which alltogether won three awards, achieving
+The authors submitted a \solver{32} and a \solver{64} threaded variant, which altogether won three awards, achieving
  the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
@@
 In this section, we provide additional analysis of the Main track results, going beyond the rankings.
-In paricular, we focus on metrics complementing the PAR-2 score used for ranking the solvers in the actual competition.
+In particular, we focus on metrics complementing the PAR-2 score used for ranking the solvers in the actual competition.
 
@@
 by solving \SI{32.9}{\percent} of the solved instances in the best observed time
-and no others. Howeer,  we see from its VBS-1 score that \solver{Kissat-sat} solved \SI{9.8}{\percent}
+and no others. However, we see from its VBS-1 score that \solver{Kissat-sat} solved \SI{9.8}{\percent}
 of the solved instances in the best observed time (and some others).
@@
 that managed to solve an instance uniquely (i.e., being the only solver that solved a particular instance)
-showis up in the greedy set cover. 
+shows up in the greedy set cover.
 % for example the case of the last listed  
@@
 
-Contributions to the VBS can becaptured by clustering the instance space into instance families. 
+Contributions to the VBS can be captured by clustering the instance space into instance families.
 We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
@@
 
-Interestingly, one identifiable large cluster consists of the \solver{Maple}-decedants, 
+Interestingly, one identifiable large cluster consists of the \solver{Maple}-descendants,
 all of which are modifications of the winners in the SAT Competition 2018 and
@@
 In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
-The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competitition.
+The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competition.
 
@@
 We intend to run further instantiations of the Application track. 
-While essentially none of the solvers that participated in the Planning track seemd particularly optimized for Planning instance, we hope
+While essentially none of the solvers that participated in the Planning track seemed particularly optimized for Planning instance, we hope
 in future iterations the community will pick up on the challenge of optimizing SAT solvers towards different focus applications, as a complementary

### 2021-06-22 paper/main.tex
fixed overfull hboxes
more consistent table labeling

@@
 % , where the minimal makespan equals the length of the shortest valid plan
-together with known bounds\footnote{Upper and lower bounds on plan length are available for
+together with bounds\footnote{Upper and lower bounds on plan length are available for
 	some planning tasks from the \emph{Optimal track} that have \emph{unit cost}
@@
 generated by \emph{Tree-REX} \cite{TreeRex19}, a planner for \emph{Hierarchical
-	Task-networks} (HTN). In HTN planning the planner is provided with additional domain
-knowledge besides the problem description. The HTN benchmarks were provided by
+	Task-networks} (HTN).
+  In HTN planning additional domain knowledge besides the problem description is provided.
+The HTN benchmarks were provided by
 the solver author.
@@
 		\hline
-		                             &                           & 100   & 100 \\
+		 $\Sigma$                    &                           & 100   & 100 \\
 	\end{tabular}
@@
 
-\paragraph{Quantified Boolean Formulas (QBF)}
+\paragraph{Quantified Boolean Formulas}
 \textsf{Ijtihad} is a QBF solver which uses counterexample-guided expansion to incrementally solve a given QBF instance with a SAT solver~\cite{Bloem:2018:QBFSAT}. 
@@
 all participating parallel solvers. 
-The best solver in the Parallel track is \solver{Painless-MCOMSPS-STR32}. Interestingly,
+The best solver here is \solver{Painless-MCOMSPS-STR32}. Interestingly,
 this solver used 32 threads on the 64 virtual cores that were available. In fact, it has been observed in already 

### 2021-06-22 paper/main.tex

@@
 have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
-to thousands of different application settings. \textcolor{red}{Add various references to the several things in this sentence}
+to thousands of different application settings.
 
@@
 The focus of this track was specifically on efficiently solving
-instances arising from the domain of SAT-based automated planning.\textcolor{red}{Add references} 
+instances arising from the domain of SAT-based automated planning~\cite{Kautz1992}.
 Automated planning was chosen as the target problem domain of this first instantiation of the domain-specific tracks
@@
 The traditional Hack track (established 
-2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}\textcolor{red}{Add reference}. 
+2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}~\cite{Audemard:2018:Glucose}.
 In the past, several advances in SAT solving required only small modifications of an established solver to achieve a considerable contribution. 
@@
 the enclosing tool reaches its final state. 
-``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
+``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Niklas:2003:Incremental,Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.
 Examples for applications of incremental SAT solving are counterexample-guided abstraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
@@
 The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
-of memory, while the Cloud track was run on AWS\textcolor{red}{Was AWS spelled out a single time before this? I now notice that
-we do not really mention Amazon much, should we mention it more specifically?}
+of memory, while the Cloud track was run on Amazon Web Services (AWS)
  m4.4xlarge machines with 16 virtual CPUs and 64 GB of
@@
 It should be noted that, somewhat disappointingly,  none of the participating solvers were actually optimized for planning instances.
-
-\textcolor{red}{Hmm we don't have any result tables or anything??}
 
@@
 %\solver{exp-V-LGB-MLD-CBT-DL}.
-Highlighting solvers that uniquely solve instance is a property of the greedy set cover metric
-which we believe is congruent with documenting contributions to the state of the art.
-\textcolor{red}{congruent...? maybe a better choice of words here?}
+Highlighting solvers that uniquely solve instance is a property of 
+Indeed, the greedy set cover metric highlights solvers which are able to uniquely solve specific benchmark instances
+and thereby contributing to the current state of the art.
 

### 2021-06-28 paper/main.tex
minor rerewordings

@@
 
-In all tracks solvers were required to output a solution (a satisfying truth assignment, i.e., a model on the instance in question)
- to certify recognizing a satisfiable instance.
-On the other hand, 
-certificates for unsatisfiable instances (proofs) were required only 
-in the Main track (besides the No-Limits track).
+In all tracks solvers were required to output a solution (a satisfying truth assignment, i.e., a model on the instance in question) to certify recognizing a satisfiable instance.
+On the other hand, certificates for unsatisfiable instances (proofs) were required only in the Main track (besides the No-Limits track). 
 In some cases, a solver output the correct result, but the respective certificate was wrong. 
@@
 
-The proofs were validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim}
-was used for initial checking and optimizing the emitted proof, deriving a so-called LRAT proof file.
-Afterwards, an independent formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub}
-was used for validating the LRAT proof as a correct proof of unsatisfiability of the given formula.
-In the Main track, only those unsatisfiable benchmark instances for which the proof emitted by a specific solver
-could be validated by {\tt DRAT-trim} were considered solved by the  solver.
-It should be noted that, while there were several cases where {\tt cake\_lpr} ran out of resources before 
-there was no case where {\tt DRAT-trim} would accept
-a proof and {\tt cake\_lpr} would later disagree with the verdict.
-\textcolor{red}{This is pretty vague... does not really say if there were proofs that could not be validated with DRAT-trim??}
+Each unsatisfiability proof produced by 
+each solver was validated in a two-step fashion. First, the tool {\tt DRAT-trim}~\cite{DRATtrim} was used for initial checking and optimizing the 
+ proof, thereby obtaining a so-called LRAT proof file. 
+An independent formally-verified checker {\tt cake\_lpr} \cite{cakeLprGithub} was then used for validating the 
+LRAT proof as a correct proof of unsatisfiability.
+
+In a few cases {\tt DRAT-trim} ran into the verification timeout of 40,000 seconds. 
+In the Main track, only those unsatisfiable benchmark instances for which the proof produced by a solver 
+could be validated at least by {\tt DRAT-trim} were considered solved by the solver. 
+While there were several cases where {\tt cake\_lpr} ran out of resources, 
+there was no case where {\tt DRAT-trim} would accept a proof and {\tt cake\_lpr} would not.
 
@@
 
-\section{Main Track}
+\subsection{Main Track}
 
@@
 
-\emph{Stable AllUip} resolves additional clauses beyond the First Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size or LBD than the 1-UIP clause. 
+\emph{Stable AllUip} resolves additional clauses beyond the First Unit Implication Point (1-UIP) and keeps them whenever they are of smaller size and their 
+LBD not greater than that of the 1-UIP clause. 
 By monitoring the frequency of clauses which successfully pass that filter, the solver dynamically limits the amount of such extended learning attempts~\cite{Zhang:2001:ClauseLearning,Bacchus:SC2020}.
@@
 \solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
-The authors submitted a \solver{32} and a \solver{64} threaded variant, which altogether won three awards, achieving
- the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
-The \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant overall
-Furthermore, 
- the \solver{32} threaded variants geared towards either satisfiable or unsatisfiable instances 
-showed much better  than the the \solver{64} threaded variants.
-\textcolor{red}{Not sure if I got this right: did the submit variants of the solver geared specifically towards SAT and UNSAT, resp.?
-The writing was really confusing here...}
-% such that the runner-up solvers outperformed the \solver{64} threaded variant.
+The authors submitted a \solver{32} and a \solver{64} threaded variant, which altogether won three awards, achieving the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances.
+Interestingly, the \solver{32} threaded variant performed better than the \solver{64} threaded variant.
 

### 2021-06-28 paper/main.tex
a couple of minor fixes in section 1 and 2

@@
 participating solvers, benchmarks, and the empirical results from the competition.
-In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, where introduced in 2020,
+In terms of competition tracks, two new tracks, namely the cloud track and an application-specific track, were introduced in 2020,
 in addition to the already earlier established main, parallel, and incremental tracks; we
@@
 
-The rest of this article is organized as follows. 
+This article is organized as follows. 
 We start by providing an overview on the competition, including details on and motivations for the several
@@
 enclosing tool on its own benchmark and communicate with the competing SAT solver 
-through this interface API. 
+through this interface. 
 %
-SAT solvers submitted to this track need hence implement the require interface.
+SAT solvers that are submitted for this track must hence implement the interface.
 Furthermore, it should be noted that the solutions output by a solver may, in general, influence
@@
 after the competition, the SAT community benefits by having an ever growing repository 
-of diverse problems to target with the next developments.
+of diverse problems that next developments will target.
 The descriptions of the submitted benchmarks are also made available in the competition proceedings~\cite{SC2020}.
@@
 \paragraph{Input and Output Format}
-
+No-limits
 The benchmark instances were presented to the solvers in the de facto standard
@@
 
-Apart from the No-limits track, participants were not allowed to submit a portfolio of solvers,
+Apart from the No-Limits track, participants were not allowed to submit a portfolio of solvers,
 i.e., a combination of two or more core SAT solvers developed by different groups of authors.\footnote{In other words, a submission of a combination of solvers was only possible if all the authors of all the parts
@@
 to solve a particular instance and twice the time limit, i.e.~\num{10000} points,
-if the instance was not solved. In particular, this mean that the lower the score a solver
+if the instance was not solved. In particular, this means that the lower the score a solver
 obtained, the better the solver performs.
@@
 
-In all tracks solvers were required to output a solution (a satisfying truth assignment, i.e., a model on the instance in question) to certify recognizing a satisfiable instance.
+In all tracks, solvers were required to output a solution (a satisfying truth assignment, i.e., a model on the instance in question) to certify recognizing a satisfiable instance.
 On the other hand, certificates for unsatisfiable instances (proofs) were required only in the Main track (besides the No-Limits track). 
@@
 and \SI{128}{\giga\byte} of memory.
-The time limit enforced on each solver for solving an instance was \SI{5000}{\second}. 
-In the Main track, proof validation was limited to \SI{45000}{\second} per proof.)
+The time limit enforced on each solver for solving an instance was 5,000 seconds. 
+In the Main track, proof validation was limited to 40,000 seconds per proof.)
 The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
@@
  m4.4xlarge machines with 16 virtual CPUs and 64 GB of
-memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.
+memory. These tracks used wall-clock timeouts of 5,000 seconds and 1,000 seconds, respectively.
 

### 2021-06-28 paper/main.tex
conclusion spellcheck

@@
 
-For data-driven selection of benchmark instances, we used GBD~Tools\footnote{\url{See https://pypi.org/project/gbd-tools/}} which facilitates querying for instances with desired properties, e.g., by instance author, family, result or solver runtime~\cite{Iser:2018:GBD}.
+For data-driven selection of benchmark instances, we used GBD~Tools\footnote{See \url{https://pypi.org/project/gbd-tools/}} which facilitates querying for instances with desired properties, e.g., by instance author, family, result or solver runtime~\cite{Iser:2018:GBD}.
 We also use GBD~Tools for distributing benchmark instances and their attributes to the general public.\footnote{See \url{https://gbd.iti.kit.edu}}
@@
 
-The ``Bring Your Own Benchmarks'' (BYOB) rule, first  established in SAT Competition 2017~\cite{SC2017}, was again followed
-in 2020.
-By this rule, solver authors are required to submit 20 ``new'' benchmark instances to accompany a solver submission in order to participate in the competition. 
-New refers to the fact that instances contained in benchmark sets from earlier SAT Competitions are not allowed.
-Furthermore, a least 10 of the required 20 instances are required to be ``interesting'', interpreted in loose terms by
- the standard \solver{Minisat} SAT solving needing at least one minute of runtime (on typical computing hardware) to solve an instance.
+The ``Bring Your Own Benchmarks'' (BYOB) rule, first  established in SAT Competition 2017~\cite{SC2017}, was again followed in 2020. 
+By this rule, solver authors are required to submit 20 benchmark instances to accompany a solver submission in order to participate in the competition. 
+These benchmarks have to be ``new'' in the sense that instances included in benchmark sets from previous SAT competitions are not allowed. 
+Furthermore, at least ten of the required 20 instances are required to be ``interesting'', interpreted in loose terms by the standard \solver{Minisat} SAT solving needing at least one minute of runtime (on typical computing hardware) to solve an instance.
 It should be noted that new benchmarks could be submitted to the competition without needing to submit a solver.
-As a results, as detailed in Table~\ref{tab:families}, 27 authors contributed a set of 1260 new benchmark instances from a wide range of different instance families.
+As a results, as detailed in Table~\ref{tab:families}, 27 authors contributed a set of 1,260 new benchmark instances from a wide range of different instance families.
 
@@
 
-To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than 10 minutes.\footnote{We note that
-the limit of 10 minutes is again somewhat arbitrary.
-This 10-min runtime hardness filter essentially aims to make sure that enough instances are included in the final benchmark set which allow for distinguishing in terms of relative performance between the best-performing competing solvers.
-Unfortunately this time the 10-min limit enforced  was much greater that the requirements imposed for  ``interesting'' benchmark instances
-by the BYOB rule. It could be more sensible to impose the some 10-min limited also for an instance being ``interesting''. However, this would require more efforts
-at least in terms of computation times from the solver authors in order to construct a set of 20 interesting new benchmarks required by the BYOB rule.}
-
-From the resulting 1012 instances, in order to obtain a balanced benchmark set, 
+To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than ten minutes.\footnote{We note that
+the limit of ten minutes is again somewhat arbitrary.
+This runtime hardness filter essentially aims to make sure that enough instances are included in the final benchmark set which allow for distinguishing in terms of relative performance between the best-performing competing solvers.
+Unfortunately this limit was much greater that the requirements imposed for  ``interesting'' benchmark instances
+by the BYOB rule. It could be more sensible to impose the same ten minutes limit also for an instance being ``interesting''. However, this would require more efforts
+at least in terms of computation times from the solver authors in order to construct a set of interesting new benchmarks required by the BYOB rule.}
+From the resulting 1,012 instances, in order to obtain a balanced benchmark set, 
 we randomly selected $k$~instances per author using the value  $k$ which ensured that  the resulting set contains at least 300 instances.
@@
 Algorithm~\ref{algo:select}. Specifically,
-we randomly selected 7~satisfiable and 7~unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of 14~instances (Lines~5--7). 
-Of the such obtained 308~instances, we randomly removed 8~satisfiable instances, yielding a total of 114~satisfiable, 78~unsatisfiable and 108~instances of unknown satisfiability
+we randomly selected seven satisfiable and seven unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of 14~instances (Lines~5--7).
+Of the such obtained 308~instances, we randomly removed eight satisfiable instances, yielding a total of 114~satisfiable, 78~unsatisfiable and 108~instances of unknown satisfiability
 status.
@@
 take more than 100 GB of memory to encode into SAT. We ran both Pasar and
-Madagascars $\exists$-configuration with a timeout of 3 hours on the
+Madagascars $\exists$-configuration with a timeout of three hours on the
 remaining instances to find the minimal makespans. For each planning task where
@@
 unsatisfiable SAT instances. A significant number of instances from this set were not used
-as \solver{Minisat} could solve them in under $10$ minutes.
+as \solver{Minisat} could solve them in under ten minutes.
 % From those we discarded the SAT formulas that \solver{Minisat} can solve in
@@
 We augmented the remaining domains with the last unsatisfiable formulas
-generated for planning task where the minimal makespan could not be found.
-To generate the missing benchmarks we use a \emph{sequential} encoding
+generated for planning tasks where the minimal makespan could not be found.
+To generate the missing benchmarks, we use a \emph{sequential} encoding
 % , where the minimal makespan equals the length of the shortest valid plan
@@
 	Task-networks} (HTN).
-  In HTN planning additional domain knowledge besides the problem description is provided.
+  In HTN planning, additional domain knowledge besides the problem description is provided.
 The HTN benchmarks were provided by
-the solver author.
+the author of \emph{Tree-REX}.
 
@@
 For a complete list of the encoded planning tasks we refer to the
-generation script\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}}.
+generation script.\footnote{\url{https://satcompetition.github.io/2020/downloads/planning_generator.tar.xz}}
 The benchmarks of the Planning track adhere to the following naming convention:
@@
 
-In this section we provide a high-level overview of the results of SAT Competition 2020.
+In this section, we provide a high-level overview of the results of SAT Competition 2020.
 %We focus on some interesting results.
-Later on, we will provide overview of some of the key and new solving techniques implemented in best-performing solvers
-(Section~\ref{sec:winners}) and as well as more in-depth analysis of the competition results (Section~\ref{sec:analysis}).
-
+Later on, we will provide an overview of some of the key and new solving techniques implemented in best-performing solvers
+(Section~\ref{sec:winners}) as well as a more in-depth analysis of the competition results (Section~\ref{sec:analysis}).
 An overview of the top-10 solvers in each of the competition tracks discussed in the following
@@
 Figure~\ref{main:all} shows the cumulative solved instances plot of the best-performing solver of the strongest
-10 teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
+ten teams (in short, the top-10 solvers)  together with the Virtual Best Solver (VBS---see also~\ref{subsec:vbs_explained}).
 The best-performing  solver overall on the combination of satisfiable and unsatisfiable instances
@@
 A very interesting observation is that these four top solvers all have a different code base. This has not been observed for many years; more typically
-many of the best-performing solver have been based on same code bases.
+many of the best-performing solvers have been based on same code bases.
 
@@
 solver and alternating between a SAT mode (infrequent restarts) and an UNSAT mode (frequent restarts
-and variable-move-to-front~\cite{Ryan:2004:Thesis}). The best-performing solver in  Main SAT track on satisfiable instances is \solver{Relaxed-newTech}, followed by
+and variable-move-to-front~\cite{Ryan:2004:Thesis}). The best-performing solver in the Main SAT track on satisfiable instances is \solver{Relaxed-newTech}, followed by
 \solver{Kissat-sat} and \solver{CMS-ccnr-lsids}.
@@
 Only \solver{Kissat-unsat}, the winner of the Main UNSAT track, 
-performed significantly than all other participating solvers. 
+performed significantly better than all other participating solvers. 
 It is therefore not surprising
@@
 A further, more recent line of evolution in SAT solvers
-is rooted in the \solver{CoMinisatPS} by Oh, which is itself a again a fork of \solver{Minisat}, introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
-Building on \solver{CoMinisatPS}, 
-The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{MapleSAT}. 
-The at-the-time award-winning variant \solver{MapleCOMSPS} by Liang et al.~implements a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) of \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.
+is rooted in the \solver{CoMinisatPS} by Oh, which is itself a again a fork of \solver{Minisat}, and which introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
+Building on \solver{CoMinisatPS}, the SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{MapleSAT}. 
+The at-the-time award-winning variant \solver{MapleCOMSPS} by Liang et al.~implements a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB)~\cite{Liang:2016:MapleCOMSPS}.
 
 For SAT Competition 2017, Luo et al.~integrated learned clause minimization based on unit propagation (\solver{LCM}) in their award-winning \solver{Maple\_LCM\_Dist}~\cite{Luo:2017:LCM} which also uses the new branching heuristic \solver{Distance (Dist)} in an initial solving period~\cite{Xiao:2017:MapleLCMDist}.
-Using \solver{Maple\_LCM\_Dist}, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT}, with
-the introduction of the award-winning solver \solver{Maple\_LCM\_Dist\_ChronoBT} in SAT Competition~2018~\cite{Ryvchin:SC2018:MapleChronoBT}.
+In SAT Competition~2018, Ryvchin and Nadel successfully integrated conditional chronological backtracking (\solver{ChronoBT})~\cite{Nadel:2018:CBT} in their award award-winning solver \solver{Maple\_LCM\_Dist\_ChronoBT}~\cite{Ryvchin:SC2018:MapleChronoBT}.
 
@@
 
-Starting as a fork of \solver{Minisat} with the integration of special treatment for XOR constraints ~\cite{Soos:2009:Crypto},
+Also starting as a fork of \solver{Minisat} with the integration of special treatment for XOR constraints ~\cite{Soos:2009:Crypto},
 \solver{CryptoMinisat} by Soos continues to be a state-of-the-art and feature-rich SAT solver. 
@@
 As of SAT Competition~2017, \solver{CaDiCaL} % \cite{Biere:SC2020} - or cite some older proceedings to match the "As of SAT Competition~2017" part?
-by Biere is another independent representative of state-of-the-art SAT solvers.
-Its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} was quite successful in the 2020 competition.
-
-The sequential variant of the \emph{new code-base} \solver{ParaFrost} by Osama and Wijs was submitted for the first time to the 2020 SAT Competition,
- introducing several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
+by Biere is another independent representative of state-of-the-art SAT solvers and its improved re-implementation \solver{Kissat}~\cite{Biere:SC2020} was successful in the 2020 competition.
+
+%The sequential variant of the \emph{new code-base} \solver{ParaFrost} by Osama and Wijs was submitted for the first time to the 2020 SAT Competition, introducing several interesting new concepts~\cite{Osama:SC2020:Parafrost}.
 
@@
 Sequential SAT solvers have been evaluated in the Main, Planning and Incremental Library track of SAT Competition~2020. 
-$18$ teams submitted a total of $48$ solvers and configurations to the Main track and the Planning track of the competition, and $4$ solvers participated the Incremental Library track. 
+$18$ teams submitted a total of $48$ solvers and configurations to the Main track and the Planning track of the competition, and four solvers participated the Incremental Library track. 
 %and were ranked by the number of application categories in which they won based on their PAR-2 score. 
@@
 Three configurations of \solver{Kissat} were submitted to the 2020  competition, including one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively.
-\solver{Kissat} received \emph{four awards},achieving the first place in the Main track, 
+\solver{Kissat} received \emph{four awards}, achieving the first place in the Main track, 
 the best score on unsatisfiable instances, the second-best score on satisfiable instances and the third place in the Planning track.
@@
 Based on \solver{CaDiCaL}, its variants \solver{Trail} and \solver{AllUip} present implementations of a new \emph{Trail Saving} approach~\cite{Hickey:2020:TrailSaving} 
-and an improved clause-learning \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
+and the improved clause-learning heuristic \emph{Stable AllUIP}~\cite{Bacchus:SC2020}. 
 Submitted were the three variants \solver{Trail}, \solver{AllUip} and \solver{AllUip+Trail}. 
@@
 
-\solver{Relaxed} integrates short runs of the local search solver \solver{CCAnr} through periodic export and import of assignments~\cite{Xindi:SC2019} and uses a probabilistic schedule for switching between $10$ phase selection modes.
+\solver{Relaxed} integrates short runs of the local search solver \solver{CCAnr} through periodic export and import of assignments~\cite{Xindi:SC2019} and uses a probabilistic schedule for switching between ten phase selection modes.
 The \solver{Relaxed newTech} variant uses occurrence counts of variables in unsatisfied clauses during stochastic local search runs to recalculate variable priorities for their modified branching heuristic~\cite{Xindi:SC2020}.
@@
 
-Six teams submitted a total of $10$ solvers and configurations to the Parallel track. 
+Six teams submitted a total of ten solvers and configurations to the Parallel track. 
 In the following, we outline  the best-performing parallel solver implementations.
@@
 Two special solver instances perform concurrent clause strengthening~\cite{Wieringa:2013:CCS} and Gaussian elimination, respectively. 
-Regarding sharing, \solver{Painless-MCOMSPS-STR} uses an all-to-all strategy with a fixed-size clause buffer and an LBD filter with a dynamic limit~\cite{SC2020}.
+Regarding sharing, \solver{Painless-MCOMSPS-STR} uses an all-to-all strategy with a fixed-size clause buffer and a dynamic LBD filter~\cite{SC2020}.
 
@@
 \solver{Plingeling} is built around the well-known \solver{Lingeling} and did not change since 2016. 
-In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of~$8$. 
+In a global master queue, \solver{Plingeling} shares unit clauses, equivalences and short clauses with a size limit of~$40$ and an LBD limit of eight. 
 \solver{Plingeling} uses random seeds for diversification via variable polarities~\cite{Biere:SC2020,Biere:2012:Lingeling}.
@@
 
-Five teams submitted a total of $6$ solvers and configurations in the Cloud track. 
+Five teams submitted a total of six solvers and configurations in the Cloud track. 
 In the following, we outline the best-performing massively parallel solver implementations.
@@
 Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
-Duplicates are avoided by using a Bloom filter which is cleared periodically~\cite{Schreiber:SC2020}.
+Duplicates are avoided by using a Bloom filter which is cleared periodically~\cite{Schreiber:2021:Mallob}.
 
@@
  uses lock-free clause-exchange for solvers on the same machine and the message passing interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
-\solver{TopoSAT~2} also strengthens clauses before export and delays clause import until the trail-size reaches a local minimum, as well as
-diversifies via strategies used for branching, restarting, and clause forgetting~\cite{Ehlers:SC2020}.
+\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
+\solver{TopoSAT~2} diversifies via strategies used for branching, restarting, and clause forgetting~\cite{Ehlers:SC2020}.
 
@@
 
-In this section, we provide additional analysis of the Main track results, going beyond the rankings.
+In this section, we provide an additional analysis of the Main track results, going beyond the rankings.
 In particular, we focus on metrics complementing the PAR-2 score used for ranking the solvers in the actual competition.
@@
 The Virtual Best Solver (VBS) is a fictitious solver consisting 
-of all the solvers that actually participated in the competition (or a specific track)
+of all solvers that actually participated in the competition (or a specific track)
 and an oracle which, when given an input instance,
 invokes  the  solver which performed the best on that instance.
-In this way, the performance of the VBS highlights a certain upper bound 
-on performance achievable in principle by the 
+This way, the performance of the VBS highlights a certain upper bound 
+on the performance achievable in principle by the 
  participating solvers (cf.~the figures in Section~\ref{sec:results}).
 
-One can see that the VBS solves all the instances that
+One can see that the VBS solves all instances that
 were solved by at least one solver and solves each instance in the best observed time.
@@
 
-We remark that the sum of VBS-1 points as well as the sum of VBS-3 points computed across all the solvers
+We remark that the sum of VBS-1 points as well as the sum of VBS-3 points computed across all solvers
 is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
@@
 In the case of VBS-3, where we discard the information about the solution times, 
-we evenly split the one point reward for solving an instance among those solvers which succeeded in solving the instance.
+we evenly split the one-point reward for solving an instance among those solvers which succeeded in solving the instance.
 In contrast, VBS-2 does not have this property as it in general distributes more than one point per instance.
@@
 Similarly as VBS-3, it does not award just the best solver on an instance.
-For example, a solver that uses twice as much runtime as  the fastest solver on an instance received half a point.
-Further, if all the solvers solve an instance equally fast,
+For example, a solver that uses twice as much runtime as the fastest solver on an instance receives a half a point.
+Furthermore, if all solvers solve an instance equally fast,
 each solver receives a whole point for the instance.
@@
 VBS-1 tells us that \solver{Kissat-unsat} was most often the fastest solver,
-in particular on \SI{11.5}{\percent} of all the solved instances.
+in particular on \SI{11.5}{\percent} of the solved instances.
 
 The metric VBS-2 identifies \solver{Kissat-sat} as the best solver. Its leading score of \SI{32.9}{\percent} of the total
-is somewhat more difficult to interpret, though: a solver can score \SI{32.9}{\percent} of VBS-2 total
+is more difficult to interpret, though: a solver can score \SI{32.9}{\percent} of VBS-2 total
 by solving \SI{32.9}{\percent} of the solved instances in the best observed time
@@
 of the solved instances in the best observed time (and some others).
-A solver can also score \SI{32.9}{\percent} of VBS-2 total by solving all the solved instances,
+A solver can also score \SI{32.9}{\percent} of VBS-2 total by solving all solved instances,
 but always being roughly three times slower than the VBS. 
-The performance of \solver{Kissat-sat} lies (obviously) somewhere between these two extremes.
+The performance of \solver{Kissat-sat} lies (clearly) somewhere between these two extremes.
 
@@
 at least among the first 10 solvers. 
-(The last solver receives 0.9 points which is \SI{0.221}{\percent} of the total.)
+(The last solver receives 0.9 points, which is \SI{0.221}{\percent} of the total.)
 One can conclude from this that most of the benchmarks are solved
@@
 (rather than relying on an oracle to pick one solver for each instance, as with VBS)
-and observing how big a role each solvers plays in such a schedule. Since constructing 
+and observing how big role each solver plays in such a schedule. Since constructing 
 an optimal schedule tends to be computationally hard, we start here by 
-presenting a a computationally more efficient alternative---a greedy set cover approach.
+presenting a computationally more efficient alternative---a greedy set cover approach.
 
@@
 In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
-With these
- 264 instances already covered, \solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
+With these 264 instances already covered,
+\solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
 We can see that the further iterations tend to add very little,
@@
 %\solver{exp-V-LGB-MLD-CBT-DL}.
-Highlighting solvers that uniquely solve instance is a property of 
+% Highlighting solvers that uniquely solve an instance is a property of 
 Indeed, the greedy set cover metric highlights solvers which are able to uniquely solve specific benchmark instances
-and thereby contributing to the current state of the art.
+and thereby contribute to the current state of the art.
 
@@
 
-The greedy set cover 
-disregards the time it would take to execute the obtained ``schedule'' of running the solvers covering instances. 
+The greedy set cover disregards the time it would take to execute 
+the obtained ``schedule'' (of running the solvers that jointly cover all solved instances).
 However, we can
@@
 
-To this end, by employing a brute-force approach, we first construct a sequences of schedules 
+To this end, by employing a brute-force approach, we first construct a sequence of schedules 
 where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
@@
 does not continue further with additional solvers allowed,
-although its still better to use three solvers in a fair time split 
+although it is still better to use three solvers in a fair time split 
 (and cover 272 instances) than just one.
 Based on this observation, it is plausible that the really hard 
-instance that were solved actually may require quite large runtime to 
+instances that were solved actually may require quite large runtime to 
 get ``cracked'' by any solver and thus the advantage of adding more solvers to the schedule
@@
 For each solver (and its configuration) $S$ we introduce an integer variable $R^S$ denoting the number of seconds $S$ runs in the new schedule. 
-We then construct a formula with the hard constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one soft constraint for every instance $I$ of the form \[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
+We then construct a formula with  hard constraints $0 \leq R^S$ for every $S$ and $\sum_{S\in\mathcal{S}} R^S \leq 5000$ and with one soft constraint for every instance $I$ of the form \[\bigvee_{S \in \mathcal{S}_I} T^S_I \leq R^S,\]
 where $\mathcal{S}_I$ is the set of solvers which solved the instance $I$ and $T^S_I$ is the time it took solver $S$ to solve $I$ here rounded up to the nearest integer.
-(Note that while $R^S$ are variables, i.e.~unknowns, the $T^S_I$ are known constants in the formula.)
+(Note that while $R^S$ are variables, i.e.,~unknowns, the $T^S_I$ are known constants in the formula.)
 
@@
 
-Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
+Finding a solution which satisfies all hard constraints and as many soft constraints as possible,
 Z3 provided  the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
@@
 % The following three lines could be skipped without much harm:
-All the 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
+The 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
 This result is due to the fact that Z3 was not asked to produce a schedule with a minimal number of
@@
 We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
-and report their place and score in Table~\ref{tab:eval-by-family}. 
+and report their places and scores in Table~\ref{tab:eval-by-family}. 
 Interestingly, the overall best solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.
@@
 To investigate the similarity of solvers from the Main track, we define a
-similarity metric based on measured runtimes. We start by removing $84$
+similarity metric based on the measured runtimes. We start by removing $84$
 benchmarks that have not been solved by any solver. For the rest, a PAR-2 score
@@
 best average PAR-2 score in the Main track. The results are shown in
-Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
+Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. 
+Additionally, the result
 of hierarchically clustering the solvers based on their similarity is
 illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
-are joined reflects how similar they are. For example, enabling the \emph{trail
-  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
-a similarity above \num{0.999}. Therefore the two solvers are joined low in the
+are joined reflects how similar they are. For example, enabling \emph{trail saving}
+in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
+a similarity above \num{0.999}. Therefore, the two solvers are joined low in the
 dendrogram.
@@
 the SAT Race 2019.
-The similarity within the cluster is high, with the exception of
+The similarity within the cluster is high, except for
 \solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
-They form a sub-cluster
-with a lower similarity compared to the rest, but a high similarity within. In fact, the highest measured similarity,
+They form a subcluster
+with a lower similarity compared to the rest, but a high similarity within. 
+In fact, the highest measured similarity,
 % of $0.96$
@@
 The two configurations of \solver{Relaxed} by \emph{Zhang} and \emph{Cai}
-use the same code-base as a lot of solvers in the \solver{Maple}-cluster. However, the
+use the same codebase as a lot of solvers in the \solver{Maple}-cluster. However, the
 overall performance of the solver is better and closer to the \solver{CMS}-cluster.
@@
 The 2020 version of \solver{CaDiCaL}
-exhibit weaker performance than the modifications based on the 2019 version and
+exhibits weaker performance than the modifications based on the 2019 version and
 does not quite fit into any cluster.
 
-The leftmost cluster in the heat map is comprised of the other solvers
+The leftmost cluster in the heat map is comprised of other solvers
 originally written by \emph{Biere}. What is interesting to note is that the
 \solver{Kissat} configuration specialized for unsatisfiable instances joins the
-others configurations in the cluster high in the dendrogram. In fact \solver{Kissat-unsat} has
+others configurations in the cluster high in the dendrogram. In fact, \solver{Kissat-unsat} has
 the lowest average similarity to all other solvers in the top 30.
@@
 rank still gives a value of $\rho = 0.9974$. On the other hand, switching the
-highest ranked solver (\solver{Kissat-sat}) with the lowest,
+highest ranked solver (\solver{Kissat-sat}) with the lowest
 results in a rank correlation of $\rho = 0.7602$. Moving \solver{Kissat-sat} to
@@
 Figure~\ref{fig:sampleFamily} shows the rank
-correlation coefficient resulting from removing a complete benchmark family. As expected, removing a non-random subset can have a
+correlation coefficient resulting from removing a complete benchmark family. As expected, removing a nonrandom subset can have a
 higher impact on the ranking even if it is small. Removing the $13$ \emph{hgen} benchmarks
@@
 $0.9895$. Additionally, the ranking of the top five solvers stays the same.
-The individual removal of all other benchmarks families results in a rank correlation above $0.99$.
+The individual removal of all other benchmark families results in a rank correlation above $0.99$.
 
@@
 strategies include the following.
-All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
+All winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
 solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As observed
 from the results of the\emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart.
-However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
-It appear challenging to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
-The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use-case.
-
-\subsection*{Future Prospects}
-
-In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances turned out often counter-productive as it 
+However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classical all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
+It appears challenging to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use case. 
+The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use case.
+
+\subsection*{Prospects}
+
+In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances turned out often counterproductive as it 
 did not lead to a more balanced overall selection of new instances. 
@@
 The hardness criterion of 10 \solver{Minisat} minutes was set higher than the hardness criterion of 1 \solver{Minisat} minute of the ``bring your own benchmarks'' rule, 
-which can be viewed as problematic. As lessons learned
-in future competitions we will not aim balance by satisfiability status on the benchmarks author level. will aim to be more consistent with the imposed \emph{hardness} criteria
+which can be viewed as problematic. As lessons learned,
+in future competitions we will not aim to balance the benchmarks by satisfiability status on author level,
+will aim to be more consistent with the imposed \emph{hardness} criteria
 for benchmark selection, and will also make sure to clearly communicate what it means for an instance to be counted as \emph{unknown}.
@@
 In contrast to benchmarking with instances given in the 
-DIMACS CNF format, there are only few benchmark applications available for the Incremental track.
+DIMACS CNF format, there are only a few benchmark applications available for the Incremental track.
 This calls for more community-level efforts for constructing a more diverse and well-organized repository of applications for incremental SAT solvers. 
-Proper benchmarking and new tools for testing incremental SAT solvers may also help solver authors to deal with the more complex use-cases.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
-
-This year the Hack track was organized for hacks of \solver{Glucose 3}. 
-In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
+Proper benchmarking and new tools for testing incremental SAT solvers may also help solver authors to deal with more complex use cases.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
+
+This year, the Hack track was organized for hacks of \solver{Glucose 3}. 
+In the next competition, we plan on moving to the well-structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
 The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competition.
 
-The first instantiation of an Application track was the Planning track organized as a one-time track in 2020.. 
+The first instantiation of an Application track was the Planning track organized as a one-time track in 2020. 
 The results show that different solvers take the lead when we only evaluate for a single application, when compared to the overall Main track results.
 We intend to run further instantiations of the Application track. 
-While essentially none of the solvers that participated in the Planning track seemed particularly optimized for Planning instance, we hope
+While none of the solvers that participated in the Planning track seemed particularly optimized for planning instances, we hope that
 in future iterations the community will pick up on the challenge of optimizing SAT solvers towards different focus applications, as a complementary
@@
 
-The portfolio rule has been established to prohibit participation of pure solver portfolios, in order to stimulate development of new code-bases and
+The portfolio rule has been established to prohibit the participation of pure solver portfolios
+to stimulate the development of new codebases and
 to ensure fair competition among  sequential solvers.
-The rule was challenged in this competition as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.
-We aim to revisit and refine the portfolio rule in future instantiations of the competition in order to ensure that the rule does not unnecessarily hinder interesting 
+The rule was challenged in this competition as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated subsystems in their own codebase.
+We aim to revisit and refine the portfolio rule in future instantiations of the competition to ensure that the rule does not unnecessarily hinder interesting 
 algorithmic developments in SAT solving.

### 2021-06-28 paper/main.tex
consolidations

@@
 
-In a few cases {\tt DRAT-trim} ran into the verification timeout of 40,000 seconds. 
+In a few cases {\tt DRAT-trim} ran into the verification timeout of 45,000 seconds. 
 In the Main track, only those unsatisfiable benchmark instances for which the proof produced by a solver 
@@
 The time limit enforced on each solver for solving an instance was 5,000 seconds. 
-In the Main track, proof validation was limited to 40,000 seconds per proof.)
+In the Main track, proof validation was limited to 45,000 seconds per proof.)
 The solvers were allowed to use the full \SI{128}{\giga\byte} of RAM.\footnote{
@@
 
-To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than ten minutes.\footnote{We note that
+To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than ten minutes.\footnote{Note that
 the limit of ten minutes is again somewhat arbitrary.
@@
 With these 264 instances already covered,
-\solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
+\solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in the second iteration.
 We can see that the further iterations tend to add very little,
@@
 Interestingly, each of the first five tuples $T_{k \leq 5}$ contains exactly one of the three \solver{Kissat} variants. 
+The set $T_2$ is composed of the two winners of the Main SAT and Main UNSAT tracks. 
 For $i < 5$ the relation $T_{i} \subset T_{i+1}$ holds only under projection to base solvers due to the fluctuating variants of \solver{Kissat}.
+
 The composition changes more strongly in $T_6$. 
@@
 
-Contributions to the VBS can be captured by clustering the instance space into instance families.
+Contributions to the VBS can be captured by clustering the instances by their family. 
 We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
@@
 % based on the \num{5000}-second timeout
-\emph{i.e.}, we set a score of \num{10000} for unsolved instances.
+i.e., we set a score of 10,000 for unsolved instances.
 Each solver $S$ is thus associated with the PAR-2 scores $S_{1},\dots,S_{316}$.
@@
 % $S_{1},\dots,S_{316}$ for each solver $S$.
-The \emph{similarity} of two solvers $S$
+The \textsf{similarity} of two solvers $S$
 and $S'$, normalized to the interval $[0,1]$ is defined
@@
 \[
-	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
+	\mathsf{similarity}(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
 \]
 % \end{equation}
-We calculate the \emph{similarity} of the $30$ solvers with the
+We calculate the \textsf{similarity} of the $30$ solvers with the
 best average PAR-2 score in the Main track. The results are shown in
@@
 Additionally, the result
-of hierarchically clustering the solvers based on their similarity is
+of hierarchically clustering the solvers based on their \textsf{similarity} is
 illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
@@
 where $n$ is the number of solvers in the Main track ($48$), and the rankings
-$r_{\{1,2\}}(S)$ map a solver $S$ to its rank, \emph{i.e.,} $1$ for the best
+$r_{\{1,2\}}(S)$ map a solver $S$ to its rank, i.e., $1$ for the best
 performing solver, whereas $48$ is assigned to the solver
@@
 solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As observed
-from the results of the\emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart.
+from the results of the \emph{Parallel} track, it appears difficult to make proper use of more than $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart.
 However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classical all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
@@
 challenge when compared to the generality of the Main track.
-In the next competition, the  planned focus of Application track will be on SAT solver applications in cryptology.
+In the next competition, the  planned focus of Application track will be on SAT solver applications in cryptography.
 
